# Model estimates

## Recruitment (numbers of fish)

```{r main-recruitment-fig, fig.height = 4, out.height = "85%"}

plot_recruitment(list(base_model),
                 list(base_model_name),
                 inc_means = TRUE,
                 leg_pos = "none") +
  theme(axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12),
        legend.key.size = unit(0.5, units = "cm"),
        legend.text = element_text(size = 10))
```

## Spawning Biomass

```{r jmc-biomass-fig, fig.height = 4, out.height = "85%"}

plot_biomass(list(base_model),
             list(base_model_name),
             ylim = c(0, 5),
             point_shape = ts_single_model_pointshape,
             leg_pos = "none") +
  theme(axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12),
        legend.key.size = unit(0.5, units = "cm"),
        legend.text = element_text(size = 10))
```

## Relative Spawning Biomass

```{r jmc-relative-biomass-fig, fig.height = 4, out.height = "85%"}

plot_rel_biomass(model_lst = list(base_model),
                 model_names = list(base_model_name),
                 ylim = c(0, 2.5),
                 alpha = 0.2,
                 leg_pos = "none") +
  theme(axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12),
        legend.key.size = unit(0.5, units = "cm"),
        legend.text = element_text(size = 10))
```

## Fishing intensity and exploitation rate
:::::: {.columns}
::: {.column width="50%"}
<!-- \center Relative fishing intensity \center -->
```{r jmc-fishing-intensity-fig, fig.height = 4, fig.width = 4, out.height = "75%"}

plot_fishing_intensity(base_model,
                       line_width = 0.5,
                       point_size = 1.5,
                       point_stroke = 1,
                       fspr40_text_x = 1970) +
  theme(axis.title.x = element_text(size = 10),
        axis.title.y = element_text(size = 10),
        axis.text.x = element_text(size = 8),
        legend.key.size = unit(0.5, units = "cm"),
        legend.text = element_text(size = 10))
```

:::

::: {.column width="50%"}
<!-- \center Exploitation rate \center -->
```{r jmc-exploitation-fraction-fig, fig.height = 4, fig.width = 4, out.height = "75%"}

plot_exploitation_fraction(base_model,
                           line_width = 0.5,
                           point_size = 1.5,
                           point_stroke = 1) +
  theme(axis.title.x = element_text(size = 10),
        axis.title.y = element_text(size = 10),
        axis.text.x = element_text(size = 8),
        legend.key.size = unit(0.5, units = "cm"),
        legend.text = element_text(size = 10))
```

:::
::::::

## Biomass and Relative Fishing Intensity

* Biomass has remained above `r b_40` since 2010; current estimate is  
  *B*~`r assess_yr`~/`r b_0` = `r f(base_model$mcmccalcs$dmed[names(base_model$mcmccalcs$dmed) %in% end_yr], 2)`
* Fishing intensity has continually remained below `r f_40`; current estimate
  is  
  (1 - SPR~`r last_data_yr`~)/(1 - SPR~40%~) =
  `r f(base_model$mcmccalcs$pmed[names(base_model$mcmccalcs$pmed) == assess_yr - 1], 2)`
* The estimated probability that spawning biomass at the start of
  `r assess_yr` is below the `r b_40` (40% of `r b_0`) reference point is
   `r probs_curr_below_b40`%
* The probability that the relative fishing intensity is above `r f_40`
  at the end of `r end_yr - 1` is `r probs_curr_rel_fish_intens_above_1`%
* The probability of both of these things occurring is
  `r joint_percent_prob_above_below`%

## Joint history of rel. fishing intensity and rel. biomass

```{r jmc-phase-plot, fig.height = 3, out.height = "85%"}

plot_phase(base_model,
           start_yr,
           end_yr,
           init_lbl_x_off = -0.04,
           init_lbl_y_off = -0.04,
           final_lbl_x_off = 0.04,
           final_lbl_y_off = 0.04,
           cross_line_width = 0.25,
           cross_line_color = "black") +
  theme(axis.title.x = element_text(size = 10),
        axis.title.y = element_text(size = 7),
        axis.text.x = element_text(size = 8),
        legend.key.size = unit(0.5, units = "cm"),
        legend.text = element_text(size = 10))
```
