# Cohorts

## Estimated cumulative catch for select cohorts
:::::: {.columns}
::: {.column width="50%"}
\
\

Estimated total catch from each cohort

* 1999 cohort (ages 1--`r last_data_yr - 1999`): `r f(max(cohort_cum_sum_1999))` t
* 2010 cohort (ages 1--`r last_data_yr - 2010`): `r f(max(cohort_cum_sum_2010))` t
* 2014 cohort (ages 1--`r last_data_yr - 2014`): `r f(max(cohort_cum_sum_2014))` t
* 2016 cohort (ages 1--`r last_data_yr - 2016`): `r f(max(cohort_cum_sum_2016))` t
* 2020 cohort (ages 1--`r last_data_yr - 2020`): `r f(max(cohort_cum_sum_2020))` t
* 2021 cohort (ages 1--`r last_data_yr - 2021`): `r f(max(cohort_cum_sum_2021))` t
:::

::: {.column width="50%"}
```{r jmc-cumulative-catch-cohorts, fig.height = 4, fig.width = 4, out.height = "85%"}

plot_cumulative_catch_cohorts(base_model)
```

:::
::::::

## Estimates of above-average cohorts

```{r above-average-cohorts-table, results = "asis"}

cohorts <- sort(c(large_cohorts, 2010))
last_few_yrs <- c(last_assess_yr, assess_yr)
table_above_avg_cohorts_yrs(cohorts, last_few_yrs)
```

## Retrospective -- squid plot
```{r jmc-squid, fig.height = 4, out.height = "85%"}

plot_squid(base_model,
           show_ci = TRUE,
           ci_yrs = c(2014, 2015, 2020, 2021)) +
  theme(axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12))
```

