# Probability tables

## Probability table definitions

Probabilities associated with biomass and fishing-based metrics for different
fixed catch levels (see Executive Summary: Tables i, j, and k; Figures k, l, and
m)

-   Fix the catch in `r assess_yr` to estimate
    *B*\textsubscript{`r assess_yr + 1`}
-   Fix the catches in `r assess_yr` and `r assess_yr + 1` to estimate
    *B*\textsubscript{`r assess_yr + 2`}
-   Fix the catches in `r assess_yr`, `r assess_yr + 1`, and `r assess_yr + 2`
    to estimate *B*\textsubscript{`r assess_yr + 3`}
-   P(*B*\textsubscript{`r assess_yr + 1`} \< *B*~y~): Probability that biomass
    in `r assess_yr + 1` is less a specified biomass such as
    *B*\textsubscript{`r assess_yr`} or `r b_40`
-   P(relative FI \> 100% target): Probability that relative fishing intensity
    in fixed catch year is greater than the target fishing intensity

## Probabilities based on `r end_yr` catch

```{r jmc-main-risk-forecast-year-1-tab, results = 'asis'}

table_risk(base_model,
           forecast_yrs,
           index = 1,
           type = "probability",
           font_size = 8,
           header_font_size = 9) |> 
  row_spec(6,
           bold = table_highlight_bold,
           background = table_highlight_color)
```

## Probabilities based on `r end_yr` catch

```{r jmc-forecast-risk-comparison-plot-year-1, out.height = "80%"}

plot_fore_compare(base_model,
                  forecast_yrs = forecast_yrs,
                  fore_yr = forecast_yrs[1],
                  leg_pos = c(0.15, 0.28),
                  leg_font_size = 5,
                  remove_x_val = 325) +
  # Following make the legend smaller and legend items closer together
  theme(legend.key.size = unit(0.25, "cm"),
        legend.spacing.y = unit(0.01, "cm"),
        legend.box.background = element_rect(colour = "black")) +
  guides(color = guide_legend(byrow = TRUE))

```

## Probabilities based on `r end_yr` and `r end_yr + 1` catch

```{r jmc-main-risk-forecast-year-2-tab, results = 'asis'}

table_risk(base_model,
           forecast_yrs,
           index = 2,
           type = "probability",
           font_size = 8,
           header_font_size = 9)
```

## Probabilities based on `r end_yr` and `r end_yr + 1` catch

```{r jmc-forecast-risk-comparison-plot-year-2, out.height = "80%"}

plot_fore_compare(base_model,
                  forecast_yrs = forecast_yrs,
                  fore_yr = forecast_yrs[2],
                  leg_pos = c(0.28, 0.44),
                  leg_font_size = 5,
                  remove_x_val = c(315, 342, 740)) +
  # Following make the legend smaller and legend items closer together
  theme(legend.key.size = unit(0.25, "cm"),
        legend.spacing.y = unit(0.01, "cm"),
        legend.box.background = element_rect(colour = "black")) +
  guides(color = guide_legend(byrow = TRUE))

```

## Probabilities based on `r end_yr`, `r end_yr + 1`, and `r end_yr + 2` catch

```{r jmc-main-risk-forecast-year-3-tab, results = 'asis'}

table_risk(base_model,
           forecast_yrs,
           index = 3,
           type = "probability",
           font_size = 8,
           header_font_size = 9)
```

## Probabilities based on `r end_yr`, `r end_yr + 1`, and `r end_yr + 2` catch

```{r jmc-forecast-risk-comparison-plot-year-3, out.height = "80%"}

plot_fore_compare(base_model,
                  forecast_yrs = forecast_yrs,
                  fore_yr = forecast_yrs[3],
                  leg_pos = c(0.28, 0.44),
                  leg_font_size = 7,
                  remove_x_val = 621) +
  # Following make the legend smaller and legend items closer together
  theme(legend.key.size = unit(0.25, "cm"),
        legend.spacing.y = unit(0.01, "cm"),
        legend.box.background = element_rect(colour = "black")) +
  guides(color = guide_legend(byrow = TRUE))

```
