# Catches

## Catches
```{r main-catches-fig, fig.height = 3, fig.asp = 0.7, out.height = "85%"}

plot_catches(ct, xlim = c(start_yr, last_data_yr),
            leg_font_size = 8,
            leg_key_size = 0.5,
            leg_ratio = c(0.5,2))
```

## Catch by month and sector

```{r catch-by-month-fig, fig.height = 3, fig.asp = 0.7, out.height = "85%"}

plot_catch_by_month(list(us_ss_catch_by_month_df,
                         can_ss_catch_by_month_df,
                         us_cp_catch_by_month_df,
                         can_ft_catch_by_month_df,
                         us_ms_catch_by_month_df),
                    list("U.S. Shoreside",
                         "Canadian Shoreside",
                         "U.S. Catcher-Processor",
                         "Canadian Freezer-Trawlers",
                         "U.S. Mothership"),
                    type = "catch",
                    disclaimer_text = paste0(
                      "These plots have different y-axis ranges\n",
                      "and are not directly comparable\n",
                      "with each other."),
                    yrs = c(last_data_yr - 4, last_data_yr),
                    leg_font_size = 8,
                    title_font_size = 10,
                    ax_text_x = 8,
                    ax_text_y = 8)
```
## Summary -- Catches

* TAC (adjusted for carryovers) for `r end_yr-1` was `r last_yr_tac` t

* Coastwide catch in `r end_yr-1` was `r last_yr_landings` t  -- near the
time series average catch

* Attainment in the U.S. was `r last_yr_us_attained`% of its quota
  (`r paste0(ifelse(last_2yr_us_attained_diff < 0, "down", "up"))`
  `r abs(as.numeric(last_2yr_us_attained_diff))`% from last year)
  
* Attainment in Canada was `r last_yr_can_attained`% of its quota
  (`r paste0(ifelse(last_2yr_can_attained_diff < 0, "down", "up"))`
  `r abs(as.numeric(last_2yr_can_attained_diff))`% from last year)