# Sensitivities

## Key Structural Uncertainties for `r assess_yr`

Recall: base model uses fixed median recruitment levels for 2023 onwards
  with extra standard deviation added to the survey index time series.

* Sensitivity 1 -- Stochastic recruitment (not fixed) since 2023 and into the forecast period.

* Sensitivity 2 -- Turn off added uncertainty when fitting the survey time
  series (force improved fit to survey) and keep fixed median recruitment since 2023
  and into forecast period.

* Sensitivity 3 -- Turn off added uncertainty when fitting the survey time series
  (force improved fit to survey) and add stochastic recruitment since 2023 and into
  forecast period.

## Recruitment -- Fixed at median from 2023 onwards

```{r rec-abs, fig.height = 4, out.height = "80%"}

plot_recruitment(list(base_model),
                 list(base_model_name),
                 inc_means = TRUE,
                 leg_pos = "none") |>
  suppressWarnings()
```

## Recruitment -- Stochastic from 2023 onwards

```{r rec-abs1, fig.height = 4, out.height = "80%"}

plot_recruitment(list(base_model),
                 list(base_model_name),
                 inc_means = TRUE,
                 leg_pos = "none") |>
  suppressWarnings()
```