# Weight and fecundity-at-age data
## Summary of weight at age

* Fixed inputs to Stock Synthesis from GLMM thanks to Andrea Odell, Eric Ward, and Kristin Marshall.
* Pre-1975 weight-at-age data are available from the U.S.~Shorebased fleet;
  these data were included in the GLMM but pre-1975 values are age-specific
  means across all years.
* $weight \sim sex + s(age) + (1|year) + (1|cohort) + lognormal(0, \mu)$
* No spatial effects because we cannot share sample location information
  between JTC members and some samples do not have associated locations.
* Forecasted weight is age-specific means from most recent five years.

## Weight-at-age annual sample size
```{r main-weight-at-age-numbers, fig.height = 4, out.height = "85%"}
plot_heatmap_sample_size_weight_at_age(
  base_model,
  cell_font_size = 2,
  sample_size_df = weight_age_sample_sizes_df,
  pre_yrs = start_yr_age_comps:base_model$endyr,
  pre_func = mean,
  post_yrs = (base_model$endyr - 4):base_model$endyr,
  post_func = mean,
  cols = c("red",
           "yellow",
           "green",
           "dodgerblue")) +
  theme(axis.text.x = element_text(size = 8),
        axis.text.y = element_text(size = 6))
```

## Annual weight-at-age model estimates
```{r wt-at-age, fig.height = 4, out.height = "85%"}

plot_weight_at_age(wt_at_age,
                   ages = 2:10,
                   bold_ages = 5,
                   cols = c("purple",
                            "darkblue",
                            "yellow",
                            "darkgreen"),
                   max.overlaps = 15)
```

## Weight-at-age GLMM
### Results
* Females weigh more, on average, than males.
* Cohort effect is now equal to, rather than larger than, than year effect.

```{r plot-weight-at-age-by-sex, fig.height = 2.75}
wtaa_preds <- readRDS(fs::path("/srv/hake/other/tv", "weight-at-age-preds.rds"))
# Make figure
wtaa_preds |>
  dplyr::filter(year %in% c(2016, 2018)) |>
  ggplot2::ggplot(ggplot2::aes(
    x = age,
    y = est_weight,
    group = interaction(sex, year),
    colour = fyear,
    pch = sex
  )) +
  ggplot2::geom_line() +
  ggplot2::geom_point() +
  ggplot2::xlab("age (years)") +
  ggplot2::ylab("estimated mass (kg)")
```

## Summary of fecundity at age

* Ovary sampling occurs in U.S.~at-sea sectors by at-sea observers, acoustic
  survey, and U.S.~West Coast Groundfish Bottom Trawl Survey.
* Survey-based ovary sampling is length stratified with target numbers for 2~cm
length bins and biased towards summer samples.
* 2024 ovaries have yet to be analyzed.
* Canadian and Southern of Point Conception samples are not included.
* Historical maturity at age is the age-specific mean from all years.
* Forecasted maturity at age is the age-specific mean from most-recent five years.
* Fecundity at age is maturity at age $*$ weight at age.
* Indeterminate batch spawners with a protracted spawning season.
* Spatial and temporal differences with younger age at 50% maturity south of
  Point Conception (i.e., 1.45 vs. 2.56 years) and annual differences in age at
  50% maturity north of Point Conception from 2.0--3.3.

<!-- ### Definitions
* Histological sampling: taking cross sectional samples of the gonads
  immediately after being caught for later viewing under a microscope.
* Macroscopic sampling: taking samples of the gonads to assess maturity status
  without using a microscope.
* Biological maturity: physiological evidence of progressing towards a mature
  state.
* Functional maturity: physical evidence of spawning.
* Atresia: degeneration of ovarian follicles.
* Senescence: deterioration with age.
* Skipped spawning: ability to spawn but lack thereof.
* Batch spawning: spawning multiple batches of oocytes during the individual
  spawning period.
* Batch fecundity: the number of eggs produced in a single spawning batch,
  where annual fecundity is a function of both batch fecundity and the number
  of spawnings per year. -->

## Sample sizes of ovaries by year
```{r ovary-table, results = "asis"}

table_ovary_samples(
  ovary_samples_df,
  font_size = 7,
  header_font_size = 6)
```


## Maturity at age by year
```{r maturity-ogive-figure, fig.height = 4, out.height = "85%"}

plot_maturity_ogives(eq_x_start_legend = 10,
                     eq_y_start_legend = -0.1,
                     eq_fore_alpha = 0.7,
                     eq_fore_line_width = 1,
                     leg_line_size_cm = 0.5,
                     leg_font_size = 10)
```

## Fecundity-at-age GLMM

* Led by Melissa Head, Eric Ward, and Kristin Marshall.
* $P(mature) \sim ASHOP~vs.~Survey + s(day~of~year) + temperature + temperature^2 + GMRF() + GMRF(age) + GMRF(age^2)$
* February average from GLORYS12v1 at 130.67~m, weighted by July 1 biomass.
* Estimates of maturity were weighted by July 1 biomass.
* Higher age at 50% maturity in ASHOP samples compared to survey samples.
* Spatial patterns were similar across ages.
* Higher age at 50% maturity in moderately warm compared to colder and hot years.

<!-- spatiotemporal model with spatially varying coefficients
for the quadratic function of age and year effects as a quadratic function of
temperature at 130.67~m. -->

## Fecundity at age by year
```{r fecundity-figure, fig.height = 4, out.height = "85%"}

plot_heatmap_weight_at_age(
  base_model,
  fleet = -2,
  cell_font_size = 2,
  sample_size_df = weight_age_sample_sizes_df,
  pre_yrs = start_yr_age_comps:base_model$endyr,
  pre_func = mean,
  post_yrs = (base_model$endyr - 4):base_model$endyr,
  yrs = (start_yr_age_comps - 1):(base_model$endyr + 1),
  post_func = mean,
  cols = c("red",
           "yellow",
           "green",
           "dodgerblue")) +
  theme(axis.text.x = element_text(size = 8),
        axis.text.y = element_text(size = 6))
```
