# Changes from `r last_assess_yr` and Justification
## `r assess_yr` base model structure

* The `r assess_yr` model is effectively equivalent to the  `r last_assess_yr` model (unchanged structure and results) to the start of 2025.
* Model parameters are effectively the same for `r assess_yr` and `r last_assess_yr`.
* The same version of Stock Synthesis was used as last year.
* The `r assess_yr` model only includes updated 2025 total coast-wide catch data.
* Often referred to as a catch-only projection style of assessment.

## Comparison to `r last_assess_yr` (biomass)

```{r bridge-biomass-1, fig.height = 4, out.height = "80%"}
p <- list()
p[[1]] <-
  plot_biomass(model_lst = list(base_model,last_yr_base_model),
               model_names = c("Base Model","Last Year Base Model"),
               point_size = 1.5,
               xlim = c(1964, last_assess_yr),
               show_arrows = TRUE,
               dodge_bo = 0.75,
               leg_ncol = 2,
               leg_font_size = 5,
               x_labs_mod = 10,
               wrap_y_label = TRUE,
               tick_prop = 1,
               vjust_x_labels = -0.1,
               ylim = c(0, 5.5),
               leg_pos = c(0.5, 0.87))
p[[2]] <-
  plot_rel_biomass(model_lst = list(base_model,last_yr_base_model),
               model_names = c("Base Model","Last Year Base Model"),
                   xlim = c(1964, last_assess_yr),
                   ylim = c(0, 2.5),
                   x_labs_mod = 10,
                   wrap_y_label = TRUE,
                   leg_pos = "none")

plot_grid(plotlist = p,
          nrow = 1,
          ncol = 2)
```

## Comparison to `r last_assess_yr` (recruitment)

```{r bridge-recruit-1, fig.height = 4, out.height = "80%"}
  plot_recdevs(model_lst = list(base_model,last_yr_base_model),
               model_names = c("Base Model","Last Year Base Model"),
               x_labs_mod = 10,
               leg_ncol = 2,
               leg_font_size = 6,
               line_width = 0.1,
               rev_colors = TRUE,
               leg_pos = c(0.32, 0.9)) +
  theme(legend.key.size = unit(0.5, units = "cm"),
        legend.text = element_text(size = 10))

```

## Justification for `r assess_yr` base model structure
* The JTC notes:
  * The option of adding another year of fisheries age data, without the 2025 survey data, could lead to potentially misleading results.
  * The option of using the `r last_assess_yr` model projections as the basis for 2026 status could only be an approximation at best.
  * Thus, the catch-only projection option was deemed the most applicable for this year, because it bases 2026 management advice
on the approved `r last_assess_yr` assessment and uses the exact 2025 total catch for a projection. 

## `r assess_yr` base model structure

* The use of a fixed recruitment assumption maintained from 2023 onwards
  * Results in three years of relatively low recruitment leading into biomass at the start of 2026
  * Four years of low recruitment leading into single year biomass forecasts for the start of 2027
* No standard set of sensitivities were completed for this year, refer to 2025 assessment
* A few alternative sensitivity runs were evaluated (separate presentation) to:
  * Explore the impact of the fixed recruitment assumption
  * Explore the tradeoffs between fishery age composition data and survey index data

## `r assess_yr` base model projections
* A single year was projected forward from the 2026 base model to get biomass at the start of 2027
* This was done because:
  * The assumption of not using recruitment deviations during the
recent and forecast periods is not a feasible long-term model assumption because the median
recruitment is too low to sustain the population in perpetuity. Forecasting further
years ahead will exacerbate this and lead to unrealistic results given past levels of
Pacific Hake recruitment.
  * The models in the 2024 and 2025 assessments both estimated a stock biomass somewhat
larger than the biomass index from the 2023 survey. Inclusion of the 2025 survey biomass
index would have helped to determine the validity of this overfitting. Without the
2025 survey biomass index, it was deemed pragmatic to not overextend the forecasts
too far ahead from 2023 survey.
* More specific implications coming during the management presentation
