# Catches and Allocations
## Catches
```{r catches, fig.height = 4, out.height = "85%"}

plot_catches(ct, xlim = c(start_yr, last_data_yr),
             leg_font_size = 9,
             leg_key_size = 0.5,
             leg_ratio = c(1, 4))
```

## Allocations of `r end_yr - 1` TAC of `r last_yr_tac` t
:::::: {.columns}
::: {.column width="50%"}
\center \textbf{\textcolor{blue}{Canada}} \center

\

\center \textbf{TAC was `r last_yr_can_tac` t} \center

* TAC includes `r last_yr_can_carryover` t of carryover
* Freezer Trawlers and Shoreside -- `r last_yr_can_shoreside_tac` t
* Joint Venture -- `r last_yr_can_tac_jv` t

:::

::: {.column width="50%"}
\center \textbf{\textcolor{blue}{United States}} \center

\

\center \textbf{TAC was `r last_yr_us_tac` t} \center

* Research and bycatch -- `r f(last_yr_us_research)` t
* Tribal  -- `r f(last_yr_us_tribal)` t -
  `r f(last_yr_us_tribal_quota_reallocated)` t reallocated on
`r last_yr_us_tribal_reallocate_dates`
* Catcher Processor -- `r f(last_yr_us_cp_quota_reallocated)` t
* Mothership -- `r f(last_yr_us_ms_quota_reallocated)` t
* Shore-Based -- `r f(last_yr_us_shore_quota_reallocated)` t

:::
::::::

## Catches of `r end_yr - 1` TAC of `r last_yr_tac` t
:::::: {.columns}
::: {.column width="50%"}
\center \textbf{\textcolor{blue}{Canada}} \center

\

\center \textbf{TAC was `r last_yr_can_tac` t} \center
`r last_yr_can_landings` t, `r last_yr_can_attained`% of the Canadian TAC

* Freezer Trawlers -- `r last_yr_can_freezer` t,
`r last_yr_can_freezer_percent`% of Canadian catch
* Shoreside -- `r last_yr_can_shore` t,
`r last_yr_can_shore_percent`% of Canadian catch
* Joint Venture -- `r last_yr_can_jv` t,
`r last_yr_can_jv_percent`% of Canadian catch

:::

::: {.column width="50%"}
\center \textbf{\textcolor{blue}{United States}} \center

\

\center \textbf{TAC was `r last_yr_us_tac` t} \center
`r last_yr_us_landings` t, `r last_yr_us_attained`% of the U.S. TAC

* Catcher Processor -- `r f(last_yr_us_cp_ct)` t,
`r last_yr_us_cp_ct_percent`% of US CP allocation
* Mothership `r f(last_yr_us_ms_ct)` t,
`r last_yr_us_ms_ct_percent`% of US MS allocation
* Shore-Based -- `r f(last_yr_us_shore_ct)` t,
`r last_yr_us_shore_ct_percent`% of shore-based allocation, includes
`r f(round(sum(subset(us_ti_ct_by_month_df, year == last_assess_yr)$catch), 0))`
t of tribal catches

:::
::::::

## Cumulative catch by month
```{r cumulative-catches, fig.height = 4, out.height = "85%"}

plot_cumulative_catches(list(us_ss_catch_by_month_df,
                             can_ss_catch_by_month_df,
                             us_cp_catch_by_month_df,
                             can_ft_catch_by_month_df,
                             us_ms_catch_by_month_df),
                        list("U.S. Shore-Based",
                             "Canadian Shorside",
                             "U.S. Catcher-processor",
                             "Canadian Freezer-Trawlers",
                             "U.S. Mothership"),
                        type = "cumulative",
                        leg_font_size = 8,
                        title_font_size = 10,
                        ax_text_x = 8,
                        ax_text_y = 8)
```

