# Weight/fecundity at age
## Summary of weight- and fecundity-at-age data
* Fixed inputs to Stock Synthesis.
* Fecundity at age is maturity-at-age $*$ weight-at-age data.
* Pre-1975 U.S.~weight-at-age data are not included because they were
collected from the Puget Sound.
* Ovary sampling occurs in
U.S. at-sea sectors by at-sea observers,
acoustic survey, and
U.S. West Coast Groundfish Bottom Trawl Survey.
* Survey-based ovary sampling is length stratified with target numbers for 2~cm
length bins.
* 2023 ovaries have yet to be analyzed and 21 samples from Canadian acoustic-survey vessels also are not yet analyzed.
* Historical weight and fecundity are age-specific means from all years.
* Future weight and fecundity are age-specific means from most recent five
years.

## Sample sizes of weight-at-age by year
```{r main-weight-at-age-numbers, fig.height = 4, out.height = "85%"}

plot_heatmap_sample_size_weight_at_age(
  base_model,
  cell_font_size = 2,
  sample_size_df = weight_age_sample_sizes_df,
  pre_yrs = start_yr_age_comps:base_model$endyr,
  pre_func = mean,
  post_yrs = (base_model$endyr - 4):base_model$endyr,
  post_func = mean,
  cols = c("red",
           "yellow",
           "green",
           "dodgerblue")) +
  theme(axis.text.x = element_text(size = 8),
        axis.text.y = element_text(size = 6))
```
## Sample sizes of ovaries by year
```{r ovary-table, results = "asis"}

table_ovary_samples(
  ovary_samples_df,
  font_size = 7,
  header_font_size = 6)
```

## Weight-at-age data by year
```{r wt-at-age, fig.height = 4, out.height = "85%"}

plot_weight_at_age(wt_at_age,
                   ages = 2:10,
                   bold_ages = 5,
                   cols = c("purple",
                            "darkblue",
                            "yellow",
                            "darkgreen"),
                   max.overlaps = 15)
```

## Maturity at age by year
```{r maturity-ogive-figure, fig.height = 4, out.height = "85%"}

plot_maturity_ogives(eq_x_start_legend = 10,
                     eq_y_start_legend = -0.1,
                     eq_fore_alpha = 0.7,
                     eq_fore_line_width = 1,
                     leg_line_size_cm = 0.5,
                     leg_font_size = 10)
```

## Fecundity at age by year
```{r fecundity-figure, fig.height = 4, out.height = "85%"}

plot_heatmap_weight_at_age(
  base_model,
  fleet = -2,
  cell_font_size = 3,
  sample_size_df = weight_age_sample_sizes_df,
  pre_yrs = start_yr_age_comps:base_model$endyr,
  pre_func = mean,
  post_yrs = (base_model$endyr - 4):base_model$endyr,
  post_func = mean,
  cols = c("red",
           "yellow",
           "green",
           "dodgerblue")) +
  theme(axis.text.x = element_text(size = 8),
        axis.text.y = element_text(size = 6))
```

## Fecundity needs

* We need a better understanding of the following:
  - Batch fecundity and how it varies across space and time.
  - Batch spawning.
  - Links between fecundity and size, age, and weight.
  - How the above topics provide further information about factors that
influence varying reproductive output.
* More winter acoustic surveys may provide further information about these
questions.
* Potential to sample from U.S. shoreside vessels using dock-side sampling
or at-sea observers on shore-based vessels (n = 1) that lack electronic monitoring.
