## Data-based vs. model-based

### Data-based methods
**Weight-at-age** -- (1) calculate the mean weight within a given age--year
combination; (2) linearly interpolate across years within an age; and (3)
fill in missing values from nearest age within a year. Interpolations do not
account for sample size or cohort.

**Maturity-at-age** -- has always been model based.

### Model-based methods
**Weight-at-age** -- a model with
fixed effects for sex,
random effects for year and cohort, and
smoothed effect for age.

**Maturity-at-age** -- a spatiotemporal model with spatially varying coefficients
for the quadratic function of age and year effects as a quadratic function of
temperature at 130.67~m. Results were weighted by biomass estimates from a
spatiotemporal model fit to data from the West Coast Groundfish Bottom Trawl
Survey.

# GLMMs
## Generalized linear mixed effects models (GLMMs)
* Biological processes vary with space and time.
* GLMMs allow for distributions other than normal.
* GLMMs are more efficient than GLMs because random effects allows for
  estimating a fewer number of parameters.
* Random effects evaluate the difference between the average response in a
  group and the average response in the population.
* GLMMs allow for improved estimates of standard errors in categories (e.g.,
  years, ages) with low or missing sampling than GLMs.

## Weight-at-age GLMM

### Andrea Odell -- University of California, Davis

### Kristin Marshall -- Northwest Fisheries Science Center

### Eric Ward -- Northwest Fisheries Science Center

## Weight-at-age GLMM
### Data
  * Mass of individual fish from fishery-independent and -dependent data
    sources since 1975.
  * Removed samples from the acoustic survey with a mass of 0.001 given the
    limitations of the measuring device (Alicia Billings).
  * Assumed Poland Acoustic Survey samples were from August given literature.
  * Contacted database authors about four potential outliers.

### Model
* $weight \sim sex + s(age) + (1|year) + (1|cohort) + lognormal(0, \mu)$
* No spatial effects because we cannot share sample location information
  between JTC members and some samples do not have associated locations.
* Mean of sex-specific predictions to create one matrix of weight at age.

## Weight-at-age GLMM
### Results
* Females weigh more on average than males.
* Cohort effect is larger than year effect.
* Removing the effect of sex increases the year-to-year variance and decreases
  the global mean.

```{r plot-weight-at-age-by-sex, fig.height = 2.75}
wtaa_preds <- readRDS(fs::path("/srv/hake/other/tv", "weight-at-age-preds.rds"))
# Make figure
wtaa_preds |>
  dplyr::filter(year %in% c(last_data_yr - 5, last_data_yr)) |>
  ggplot2::ggplot(ggplot2::aes(
    x = age,
    y = est_weight,
    group = interaction(sex, year),
    colour = fyear,
    pch = sex
  )) +
  ggplot2::geom_line() +
  ggplot2::geom_point() +
  ggplot2::xlab("age (years)") +
  ggplot2::ylab("estimated mass (kg)")
```

## Weight-at-age GLMM
### Limitations
* Does not account for sampling platform.
* Does not account for month sampled.
```{r plot-weight-at-age-month, fig.height = 2.5}
wtaa_model <- readRDS(
  fs::path("", "srv", "hake", "other", "tv", "weight-at-age-model.rds")
)
wtaa_model[["data"]] |>
  dplyr::mutate(
    Source = dplyr::case_when(
      grepl("acoustic", source, ignore.case = TRUE) ~ "Survey",
      grepl("CAN", source) ~ "Fishery - Canada",
      TRUE ~ "Fishery - U.S."
    )
  ) |>
  ggplot2::ggplot() +
  ggplot2::geom_histogram(aes(y = factor(month), fill = Source), stat = "count") +
  ggplot2::ylab("Month")
```

## Maturity-at-age GLMM
### Eric Ward -- Northwest Fisheries Science Center

### Melissa Head -- Northwest Fisheries Science Center

### Kristin Marshall -- Northwest Fisheries Science Center

## Maturity-at-age GLMM
### Definitions
* Histological sampling: taking cross sectional samples of the gonads
  immediately after being caught for later viewing under a microscope.
* Macroscopic sampling: taking samples of the gonads to assess maturity status
  without using a microscope.
* Biological maturity: physiological evidence of progressing towards a mature
  state.
* Functional maturity: physical evidence of spawning.
* Atresia: degeneration of ovarian follicles.
* Senescence: deterioration with age.
* Skipped spawning: ability to spawn but lack thereof.
* Batch spawning: spawning multiple batches of oocytes during the individual
  spawning period.
* Batch fecundity: the number of eggs produced in a single spawning batch,
  where annual fecundity is a function of both batch fecundity and the number
  of spawnings per year.

## Maturity-at-age GLMM
### Data
* Historical estimates
  * $\sim$ 38 cm (Dorn and Saunders 1997)
  * 3--4 years (Best 1963; Macgregor 1996, 1971)
  * age-based functional maturity (Head 2017)
```{r plot-spline-ogive, fig.height = 2.5}
plot(
  x = seq_along(hakedataUSA::maturity_at_age) - 1,
  hakedataUSA::maturity_at_age,
  ylab = "P(mature)",
  xlab = "Age (years)",
  type = "b"
)
```
* Indeterminate batch spawners with a protracted spawning season.
* Spatial and temporal differences with younger age at 50% maturity south of
  Point Conception (i.e., 1.45 vs. 2.56 years) and annual differences in age at
  50% maturity north of Point Conception from 2.0--3.3.

## Maturity-at-age GLMM
### Data
* Fit to ASHOP, acoustic survey, West Coast Groundfish Bottom Trawl Survey data
  north of Point Conception.
* 2,836 ovary samples since 2009 (did not include 2023).

## Maturity-at-age GLMM
```{r app-maturity-analysis-sampling-platform-age-years-fig., results = "asis"}
figures_dir <- fs::path("../../../doc/image-files")
include_graphics(file.path(figures_dir,
                          "Fig_S3_samplingplatform_age_years.png"),
                 error = FALSE)
```

## Maturity-at-age GLMM
### Data
* Temperature: February average from GLORYS12v1 at 130.67 m, where temperature
  decreases with depth and warmest temperatures occur in the winter.
* Temperature was weighted by biomass estimates from the West Coast Groundfish
  Bottom Trawl Survey on July 1.

## Maturity-at-age GLMM
### Data
```{r app-maturity-analysis-temp-depth-fig, results = "asis"}
include_graphics(file.path(figures_dir,
                           "Fig_S4_temp_by_depth.png"),
                 error = FALSE)
```

## Maturity-at-age GLMM
### Model
* $P(mature) \sim ASHOP~vs.~Survey + s(day~of~year) + temperature + temperature^2 + GMRF() + GMRF(age) + GMRF(age^2)$
* Annual estimates of maturity at age were also weighted by the same biomass
  estimates as temperature.

## Maturity-at-age GLMM
### Results
* Higher age at 50% maturity in ASHOP samples compared to survey samples.
* Spatial patterns were similar across ages.
* Higher age at 50% maturity in moderately warm compared to colder and hot
  years, i.e., concave relationship.
* Temperature-based model predicted lower age at 50% maturity than the model
  without temperature in 2016.

## Maturity-at-age GLMM
### Results
```{r app-maturity-analysis-predicted-maps-byage-fig, results = "asis"}

include_graphics(file.path(figures_dir,
                           "Fig_S9_predicted_maps_byage.png"),
                 error = FALSE)
```

## Maturity-at-age GLMM
### Limitations and future research
* Estimating the timing of spawning is difficult.
* Estimates are of maturity but the input to Stock Synthesis is fecundity.
* Does maturity relate to fecundity linearly with weight?
* Getting temperature data for current year was not doable (current GLORYS
  forecasts 2--3 weeks).
* Temperature forecasts were in the wrong format but could be available in the
  future.
* Use cellular markers to confirm skip spawning.
