# Maturity and Fecundity
## Ovary sampling
* Sample sources
- Bottom trawl survey (2009, 2012 -- 2017)
- Acoustic survey (2012 -- 2013, 2015 -- 2017)
- At-sea fishery (2013 -- 2017)
* Length stratified sampling from surveys with target numbers for 2 cm length bins.
* Data from 2018 and 2019 are expected to be analyzed in 2021.

## Status of Canadian ovary samples
```{r ovary-table, results = "asis"}

table_ovary_samples(
  ovary_samples_df,
  font_size = 7,
  header_font_size = 6)
```

## Maturity
```{r maturity-ogive-figure, fig.height = 4, out.height = "85%"}

plot_maturity_ogives(base_model,
                     maturity_samples_df)
```

## Fecundity
```{r fecundity-figure, fig.height = 4, out.height = "85%"}

plot_fecundity(base_model,
               d = maturity_samples_df,
               yrs = start_yr_age_comps:(end_yr - 1),
               leg_pos = c(0.6, 0.2))
```

## Fecundity
* Fecundity-at-age is set to maturity-at-age $*$ weight-at-age in Stock
Synthesis.
* We need a better understanding of:
  - Batch spawning.
- Links between fecundity and size, age, and weight.
- How the above topics provide further information about factors that
influence varying reproductive output.
* More winter acoustic surveys may provide further information about these questions.

