---
title: "**Fisheries, data, and inputs used in the 2024 Pacific Hake stock assessment**"
params:
  sp: "Pacific Hake"
  common_name: "Pacific whiting"
  science_name: "Merluccius productus"
  simple_name: "hake"
  survey_name: "Joint U.S. and Canadian Integrated Acoustic and Trawl Survey"
  assess_yr: 2023
  last_assess_yr: 2022
  last_data_yr: 2022
  model_version: "01"
  last_yr_model_version: "01"
author: Joint Technical Committee
date: "`r format(Sys.time(), '%B %d')`\\textsuperscript{th}, `r format(Sys.time(), '%Y')`"
header: "Draft working paper --- Do not cite or circulate" # or "" to omit
output:
  beamer_presentation:
    theme: "Singapore"
    slide_level: 1
classoption: "aspectratio=169"
fontsize: 11pt
urlcolor: blue
---

```{r setup, echo = FALSE, cache = FALSE, message = FALSE, results = "hide", warning = FALSE}
library(knitr)
devtools::load_all("~/github/pacific-hake/hake")

if(is_latex_output()){
  knitr_figs_dir <<- "knitr-figs-pdf/"
  knitr_cache_dir <<- "knitr-cache-pdf/"
  fig_out_type <<- "png"
}else{
  knitr_figs_dir <<- "knitr-figs-docx/"
  knitr_cache_dir <<- "knitr-cache-docx/"
  fig_out_type <<- "png"
}
fig_width <<- 7.5
fig_dpi <<- 200
fig_align <<- "center"
fig_pos <<- "htb"
opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  results = "hide",
  comment = "#>",
  fig.path = knitr_figs_dir,
  cache.path = knitr_cache_dir,
  fig.width = fig_width,
  echo = FALSE,
  autodep = FALSE,
  cache = TRUE,
  cache.lazy = FALSE,
  cache.comments = FALSE,
  dev = fig_out_type,
  dpi = fig_dpi,
  fig.align = fig_align,
  fig.pos = fig_pos)

devtools::load_all(here::here())

fig_dir <- here::here("beamer", "srg", "data", "knitr-figs-pdf")
if(!dir.exists(fig_dir)){
  dir.create(fig_dir)
}

```

```{r loading, include = FALSE, results = "asis"}
res <- knitr::knit_child("../../../doc/001-load-packages.rmd")
cat(res, sep = '\n')
res <- knitr::knit_child("../../../doc/002-load-globals.rmd")
cat(res, sep = '\n')
res <- knitr::knit_child("../../../doc/003-load-models.rmd")
cat(res, sep = '\n')
res <- knitr::knit_child("../../../doc/004-load-project-variables.rmd")
cat(res, sep = '\n')
```

# Year in review
```{r pchangecatch}
last_yr_catch <- tail(last_5_yrs_total_ct, 1)
penult_yr_catch <- tail(last_5_yrs_total_ct, 2)[1]
pchangecatch <- percent(abs((last_yr_catch - penult_yr_catch)) / penult_yr_catch)
pchangecatch <- ifelse(last_yr_catch > penult_yr_catch,
                       paste0(pchangecatch, " increase"),
                       paste0(pchangecatch, " decrease"))

rank_catch_last_year <- rank(base_model$catch$Obs * -1) |> 
  tail(1) |> 
  scales::ordinal()

# If odd year, create survey text. If even, create "No survey this year" text
surv_text <- ifelse(last_data_yr %% 2,
                    paste0(last_survey_yr,
                           " acoustic survey biomass estimate was ",
                           last_survey_yr_biomass,
                           " Mt (",
                           as.numeric(last_factor_penult) * 100,
                           "% of ",
                           penult_survey_yr,
                           " estimate)."),
                    paste0("No survey was performed in ",
                           last_assess_yr,
                           "."))
```

* `r last_assess_yr` TAC, adjusted for carryovers, was `r last_yr_tac` t.
* Canadian and U.S. fisheries predominantly started in April and May,
  respectively.
* `r rank_catch_last_year` highest coast-wide catch.
* `r pchangecatch` in catch from last year.
* No Canadian Joint-Venture Fishery.
* Highest proportion-at-age by sector
  - Age-`r us_age_1_prop_age_cp` fish in U.S. catcher-processor sector,
  - Age-`r us_age_1_prop_age_ms` fish in U.S. mothership sector,
  - Age-`r us_age_1_prop_age_shore` fish in U.S. shore-based sector,
  - Age-`r max_freezer_trawler_age_prop_age` fish in Canadian freezer-trawler
    sector, and
  - Age-`r max_shoreside_age_prop_age` fish in Canadian shoreside sector.
* `r surv_text`

# Summary of data sources used
:::::: {.columns}
::: {.column width="38%"}
* Fishery-dependent data
  - Annual catch (`r start_yr`--`r end_yr - 1`)
  - Age compositions (1975--`r end_yr - 1`; 1$^+$)
* Acoustic survey (`r survey_start_yr`--`r survey_end_yr`)
  - Biomass index age 2$^+$
  - Age compositions (2$^+$)
  - Numbers of age-1 fish
* Weight-at-age (1975--`r end_yr - 1`)
* Ageing imprecision and biases
  - double reads
  - blind reads
* Maturity ogive (NWFSC, 2017)
:::

::: {.column width="62%"}
```{r data-overview-map, out.height = "3in", out.width = "1\\columnwidth"}
plot_data_summary(base_model,
                  label_y_placement = c(1.8, 2.5, 2.0))
```
:::
::::::

# Catches
```{r catches, fig.height = 3.2, out.height = "2.6in", out.width = "1\\columnwidth"}
plot_catches(ct, xlim = c(start_yr, last_data_yr),
             leg_font_size = 7,
             leg_key_size = 0.2,
             leg_ratio = c(1, 4))
```

# Allocations of `r end_yr - 1` TAC of `r last_yr_tac` t
:::::: {.columns}
::: {.column width="50%"}
\center \textbf{\textcolor{blue}{Canada}} \center

\

\center \textbf{TAC was `r last_yr_can_tac` t} \center

* TAC includes `r last_yr_can_carryover` t of carryover
* Freezer Trawlers and Shoreside -- `r last_yr_can_shoreside_tac` t
* Joint Venture -- `r last_yr_can_tac_jv` t
:::

::: {.column width="50%"}
\center \textbf{\textcolor{blue}{United States}} \center

\

\center \textbf{TAC was `r last_yr_us_tac` t} \center

* Research and bycatch -- `r f(last_yr_us_research)` t
* Tribal  -- `r f(last_yr_us_tribal)` t -
  `r f(last_yr_us_tribal_quota_reallocated)` t reallocated on
  `r last_yr_us_tribal_reallocate_dates`
* Catcher Processor -- `r f(last_yr_us_cp_quota_reallocated)` t
* Mothership -- `r f(last_yr_us_ms_quota_reallocated)` t
* Shore-Based -- `r f(last_yr_us_shore_quota_reallocated)` t
:::
::::::

# Catches of `r end_yr - 1` TAC of `r last_yr_tac` t
:::::: {.columns}
::: {.column width="50%"}
\center \textbf{\textcolor{blue}{Canada}} \center

\

\center \textbf{TAC was `r last_yr_can_tac` t} \center
`r last_yr_can_landings` t, `r last_yr_can_attained`% of the Canadian TAC

* Freezer Trawlers -- `r last_yr_can_freezer` t,
  `r last_yr_can_freezer_percent`% of Canadian catch
* Shoreside -- `r last_yr_can_shore` t,
  `r last_yr_can_shore_percent`% of Canadian catch
* Joint Venture -- `r last_yr_can_jv` t,
`r last_yr_can_jv_percent`% of Canadian catch
:::

::: {.column width="50%"}
\center \textbf{\textcolor{blue}{United States}} \center

\

\center \textbf{TAC was `r last_yr_us_tac` t} \center
`r last_yr_us_landings` t, `r last_yr_us_attained`% of the U.S. TAC

* Catcher Processor -- `r f(last_yr_us_cp_ct)` t,
  `r last_yr_us_cp_ct_percent`% of US CP allocation
* Mothership `r f(last_yr_us_ms_ct)` t,
  `r last_yr_us_ms_ct_percent`% of US MS allocation
* Shore-Based -- `r f(last_yr_us_shore_ct)` t,
  `r last_yr_us_shore_ct_percent`% of shore-based allocation, includes
  `r f(round(sum(subset(us_ti_ct_by_month_df, year == last_assess_yr)$catch), 0))`
   t of tribal catches
:::
::::::

# Cumulative catch by month
```{r cumulative-catches, fig.height = 3.5, out.height = "3in", out.width = "1\\columnwidth"}
plot_cumulative_catches(list(us_ss_catch_by_month_df,
                             can_ss_catch_by_month_df,
                             us_cp_catch_by_month_df,
                             can_ft_catch_by_month_df,
                             us_ms_catch_by_month_df),
                        list("U.S. Shore-Based",
                             "Canadian Shorside",
                             "U.S. Catcher-processor",
                             "Canadian Freezer-Trawlers",
                             "U.S. Mothership"),
                        type = "cumulative",
                        ax_title_font_size = 10,
                        ax_tick_font_size = 8,
                        leg_font_size = 8)
```
  