---
title: "Process the U.S. catch"
output: rmarkdown::html_vignette
date: "This document was rendered on `r hake::curr_time_date()`"
vignette: >
  %\VignetteIndexEntry{Process the U.S. catch}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, echo = FALSE, message = FALSE, results = "hide", warning = FALSE}
library(hake)
```

The code within {hake} requires that `here::here()` be functional and point R
to the appropriate directory within your cloned repository. Thus, if the
results of `here::here()` do not give you your clone of the
[Pacific hake Github repository](github.com/pacific-hake/hake-assessment)
then you must navigate to somewhere that does.

   1. Pull data from the databases and process it: \
      ```{r pull-process, echo = FALSE, eval = FALSE}
      hakedataUSA::pull_database()
      hakedataUSA::process_database()
      ```

   1. Run the following to update the `r landings_tac_fn` and
      `r catch_targets_biomass_fn` file. This function depends on the monthly
      catch files being filled out but it is not harmful to run it prior to
      all of the files being completed for the current year: \
      ```{r, echo = FALSE}
      utils_update_catch_sums()
      ```