---
title: "Process the Canadian catch"
output: rmarkdown::html_vignette
date: "This document was rendered on `r hake::curr_time_date()`"
vignette: >
  %\VignetteIndexEntry{Process the Canadian catch}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, echo = FALSE, message = FALSE, results = "hide", warning = FALSE}
library(hake)
```

This method gets the realtime data from the Fisheries Operations System (FOS)
database directly, which is the most current source of catch data. Other
databases such as Groundfish FOS (GFFOS) are built by querying FOS.

 - Open the Microsoft Edge browser (no other browsers work for this) on the
   DFO network or with the VPN turned on and go to
   http://paccfprodin/fos2/index.cfm (or http://10.112.10.29/fos2/index.cfm)
   - Enter Username (grandinc) and Password (g.....3#), and login
   - Select Groundfish Trawl
   - Enter the current year and click **Set Default Preferences**
     and **Set Session Preferences**
   - Click red "Reports" button

 - **For the DMP landings:**
   - The Dockside Monitoring Program has the most reliable landings numbers,
     so we will use this for the landed catch
   - Click **Landings by species by date (DMP)**
   - Type or select **Pacific Hake** from the species dropdown box.
   - Set Start date to April 1, 2007 (Before that catch data were in
     PacHarvTrawl not FOS)
   - Set End date to today's date
   - Leave everything else blank
   - Click **Run Report**
   - It will take several minutes. There is no visible sign that it is
     doing anything. Don't get impatient, it's working, just wait
   - Once finished, the screen will change, giving you a link to open the
     new file
   - Click the link then **Save As..**
   - Upload the file to the following directory on the server: \
     `/srv/hake/other/landings/LandingsSpeciesDateDMP.csv`

 - **For the LOGS landings:**
   - Logbook data have discards, so we need to add those to the total landings
     from the DMP data
   - On the FOS website, in the same way as above, also run the
     **Catch by species by Date (LOGS)** report
   - Note you can only do 1 year at a time due to size restrictions on
     output data. You don't need to re-run the previous years, only the new
     year
   - Leave all areas checked
   - Select January 1 for the year to the end date for that year, usually
     December 31 or the current date if before that
   - Make sure **Fishing/ASOP logs** is checked, not **Video Catch logs**
   - It will take several minutes. There is no visible sign that it is doing
     anything
   - Click the link then **Save As..**
   - Upload the file to the following directory on the server: \
     `/srv/hake/other/landings/LogCatchReportXXXX.csv` \
     where the `XXXX` is the 4-digit year

**Once the data files have been uploaded, do the following steps.** \
**Note - simply compiling this vignette will build the files, and you can
just skip to #4. Check the timestamps of the files to verify.** \

  1. Open R and load the hake package: \
     ```{r}
     devtools::load_all()
     ```

   1. Run the following to create (overwrite) the Canadian catch-by-year file
      (note the directory `dr` which contains the files created above): \
      ```{r echo = TRUE}
      fleet_catch <- canada_load_catch_data(dr = "/srv/hake/other/landings/canada") |>
                     canada_extract_fleet_catch()
      
      canada_create_fleet_year_catch_csv_files(fleet_catch)
      ```

   1. Run the following to create (overwrite) the three Canadian catch-by-month
      files (note that it uses the `fleet_catch` object created above): \
      ```{r, echo = TRUE}
       canada_create_fleet_month_catch_csv_files(fleet_catch)
      ```

   1. Run the following to update the `landings-tac-history.csv` and
      `catch-targets-biomass.csv` file. This function depends on the monthly
      catch files being filled out but it is not harmful to run it prior to
      all of the files being completed for the current year: \
      ```{r, echo = FALSE}
      utils_update_catch_sums()
      ```

   2. Manually add the new year's Canadian carryover value and JV TAC (if any)
      to this file:
      ```{r, echo = FALSE}
      here(data_tables_path, further_tac_details_fn)
      ```
