---
title: "Running the hake docker container on Windows"
output: rmarkdown::html_vignette
date: "This document was rendered on `r hake::curr_time_date()`"
vignette: >
  %\VignetteIndexEntry{Running the hake docker container on Windows}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE,
                      comment = "#>")
```

```{r setup, echo = FALSE, message = FALSE, results = "hide", warning = FALSE}
```

---

This vignette assumes you have installed Docker on your local Windows machine.
If it is an IT-controlled machine it is unlikely they will allow it to be
installed as the Docker service requires root access to run the containers,
which they see as a vulnerability. \
[Download Docker installer for Windows](https://docs.docker.com/desktop/install/windows-install/)

In MS Windows 11, open a Bash shell by Running `powershell` or `cmd` to get
a DOS terminal, then type `bash` inside that to get to a Bash prompt. Use
that for the following procedure, don't try to run anything from the
`powershell` or `cmd` terminal directly.

## Steps to run the container for the first time

1. Once you have Docker installed, open a Bash terminal and pull the
   docker image from Docker Hub: \

   ```bash
   docker pull cgrandin/hake
   ```

   The image is very large and will take about 5 minutes to download.

1. Set up the two different local directories that are required to link to
   the Docker container. They are:

   - A `srv` directory which contains a structural replica of what resides
     on the Linux server in the `/srv` directory and holds the model SS3
     input files and the output `RDS` files for each model.
       - Download the [srv directory](https://drive.google.com/drive/folders/11KCdlsgk0hj3NlQY1aV6C99QBEP1GyQV)
         from Google Drive (need share permission) and place it wherever
         you want on your local machine. Take the directory name, append
         `srv` to it, convert it to Unix form, and enter it into the run
         script as the link for the models output.
         
         For example, if you are on Windows, and place the `srv` directory into
         the directory `d:\Work\hake`, then the directory is `d:\Work\hake\srv`.
         You must convert it into Unix form which is `/d/Work/hake/srv`. This
         is what you will enter into the run script on the next step.
         Preserve case when converting to Unix paths and make sure there is
         a leading `/` on it.

   - A `hake-assessment` directory where the git repository resides. This
     should be where your working copy is on your local machine.
  
       - If you do not have it yet, run `git clone`: \

         ```bash
         git clone https://github.com/pacific-hake/hake-assessment
         ```

       - Convert the directory name to Unix form as was done above for the
         `srv` directory. If your `hake-assessment` directory was
         `C:\Users\myname\github\pacific-hake\hake-assessment` then the Unix
         eqivalent is `/c/Users/myname/github/pacific-hake/hake-assessment`.

1. Find your user name on your local machine. If you already know what it is,
   skip to the next step.

   Open a Bash terminal in Windows on your local machine (Not `powershell`
   or `cmd`) and type this to get your `USERNAME`: \

   ```bash
   echo $USERNAME
   ```

   Make sure your user name is correct in the `docker/run-hake-docker.sh`
   file during the next step.
   
1. Link the directories on your computer from the previous step with the
   corresponding directories inside the Docker container:
   
   - Edit the file `docker/run-hake-docker.sh` file and find the line in
     the `if` statement with your name in it [(Example)](https://github.com/pacific-hake/hake-assessment/blob/604b168cc6b99f28496a782edb3a1b464f0ed0fe/docker/run-hake-docker.sh#L19). While there, make sure your `USERNAME`
     is correct and replace it with the output from the previous step.
     Here is what the `if/then` block looks like using the made up directories
     from the previous steps: \

     ```bash
       if [[ "$USERNAME" == "myusername" ]]; then
         SRV_DIR="/d/Work/hake/srv"
         REPO_DIR="/c/Users/myname/github/pacific-hake/hake-assessment"
     ```

   If you commit these changes to the repository your directories will be
   remembered for the future and you will not have to do this step ever again
   when you want to run the Docker container, as long as you always
   download the `srv` folder from the Google drive to the same place on
   your machine, and don't move your `hake-assessment` repository.

1. Open a Bash terminal and navigate to `hake-assessment/docker` directory
   of the `hake-assessment` repository on your local machine, then start
   a `hake` container:

   ```bash
   ./run-hake-docker.sh
   ```

   - The container will open in a Bash terminal, in the
     `/home/rstudio/github/pacific-hake/hake-assessment` directory. Type
     `ls -al` and you should see the files which are in the repository.
     If you don't see any files, go back to the previous step, and make
     sure you put the correct directory in the `docker/run-hake-docker.sh`
     for the `REPO_DIR`. The same applies to the `/srv` directory, type
     `ls -al /srv` and you should see the `hake` directory listed. If you
     do not, go back and fix the `SRV_DIR` in the `docker/run-hake-docker.sh`
     file.

1. To launch the Rstudio server run the following command:

     ```bash
     /init
     ```

     This will start a Rstudio server on your local machine and leave
     the terminal in a paused state.

1. To connect to the container's Rstudio server, open a Web browser and,
   in the URL bar, type the following followed by `Enter`:
   
     ```
     localhost:8787
     ```

   - The Rstudio login page will appear. Enter the credentials:
     - Username: `rstudio`
     - Password: `a`

   - Rstudio will open in your browser. You will start in the `doc` directory,
     and the files `_bookdown.yml` and `000-launcher.rmd` will be open.

   - To test the container, build the assessment document:

     ```R
     render()
     ```

     For more information on building the document, see the `README.md`
     file for the [hake assessment repository](https://github.com/pacific-hake/hake-assessment).

   - To exit the Rstudio server, click the button on the top right of the
     RStudio server page which says `rstudio` to its left and looks like an
     arrow pointing to the right off a white square, OR type `q()` at the
     console.

   - To get the Bash prompt to appear again, go back to the paused
     Docker Bash terminal and press `Ctrl-c` a couple of times.

   - To exit the container completely, type `exit` in the Bash terminal.
     If you keep the Docker container Bash terminal open, Your Rstudio
     session will remain cached and start where you left off if you type
     `/init` again. Once you exit the container, you will lose any changes
     made inside it (without warning). This shouldn't matter though, as your
     changes to the repository (or `srv` directory) are made outside the
     container because they are linked.

## Steps to run the container day-to-day

Once all the steps above are completed, you only need to do the following to
run a container and work on the assessment: \

1. Open a Bash terminal and navigate to the `docker` directory in the hake
   repository on your local machine.

1. Run the script `./run-hake-docker.sh`

1. Once the Docker container's bash prompt appears, run the command `/init`

1. Go to a Web browser, open a new tab, and type `localhost:8787` in the
   URL bar and press Enter (you can bookmark this to save time).

1. Login to Rstudio in the sign-in page that appears:

   - Username: `rstudio`
   - Password: `a`

1. Rstudio will open, your working directory will be the `doc` directory, and
   `devtools::load_all()` will have been run already so the hake package
   will be loaded.

\

# Building the Docker images

---

This section doesn't need to be read if you are just running the docker
container to work on the hake assessment.

## Description of the Docker build process

The hake docker run and build scripts are found in the `docker` directory of
the `hake-assessment` repository.

The `Dockerfile` is the primary script to build the `cgrandin/hake` image
and the sub-directories `docker/ss-texlive` and `docker/ubuntu-essentials`
contain the build files to create the `cgrandin/ss-texlive` and
`cgrandin/ubuntu-essentials` images, which act as the starting images for
the `cgrandin/hake` image. They are compiled in this order (with descriptions):

To build all of the following images and produce the final `cgrandin/hake`
image from scratch, use the Bash script `build-hake-docker-scratch.sh`. If
a download times out or some other error occurs, you can continue the build
by running `build-hake-docker-cached.sh`.

1. `cgrandin/ubuntu-essentials` - This image contains:

   - Ubuntu 22.04 LTS (or whatever the latest release Ubuntu will be in the
     future)

   - the Rocker project's `rocker/tidyverse` image which in itself contains
     the latest Rstudio server, R itself, and the `tidyverse` family of
     packages. The `tidyverse` family takes many hours to build in a local
     Docker build script so using this saves a lot of time.

   - R version 4.3.2 (2023-10-31)

   - RStudio Server 2023.12.0 Build 369

   - many additional GNU libraries for Linux that are needed to compile the
     R packages added later on in the build process.

1. `cgrandin/ss-texlive` - This image contains:

   - the `cgrandin/ubuntu-essentials` image, which includes everything in it.
   
   - [ADMB](https://github.com/admb-project/admb) release version 13.1
     (12-22-2023). This is the latest ADMB release, and it is cloned and
     built from source in the Docker image build.
   
   - [SS3](https://github.com/nmfs-ost/ss3-source-code) release version 3.30.22
     (2023-10-31). This is the latest SS3 release, and it is cloned and
     built from source in the Docker image build.
   
   - TexLive 2023 (texlive-base version) (https://www.tug.org/texlive/) which
     is the latest TexLive base version (texlive-base). TexLive takes a long
     time to install during the Docker image build process, so it is separated
     into its own image, to avoid having to wait every time a small change in
     the final image needs to be done.
     
1. `cgrandin/hake` - This image contains:

   - Everything present in the `cgrandin/ss-teclive` image.

   - Many R packages, that are needed for the `hake-assessment` package to be
     used.
     
   - A fully-specified `rstudio-prefs.json` file, which holds settings for the
     Rstudio GUI.
     
   - A `.Renviron` file, which contains a `GITHUB_PAT` token which was needed to
     allow many pulls for the R packages we need. Without it, the build
     process will error out due to *"too many GitHub API calls"*.
     
   - A .Rprofile file, which has R commands that are run when the Rstudio
     server starts. This includes setting the working directory to the
     `hake-assessment/doc` directory, syncing the 'Files' panel to that
     directory, opening two files (`_bookdown.yml` and `000-launcher.rmd`),
     and setting an option to ensure plots can be shown in the 'Plots' panel.
     
   - A .Rhistory file, which contains some often-used commands, so that we
     can just press the up and down arrows instead of typing them out.

   - new environment variables:

     - $HOME (`/home/rstudio`)
     - $INST (`/usr/bin`)
     - $ADMB_HOME (`/usr/bin/admb/build/admb`)
     - $ADMB_AD2CSV (`/usr/bin/admb/contrib/ad2csv`)
     - $SS3_EXE_NAME (`ss3_2024`)
     - $SS3_HOME (`/usr/bin/ss3`)
     - $TEXLIVE_HOME (`/usr/local/texlive/2023/bin/x86_64-linux`)
     - $MANPATH (`/usr/local/texlive/2023/texmf-dist/doc/man`)
     - $INFOPATH (`/usr/local/texlive/2023/texmf-dist/doc/info`)

   - A modified `$PATH` environment variable, containing the directories
     for the ADMB, SS3, and TexLive executables. In particular, the
     paths added to the `$PATH` are (from the list above):

   - $HOME (`/home/rstudio`)
   - $ADMB_HOME/bin (`/usr/bin/admb/build/admb/bin`)
   - $ADMB_AD2CSV (`/usr/bin/admb/contrib/ad2csv`)
   - $SS3_HOME (`/usr/bin/ss3`)
   - $TEXLIVE_HOME (`/usr/local/texlive/2023/bin/x86_64-linux`)

*Note: The `cgrandin/` part of the image names are necessary because that
is how docker knows which Docker Hub account to push the image to when
you run `docker push cgrandin/hake`. Without it, you cannot push the image
and it will not be shareable unless done manually (i.e. upload/download
to/from Google drive).*
