---
title: "Generate and use a new GitHub GPG key"
output: rmarkdown::html_vignette
date: "This document was rendered on `r hake::curr_time_date()`"
vignette: >
  %\VignetteIndexEntry{Generate and use a new GitHub GPG key}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE,
                      comment = "#>")
```

```{r setup, echo = FALSE, message = FALSE, results = "hide", warning = FALSE}
```

To have **<span style="color:green;">Verified</span>** appear on your GitHub
commits, follow this vignette.

1. Delete old GPG keys from GitHub and Linux:

   - List secret keys: \
     ```{bash, echo = TRUE}
     gpg --list-keys
     ```
   - Delete all keys, one by one. For each key, do the following, pasting the
     key in from the listing above which is the long key under **pub** \
     ```{bash, eval = FALSE}
     gpg --delete-key 89B7B58F6D30E38C695A5EB6322404A623C5E50C
     ```
   - Go to your GitHub account, click your picture on the top right, choose
     **Settings**, then **SSH and GPG keys**. Press the
     **<span style="color:red;">Delete</span>** button for each GPG key,
     until there are none left.

1. Create a new passphrase-less secret key, where **USER_ID** is your email
   address used for our GitHub account: \
   ```{bash, eval = FALSE}
   gpg --batch --passphrase '' --quick-gen-key USER_ID default default
   ```
   List secret keys to get the key value for the next step: \
   ```{bash, echo = TRUE}
   gpg --list-keys
   ```

1. Create the public key in **armor** format (key cut/paste from listing 
   above): \
   ```{bash, eval = FALSE}
   gpg --armor --export 89B7B58F6D30E38C695A5EB6322404A623C5E50CD
   ```
   This will output a long string of many rows taking up a whole screen,
   called a **GPG public key block**.
   
1. Copy the **GPG public key block** to the clipboard. It begins with: \
   **<span style="color:purple;">-----BEGIN PGP PUBLIC KEY BLOCK-----</span>** \
   and ends with: \
   **<span style="color:purple;">-----END PGP PUBLIC KEY BLOCK-----</span>** \
   Make sure to copy the begin and end lines and everything inbetween.
    
1. Paste the public GPG key block into the **New GPG key** box in Github.
   You add a GPG key to GitHub by clicking your picture on the top right
   in GitHub and then select **Settings** and **SSH and GPG Keys**.
   
1. List the secret key: \
   ```{bash, echo = TRUE}
   gpg --list-secret-keys --keyid-format=long
   ```
   The first line should look like the following. The blue text shows the key: \
   <span style="color:grey;">sec   rsa3072/</span><span style="color:blue;">322404A623C5E50C</span> <span style="color:grey;">2023-12-12 [SC] [expires: 2025-12-11]</span> \
   Copy the **key** to the clipboard: \
   <span style="color:blue;">322404A623C5E50C</span>

1. Run the following command with that copied key: \
   ```{bash, eval = FALSE}
   git config --global user.signingkey 322404A623C5E50C
   ```

1. Try and commit a staged change. For example: \
   ```{bash, eval = FALSE}
   git commit -a -m "Example commit"
   ```
   which should work and <span style="color:green;">Verified</span>
   should appear on the GitHub site in the commits list, next to your
   new commit. If instead <span style="color:red;">Unverified</span>
   appears, proceed to the next step.
   
1. Edit the key and make sure the username and email information
   is correct: \
   ```{bash, eval = FALSE}
   gpg --edit-key 322404A623C5E50C
   ```

1. At the gpg prompt (>), type: \
   `adduid`

1. Follow the prompts to add your real name and email address, Make sure
   the email address you enter is the one that your GitHub account is
   connected to. Enter "o" for Okay when it asks. When the gpog prompt
   appears again (>), type:
   `save`
   
1. Create the public key in **armor** format (key cut/paste from listing 
   above): \
   ```{bash, eval = FALSE}
   gpg --armor --export 89B7B58F6D30E38C695A5EB6322404A623C5E50CD
   ```
   
1. Copy the **GPG public key block** to the clipboard. It begins with: \
   **<span style="color:purple;">-----BEGIN PGP PUBLIC KEY BLOCK-----</span>** \
   and ends with: \
   **<span style="color:purple;">-----END PGP PUBLIC KEY BLOCK-----</span>** \
   Make sure to copy the begin and end lines and everything inbetween.
    
1. Paste the public GPG key block into the **New GPG key** box in Github.
   You add a GPG key to GitHub by clicking your picture on the top right
   in GitHub and then select **Settings** and **SSH and GPG Keys**.
   
1. Try and commit a staged change. For example: \
   ```{bash, eval = FALSE}
   git commit -a -m "Example commit"
   ```
   which should work and **VERIFIED** should appear on the GitHub site
   in the commits list, next to your new commit.
   
