---
title: "Process the Canadian catch"
output: rmarkdown::html_vignette
date: "This document was rendered on `r hake::curr_time_date()`"
vignette: >
  %\VignetteIndexEntry{Process the Canadian catch}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, echo = FALSE, message = FALSE, results = "hide", warning = FALSE}
```

1. Delete old GPG keys from GitHub and Linux

   - List secret keys: \
     `gpg --list-keys`
   - Delete all keys, one by one. For each key, do the following, pasting the
     key in from the listing above which is the long key under **pub** \
     `gpg --delete-key 89B7B58F6D30E38C695A5EB6322404A623C5E50C`

1. Create a new passphrase-less secret key, where **USER_ID** is your email
   address used for our GitHub account: \
   `gpg --batch --passphrase '' --quick-gen-key USER_ID default default`
   - List secret keys to get the key value for the next step: \
     `gpg --list-keys`

1. Create the public key in **armor** format (key cut/paste from listing 
   above): \
   `gpg --armor --export 89B7B58F6D30E38C695A5EB6322404A623C5E50CD`
   
1. Copy the public GPG key block, beginning with: \
   `-----BEGIN PGP PUBLIC KEY BLOCK-----` \
   and ending with: \
   `-----END PGP PUBLIC KEY BLOCK-----`
    
1. Paste the public GPG key block into the **New GPG key** box in Github.
   You add a GPG key to GitHub by clicking your picture on the top right
   in GitHub and then select **Settings** and **SSH and GPG Keys**.
   
