This vignette creates a single folder for each bridging step. Within each
folder, the input files are saved but Stock Synthesis is not run. To do that
users will need to run the bash scrips for the bridging models. The initial two
chunks must be executed prior to running any of the subsequent chunks. But,
after that, each chunk can be executed in any order in theory but sometimes
a previously created folder is needed because the input files depend on the
next step.

```{r setup-inputs, eval = FALSE}
library(devtools)
library(sdmTMB)
load_all()

# These objects must be altered EVERY YEAR
survey_age_comps <- c(
  0, 50.5802, 24.6599, 1.0311, 1.1722, 2.9196, 8.0851, 0.8808, 5.3789,
  0.7693, 0.5831, 0.6698, 2.2987, 0.4084, 0.5628
)
survey_age_comps_n <- 64

# These objects might need to be altered at the start
current_yr <- 2025
model_dir_srv <- "/srv/hake/models"
model_dir_version <- "01-version"
model_dir_base <- fs::path("01-base-models", "01-base")

# These objects do not need to be altered but are needed in other chunks
# Specify path to a bridging directory
bridge_dir <- fs::path(
  model_dir_srv, current_yr,
  model_dir_version, "02-bridging-models"
)
# Find the highest version in last year's folder of the base model
dir_last_yr <- fs::path(
  fs::path(model_dir_srv, current_yr - 1) |>
    fs::dir_ls(regexp = "version", type = "dir") |>
    tail(1),
  model_dir_base
)

# Local functions
insert_survey_value <- function(year,
                                data,
                                archive,
                                fleet = 2,
                                season = 7) {
  new_vector <- c(
    year, season, fleet, data
  )
  names(new_vector) <- NULL
  output <- rbind(
    archive,
    new_vector
  ) |>
    dplyr::arrange(abs(index), year)
  return(output)
}
```

```{r create-directories, eval = FALSE}
create_version_dirs(year = current_yr)
```

The first step is to copy last year's model over into the bridging directory. Though, it will end up not being an actual duplicate because it will be ran with the new Stock Synthesis executable.

```{r update-ss3-exe, eval = FALSE}
# Copy last year's model and run with new exe
r4ss::copy_SS_inputs(
  dir.old = dir_last_yr,
  dir.new = fs::path(bridge_dir, "00-update-ss3-exe"),
  overwrite = TRUE,
  use_ss_new = FALSE,
  verbose = FALSE,
  recursive = TRUE
)
```

The updating of data goes through two cycles, first the old data is updated for each data type. Then once that is complete, the newest years of data are tacked on.

```{r fix-catches, eval = FALSE}
r4ss::copy_SS_inputs(
  dir.old = fs::path(bridge_dir, "00-update-ss3-exe"),
  dir.new = fs::path(bridge_dir, "01-fix-catches"),
  overwrite = TRUE,
  use_ss_new = FALSE,
  verbose = FALSE,
  recursive = TRUE
)
fix_catches_dat <- update_ss3_catch(
  fs::path(bridge_dir, "01-fix-catches", "hake_data.ss")
)
fix_catches_dat[["endyr"]] <- current_yr - 2
fix_catches_dat[["catch"]] <- dplyr::filter(
  fix_catches_dat[["catch"]],
  year <= fix_catches_dat[["endyr"]]
)
r4ss::SS_writedat(
  fix_catches_dat,
  outfile = fs::path(bridge_dir, "01-fix-catches", "hake_data.ss"),
  overwrite = TRUE,
  verbose = FALSE
)
```

```{r fix-weight-at-age, eval = FALSE}
r4ss::copy_SS_inputs(
  dir.old = fs::path(bridge_dir, "01-fix-catches"),
  dir.new = fs::path(bridge_dir, "02-fix-weight-at-age"),
  overwrite = TRUE,
  use_ss_new = FALSE,
  verbose = FALSE,
  recursive = TRUE
)
inputs <- r4ss::SS_read(
  dir = fs::path(bridge_dir, "02-fix-weight-at-age"),
  ss_new = FALSE,
  verbose = FALSE
)
# TODO: combine these two functions, maybe do not even need
#       write_wtatage_file as long as the data frame is padded
# Update with the tv weight-at-age data first and just a vector
# of average maturity to use legacy function
write_wtatage_file(
  file = fs::path(bridge_dir, "02-fix-weight-at-age", "wtatage.ss"),
  data = pad_weight_at_age(
    dplyr::filter(weight_at_age_estimates_df, year <= current_yr - 2)
  ),
  maturity = maturity_estimates_df |>
    dplyr::filter(doy == 278, year <= current_yr - 2) |>
    dplyr::summarize(p_mature = mean(p_mature), .by = c(age)) |>
    dplyr::pull(p_mature)
)
# Read that weight-at-age data back in and update it with the
# time-varying maturity and write back out
weight_at_age <- r4ss::SS_readwtatage(
  file = fs::path(bridge_dir, "02-fix-weight-at-age", "wtatage.ss")
)
inputs[["wtatage"]] <- update_ss3_maturity(
  maturity = maturity_estimates_df |>
    dplyr::filter(
      model == "Spatial + temperature",
      !is.na(p_mature),
      year <= current_yr - 2,
      doy == 278
    ),
  weight_at_age = weight_at_age
)
inputs[["par"]] <- NULL
r4ss::SS_write(
  inputlist = inputs,
  dir = fs::path(bridge_dir, "02-fix-weight-at-age"),
  overwrite = TRUE,
  verbose = FALSE
)
# Chris wrote this function and I am not sure what it does but the files
# will not run without doing it
purrr::walk(
  fs::path(bridge_dir, "02-fix-weight-at-age"),
  .f = \(x) system(glue::glue("cd {x} && clean_ss3"))
)
```

```{r fix-survey-1, eval = FALSE}
r4ss::copy_SS_inputs(
  dir.old = fs::path(bridge_dir, "02-fix-weight-at-age"),
  dir.new = fs::path(bridge_dir, "03-fix-survey-1"),
  overwrite = TRUE,
  use_ss_new = FALSE,
  verbose = FALSE,
  recursive = TRUE
)
# inputs <- r4ss::SS_read(
#   dir = fs::path(bridge_dir, "03-fix-survey-1"),
#   ss_new = FALSE,
#   verbose = FALSE
# )
# # TODO: put age-1 survey values in a spreadsheet that is version controlled
# inputs[["dat"]][["CPUE"]] <- insert_survey_value(
#   fleet = 3,
#   year = 2021,
#   data = c(2276192.127, 0.5),
#   archive = inputs[["dat"]][["CPUE"]] |>
#     dplyr::filter(!(year == 2021 & index == 3))
# )
# r4ss::SS_write(
#   inputs,
#   dir = fs::path(bridge_dir, "03-fix-survey-1"),
#   overwrite = TRUE
# )
```

```{r 04-fix-fishery-comps, eval = FALSE}
r4ss::copy_SS_inputs(
  dir.old = fs::path(bridge_dir, "03-fix-survey-1"),
  dir.new = fs::path(bridge_dir, "04-fix-fishery-comps"),
  overwrite = TRUE,
  use_ss_new = FALSE,
  verbose = FALSE,
  recursive = TRUE
)

inputs <- r4ss::SS_read(
  dir = fs::path(bridge_dir, "04-fix-fishery-comps"),
  ss_new = FALSE,
  verbose = FALSE
)
# Create the fishery age composition information
fishery_age_composition <- calc_fishery_ages(
  weight_at_age = inputs[["wtatage"]]
)
colnames(fishery_age_composition) <- colnames(inputs[["dat"]][["agecomp"]])
inputs[["dat"]][["agecomp"]] <- dplyr::bind_rows(
  dplyr::filter(
    inputs[["dat"]][["agecomp"]],
    !(fleet == 1 & year >= 2008)
  ),
  fishery_age_composition |>
    dplyr::filter(year < current_yr - 1, Yr >= 2008)
) |>
  dplyr::arrange(-fleet, year)

r4ss::SS_write(
  inputs,
  dir = fs::path(bridge_dir, "04-fix-fishery-comps"),
  overwrite = TRUE
)
```

```{r add-catches, eval = FALSE}
r4ss::copy_SS_inputs(
  dir.old = fs::path(bridge_dir, "04-fix-fishery-comps"),
  dir.new = fs::path(bridge_dir, "10-add-catches"),
  overwrite = TRUE,
  use_ss_new = FALSE,
  verbose = FALSE,
  recursive = TRUE
)
inputs <- r4ss::SS_read(
  dir = fs::path(bridge_dir, "10-add-catches"),
  ss_new = FALSE,
  verbose = FALSE
)
updated_catches_dat <- update_ss3_catch(
  fs::path(bridge_dir, "10-add-catches", "hake_data.ss")
)
inputs[["dat"]] <- updated_catches_dat
r4ss::SS_write(
  inputs,
  dir = fs::path(bridge_dir, "10-add-catches"),
  overwrite = TRUE
)
```

```{r add-weight-at-age, eval = FALSE}
r4ss::copy_SS_inputs(
  dir.old = fs::path(bridge_dir, "10-add-catches"),
  dir.new = fs::path(bridge_dir, "20-add-weight-at-age"),
  overwrite = TRUE,
  use_ss_new = FALSE,
  verbose = FALSE,
  recursive = TRUE
)
inputs <- r4ss::SS_read(
  dir = fs::path(bridge_dir, "20-add-weight-at-age"),
  ss_new = FALSE,
  verbose = FALSE
)
# TODO: combine these two functions, maybe do not even need
#       write_wtatage_file as long as the data frame is padded
# Update with the tv weight-at-age data first and just a vector
# of average maturity to use legacy function
write_wtatage_file(
  file = fs::path(bridge_dir, "20-add-weight-at-age", "wtatage.ss"),
  data = pad_weight_at_age(
    dplyr::filter(weight_at_age_estimates_df, year <= current_yr - 2)
  ),
  maturity = maturity_estimates_df |>
    dplyr::filter(doy == 278) |>
    dplyr::summarize(p_mature = mean(p_mature), .by = c(age)) |>
    dplyr::pull(p_mature)
)
# Read that weight-at-age data back in and update it with the
# time-varying maturity and write back out
weight_at_age <- r4ss::SS_readwtatage(
  file = fs::path(bridge_dir, "20-add-weight-at-age", "wtatage.ss")
)
inputs[["wtatage"]] <- update_ss3_maturity(
  maturity = maturity_estimates_df |>
    dplyr::filter(
      model == "Spatial + temperature",
      !is.na(p_mature),
      doy == 278
    ),
  weight_at_age = weight_at_age
)
inputs[["par"]] <- NULL
r4ss::SS_write(
  inputlist = inputs,
  dir = fs::path(bridge_dir, "20-add-weight-at-age"),
  overwrite = TRUE,
  verbose = FALSE
)
# Chris wrote this function and I am not sure what it does but the files
# will not run without doing it
purrr::walk(
  fs::path(bridge_dir, "20-add-weight-at-age"),
  .f = \(x) system(glue::glue("cd {x} && clean_ss3"))
)
```

```{r add-survey-2, eval = FALSE}
r4ss::copy_SS_inputs(
  dir.old = fs::path(bridge_dir, "20-add-weight-at-age"),
  dir.new = fs::path(bridge_dir, "30-add-survey-2"),
  overwrite = TRUE,
  use_ss_new = FALSE,
  verbose = FALSE,
  recursive = TRUE
)
# inputs <- r4ss::SS_read(
#   dir = fs::path(bridge_dir, "30-add-survey-2"),
#   ss_new = FALSE,
#   verbose = FALSE
# )
# inputs[["dat"]][["CPUE"]] <- insert_survey_value(
#   fleet = -2,
#   year = current_yr - 2,
#   data = c(1, 1),
#   archive = inputs[["dat"]][["CPUE"]]
# )
# # TODO: replace the entire time series and add -fleet for the missing year rows
# #       this will need to be done for the age-1 survey as well
# inputs[["dat"]][["CPUE"]] <- insert_survey_value(
#   year = current_yr - 1,
#   data = survey_by_country_df |>
#     dplyr::filter(year == current_yr - 1) |>
#     dplyr::mutate(
#       total = total * 1000,
#       total.cv = total.cv / 100
#     ) |>
#     dplyr::select(total, total.cv) |>
#     as.vector(),
#   archive = inputs[["dat"]][["CPUE"]]
# )
# r4ss::SS_write(
#   inputs,
#   dir = fs::path(bridge_dir, "30-add-survey-2"),
#   overwrite = TRUE
# )
```

```{r add-survey-age-comps, eval = FALSE}
r4ss::copy_SS_inputs(
  dir.old = fs::path(bridge_dir, "30-add-survey-2"),
  dir.new = fs::path(bridge_dir, "31-add-survey-age-comps"),
  overwrite = TRUE,
  use_ss_new = FALSE,
  verbose = FALSE,
  recursive = TRUE
)
inputs <- r4ss::SS_read(
  dir = fs::path(bridge_dir, "31-add-survey-age-comps"),
  ss_new = FALSE,
  verbose = FALSE
)
# inputs[["dat"]][["agecomp"]] <- rbind(
#   inputs[["dat"]][["agecomp"]],
#   c(
#     current_yr - 1, 7, 2, 0, 0, 51, -1, -1, survey_age_comps_n,
#     survey_age_comps
#   )
# ) |>
#   dplyr::arrange(-fleet, year)
# inputs[["dat"]] <- update_ss3_ageing_error(inputs[["dat"]])
# r4ss::SS_write(
#   inputs,
#   dir = fs::path(bridge_dir, "31-add-survey-age-comps"),
#   overwrite = TRUE
# )
```

```{r survey-1, eval = FALSE}
r4ss::copy_SS_inputs(
  dir.old = fs::path(bridge_dir, "31-add-survey-age-comps"),
  dir.new = fs::path(bridge_dir, "40-add-survey-1"),
  overwrite = TRUE,
  use_ss_new = FALSE,
  verbose = FALSE,
  recursive = TRUE
)
# inputs <- r4ss::SS_read(
#   dir = fs::path(bridge_dir, "40-add-survey-1"),
#   ss_new = FALSE,
#   verbose = FALSE
# )
# inputs[["dat"]][["CPUE"]] <- insert_survey_value(
#   fleet = -3,
#   year = current_yr - 2,
#   data = c(1, 1),
#   archive = inputs[["dat"]][["CPUE"]]
# )
# # TODO: put age-1 survey values in a spreadsheet that is version controlled
# inputs[["dat"]][["CPUE"]] <- insert_survey_value(
#   fleet = 3,
#   year = current_yr - 1,
#   data = c(1186865.482, 0.5),
#   archive = inputs[["dat"]][["CPUE"]]
# )
# # TODO: Fix this so non-survey year works because you must subtract 2!
# inputs[["ctl"]][["MainRdevYrLast"]] <- inputs[["dat"]][["endyr"]] - 1
# r4ss::SS_write(
#   inputs,
#   dir = fs::path(bridge_dir, "40-add-survey-1"),
#   overwrite = TRUE
# )
```

```{r fishery-comp, eval = FALSE}
r4ss::copy_SS_inputs(
  dir.old = fs::path(bridge_dir, "40-add-survey-1"),
  dir.new = fs::path(bridge_dir, "50-add-fishery-ages"),
  overwrite = TRUE,
  use_ss_new = FALSE,
  verbose = FALSE,
  recursive = TRUE
)
inputs <- r4ss::SS_read(
  dir = fs::path(bridge_dir, "50-add-fishery-ages"),
  ss_new = FALSE,
  verbose = FALSE
)

fishery_age_composition <- calc_fishery_ages(
  weight_at_age = inputs[["wtatage"]]
)
colnames(fishery_age_composition) <- colnames(inputs[["dat"]][["agecomp"]])
inputs[["dat"]][["agecomp"]] <- dplyr::bind_rows(
  dplyr::filter(
    inputs[["dat"]][["agecomp"]],
    !(fleet == 1 & year >= 2008)
  ),
  fishery_age_composition |>
    dplyr::filter(year >= 2008)
) |>
  dplyr::arrange(-fleet, year)
# Ensure that ageing error is updated in case this is a non-survey year
inputs[["dat"]] <- update_ss3_ageing_error(inputs[["dat"]])

# Fix terminal year for time-varying selectivity
inputs[["ctl"]][["age_selex_parms"]][, "dev_maxyr"] <- ifelse(
  inputs[["ctl"]][["age_selex_parms"]][, "dev_maxyr"] == 0,
  0,
  max(inputs[["dat"]][["agecomp"]][, "year"])
)

r4ss::SS_write(
  inputs,
  dir = fs::path(bridge_dir, "50-add-fishery-ages"),
  overwrite = TRUE
)
```

```{r base, eval = FALSE}
r4ss::copy_SS_inputs(
  dir.old = fs::path(bridge_dir, "50-add-fishery-ages"),
  dir.new = fs::path(dirname(bridge_dir), model_dir_base),
  overwrite = TRUE,
  use_ss_new = FALSE,
  verbose = FALSE,
  recursive = TRUE
)
```

```{r summarize, eval = FALSE}
rds_files <- fs::dir_ls(
  bridge_dir,
  type = "file",
  recurse = TRUE,
  regexp = "rds$"
)
res <- purrr::map(rds_files, .f = readRDS)
names(res) <- gsub(
  "^[0-9]{1,3}-(.+)\\.rds",
  "\\1",
  basename(rds_files)
) |>
  gsub(pattern = "-", replacement = " ")
i_runs <- list(seq_along(res))
for (i in seq_along(i_runs)) {
ggplot2::ggsave(
  filename = fs::path(bridge_dir, paste0("sb-", i, ".png")),
  plot = plot_biomass(
    res[i_runs[[i]]],
    names(res)[i_runs[[i]]],
    xlim = c(1960, current_yr),
    leg_pos = c(0.5, 0.9),
    leg_ncol = 3,
    point_color = rainbow(17)
  )
)
ggplot2::ggsave(
  filename = fs::path(bridge_dir, paste0("age-2-", i, ".png")),
  plot = plot_survey_index_fits(
    d_obj = create_group_df_index(
      res[i_runs[[i]]],
      names(res)[i_runs[[i]]],
      survey_type = "age2"
    ),
    survey_type = "age2",
    rev_colors = FALSE,
    leg_pos = c(0.5, 0.9),
    leg_ncol = 3,
    xlim = c(1995, current_yr - 1),
    ylim = c(-0.1, 3.4),
    model_names = names(res)[i_runs[[i]]]
  )
)
ggplot2::ggsave(
  filename = fs::path(bridge_dir, paste0("rec-dev-", i, ".png")),
  plot_recruitment(
    model_lst = res[i_runs[[i]]],
    model_names = names(res)[i_runs[[i]]]
  )
)
}
```
