---
title: "Pacific Hake MCMC runs with varying acceptances"
output:
   bookdown::html_document2:
      toc: true
      toc_depth: 4
      number_sections: true
      pandoc_args: ["--number-offset=1"]
date: "This document was rendered on `r hake::curr_time_date()`"
vignette: >
  %\VignetteIndexEntry{Pacific Hake MCMC runs with varying acceptances}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  fig.width = 10,
  fig.height = 8,
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, echo = FALSE, results = "hide"}
devtools::load_all(here::here())
library(hake)
theme_set(hake_theme())

# Need this function to show LaTeX tables in HTML
tex2markdown <- \(texstring){
  writeLines(text = texstring,
             con = myfile <- tempfile(fileext = ".tex"))
  texfile <- pandoc(input = myfile, format = "html")
  cat(readLines(texfile), sep = "\n")
  unlink(c(myfile, texfile))
}

type_path <- "/srv/hake/models/2024/02-version/05-test-models"

if(!exists("long_chain")){
  long_chain <- readRDS(file.path(type_path,
                                  "14-long-base/14-long-base.rds"))
}

if(!exists("chain_lst")){
  num_samples <- c(500, 1000, 2500, 5000, 10000)
  chain_lst <- map(num_samples, ~{
    load_all_models_in_subdir(.x, type_path = type_path)
  })
  names(chain_lst) <- num_samples
}
if(!exists("lst_ad")){
  lst_ad <- map(chain_lst, ~{
    j <- group_test_models(.x, group_by = "adapt_delta")
    for(i in seq_along(j)){
      nms <- names(j[[i]])
      j[[i]] <- append(list(long_chain), j[[i]])
      names(j[[i]]) <- c("Long chain base model", nms)
    }
    j
  })
}
if(!exists("lst_nc")){
  lst_nc <- map(chain_lst, ~{
    j <- group_test_models(.x, group_by = "num_cores")
    for(i in seq_along(j)){
      nms <- names(j[[i]])
      j[[i]] <- append(list(long_chain), j[[i]])
      names(j[[i]]) <- c("Long chain base model", nms)
    }
    j
  })
}

# NUTS fits
dirs <- c("15-500-samples-group",
          "16-1000-samples-group",
          "17-2500-samples-group",
          "18-5000-samples-group",
          "19-10000-samples-group")

subdirs <- c("01-80-delta-2-cores",
             "02-80-delta-4-cores",
             "03-80-delta-14-cores",
             "04-85-delta-2-cores",
             "05-85-delta-4-cores",
             "06-85-delta-14-cores",
             "07-90-delta-2-cores",
             "08-90-delta-4-cores",
             "09-90-delta-14-cores",
             "10-95-delta-2-cores",
             "11-95-delta-4-cores",
             "12-95-delta-14-cores")

all_dirs <- map(dirs, ~{
  file.path(.x, subdirs)
}) |>
  unlist()

if(!exists("fits")){
  fits <- save_nuts_fits(mdl_nms = all_dirs)
  long_chain_fit <- save_nuts_fits(mdl_nms = "14-long-base")
  fits <- append(long_chain_fit, fits, after = 0)
  long_chain_nm <- "14-32000-samples-group/00-99-delta-1-cores"
  names(fits) <- c(long_chain_nm, all_dirs)
}
```

_______________________________________________________________________

# Comparisons between models with the same number of samples

```{r acceptance-tab, echo = FALSE, message = FALSE, results = "asis"}

# Extract the number of samples, adapt_delta, and number of cores values
nms <- names(fits)
num_samples <- gsub("\\d{2}-(\\d+)-samples-group\\/\\d+-\\d+-delta-\\d+-cores",
                 "\\1",
                 nms)
num_cores <- gsub("\\d{2}-\\d+-samples-group\\/\\d+-\\d+-delta-(\\d+)-cores",
                 "\\1",
                 nms)
adapt_deltas <- gsub("\\d{2}-\\d+-samples-group\\/\\d+-(\\d+)-delta-\\d+-cores",
                 "\\1",
                 nms)
adapt_deltas <- f(as.numeric(adapt_deltas) / 100, 2)

d <- map_df(fits, \(fit){
  all_chains_d <- map_df(fit$sampler_params, \(chain_df){
    chain_df |> 
      as_tibble()
  })

  out <- all_chains_d |> 
    as_tibble() |> 
    mutate(divergent__ = divergent__ * 10000) |> 
    summarize(across(everything(), mean)) |> 
    mutate(across(-divergent__, ~f(.x, 4))) |> 
    mutate(across(divergent__, ~f(.x)))
  names(out) <- c("Accept stat",
                  "Step size",
                  "Tree depth",
                  "N leapfrog",
                  "Divergent",
                  "Energy")
  out
    }) |> 
  mutate(`Num samples` = num_samples,
         `Num cores` = num_cores,
         `Adapt delta` = adapt_deltas) |> 
  select(`Num samples`,
         `Num cores`,
         `Adapt delta`,
         everything()) |> 
  mutate(`Num samples` = f(as.numeric(`Num samples`)))

  k <- kbl(d,
           format = "html",
           align   = rep("r", ncol(d)),
           caption = paste0("Convergence statistics for models with ",
                            "several different number of samples, ",
                            "Adapt delta and number of cores used. The ",
                            "first row contains the output for the long ",
                            "chain base model which can be used as a ",
                            "reference.")) |> 
    kable_styling("striped",
                  full_width = TRUE,
                  font_size = 14) |> 
    pack_rows("500 Samples", 2, 13,
              label_row_css = "background-color: #666; color: #fff;") |> 
    pack_rows("1,000 Samples", 14, 25,
              label_row_css = "background-color: #666; color: #fff;") |> 
    pack_rows("2,500 Samples", 26, 37,
              label_row_css = "background-color: #666; color: #fff;") |>  
    pack_rows("5,000 Samples", 38, 49,
              label_row_css = "background-color: #666; color: #fff;") |> 
    pack_rows("10,000 Samples", 50, 61,
              label_row_css = "background-color: #666; color: #fff;")
k 
```

# Biomass trajectory comparisons between models

## Models with 500 samples

This is a summary of the outputs of models run with sample size output set
to 500, with varying `adapt_delta` and number of cores values.

```{r adapt-delta-500-samples, echo = FALSE, fig.cap = "Spawning biomass for models with 500 samples saved. Each panel represents the `adapt_delta` value , multiplied by 100, and each panel has the model runs done with a variable number of cores. The 'Long chain base model' is a comparison run with the number of samples set to 32,000 and the `adapt_delta` set to 0.99."}

panels_title_size <- 11
plot_comparison(lst_ad$`500`,
                plot_func = plot_biomass,
                label_text = "Adapt delta",
                ylim = c(0, 5),
                leg_pos = c(0.7, 0.8),
                scale = 100,
                digits = 2)
```

```{r num-cores-500-samples, echo = FALSE, fig.cap = "Spawning biomass for models with 500 samples saved. Each panel represents the `num_cores` value, and each panel has the model runs done with a variable number of `adapt_delta` values. The 'Long chain base model' is a comparison run with the number of samples set to 32,000 and the `adapt_delta` set to 0.99."}

plot_comparison(lst_nc$`500`,
                plot_func = plot_biomass,
                label_text = "Number of cores",
                ylim = c(0, 5),
                leg_pos = c(0.7, 0.8))
```

## Models with 1,000 samples

This is a summary of the outputs of models run with sample size output set
to 1,000, with varying `adapt_delta` and number of cores values.

```{r adapt-delta-1000-samples, echo = FALSE, fig.cap = "Spawning biomass for models with 1,000 samples saved. Each panel represents the `adapt_delta` value , multiplied by 100, and each panel has the model runs done with a variable number of cores. The 'Long chain base model' is a comparison run with the number of samples set to 32,000 and the `adapt_delta` set to 0.99."}

panels_title_size <- 11
plot_comparison(lst_ad$`1000`,
                plot_func = plot_biomass,
                label_text = "Adapt delta",
                ylim = c(0, 5),
                leg_pos = c(0.7, 0.8),
                scale = 100,
                digits = 2)
```

```{r num-cores-1000-samples, echo = FALSE, fig.cap = "Spawning biomass for models with 1,000 samples saved. Each panel represents the `num_cores` value, and each panel has the model runs done with a variable number of `adapt_delta` values. The 'Long chain base model' is a comparison run with the number of samples set to 32,000 and the `adapt_delta` set to 0.99."}

plot_comparison(lst_nc$`1000`,
                plot_func = plot_biomass,
                label_text = "Number of cores",
                ylim = c(0, 5),
                leg_pos = c(0.7, 0.8))
```

## Models with 2,500 samples

This is a summary of the outputs of models run with sample size output set
to 2,500, with varying `adapt_delta` and number of cores values.

```{r adapt-delta-2500-samples, echo = FALSE, fig.cap = "Spawning biomass for models with 2,500 samples saved. Each panel represents the `adapt_delta` value , multiplied by 100, and each panel has the model runs done with a variable number of cores. The 'Long chain base model' is a comparison run with the number of samples set to 32,000 and the `adapt_delta` set to 0.99."}

panels_title_size <- 11
plot_comparison(lst_ad$`2500`,
                plot_func = plot_biomass,
                label_text = "Adapt delta",
                ylim = c(0, 5),
                leg_pos = c(0.7, 0.8),
                scale = 100,
                digits = 2)
```

```{r num-cores-2500-samples, echo = FALSE, fig.cap = "Spawning biomass for models with 2,500 samples saved. Each panel represents the `num_cores` value, and each panel has the model runs done with a variable number of `adapt_delta` values. The 'Long chain base model' is a comparison run with the number of samples set to 32,000 and the `adapt_delta` set to 0.99."}

plot_comparison(lst_nc$`2500`,
                plot_func = plot_biomass,
                label_text = "Number of cores",
                ylim = c(0, 5),
                leg_pos = c(0.7, 0.8))
```

## Models with 5,000 samples

This is a summary of the outputs of models run with sample size output set
to 5,000, with varying `adapt_delta` and number of cores values.

```{r adapt-delta-5000-samples, echo = FALSE, fig.cap = "Spawning biomass for models with 5,000 samples saved. Each panel represents the `adapt_delta` value , multiplied by 100, and each panel has the model runs done with a variable number of cores. The 'Long chain base model' is a comparison run with the number of samples set to 32,000 and the `adapt_delta` set to 0.99."}

panels_title_size <- 11
plot_comparison(lst_ad$`5000`,
                plot_func = plot_biomass,
                label_text = "Adapt delta",
                ylim = c(0, 5),
                leg_pos = c(0.7, 0.8),
                scale = 100,
                digits = 2)
```

```{r num-cores-5000-samples, echo = FALSE, fig.cap = "Spawning biomass for models with 5,000 samples saved. Each panel represents the `num_cores` value, and each panel has the model runs done with a variable number of `adapt_delta` values. The 'Long chain base model' is a comparison run with the number of samples set to 32,000 and the `adapt_delta` set to 0.99."}

plot_comparison(lst_nc$`5000`,
                plot_func = plot_biomass,
                label_text = "Number of cores",
                ylim = c(0, 5),
                leg_pos = c(0.7, 0.8))
```

## Models with 10,000 samples

This is a summary of the outputs of models run with sample size output set
to 10,000, with varying `adapt_delta` and number of cores values.

```{r adapt-delta-10000-samples, echo = FALSE, fig.cap = "Spawning biomass for models with 10,000 samples saved. Each panel represents the `adapt_delta` value , multiplied by 100, and each panel has the model runs done with a variable number of cores. The 'Long chain base model' is a comparison run with the number of samples set to 32,000 and the `adapt_delta` set to 0.99."}

panels_title_size <- 11
plot_comparison(lst_ad$`10000`,
                plot_func = plot_biomass,
                label_text = "Adapt delta",
                ylim = c(0, 5),
                leg_pos = c(0.7, 0.8),
                scale = 100,
                digits = 2)
```

```{r num-cores-10000-samples, echo = FALSE, fig.cap = "Spawning biomass for models with 10,000 samples saved. Each panel represents the `num_cores` value, and each panel has the model runs done with a variable number of `adapt_delta` values. The 'Long chain base model' is a comparison run with the number of samples set to 32,000 and the `adapt_delta` set to 0.99."}

plot_comparison(lst_nc$`10000`,
                plot_func = plot_biomass,
                label_text = "Number of cores",
                ylim = c(0, 5),
                leg_pos = c(0.7, 0.8))
```

# Estimated recruitment comparisons between models

## Models with 500 samples

This is a summary of the outputs of models run with sample size output set
to 500, with varying `adapt_delta` and number of cores values.

```{r adapt-delta-500-samples-recr, echo = FALSE, fig.cap = "Recruitment for models with 500 samples saved. Each panel represents the `adapt_delta` value , multiplied by 100, and each panel has the model runs done with a variable number of cores. The 'Long chain base model' is a comparison run with the number of samples set to 32,000 and the `adapt_delta` set to 0.99."}

panels_title_size <- 11
plot_comparison(lst_ad$`500`,
                plot_func = plot_recruitment,
                label_text = "Adapt delta",
                ylim = c(0, 40),
                leg_pos = c(0.7, 0.8),
                scale = 100,
                digits = 2)
```

```{r num-cores-500-samples-recr, echo = FALSE, fig.cap = "Recruitment for models with 500 samples saved. Each panel represents the `num_cores` value, and each panel has the model runs done with a variable number of `adapt_delta` values. The 'Long chain base model' is a comparison run with the number of samples set to 32,000 and the `adapt_delta` set to 0.99."}

plot_comparison(lst_nc$`500`,
                plot_func = plot_recruitment,
                label_text = "Number of cores",
                ylim = c(0, 40),
                leg_pos = c(0.7, 0.8))
```

## Models with 1,000 samples

This is a summary of the outputs of models run with sample size output set
to 1,000, with varying `adapt_delta` and number of cores values.

```{r adapt-delta-1000-samples-recr, echo = FALSE, fig.cap = "Recruitment for models with 1,000 samples saved. Each panel represents the `adapt_delta` value , multiplied by 100, and each panel has the model runs done with a variable number of cores. The 'Long chain base model' is a comparison run with the number of samples set to 32,000 and the `adapt_delta` set to 0.99."}

panels_title_size <- 11
plot_comparison(lst_ad$`1000`,
                plot_func = plot_recruitment,
                label_text = "Adapt delta",
                ylim = c(0, 40),
                leg_pos = c(0.7, 0.8),
                scale = 100,
                digits = 2)
```

```{r num-cores-1000-samples-recr, echo = FALSE, fig.cap = "Recruitment for models with 1,000 samples saved. Each panel represents the `num_cores` value, and each panel has the model runs done with a variable number of `adapt_delta` values. The 'Long chain base model' is a comparison run with the number of samples set to 32,000 and the `adapt_delta` set to 0.99."}

plot_comparison(lst_nc$`1000`,
                plot_func = plot_recruitment,
                label_text = "Number of cores",
                ylim = c(0, 40),
                leg_pos = c(0.7, 0.8))
```

## Models with 2,500 samples

This is a summary of the outputs of models run with sample size output set
to 2,500, with varying `adapt_delta` and number of cores values.

```{r adapt-delta-2500-samples-recr, echo = FALSE, fig.cap = "Recruitment for models with 2,500 samples saved. Each panel represents the `adapt_delta` value , multiplied by 100, and each panel has the model runs done with a variable number of cores. The 'Long chain base model' is a comparison run with the number of samples set to 32,000 and the `adapt_delta` set to 0.99."}

panels_title_size <- 11
plot_comparison(lst_ad$`2500`,
                plot_func = plot_recruitment,
                label_text = "Adapt delta",
                ylim = c(0, 40),
                leg_pos = c(0.7, 0.8),
                scale = 100,
                digits = 2)
```

```{r num-cores-2500-samples-recr, echo = FALSE, fig.cap = "Recruitment for models with 2,500 samples saved. Each panel represents the `num_cores` value, and each panel has the model runs done with a variable number of `adapt_delta` values. The 'Long chain base model' is a comparison run with the number of samples set to 32,000 and the `adapt_delta` set to 0.99."}

plot_comparison(lst_nc$`2500`,
                plot_func = plot_recruitment,
                label_text = "Number of cores",
                ylim = c(0, 40),
                leg_pos = c(0.7, 0.8))
```

## Models with 5,000 samples

This is a summary of the outputs of models run with sample size output set
to 5,000, with varying `adapt_delta` and number of cores values.

```{r adapt-delta-5000-samples-recr, echo = FALSE, fig.cap = "Recruitment for models with 5,000 samples saved. Each panel represents the `adapt_delta` value , multiplied by 100, and each panel has the model runs done with a variable number of cores. The 'Long chain base model' is a comparison run with the number of samples set to 32,000 and the `adapt_delta` set to 0.99."}

panels_title_size <- 11
plot_comparison(lst_ad$`5000`,
                plot_func = plot_recruitment,
                label_text = "Adapt delta",
                ylim = c(0, 40),
                leg_pos = c(0.7, 0.8),
                scale = 100,
                digits = 2)
```

```{r num-cores-5000-samples-recr, echo = FALSE, fig.cap = "Recruitment for models with 5,000 samples saved. Each panel represents the `num_cores` value, and each panel has the model runs done with a variable number of `adapt_delta` values. The 'Long chain base model' is a comparison run with the number of samples set to 32,000 and the `adapt_delta` set to 0.99."}

plot_comparison(lst_nc$`5000`,
                plot_func = plot_recruitment,
                label_text = "Number of cores",
                ylim = c(0, 40),
                leg_pos = c(0.7, 0.8))
```

## Models with 10,000 samples

This is a summary of the outputs of models run with sample size output set
to 10,000, with varying `adapt_delta` and number of cores values.

```{r adapt-delta-10000-samples-recr, echo = FALSE, fig.cap = "Recruitment for models with 10,000 samples saved. Each panel represents the `adapt_delta` value , multiplied by 100, and each panel has the model runs done with a variable number of cores. The 'Long chain base model' is a comparison run with the number of samples set to 32,000 and the `adapt_delta` set to 0.99."}

panels_title_size <- 11
plot_comparison(lst_ad$`10000`,
                plot_func = plot_recruitment,
                label_text = "Adapt delta",
                ylim = c(0, 40),
                leg_pos = c(0.7, 0.8),
                scale = 100,
                digits = 2)
```

```{r num-cores-10000-samples-recr, echo = FALSE, fig.cap = "Recruitment for models with 10,000 samples saved. Each panel represents the `num_cores` value, and each panel has the model runs done with a variable number of `adapt_delta` values. The 'Long chain base model' is a comparison run with the number of samples set to 32,000 and the `adapt_delta` set to 0.99."}

plot_comparison(lst_nc$`10000`,
                plot_func = plot_recruitment,
                label_text = "Number of cores",
                ylim = c(0, 40),
                leg_pos = c(0.7, 0.8))
```

