---
title: "Pacific Hake NUTS"
output:
   bookdown::html_document2:
      toc: true
      toc_depth: 4
      number_sections: true
      pandoc_args: ["--number-offset=1"]
date: "This document was rendered on `r hake::curr_time_date()`"
vignette: >
  %\VignetteIndexEntry{Pacific Hake NUTS}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, echo = FALSE, message = FALSE, results = "hide", warning = FALSE}
library(hake)

# Need this function to show LaTeX tables in HTML
tex2markdown <- \(texstring){
  writeLines(text = texstring,
             con = myfile <- tempfile(fileext = ".tex"))
  texfile <- pandoc(input = myfile, format = "html")
  cat(readLines(texfile), sep = "\n")
  unlink(c(myfile, texfile))
}

```

_______________________________________________________________________

## Introduction

Running the models for the hake assessment using NUTS requires that the user
provide the sample size, adapt delta, and the number of chains for the run.

## Burn-in investigation

To determine the ideal burn-in for this assessment model, 11 models were run
each with a different burn-in value. The models were identical in every other
way, and used the same `adapt_delta` value of 0.95 and 8 chains. The values
used for burn-in were: 1, 50, 100, 150, 200, 250, 300, 350, 400, 450, and 500.

There were divergent iterations in all cases, but with decreasing numbers
after a burn-in of only 50 samples (Table \@ref(tab:burnin-tab)).

To view detailed stats for any one of these models, run the following where 1
can be any number between 1 and 11:

```{r shiny-ex, echo = TRUE, eval = FALSE}
fits <- save_nuts_fits()
adnuts::launch_shinyadmb(fits[[1]])
```

```{r burnin-tab, echo = FALSE, message = FALSE, results = "asis"}

fits <- save_nuts_fits()

# If only some of the runs are done. Don't forget to change the values in
# line about 15 lines down:   mutate(`Burn-in` = c(1, seq(50, 500, 50))) |> 
#
# fits <- map(fits, ~{
#   if(is.na(.x[1])){
#     return(NULL) 
#   }else{
#     return(.x) 
#   }})
# fits[sapply(fits, is.null)] <- NULL

d <- map_df(fits, \(fit){
  all_chains_d <- map_df(fit$sampler_params, \(chain_df){
    chain_df |> 
      as_tibble()
  })

  out <- all_chains_d |> 
    as_tibble() |> 
    mutate(divergent__ = divergent__ * 10000) |> 
    summarize(across(everything(), mean)) |> 
    mutate(across(-divergent__, ~f(.x, 4))) |> 
    mutate(across(divergent__, ~f(.x)))
  names(out) <- c("Accept stat",
                  "Step size",
                  "Tree depth",
                  "N leapfrog",
                  "Divergent",
                  "Energy")
  out
    }) |> 
  mutate(`Burn-in` = c(1, seq(50, 500, 50), 50)) |> 
  select(`Burn-in`, everything())

  k <- kbl(d,
           format = "latex",
           booktabs = TRUE,
           align = rep("r", ncol(d)),
           linesep = "",
           escape = FALSE,
           caption = paste0("Convergence statistics for models with ",
                            "several different burn-in oprions.")) |> 
    row_spec(0, bold = TRUE)

tex2markdown(k)
```