# Past management

## Total allowable catch
:::::: {.columns}
::: {.column width="40%"}

* March `r last_assess_yr`
  - Default harvest rule TAC = `r f((catch_targets_df %>% dplyr::filter(Year == last_assess_yr))[["Default HCR TAC"]])` t
  - Sum of unilateral TACs = `r last_yr_tac` t
* When default HR suggests a large catch, TAC is often set less
* Catches are often less than the TAC
* Box colors correspond to year in the time series (darker are more recent)
:::

::: {.column width="50%"}
```{r jmc-tac-vs-realized-catch, fig.height = 4, fig.width = 4, out.height = "85%"}

plot_management_catch_vs_tac_1_to_1(catch_targets_df,
                                    yrs_nudge_right = c(2006, 2010, 2011,
                                                        2012, 2014, 2019,
                                                        2020))
```
:::
::::::

## Total allowable catch
```{r jmc-tac-vs-realized-catch-ts, fig.height = 3.5, fig.width = 7.5, out.height = "80%"}

plot_management_catch_vs_tac(catch_targets_df,
                             curr_assess_biomass = base_model$catch_default_policy[1],
                             leg_pos = c(0.12, 0.87),
                             leg_font_size = 8)
```
