## Request 2 -- "on Figure G.11 add the data for proportion mature"

Description

* The first figure shows empirical results for age 2 and the second figure shows
  empirical results for age 3. Data are included from non-ASHOP samples because
  that is what the curve is predicting. For each year (denoted on the smooth
  line) the points appear above or below the labeled point from the same year.
* We do not expect the points to overlap or lie on the line because the curve
  represents the marginal effect of temperature (e.g., predicted maturity from
  non-ASHOP samples collected from an average sample location on July 1).
* Changing the reference date from July 1 to a later date for age-3 fish would
  have the effect of shifting the curve up closer to the points because the
  non-ASHOP samples occur later in the year (25% before July1/75% after). The
  points are also affected by variable sampling effort year to year.
* In conclusion, we would never really expect the empirical estimates to
  perfectly match the model-based ones. Sampling varies across space and time,
  and the empirical estimates do not account for any of this variation.

## Request 2 -- "on Figure G.11 add the data for proportion mature"

```{r 02-fig-a, results = "asis", out.height = "85%"}
figures_dir <- fs::path("../../../doc/image-files")
include_graphics(file.path(figures_dir,
                           "2024-srg-response-1-2-a.png"),
                 error = FALSE)
```

## Request 2 -- "on Figure G.11 add the data for proportion mature"

```{r 02-fig-b, results = "asis", out.height = "85%"}
figures_dir <- fs::path("../../../doc/image-files")
include_graphics(file.path(figures_dir,
                           "2024-srg-response-1-2-b.png"),
                 error = FALSE)
```