## Request 7 -- "Survey and catch biomass at age"

Proportion of survey biomass estimated in Canada.

```{r, can-prop-survey-biomass-fig, results = "asis", out.height="80%"}

include_graphics(file.path(here::here(),"beamer/srg/requests-1/survey-biomass-files/Proportion-by-age-CAN-hake.png"), error = FALSE)
```

## Request 7 -- "Survey and catch biomass at age"

```{r, can-survey-biomass-at-age-load, echo=FALSE}

survey_biomass_at_age_can <- read_csv(file.path(here::here(), "beamer/srg/requests-1/survey-biomass-files/Survey_Biomass_at_Age_CAN.csv"))

survey_biomass_at_age_us <- read_csv(file.path(here::here(), "beamer/srg/requests-1/survey-biomass-files/Survey_Biomass_at_Age_US.csv"))
```


Fishery Catch-at-age for Canada (tonnes)

```{r can-catch-at-age, results = "asis"}

table_catch_by_fleet(country = 1, font_size = 4)
```

## Request 7 -- "Survey and catch biomass at age"

Fishery Catch-at-age for U.S. (tonnes)

```{r us-catch-at-age, results = "asis"}

table_catch_by_fleet(country = 2, font_size = 4)
```

The following code was pasted into doc using gotest() from the doc directory
so that landscape pages could be used to show the wide tables

BEGIN LANDSCAPE

```{r, survey-at-age-us, results = "asis"}

d <- read_csv("~/github/pacific-hake/hake-assessment/beamer/srg/requests-1/survey-biomass-files/Survey_Biomass_at_Age_US.csv",
              col_types = cols()) |> 
  rename(wgt = wgt_total) |> 
  mutate(across(-year, ~{f(.x / 1e3)})) |> 
  rename(Year = year,
         Biomass = wgt)

kbl(d,
    format = "latex",
    booktabs = TRUE,
    align = c("l",
              rep("r", ncol(d) - 1)),
    linesep = "",
    caption = "Proportion of survey biomass estimated in the U.S.",
    escape = FALSE) |>
  kable_styling(font_size = 7) |>
  row_spec(0, bold = TRUE)
```

```{r, survey-at-age-can, results = "asis"}

d <- read_csv("~/github/pacific-hake/hake-assessment/beamer/srg/requests-1/survey-biomass-files/Survey_Biomass_at_Age_CAN.csv",
              col_types = cols()) |> 
  rename(wgt = wgt_total) |> 
  mutate(across(-year, ~{f(.x / 1e3)})) |> 
  rename(Year = year,
         Biomass = wgt)

kbl(d,
    format = "latex",
    booktabs = TRUE,
    align = c("l",
              rep("r", ncol(d) - 1)),
    linesep = "",
    caption = "Proportion of survey biomass estimated in Canada",
    escape = FALSE) |>
  kable_styling(font_size = 8) |>
  row_spec(0, bold = TRUE)
```

END LANDSCAPE


