# Request 1
**Summarize the number of aged fish by month for each sector in the US and Canada (if possible). Compare these to the monthly catch plots**

**Justification:** This will help to determine if the age data are representative of the fishery catches. If the number of ages are consistent with the catch, then the ages are likely to be representative.

## Request 1 Results: Catch by Month

```{r catch-by-month-fig, fig.height = 5, fig.asp = 0.5, out.height = "80%"}

plot_catch_by_month(list(us_ss_catch_by_month_df,
                         can_ss_catch_by_month_df,
                         us_cp_catch_by_month_df,
                         can_ft_catch_by_month_df,
                         us_ms_catch_by_month_df),
                    list("U.S. Shoreside",
                         "Canadian Shoreside",
                         "U.S. Catcher-Processor",
                         "Canadian Freezer-Trawlers",
                         "U.S. Mothership"),
                    type = "catch",
                    disclaimer_text = paste0(
                      "These plots have different y-axis ranges\n",
                      "and are not directly comparable\n",
                      "with each other."),
                    yrs = c(2025, 2025),
                    leg_font_size = 8,
                    title_font_size = 10,
                    ax_text_x = 8,
                    ax_text_y = 8)
```

## Request 1 Results: Canadian Samples by Month

```{r age-comp-comparison, results = "asis"}

sample_df <- canada_load_sample_data() |> 
  dplyr::filter(sex %in% c(1, 2))

samples_fleet_lst <- canada_get_fleet_samples(sample_df)
# Remove JV for this table
samples_fleet_lst <- samples_fleet_lst[names(samples_fleet_lst) != "jv"]

samples_summary_tbls_lst <- canada_extract_sampling_by_month(
  samples_fleet_lst,
  yr = last_data_yr + 1)

```

:::::: {.columns}
::: {.column width="45%"}
\begin{center}\textbf{Freezer trawlers}\end{center}
```{r canada-sample-summary-ft, results = "asis"}
table_sampling_by_month(
  samples_summary_tbls_lst$ft,
  font_size = 8,
  header_font_size = 9)
```
:::

::: {.column width="45%"}
\begin{center}\textbf{Shoreside}\end{center}
```{r canada-sample-summary-ss, results = "asis"}
table_sampling_by_month(
  samples_summary_tbls_lst$ss,
  font_size = 8,
  header_font_size = 9)
```
:::
::::::



## Request 1 Results: U.S. At-Sea Samples by Month

:::::: {.columns}
::: {.column width="45%"}
\begin{center}\textbf{Catcher-Processor}\end{center}
```{r us-atsea-cp-sampling-summary, results = "asis"}
d<- tibble(month = c("May", "Jun", "Jul", "Aug", "Sep", "Oct", "Total"),
           num_age = c(250, 135, 0, 0, 0, 170, 555),
           num_length = c(507, 269, 0, 0, 0, 541, 1317),
            num_weight = c(507, 269, 0, 0, 0, 541, 1317))

table_sampling_by_month(d,
                        font_size = 8,
                        header_font_size = 9)
```
:::

::: {.column width="45%"}
\begin{center}\textbf{Mothership}\end{center}
```{r us-at-sea-ms-sampling-summary, results = "asis"}
d <- tibble(month = c("May", "Jun", "Jul", "Aug", "Sep", "Oct", "Total"),
            num_age = c(0, 134, 164, 177, 150, 38, 663),
            num_length = c(0, 266, 311, 319, 276, 64, 1236),
            num_weight = c(0, 266, 311, 319, 276, 64, 1236))
table_sampling_by_month(d,
                        font_size = 8,
                        header_font_size = 9)
```
:::
::::::

## Request 1 Results: U.S. Shoreside Samples by Month

\begin{center}\textbf{Shoreside}\end{center}
```{r us-sb-sampling-summary, results = "asis"}
d <- tibble(month = c("April", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Total"),
            num_age = c(2, 118, 229, 450, 370, 290, 170, 0, 1629),
            num_length = c(6, 78, 360, 440, 440, 340, 388, 20, 2066),
            num_weight = c(6, 78, 360, 440, 440, 340, 388, 20, 2066))
table_sampling_by_month(d,
                        font_size = 8,
                        header_font_size = 9)
```
