## Request 2
**Show the expected fishery age proportions for 2025 and 2026 fishery (this is fig 43 in 2025 assessment and slide 10 of management outcomes presentation). Possibly overlay this with 2025 fishery observations to compare the two. The JTC can decide how to present the observed 2025 fishery data.**

**Justification:** This request will identify the correct predictions of fishery proportions-at-age for 2025 and 2026, thus providing insights into what the model expects  for 2025 fisheries proportions-at-age. Comparing to the observations from 2025 will help to identify potential biases in the assessment, in particular related to the assumption of fixing recent recruitment to less than average recruitment.

## Request 2 results (1/2)
:::::: {.columns}
::: {.column width="45%"}
**Median proportions:**
```{r fore-age-props, results = "asis"}

table_fore_age_props(fore_catch_prop,
                     fore_catch_prop_wt,
                     ages_filt = 1:15,
                     font_size = 8) |>
    # Highlight two largest cohorts
    row_spec(10:11,
           bold = table_highlight_bold,
           background = table_highlight_color)
```
:::

::: {.column width="55%"}
```{r main-age-comp-forecast, fig.height = 3.5, fig.width = 5.5, out.height = "80%"}
plot_fore_age_comps(base_model,
                    y_lim = c(0, 0.7),
                    is_catch_proj = TRUE)
```
:::
::::::

## Request 2 results (2/2)

**\Large Additional request 2 results found in the attached file: request-2-day-1-2026.pdf**

<!-- Copy thr following into a blank RMD in a doc folder and build (or run gotest() from with doc-catch-proj or doc folders and paste and build there) -->

<!-- # Request 2 results -->

<!-- Actual 2025 fishery age proportions compared with projected 2025 fishery age proportions from the 2025 assessment model and projected 2026 fishery age proportions from the 2026 assessment model. -->

<!-- ```{r main-age-comp-forecast-single, fig.height = 5, fig.asp = 0.8, out.height = "6in"} -->

<!-- # load fishery 2025 age props and plot -->
<!-- d <- read_csv("fishery-age-props-2025.csv", col_types = cols()) -->
<!-- x_lim <- c(1, 15) -->
<!-- x_breaks <- seq(x_lim[1], x_lim[2], 2) -->
<!-- y_lim = c(0, 0.55) -->

<!-- plist <- NULL -->
<!-- plist[[1]] <- ggplot(d, -->
<!--                      aes(x = age, -->
<!--                          y = prop)) + -->
<!--   geom_bar(stat = "identity", -->
<!--            fill = main_fill, -->
<!--            alpha = main_alpha) + -->
<!--   scale_x_continuous(breaks = x_breaks, -->
<!--                      labels = x_breaks) + -->
<!--   scale_y_continuous(expand = c(0, 0)) + -->
<!--   coord_cartesian(xlim = x_lim, -->
<!--                   ylim = y_lim, -->
<!--                   expand = TRUE) + -->
<!--   xlab("") + -->
<!--   ylab("Prop. 2025 catch") + -->
<!--   ggtitle("") + -->
<!--   theme(plot.title = element_text(hjust = 0.5)) -->

<!-- plist[[2]] <- plot_fore_age_comps(last_yr_base_model, -->
<!--                                   y_lim = c(0, 0.7), -->
<!--                                   by_number_only = TRUE, -->
<!--                                   show_x_title = FALSE) -->

<!-- plist[[3]] <- plot_fore_age_comps(base_model, -->
<!--                                   y_lim = c(0, 0.7), -->
<!--                                   by_number_only = TRUE, -->
<!--                                   is_catch_proj = TRUE) -->


<!--   plot_grid(plotlist = plist, nrow = 3, align = "v") -->

<!-- ``` -->

