## Request 5
**Calculate and present probability tables (slide 15 of management outcomes) for each sensitivity run (at least the no additional standard error on the survey and the stochastic recruitment runs).**

**Justification:** This will provide an insight into the management outcomes for alternative model runs and identify the importance (through the size of the effect) to management outcomes.

## Probabilities based on `r end_yr` catch (Base Model)

```{r main-risk-forecast-year-1-table-req-base, results = "asis"}

table_risk(base_model,
           forecast_yrs,
           index = 1,
           is_catch_proj = TRUE,
           type = "probability",
           font_size = 8,
           header_font_size = 9) |> 
    row_spec(4,
           bold = table_highlight_bold,
           background = table_highlight_color)
```

## Probabilities based on `r end_yr` catch (Stoch. Fore. Recr.)

```{r main-risk-forecast-year-1-table-req-sens1, results = "asis"}

sens1 <- readRDS("~/Desktop/Hake models/models/2026/01-version/05-test-models/06-base-stochastic-forecast-recruitment/06-base-stochastic-forecast-recruitment.rds")

table_risk(sens1,
           forecast_yrs,
           index = 1,
           is_catch_proj = TRUE,
           type = "probability",
           font_size = 8,
           header_font_size = 9) |> 
    row_spec(4,
           bold = table_highlight_bold,
           background = table_highlight_color)
```

## Probabilities based on `r end_yr` catch (Stoch. Fore. Recr. & Fit Survey)

```{r main-risk-forecast-year-1-table-req-sens2, results = "asis"}

sens2 <- readRDS("~/Desktop/Hake models/models/2026/01-version/05-test-models/10-base-stochastic-forecast-rec-fit-survey/10-base-stochastic-forecast-rec-fit-survey.rds")

table_risk(sens2,
           forecast_yrs,
           index = 1,
           is_catch_proj = TRUE,
           type = "probability",
           font_size = 8,
           header_font_size = 9) |> 
    row_spec(4,
           bold = table_highlight_bold,
           background = table_highlight_color)
```

## Probabilities based on `r end_yr` catch (Fit Survey)

```{r main-risk-forecast-year-1-table-req-sens3, results = "asis"}

sens3 <- readRDS("~/Desktop/Hake models/models/2026/01-version/05-test-models/11-base-fit-survey/11-base-fit-survey.rds")


table_risk(sens3,
           forecast_yrs,
           index = 1,
           is_catch_proj = TRUE,
           type = "probability",
           font_size = 8,
           header_font_size = 9) |> 
    row_spec(4,
           bold = table_highlight_bold,
           background = table_highlight_color)
```


