# Cohorts

## Estimates of above average cohorts

```{r jmc-above-avg-cohorts, results = "asis"}

hdr <- c("Calculation (billions)",
         "Low (2.5\\%)",
         "Median",
         "High (97.5\\%)",
         "Interval size")
d <- tibble(col1 = c(paste0(assess_yr - 1, " assessment recruitment in 2010"),
                     paste0(assess_yr, " assessment recruitment in 2010"),
                     paste0(assess_yr - 1, " assessment recruitment in 2014"),
                     paste0(assess_yr, " assessment recruitment in 2014"),
                     paste0(assess_yr - 1, " assessment recruitment in 2016"),
                     paste0(assess_yr, " assessment recruitment in 2016"),
                     paste0(assess_yr - 1, " assessment recruitment in 2020"),
                     paste0(assess_yr, " assessment recruitment in 2020")),
            col2 = c(rec_2010[[1]][1], rec_2010[[2]][1],
                     rec_2014[[1]][1], rec_2014[[2]][1],
                     rec_2016[[1]][1], rec_2016[[2]][1],
                     rec_2020[[1]][1], rec_2020[[2]][1]),
            col3 = c(rec_2010[[1]][2], rec_2010[[2]][2],
                     rec_2014[[1]][2], rec_2014[[2]][2],
                     rec_2016[[1]][2], rec_2016[[2]][2],
                     rec_2020[[1]][2], rec_2020[[2]][2]),
            col4 = c(rec_2010[[1]][3], rec_2010[[2]][3],
                     rec_2014[[1]][3], rec_2014[[2]][3],
                     rec_2016[[1]][3], rec_2016[[2]][3],
                     rec_2020[[1]][3], rec_2020[[2]][3]),
            col5 = c(rec_2010[[1]][4], rec_2010[[2]][4],
                     rec_2014[[1]][4], rec_2014[[2]][4],
                     rec_2016[[1]][4], rec_2016[[2]][4],
                     rec_2020[[1]][4], rec_2020[[2]][4]))

kbl(d,
    format = "latex",
    booktabs = TRUE,
    escape = FALSE,
    linesep = "",
    col.names = hdr) |>
  row_spec(0, bold = TRUE) |> 
  row_spec(c(2, 4, 6), hline_after = TRUE) |> 
  kable_styling(position = "center") |> 
  kable_styling(font_size = 10)
```

## Estimated cumulative catch for select cohorts
:::::: {.columns}
::: {.column width="50%"}
\
\

Estimated total catch from each cohort

* 1999 cohort (ages 1--`r last_data_yr - 1999`): `r f(max(cohort_cum_sum_1999))` t
* 2010 cohort (ages 1--`r last_data_yr - 2010`): `r f(max(cohort_cum_sum_2010))` t
* 2014 cohort (ages 1--`r last_data_yr - 2014`): `r f(max(cohort_cum_sum_2014))` t
* 2016 cohort (ages 1--`r last_data_yr - 2016`): `r f(max(cohort_cum_sum_2016))` t
* 2020 cohort (ages 1--`r last_data_yr - 2020`): `r f(max(cohort_cum_sum_2020))` t
:::

::: {.column width="50%"}
```{r jmc-cumulative-catch-cohorts, fig.height = 4, fig.width = 4, out.height = "85%"}

plot_cumulative_catch_cohorts(base_model)
```

:::
::::::

