# Decision tables

## Decision tables
* Decision table format (as improved last year)
  - Quantiles from the posterior distribution for relative spawning biomass
    and fishing intensity
* Catch alternatives
  - **a**: `r ct_levels[[1]][[2]]` (zero catch)
  - **b**--**i**: Constant catches of
    `r str_comma_sep(map_chr(ct_levels[2:9], ~{.x[[2]]}))`.
  - **j**: Constant catch equal to the `r ct_levels[[10]][[2]]`
* Constant catch of 525,000 t added per request at SRG (see Appendix I)

## Relative spawning biomass
```{r jmc-decisions-biomass-zero-table, results = "asis"}

table_decision(base_model,
               is_catch_proj_model = TRUE,
               num_yrs_to_show = 1,
               type = "biomass",
               #rows_to_show = c("a", "b", "e", "j"),
               font_size = 6,
               header_font_size = 7) |> 
    row_spec(5,
           bold = table_highlight_bold,
           background = table_highlight_color)

```

## Fishing intensity
```{r jmc-decisions-fishin-intensity-selected-table, results = "asis"}

table_decision(base_model,
               is_catch_proj_model = TRUE,
               num_yrs_to_show = 1,
               type = "spr",
               #rows_to_show = c("a", "b", "e", "j"),
               font_size = 6,
               header_font_size = 7) |> 
    row_spec(5,
           bold = table_highlight_bold,
           background = table_highlight_color)
```
