\newpage

\rfoot{Executive summary}

# Executive summary {-}

## Stock {-}

This assessment reports the status of the coastal `r sp` (or `r common_name`,
*`r science_name`*) stock off the west coast of the United States and Canada
at the start of `r assess_yr`. This stock exhibits seasonal migratory
behavior, ranging from offshore and generally southern waters during the
winter spawning season to coastal areas between northern California and
northern British Columbia during the spring, summer, and fall when the
fishery is conducted. In years with warmer water the stock tends to move
farther to the north during the summer. Older `r simple_name` tend to migrate
farther north than younger fish in all years, with catches in the Canadian
zone typically consisting of fish greater than four years old. Separate, and
much smaller, populations of `r simple_name` occurring in the major inlets
of the Northeast Pacific Ocean, including the Strait of Georgia, Puget Sound,
and the Gulf of California, are not included in this analysis.

(ref:es-catches-cap) Total `r sp` catch used in the assessment by sector,
`r start_yr`--`r last_data_yr`. U.S. tribal catches are included in the
sectors where they are represented.

(ref:es-catches-alt) This figure shows that catches in four of the last six
years have been the largest in the time series.

```{r es-catches-fig, fig.cap = "(ref:es-catches-cap)", fig.height = 4}

plot_catches(ct, xlim = c(start_yr, last_data_yr))
```

## Catches {-}

Coast-wide fishery landings of `r sp` averaged `r f(mean(ct$Total))`~t
from `r min(ct$Year)` to `r max(ct$Year)`, with a low of
`r f(min(ct$Total))`~t in
`r ct$Year[ct$Total == min(ct$Total)]` and a peak of
`r f(max(ct$Total))`~t in
`r ct$Year[ct$Total == max(ct$Total)]`
(Figure \@ref(fig:es-catches-fig)).
Prior to `r min(ct$Year)`, total removals were negligible compared to the
modern fishery. Over the early period (`r min(ct$Year)`--1990) most removals
were from foreign or joint-venture fisheries. Across the time series, annual
catch in U.S. waters averaged `r f(mean(ct[["U.S. Total"]]))`~t
(`r f(sum(ct[["U.S. Total"]]) / sum(ct$Total) * 100, 1)`% of the total catch),
while catch from Canadian waters averaged `r f(mean(ct[["Canada Total"]]))`~t.
Over the last 10 years, `r max(ct$Year) - 9`--`r max(ct$Year)`
(Table \@ref(tab:es-catches-tab)), the average coast-wide catch was
`r ct_mean_10yrs`~t with U.S. and Canadian catches averaging
`r ct_us_mean_10yrs`~t and `r ct_can_mean_10yrs`~t, respectively. Since 2017,
the coast-wide catch has been declining annually through `r end_yr - 1`,
when it was `r last_yr_landings`~t out of a total allowable catch (TAC,
adjusted for carryovers) of `r last_yr_tac`~t. Attainment in the U.S. was
`r last_yr_us_attained`% of its quota and in Canada it was
`r last_yr_can_attained`%.


```{r es-catches-tab, results = "asis", echo = FALSE}

table_catch(
  ct,
  inc_foreign_jv = FALSE,
  start_yr = end_yr - 10,
  end_yr = end_yr - 1,
  caption = paste0(
    "Total ", sp, " catch used in the assessment by sector, ", start_yr,
    "--", last_data_yr, ". U.S. tribal catches are included in the sectors ",
    "where they are represented."),
  font_size = 7,
  header_font_size = 7,
  longtable = TRUE)
```

In this document, the terms catch and landings are used interchangeably.
Estimates of discard within the target fishery are included, but discarding
of `r sp` in non-target fisheries is not. Discard from all fisheries, 
including those that do not target hake, is estimated to be less than 1% of
landings in recent years. During the last five years, catches were
considerably above the long-term average catch (`r f(long_term_avge_ct)`~t),
but have been in decline over that period (especially in Canada). Landings
between 2001 and 2008 were predominantly comprised of fish from the very large
1999 year class, with the cumulative removal (through `r end_yr - 1`) from
that cohort estimated at approximately
`r f(cohort_catch_1999 / 1e6, 2)` Mt. Through `r last_data_yr`, the
cumulative catch of the 2010, 2014, and 2016 year classes is estimated to be
about `r f(cohort_catch_2010 / 1e6, 2)` Mt,
`r f(cohort_catch_2014 / 1e6, 2)` Mt, and
`r f(cohort_catch_2016 / 1e6, 2)` Mt, respectively. In the
`r end_yr - 1` catch, `r top_coh(base_model, last_data_yr, 3, cap = FALSE)`.

## Data and assessment {-}

This Joint Technical Committee (JTC) assessment depends on the fishery
landings (`r start_yr`--`r last_data_yr`), an acoustic survey biomass index
of age-2+ fish (Figure~\@ref(fig:es-survey-biomass-fig) and age compositions
(`r survey_start_yr`--`r survey_end_yr`), a relative index of age-1 fish (Figure~\@ref(fig:es-survey-age1-fig); `r survey_start_yr`--`r survey_end_yr`),
fishery age compositions (`r start_yr_age_comps`--`r last_data_yr`), and
mean weight-at-age data (`r start_yr_age_comps`--`r last_data_yr`). In 2011
the survey biomass index was the lowest in the time series and was followed
by the index increasing in 2012, 2013, and again in 2015 before decreasing to
near the time series average in 2017. The 2019 estimate is the fourth highest
of the series, and the 2021 estimate is near the time series average.
Age-composition data from the aggregated fisheries and the acoustic survey,
along with the age-1 index, provide data that facilitates estimating relative
cohort strength, i.e., strong and weak cohorts. The age-1 index suggests
particularly large numbers of age-1 fish in 2009, 2011, 2015, and 2021 (2008,
2010, 2014, and 2020 year classes, respectively), and is not available for
most even years (odd year classes). There is not data to inform the size of
the `r last_data_yr` year class.

(ref:es-survey-biomass-cap) Acoustic survey biomass index of age-2+ fish
(Mt). Approximate 95% confidence intervals are based on
sampling variability (intervals without squid/hake apportionment
uncertainty in 2009 are displayed in black).
  
(ref:es-survey-biomass-alt) This figure shows that the survey estimate has
decreased from 2019 to 2021.

```{r es-survey-biomass-fig, fig.cap = "(ref:es-survey-biomass-cap)"}

plot_survey_biomass(base_model, index = "age2")
```

The assessment uses a Bayesian estimation approach, sensitivity analyses, and
retrospective investigations to evaluate the potential consequences of
parameter uncertainty, alternative structural models, and historical
performance of the assessment model, respectively. The Bayesian approach
combines prior knowledge about natural mortality, stock-recruitment steepness
(a parameter for stock productivity), and several other parameters, with
likelihoods for the acoustic survey biomass index, acoustic survey
age-composition data, the relative age-1 index, and fishery age-composition
data. Integrating the joint posterior distribution over model parameters
provides probabilistic inferences about uncertain model parameters and
forecasts derived from those parameters; this is done via Markov chain Monte
Carlo sampling using the efficient No-U-Turn Sampler (NUTS) that was
successfully tested in 2020 and used in subsequent assessments. Sensitivity
analyses are used to identify alternative model assumptions that may also
be consistent with the data. All models, including bridging, sensitivity,
and retrospective models, use a Bayesian framework for estimation.
Retrospective analyses identify possible poor performance of the assessment
model with respect to future predictions. Past assessments have conducted
closed-loop simulations that provide insights into how alternative
combinations of survey frequency, assessment model selectivity assumptions,
changes in hake distribution, and harvest control rules affect expected
management outcomes given repeated application of these procedures over
the long-term. The results of past (and ongoing) closed-loop simulations
help inform decisions made for this assessment.

(ref:es-survey-age1-cap) Relative index of age-1 fish (numbers of fish) and
approximate 95\% confidence intervals based on sampling variability. The index
is relative because the survey does not attempt to sample all available age-1
fish and the analysis does not include kriging as is done to estimate age-2+
biomass.

(ref:es-survey-age1-alt) This figure shows that the age-1 survey estimate has
increased from 2019 to 2021.

```{r es-survey-age1-fig, fig.cap = "(ref:es-survey-age1-cap)"}

plot_survey_biomass(base_model, index = "age1", y_lim = c(0, 16))
```

This `r assess_yr` assessment retained the same general population dynamics
structure as the base assessment model from `r last_assess_yr` and again is
configured using Stock Synthesis. This includes the continued use (since 2014)
of time-varying (rather than fixed) selectivity to maintain flexibility with
fishing dynamics given variability in `r sp` distribution patterns.

The Dirichlet-multinomial estimation approach to weighting composition data
was retained, and sensitivity to an alternative data-weighting approach was
investigated. Time-varying fecundity, which was introduced in 2019, was
retained. Assumptions for the forecast period for weight at age and
selectivity continue to be based on conditions during the last five years,
as done since the 2020 assessment. The main change from the `r last_assess_yr`
assessment is the addition of `r last_data_yr` data.

## Stock Biomass {-}

Results from the base model
indicate that since the 1960s, `r sp` female spawning biomass has ranged from
well below to above unfished equilibrium (Figures~\@ref(fig:es-biomass-fig)
and~\@ref(fig:es-relative-biomass-fig)). Model estimates suggest
that it was below the unfished equilibrium in the 1960s, at the start of the
assessment period, due to lower than average recruitment.

(ref:es-biomass-cap) Median (solid line) of the posterior
distribution for beginning of the year female spawning biomass
($B_t$ in year $t$; Mt) through `r end_yr` (solid line) with 95%
posterior credibility intervals (shaded area). The left-most circle with a 95%
posterior credibility interval is the estimated unfished equilibrium biomass,
`r b_0`.

(ref:es-biomass-alt) This figure shows that the median spawning biomass has
been increasing in size since 2021.

```{r es-biomass-fig, fig.cap = "(ref:es-biomass-cap)"}

plot_biomass(list(base_model),
             list(base_model_name),
             ylim = c(0, 5),
             point_shape = 1,
             leg_pos = "none")
```

The stock is estimated to have increased rapidly and was above unfished
equilibrium in the mid-1970s and mid-1980s (after two large recruitment
events in the early 1980s). It then declined steadily to a low in 1999. This
was followed by a brief increase to a peak in 2002 as the very large 1999 year
class matured. The 1999 year class largely supported the fishery for several
years due to relatively small recruitment events between 2000 and 2007. With
the aging 1999 year class, median female spawning biomass declined throughout
the late 2000s, reaching a time-series low of `r median_bio_min` Mt in
`r median_bio_min_yr`. Median female spawning biomass is estimated to have
peaked again in 2013 and 2014 due to a very large 2010 year class and an
above-average 2008 year class. The subsequent decline from 2014 to 2016 is
primarily from the 2010 year class surpassing the age at which the gains in
weight from growth are greater than the losses in weight from mortality
(growth-mortality transition). The 2014 year class is estimated to be large,
though not as large as the 1999 and 2010 year classes, increasing the biomass
in 2017. The estimated biomass was relatively steady from 2017 to 2019 and then
declined in 2020 and 2021 due to the 2014 and 2016 year classes moving through
the growth-mortality transition during a period of high catches. The increase
in female spawning biomass since 2021 is due to the expected above average
2020 cohort entering maturity and the recent declining trend in catch.

The median estimate of the `r end_yr` relative spawning biomass (female
spawning biomass at the start of `r end_yr` divided by that at unfished
equilibrium, `r b_0`) is `r curr_depl_median`%. However, the uncertainty
is particularly large this year, with a 95% posterior credibility interval
from `r curr_depl_lower`% to `r curr_depl_upper`%
(Table~\@ref(tab:es-biomass-tab), due to high uncertainty about the size of
the 2020 cohort, which has not yet been sampled in the acoustic survey
biomass index of age-2+ fish. The median estimate of the `r end_yr` female
spawning biomass is `r curr_bio_median` Mt, with a 95% posterior
credibility interval from `r curr_bio_lower` to `r curr_bio_upper` Mt.
The current estimate of the `r end_yr - 1` female spawning biomass is
`r prev_bio_median` (`r prev_bio_lower`--`r prev_bio_upper`) Mt. This is
higher than the `r prev_bio_median_last_assess` (`r prev_bio_lower_last_assess`
--`r prev_bio_upper_last_assess`) Mt estimated in the `r end_yr - 1`
assessment. The increase appears to be due to the addition of 2022 fishery
age-composition data, which suggests the 2020 cohort may be larger than the
age-1 index alone was indicating in the last assessment.

(ref:es-relative-biomass-cap) Median (solid line) of the posterior
distribution for relative spawning biomass ($B_t / B_0$) through `r end_yr`
with 95% posterior credibility intervals (shaded area). Dashed horizontal
lines show 10%, 40%, and 100% of the unfished equilibrium (`r b_0`).

(ref:es-relative-biomass-alt) This figure shows that the relative spawning
biomass has been increasing since 2021. The value for 2023 is just above B0.

```{r es-relative-biomass-fig, fig.cap = "(ref:es-relative-biomass-cap)"}

plot_rel_biomass(list(base_model),
                 list(base_model_name),
                 point_shape = 1,
                 ylim = c(0, 3),
                 alpha = 0.2,
                 leg_pos = "none")
```

```{r es-biomass-tab, results = "asis", echo = FALSE}

table_biomass(
  base_model,
  start_yr = end_yr - 9,
  end_yr = end_yr,
  caption = paste0(
    "Recent trends in estimated beginning of the year female spawning ",
    "biomass (SSB; kt) and spawning biomass relative to estimated ",
    "unfished equilibrium (Rel. SSB; \\%)."),
  font_size = 10,
  header_font_size = 8)
```
\clearpage

## Recruitment {-}

The addition of `r last_data_yr` data does not substantially change estimates
of historical recruitment but recent recruitment estimates have changed
substantially. For example, this assessment's median estimate of the 2020
recruitment is
`r med_est_2020_rec`~billion fish higher than in the last assessment (a 
`r perc_inc_2020_rec_from_last_yr`% increase). Similarly, estimates for 2019
and 2021 recruitments have changed by `r perc_inc_2019_rec_from_last_yr`%
(`r med_est_2019_rec`~billion fish) and `r perc_inc_2021_rec_from_last_yr`%
(`r med_est_2021_rec`~billion fish), respectively, but the general notion
remains that recent recruitment is highly uncertain.

```{r es-recruitment-tab, results = "asis", echo = FALSE}

table_recruitment(
  base_model,
  start_yr = end_yr - 10,
  end_yr = end_yr - 1,
  caption = paste0(
    "Estimates of recent recruitment (millions of age-0 fish) and ",
    "recruitment, deviations, where deviations below (above) zero indicate ",
    "recruitment below (above) that estimated from the stock-recruit ",
    "relationship."),
  font_size = 10,
  header_font_size = 9)
```

`r sp` have low to moderate recruitment with occasional large year classes
(Table~\@ref(tab:es-recruitment-tab) and Figure~\@ref(fig:es-recruitment-fig)).

(ref:es-recruitment-cap) Medians (solid circles) and means ($\mathrm{X}$) of the
posterior distribution for recruitment (billions of age-0 fish) with 95%
posterior credibility intervals (blue, vertical lines). The median of the
posterior distribution for mean unfished equilibrium recruitment ($R_0$) is
shown as the horizontal dashed line with the 95% posterior credibility
interval shaded between the dotted lines.

(ref:es-recruitment-alt) This figure shows that recruitment for each cohort.
There are currently three above-average cohorts in the stock with 2020 being
the fourth. The 2020 cohort is highly uncertain which can be seen in the
size of the credible interval.

```{r es-recruitment-fig, fig.cap = "(ref:es-recruitment-cap)"}
plot_recruitment(list(base_model),
                 list(base_model_name),
                 inc_means = TRUE,
                 leg_pos = "none")
```

Large year classes in 1980, 1984, and 1999 supported much of the commercial
catch from the 1980s to the mid-2000s. From 2000 to 2007, estimated
recruitment was at some of the lowest values in the time series but this
was followed by an above average 2008 year class. The strong 2010 year class
comprised `r top_coh(base_model, 2014, ret_cohort = 2010)`% of the
coast-wide commercial catch in 2014,
`r top_coh(base_model, 2016, ret_cohort = 2010)`% of the 2016 catch,
`r top_coh(base_model, 2018, ret_cohort = 2010)`% of the 2018 catch,
`r top_coh(base_model, 2020, ret_cohort = 2010)`% of the 2020 catch, and
`r top_coh(base_model, 2022, ret_cohort = 2010)`% of the 2022 catch.
The decline from 2014 to 2016 was partly due to the large influx of the 2014
year class (`r top_coh(base_model, 2016, ret_cohort = 2014)`% of the 2016
catch was age-2 fish from the 2014 year class; this was larger than the
proportion of age-2 fish, `r top_coh(base_model, 2012, ret_cohort = 2010)`%,
from the 2010 year class in 2012). Since 2010, the model currently
estimates small 2011, 2012, 2013, 2015, 2018, 2019 and 2021 year classes
(median recruitment well below the mean of all median recruitments).

The 2014 and 2016 year classes are both larger than average, with 2014
larger than 2016 but smaller than 2010. With the inclusion of the
relative age-1 index, there is information beyond just fishery encounters in
the data to estimate the size of the 2020 year class. Collectively, these
data indicate that the 2020 year class is likely well above average. The
much smaller 2019 year class is informed by the `r last_survey_yr`
biomass index and fishery data but is not informed by the relative age-1
index, and the 2021 year class is informed only by 2022 fishery data.
There is no information in the data to estimate the sizes of the
`r end_yr - 1` and `r end_yr` year classes. Retrospective analyses of
year-class strength for young fish have shown the estimates of recent
recruitment to be unreliable prior to at least a model age of three (i.e.,
fish observed at age two) without a survey in the most recent year and
two (i.e., fish observed at age one) with a survey. While the 2020 cohort
was observed by the relative age-1 index in 2021, it will not be observed
by the acoustic survey until 2023.

## Default harvest policy {-}

The default `r f_40_40_10` harvest policy prescribes the maximum rate of fishing
mortality to equal `r fspr_40`. This rate gives a spawning potential ratio (SPR)
of 40%, meaning that the female spawning biomass per recruit with `r fspr_40` is
40% of that without fishing. If female spawning biomass is below `r b_40`
(40% of `r b_0`), the policy reduces the TAC linearly until it equals zero at
`r b_10` (10% of `r b_0`). Relative fishing intensity for fishing rate
$\mathrm{F}$ is `r fishing_rate`, where `r spr_40` is an SPR of 40%;
it is reported here interchangeably as a proportion or a percentage. A
relative fishing intensity above 1.0 means fishing at a rate above `r fspr_40`.

## Exploitation status {-}

```{r es-fishing-intensity-tab, results = "asis", echo = FALSE}

table_fishing_intensity(
  base_model,
  start_yr = end_yr - 10,
  end_yr = end_yr - 1,
  digits = 3,
  caption = paste0(
    "Recent estimates of relative fishing intensity, ",
    rel_fishing_intensity_for_latex_table, ", and exploitation ",
    "fraction (catch divided by age-2+ biomass)."),
  font_size = 10,
  header_font_size = 9)

```

The median estimated relative fishing intensity on the stock is below the
management level of 1.0 `r median_intensity_above_1_text` (see 
Table~\@ref(tab:es-fishing-intensity-tab) for recent years and
Figure~\@ref(fig:es-fishing-intensity-fig)).

(ref:es-fishing-intensity-cap) Trend in median relative fishing intensity
(relative to the `r fspr_40` management level) through `r end_yr - 1`} with
95% posterior credibility intervals. The `r fspr_40` management level defined
in the Joint U.S.-Canada Agreement for `r sp` is shown as a horizontal line
at 1.0.

(ref:es-fishing-intensity-alt) This figure shows that we have been below
the management value of 1 for FSPR 40 percent throughout the entire time
series.

```{r es-fishing-intensity-fig, fig.cap = "(ref:es-fishing-intensity-cap)"}

plot_fishing_intensity(base_model, show_arrows = TRUE)
```

Median exploitation fraction (catch divided by biomass of fish of age-2 and
above) peaked in 2006 and reached similar levels in 1999 and 2008
(Figure~\@ref(fig:es-exploitation-fraction-fig). Over the last five years, the
median estimated exploitation fraction was the highest in 2020 followed
closely by 2021 before dropping by nearly half in 2022
(Table~\@ref(tab:es-fishing-intensity-tab). Median relative fishing intensity is
estimated to have declined from `r median_intensity_2010`% in 2010 to 
`r median_intensity_2015`% in 2015. It then leveled off around 70% from 2016
to 2019 before declining to `r median_intensity_2022`% in 2022. The median
exploitation fraction has, on average, increased from a recent low of
`r exploitation_med_2012` in 2012 to `r exploitation_med_2020` in 2020
before dropping back to 2012--2015 levels in 2022. There is a considerable
amount of uncertainty around estimates of relative fishing intensity, with
the 95% posterior credibility interval reaching above the `r fspr_40` management
level (of 1.0) in 2017 and 2018 over the past decade
(Figure~\@ref(fig:es-fishing-intensity-fig). Exploitation and fishing intensity
rates do not always track well due to a combination of changing age
distributions and changing selectivities over time.

## Management performance {-}

Over the last decade (`r end_yr-10`--`r end_yr - 1`), the mean coast-wide
utilization rate (proportion of catch target removed) has been
`r tot_last_10_yrs_attainment`% (Table~\@ref(tab:es-landings-tac-tab). Over
the last five years (`r end_yr - 5` to `r end_yr - 1`), the mean utilization
rates were `r us_last_5_yrs_attainment`% for the United States
and `r can_last_5_yrs_attainment`% for Canada. While relatively stable during
this time in the United States, the utilization rate in Canada has been
declining since 2020 to a time-series low of 20.3% in 2022. Country-specific
quotas (or catch targets) in 2020 and 2021 were specified unilaterally, due to
the lack of an agreement on coast-wide 2020 and 2021 TACs. The usual
`r us_allotment_percent`% and
`r can_allotment_percent`% allocation of coast-wide TAC, as specified in the
Joint U.S.-Canada Agreement for `r sp`, was once again implemented in 2022.

Total landings last exceeded the coast-wide quota in 2002 when utilization
was 112%, though the fishing intensity was relatively low that year due to
the appearance of the 1999 year class.

(ref:es-exploitation-fraction-cap) Trend in median exploitation fraction
(catch divided by age-2+ biomass) through `r end_yr - 1` with 95% posterior
credibility intervals.

(ref:es-exploitation-fraction-alt) This figure shows that the current
exploitation fraction of the female spawning biomass is approximately 0.05.
This is a drop from the last five years which have been approximately 0.1.

```{r es-exploitation-fraction-fig, fig.cap = "(ref:es-exploitation-fraction-cap)"}

plot_exploitation_fraction(base_model, show_arrows = TRUE)
```

```{r es-landings-tac-tab, results = "asis", echo = FALSE}

table_landings_tac(
  ct,
  start_yr = end_yr - 10,
  end_yr = end_yr - 1,
  caption = paste0(
    "Recent trends in ", sp, " landings and management decisions. Catch ",
    "targets in 2020 and 2021 were specified unilaterally. All landings ",
    "and catch targets are given in tonnes."),
  font_size = 7,
  header_font_size = 7,
  longtable = TRUE)
```

(ref:es-phase-cap) Estimated historical path of median relative spawning
biomass in year $t$ and corresponding median relative fishing intensity in
year $t - 1$. Labels show the time series start and end years and the year
after the highest relative fishing intensity; labels correspond to year $t$
(i.e., year of the relative spawning biomass). Gray bars span the 95%
credibility intervals for `r end_yr` relative spawning biomass (horizontal)
and `r end_yr - 1` relative fishing intensity (vertical).

(ref:es-phase-alt) This figure shows that we are currently not overfishing
nor in an overfished state.

```{r es-phase-fig, fig.cap = "(ref:es-phase-cap)"}

plot_phase(base_model,
           1966,
           2023,
           cross_line_width = 0.5,
           cross_line_color = "black",
           init_lbl_x_off = -0.04,
           init_lbl_y_off = -0.04,
           final_lbl_x_off = 0.04,
           final_lbl_y_off = 0.04)
```

\clearpage

The median relative fishing intensity was below 1.0 in all years
(Figures~\@ref(fig:es-fishing-intensity-fig) and~\@ref(fig:es-phase-fig)).
The median relative spawning biomass was above the `r b_40` reference point
in all years except 2007--2010 (Figures~\@ref(fig:es-relative-biomass-fig)
and~\@ref(fig:es-phase-fig), and the median relative fishing intensity was below
1.0 (Figure~\@ref(fig:es-phase-fig)).
The benchmark quantities, `r fspr_40` and `r b_40`, result in different median
population sizes (see Table~\@ref(tab:es-reference-points-tab)), highlighting
that there are subtle differences in these conceptual reference points.
Between 2007 and 2010, median relative fishing intensity ranged from
`r median_intensity_2007_to_2010_min`% to
`r median_intensity_2007_to_2010_max`% and median relative spawning biomass
between `r median_relative_bio_2007_to_2010_min` and
`r median_relative_bio_2007_to_2010_max`. Biomass has risen from the 2010 low
with the 2008, 2010, 2014, 2016, and 2020 recruitments, and median relative
spawning biomass has been above the reference point of 40% since
`r median_relative_bio_above_target_since`.

While there is large uncertainty in the estimates of relative fishing
intensity and relative spawning biomass, the model estimates a
`r joint_percent_prob_above_below`% joint probability of being both
above a relative fishing intensity of 1.0 in `r end_yr - 1` and below the
`r b_40` relative spawning biomass level at the start of `r end_yr`.

## Reference points {-}

The term `reference points' is used throughout this document to describe common
conceptual summary metrics (Table~\@ref(tab:es-reference-points-tab)).
The Agreement specifically identifies `r f_40` as the default harvest rate
and `r b_40` as a point where the 40:10 TAC adjustment is triggered
(see the Glossary in Appendix~\@ref(sec:app-glossary)).
The medians of sustainable yields and biomass reference points are similar
to what was reported in the `r last_assess_yr` assessment. The probability
that female spawning biomass at the beginning of `r assess_yr` is below
`r b_40` is P(*B*~`r assess_yr`~ < `r b_40`) = `r probs_curr_below_b40`%,
and of being below `r b_25` is
P(*B*~`r assess_yr`~ < `r b_25`) = `r probs_curr_below_b25`%.
The probability that the relative fishing intensity was above the `r f_40`
level of 1.0 at the end of `r end_yr - 1`
is~`r probs_curr_rel_fish_intens_above_1`%.

```{r es-reference-points-tab, results = "asis", echo = FALSE}

table_reference_points(
  base_model,
  category_bold = TRUE,
  category_italics = TRUE,
  category_underline = TRUE,
  category_line_above = FALSE,
  category_line_below = FALSE,
  caption = paste0(
    "Summary of median and 95\\% credibility intervals of equilibrium ",
    "conceptual reference points for the base assessment model. ",
    "Equilibrium reference points were computed using ", start_yr_age_comps,
    "--", end_yr - 1, " averages for mean weight-at-age and baseline ",
    "selectivity-at-age (1966--1990; prior to time-varying deviations). ",
    "Dashes (--) indicate values that are static at one value and do not ",
    "have a credible interval associated with them."),
  font_size = 10,
  header_font_size = 11,
  longtable = TRUE)
```

## Unresolved problems and major uncertainties {-}

Measures of uncertainty in the base model underestimate the total uncertainty
in the current stock status and projections because they do not account for
possible alternative structural models for `r `simple_name` population
dynamics and fishery processes (e.g., selectivity) and the scientific basis
for prior probability distributions. To address such structural uncertainties,
we performed sensitivity analyses to investigate a range of alternative
assumptions and present the key ones in the main document.

The `r sp` stock displays high recruitment variability relative to other west
coast groundfish stocks, resulting in large and rapid biomass changes. This
leads to a dynamic fishery that potentially targets strong cohorts and results
in time-varying fishery selectivity. This volatility results in a high level
of uncertainty in estimates of current stock status and stock projections
because, with limited data to estimate incoming recruitment, the cohorts are
fished before the assessment can accurately determine how big they are (i.e.,
cohort strength is typically not well known until it is observed by the
fishery and survey, typically at a minimum age of three).  While the addition
of the age-1 index helps inform recent recruitment, the survey is conducted
every other year and does not directly address current or future recruitment
expectations. In particular, while the model estimates the 2020 cohort as
above average in size, its absolute size remains highly uncertain. This
uncertainty propagates directly into current and forecasted estimates of female
spawning biomass. The upcoming 2023 acoustic survey will provide additional
information on the size of the 2020 year-class (as well as inform the 2021 and
2022 year classes), which will lessen uncertainty of estimates of female
spawning biomass. Further, the interactions among variance parameters that
govern variability in fishery selectivity and recruitment parameters through
time, as well as those used in relative data weighting, are not well understood
and could propagate uncertainty beyond what is presented in this assessment.

## Forecast decision tables {-}

The catch limit for `r min(forecast_yrs)` based on the default `r f_40_40_10`
harvest policy has a median of `r ct_limit_quantiles["median"]`~t with a
wide range of uncertainty, the 95% credibility interval being
`r ct_limit_quantiles["lower"]`--`r ct_limit_quantiles["upper"]`~t.

Decision tables give the projected population status (relative spawning
biomass) and fishing intensity relative to the target under different
catch alternatives for the base model (Tables~\@ref(tab:es-decisions-biomass-tab)
and~\@ref(tab:es-decisions-spr-tab)). The tables are organized to show the
projected outcome for each potential catch level and year (row) across the
quantiles (columns) of the posterior distribution. Tables show results for up
to three years of future catch levels based on subsequent estimates of stock
status and fishing intensity.
Figure~\@ref(fig:es-depletion-comparison-fig) shows the projected relative
spawning biomass for several of the catch alternatives. Population dynamics
and governing parameters assumed during the forecast period include random
recruitment; selectivity, weight-at-age and fecundity averaged over the five
most recent years (`r assess_yr - 5`--`r assess_yr - 1`); and constant
values for all other parameters.

A relative fishing intensity of 1 should indicate fishing at the `r f_40`
default harvest rate catch target but the projected median relative fishing
intensity can be slightly different than the target because the `r f_40`
default harvest-rate catch limit is calculated using baseline
selectivity-at-age (1966--1990; prior to time-varying deviations), whereas the
forecasted catches are removed using selectivity averaged over the last five
years. Recent changes in selectivity will thus be reflected in the
determination of fishing relative to the default harvest policy. For example,
fishing at the `r f_40` default harvest-rate catch limit (scenario n: default
HR) in 2023 results in a median relative fishing intensity of 0.91 (Table~\@ref(tab:es-decisions-spr-tab)).

\newpage

```{r es-decisions-biomass-tab, results = "asis", echo = FALSE}

table_decision(
  base_model,
  type = "biomass",
  forecast_inds =
    seq_along(base_model$forecasts[[length(base_model$forecasts)]]),
  caption = paste0(
      "Forecast quantiles of ", sp, " relative spawning biomass at the ",
      "beginning of the year. Catch alternatives are based on: constant ",
      "catches (rows ", ct_constant_str, "), including catch similar to ",
      min(forecast_yrs) - 1," (row~", letters[ct_actual_ind],
      ") and to the TAC from ", min(forecast_yrs) - 1," (row~",
      letters[ct_tac_ind], "); and non-constant catches that result in ",
      "annual 10\\% declines in catch (rows ", ct_reduction_str,
      "), median relative fishing intensity of 100\\% (row ",
      letters[ct_spr100_ind], "), median catch estimated via the default ",
      "harvest policy (", f_40_40_10_for_latex_table, ", row~",
      letters[ct_default_policy_ind], "), and the fishing intensity that ",
      "results in the median projected catch remaining the same in ",
      min(forecast_yrs), " and ", min(forecast_yrs) + 1, " (row~",
      letters[ct_stable_ind], ")."),
  bold_letters = TRUE,
  digits = 2,
  # Font values higher than 8 and 11 for table and header respectively
  # will cause the table to wrap to a second page
  font_size = 8,
  header_font_size = 11,
  # If the font is changed it is almost guaranteed that `left_col_cm` and
  # `right_cols_cm` will have to be changed, especially if the font is made
  # larger. You will have to check this with trial-and-error, building the
  # document, checking the table and adjusting, over and over until it looks
  # right
  left_col_cm = 3,
  right_cols_cm = 1.2,
  longtable = TRUE)
```

```{r es-decisions-spr-tab, results = "asis", echo = FALSE}

table_decision(
  base_model,
  type = "spr",
  forecast_inds =
    seq_along(base_model$forecasts[[length(base_model$forecasts)]]),
  caption = paste0(
    "Forecast quantiles of ", sp, " relative fishing intensity ",
    rel_fishing_intensity_for_latex_table, ", expressed as a proportion, for ",
    "the ", min(forecast_yrs), "--", max(forecast_yrs) - 1, " catch ",
    "alternatives presented in Table~\\@ref(tab:es-decisions-biomass-tab). ",
    "Values greater than 1 indicate relative fishing intensities greater ",
    "than the ", fspr_40_for_latex_table, " harvest policy calculated using ",
    "baseline selectivity."),
  bold_letters = TRUE,
  digits = 2,
  # Font values higher than 8 and 11 for table and header respectively
  # will cause the table to wrap to a second page
  font_size = 8,
  header_font_size = 11,
  # If the font is changed it is almost guaranteed that `left_col_cm` and
  # `right_cols_cm` will have to be changed, especially if the font is made
  # larger
  left_col_cm = 3,
  right_cols_cm = 1.2,
  longtable = TRUE)
```

Management metrics that were identified as important to the Joint Management
Committee and the Advisory Panel in 2012 are presented for
`r str_flatten_comma(forecast_yrs[-1], last = ", and ")` projections
(Tables~\@ref(tab:es-risk-year-1-tab), \@ref(tab:es-risk-year-2-tab),
and~\@ref(tab:es-risk-year-3-tab);
Figures~\@ref(fig:es-risk-year-1-fig),
\@ref(fig:es-risk-year-2-fig),
and~\@ref(fig:es-risk-year-3-fig)).
These metrics summarize the probability of various outcomes from the base model
given each potential management action. Although not linear, probabilities can
be interpolated from these results for intermediate catch values in
`r assess_yr` (Table~\@ref(tab:es-risk-year-1-tab) and
Figure~\@ref(fig:es-risk-year-1-fig)).
However, interpolation is not appropriate for all catches in `r assess_yr + 1`
or `r assess_yr + 2` because they are conditional on previous year(s) catch
levels. This explains why a few probabilities decline (rather than rise) with
increased `r assess_yr + 1` and `r assess_yr + 2` catch levels
(Tables~\@ref(tab:es-risk-year-2-tab) and~\@ref(tab:es-risk-year-3-tab)
and Figures~\@ref(fig:es-risk-year-2-fig) and~\@ref(fig:es-risk-year-3-fig)).

(ref:es-depletion-comparison-cap) Median and 95 posterior
credibility intervals of estimated relative spawning biomass to the start
of `r end_yr` from the base model and projections to the start of `r forecast_yrs[length(forecast_yrs)]` for several management actions, which
are defined in Table~\@ref(tab:es-decisions-biomass-tab).

(ref:es-depletion-comparison-alt) This figure shows that the median
relative spawning biomass is projected to remain flat for the next 3 years
with zero catch and to decline for all non-zero catch levels evaluated.

```{r es-depletion-comparison-fig, fig.cap = "(ref:es-depletion-comparison-cap)"}

# See the file `forecast-catch-levels.R` at the list called `ct_levels`. The values in
# `fore_inds` below are the indices of those forecast values in that list.
plot_depl_fore_comparison(base_model,
                          fore_inds = c(1, 2, 6, 12, 14),
                          forecast_yrs = forecast_yrs)
```

The predicted relative spawning biomass trajectory through
  `r forecast_yrs[length(forecast_yrs)]` is shown in
Figure~\@ref(fig:es-depletion-comparison-fig) for several of the
management actions. With zero catch for the next three years, the biomass has
a `r zero_catch_prob_bio_down_1`% probability of decreasing from
`r forecast_yrs[1]` to `r forecast_yrs[2]` (Table~\@ref(tab:es-risk-year-1-tab)), a
`r zero_catch_prob_bio_down_2`% probability of decreasing from
`r forecast_yrs[2]` to `r forecast_yrs[3]` (Table~\@ref(tab:es-risk-year-2-tab)),
and a `r zero_catch_prob_bio_down_3`% probability of decreasing from
`r forecast_yrs[3]` to `r forecast_yrs[4]` (Table~\@ref(tab:es-risk-year-3-tab)).

The probability of the female spawning biomass decreasing from `r end_yr` to
`r end_yr + 1` is above 72% for all non-zero catch levels examined
(Table~\@ref(tab:es-risk-year-1-tab) and
Figure~\@ref(fig:es-risk-year-1-fig)). This probability is
81% for a `r end_yr` catch level similar to that for `r end_yr - 1`
(scenario f: `r end_yr` catch). For all explored catches, the maximum
probability of female spawning biomass at the start of `r end_yr + 1` dropping
below `r b_10` is 0%, and of dropping below `r b_40` is 10%
(Table~\@ref(tab:es-risk-year-1-tab) and
Figure~\@ref(fig:es-risk-year-1-fig)).
As the large 2010, 2014, and 2016 cohorts continue to age, their biomass is
expected to decrease as losses from mortality outweigh increases from growth.
The estimated above-average (yet still highly uncertain) 2020 cohort will
continue to play a large role in determining female spawning biomass during
the forecast years presented here.

(ref:es-risk-year-1-cap) Graphical representation of
the probabilities related to spawning biomass, relative fishing intensity, and
the `r end_yr + 1` default harvest policy catch for alternative `r end_yr`
catch options (explained in Table~\@ref(tab:es-decisions-biomass-tab)) as listed in
Table~\@ref(tab:es-risk-year-1-tab). The symbols indicate points that were computed
directly from model output and lines interpolate between the points.

(ref:es-risk-year-1-alt) This figure shows that the probability that the
stock declines in 2024 is 50 percent or greater for all catch levels including
zero. The probability that the stock falls under B40 is almost zero for
catches up to approximately 350 thousand tonnes.

```{r es-risk-year-1-fig, fig.cap = "(ref:es-risk-year-1-cap)", fig.height = 4.5}

plot_fore_compare(base_model,
                  forecast_yrs = forecast_yrs,
                  fore_yr = forecast_yrs[1],
                  leg_pos = c(0.2, 0.32),
                  remove_x_val = 325)
```

```{r es-risk-year-1-tab, results = "asis", echo = FALSE}

# Index in models[[]]$risks to use, e.g. 1 means forecast year 2 compared
# to forecast year 1
table_risk(
  base_model,
  forecast_yrs,
  index = 1,
  type = "probability",
  digits = 2,
  caption = paste0(
    "Probabilities related to spawning biomass, relative fishing intensity, ",
    "and the ", end_yr + 1, " default harvest policy catch for alternative ",
    end_yr, " catch options (catch options explained in ",
    "Table~\\@ref(tab:es-decisions-biomass-tab))."),
  font_size = 10,
  header_font_size = 10,
  longtable = TRUE)
```

\newpage

(ref:es-risk-year-2-cap) Graphical representation
of the probabilities related to spawning biomass, relative fishing intensity,
and the `r end_yr + 2` default harvest policy catch for alternative
`r end_yr + 1` catch options (including associated `r end_yr` catch; catch
options explained in Table~\@ref(tab:es-decisions-biomass-tab)) as listed in
Table~\@ref(tab:es-risk-year-2-tab). The symbols indicate points that were
computed directly from model output and lines interpolate between the points.

(ref:es-risk-year-2-alt) This figure shows that the probability that the
stock declines in 2025 is 74 percent or greater for all catch levels
including zero. The probability that the stock falls under B40 is below
0.1 for catches up to approximately 380 thousand tonnes.

```{r es-risk-year-2-fig, fig.cap = "(ref:es-risk-year-2-cap)", fig.height = 4.5}

plot_fore_compare(base_model,
                  forecast_yrs = forecast_yrs,
                  fore_yr = forecast_yrs[2],
                  leg_pos = c(0.2, 0.32),
                  remove_x_val = c(325, 342, 740))
```

```{r es-risk-year-2-tab, results = "asis", echo = FALSE}

table_risk(
  base_model,
  forecast_yrs,
  index = 2,
  type = "probability",
  digits = 2,
  caption = paste0(
    "Probabilities related to spawning biomass, relative fishing intensity, ",
    "and the ", end_yr + 2, " default harvest policy catch for alternative ",
    end_yr + 1, " catch options, given the ", end_yr, " catch level shown ",
    "in Table~\\@ref(tab:es-risk-year-1-tab) (catch options explained in ",
    "Table~\\@ref(tab:es-decisions-biomass-tab))."),
  font_size = 10,
  header_font_size = 10,
  longtable = TRUE)
```

(ref:es-risk-year-3-cap) Graphical representation of
the probabilities related to spawning biomass, relative fishing intensity, and
the `r end_yr + 3` default harvest policy catch for alternative `r end_yr + 2`
catch options (including associated `r end_yr` and `r end_yr + 1` catches;
catch options explained in Table~\@ref(tab:es-decisions-biomass-tab)) as listed in
Table~\@ref(tab:es-risk-year-3-tab). The symbols indicate points that were computed
directly from model output and lines interpolate between the points.

(ref:es-risk-year-3-alt) This figure shows that the probability that the
stock declines in 2026 is approximately 65 percent or greater for all catch
levels including zero. The probability that the stock falls under B40 is
below 0.1 for catches up to approximately 350 thousand tonnes.

```{r es-risk-year-3-fig, fig.cap = "(ref:es-risk-year-3-cap)", fig.height = 4.5}

plot_fore_compare(base_model,
                  forecast_yrs = forecast_yrs,
                  fore_yr = forecast_yrs[3],
                  leg_pos = c(0.2, 0.32),
                  remove_x_val = c(259, 621))
```

```{r es-risk-year-3-tab, results = "asis", echo = FALSE}

table_risk(
  base_model,
  forecast_yrs,
  index = 3,
  type = "probability",
  digits = 2,
  caption = paste0(
    "Probabilities related to spawning biomass, relative fishing intensity, ",
    "and the ", end_yr + 3, " default harvest policy catch for alternative ",
    end_yr + 2, " catch options, given the ", end_yr, " and ", end_yr + 1,
    " catch levels shown in Tables~\\@ref(tab:es-risk-year-1-tab) and~",
    "\\@ref(tab:es-risk-year-2-tab) (catch options explained in Table~",
    "\\@ref(tab:es-decisions-biomass-tab))."),
  font_size = 10,
  header_font_size = 10,
  longtable = TRUE)
```
\clearpage

## Research and data needs {-}
```{r child = "010-research-needs/research-needs.rmd"}
```

Executive summary EOF - do not remove - required by the post-processor
\clearpage
