\newpage

\rfoot{Executive summary}

# Executive summary {-}

## Stock {-}

This assessment reports the status of the coastal `r sp` (or `r common_name`,
*`r science_name`*) stock off the west coast of the United States (U.S.) and Canada
at the start of `r assess_yr`. This stock exhibits seasonal migratory
behavior, ranging from offshore and generally southern waters during the
winter spawning season to coastal areas between northern California and
northern British Columbia during the spring, summer, and fall when the
fishery is conducted. The stock tends to move farther to the north during the
summer in years with warmer water compared to years with colder waters. Older
`r sp` tend to migrate farther north than younger `r sp` in all years, with
catches in Canadian waters typically consisting of fish greater than four years
old. Separate, and much smaller, populations of `r sp` occurring in the major
inlets of the Northeast Pacific Ocean, including the Strait of Georgia, Puget
Sound, and the Gulf of California, are not included in this analysis.

## Catches {-}

(ref:es-catches-cap) Total `r sp` catch used in the assessment by sector,
`r start_yr`--`r last_data_yr`. U.S. tribal catches are included in the
sectors where they are represented.

(ref:es-catches-alt) This figure shows that catches in four of the last six
years have been the largest in the time series.

```{r es-catches-fig, fig.cap = "(ref:es-catches-cap)", fig.height = 4}

plot_catches(ct, xlim = c(start_yr, last_data_yr))
```

Coast-wide fishery landings of `r sp` averaged `r f(mean(ct$Total))`~t
from `r min(ct$Year)` to `r max(ct$Year)`, with a low of
`r f(min(ct$Total))`~t in
`r ct$Year[ct$Total == min(ct$Total)]` and a peak of
`r f(max(ct$Total))`~t in
`r ct$Year[ct$Total == max(ct$Total)]`
(Figure \@ref(fig:es-catches-fig)).
Prior to `r min(ct$Year)`, total removals were negligible compared to the
modern fishery. Over the early period (`r min(ct$Year)`--1990) most removals
were from foreign or joint-venture fisheries. Across the time series, annual
catch in U.S. waters averaged `r f(mean(ct[["U.S. Total"]]))`~t
(`r f(sum(ct[["U.S. Total"]]) / sum(ct$Total) * 100, 1)`% of the total catch),
while catch from Canadian waters averaged `r f(mean(ct[["Canada Total"]]))`~t.
Over the last 10 years, `r max(ct$Year) - 9`--`r max(ct$Year)`
(Table \@ref(tab:es-catches-tab)), the average coast-wide catch was
`r ct_mean_10yrs`~t with U.S. and Canadian catches averaging
`r ct_us_mean_10yrs`~t and `r ct_can_mean_10yrs`~t, respectively. Since 2017,
the coast-wide catch has been declining annually through `r end_yr - 1` to
`r last_yr_landings`~t out of a total allowable catch (TAC, adjusted for
carryovers) of `r last_yr_tac`~t. Attainment in the U.S. was
`r last_yr_us_attained`% of its quota and in Canada it was
`r last_yr_can_attained`% in `r assess_yr - 1`.


```{r es-catches-tab, results = "asis", echo = FALSE}

table_catch(
  ct,
  inc_foreign_jv = FALSE,
  start_yr = end_yr - 10,
  end_yr = end_yr - 1,
  caption = paste0(
    "Total ", sp, " catch used in the assessment by sector for the most recent ",
    "ten years. U.S. tribal catches are included in the sectors where they are ",
    "represented."),
  font_size = 7,
  header_font_size = 7,
  longtable = TRUE)
```

In this document, the terms catch and landings are used interchangeably.
Estimates of discard within the target fishery are included but discarding
of `r sp` in non-target fisheries is not. Discard from all fisheries,
including those that do not target `r sp`, is estimated to be less than 1% of
landings in recent years. The catches in `r  last_data_yr` declined below
the long-term average catch (`r f(long_term_avge_ct)`~t), continuing the
pattern of declining catches over recent years (especially in Canada). Landings
between 2001 and 2008 were predominantly comprised of fish from the very large
1999 year class, with a cumulative removal (through `r end_yr - 1`) from
that cohort of
`r f(cohort_catch_1999 / 1e6, 2)` Mt [1~Mt = 1~million metric tonnes].
Through `r last_data_yr`, the cumulative catches of the 2010, 2014, and 2016
year classes were estimated at
`r f(cohort_catch_2010 / 1e6, 2)`~Mt,
`r f(cohort_catch_2014 / 1e6, 2)`~Mt, and
`r f(cohort_catch_2016 / 1e6, 2)`~Mt, respectively. In the
`r end_yr - 1` catch, `r top_coh(base_model, last_data_yr, 3, cap = FALSE)`.

## Data and assessment {-}

This Joint Technical Committee (JTC) assessment depends on fishery
landings (`r start_yr`--`r last_data_yr`), an acoustic survey biomass index
of age-2$+$ fish (Figure~\@ref(fig:es-survey-biomass-fig)) and age compositions
(`r survey_start_yr`--`r survey_end_yr`),
fishery age compositions (`r start_yr_age_comps`--`r last_data_yr`),
maturity-at-age data, and
weight-at-age data (`r start_yr_age_comps`--`r last_data_yr`). In 2011,
the survey biomass index of age-2$+$ fish was the lowest in the time series and was followed
by the index increasing in 2012, 2013, and again in 2015 before decreasing to
near the time series average in 2017. The survey
(Figure~\@ref(fig:es-survey-biomass-fig)) shows a decline from 2019 (the fourth
highest of the series) to 2023 (the third lowest of the series).
Age-composition data from the aggregated fisheries and the acoustic survey
provide data that facilitates estimating relative
cohort strength, i.e., strong and weak cohorts.
No survey data are used to inform the size of the
`r last_data_yr-2`--`r last_data_yr` year classes.

(ref:es-survey-biomass-cap) Acoustic survey biomass index of age-2$+$ fish
(Mt). Approximate 95% confidence intervals are based on
sampling variability (intervals without the additional squid/`r sp`
apportionment uncertainty included in 2009, black line).

(ref:es-survey-biomass-alt) This figure shows that the survey estimate has
decreased from 2019 to 2021.

```{r es-survey-biomass-fig, fig.cap = "(ref:es-survey-biomass-cap)"}

plot_survey_biomass(base_model, index = "age2")
```

The assessment uses a Bayesian estimation approach, sensitivity analyses, and
retrospective investigations to evaluate the potential consequences of
parameter uncertainty, alternative structural models, and historical
performance of the assessment model, respectively. The Bayesian approach
combines prior knowledge about natural mortality, stock--recruitment steepness
(e.g., a parameter for stock productivity), and several other parameters, with
likelihoods for the acoustic survey biomass index, acoustic survey
age-composition data, and fishery age-composition
data. Integrating the joint posterior distribution over model parameters
provides probabilistic inferences about uncertain model parameters and
forecasts derived from those parameters; this is done via Markov chain Monte
Carlo sampling using the efficient No-U-Turn Sampler (NUTS). Sensitivity
analyses are used to identify alternative model assumptions that may also
be consistent with the data. All models, including bridging, sensitivity,
and retrospective models, use a Bayesian framework for estimation.
Retrospective analyses identify possible poor performance of the assessment
model with respect to future predictions. Past assessments have conducted
closed-loop simulations that provide insights into how alternative
combinations of survey frequency, assessment model selectivity assumptions,
changes in the distribution or `r sp`, and harvest control rules affect expected
management outcomes given repeated application of these procedures over
the long term. The results of past (and ongoing) closed-loop simulations
help inform decisions made for this assessment.

This `r assess_yr` assessment is again configured using Stock Synthesis. The
same general population dynamics structure as the base assessment model from
`r last_assess_yr` was used except for terminal recruitment and forecast
recruitment deviations (so from 2023 onwards), which were fixed at zero in this assessment.
Updates to data in this assessment include incorporating
<!-- the new biomass estimate and age-composition data from the acoustic survey conducted in `r survey_end_yr`, -->
fishery catch and age-composition data from `r end_yr-1`, weight-at-age data for
`r end_yr-1`,
maturity-at-age data for `r end_yr-2`,
<!-- the `r survey_end_yr` age-1 index estimate, -->
and minor changes to pre-`r end_yr-1` data. The model-based
approaches used to develop the input weight-at-age matrix and time-varying
temperature-dependent maturity were retained from last year's assessment
to inform fecundity.

The relative index of age-1 fish from the survey was not used to fit this
assessment model because it was found to have a strong influence on estimates
of recruitment even for cohorts that had several years of data, and because it lacks
time-specific measurements of uncertainty.
Thus, the only data point that can directly inform the size of
the 2023 cohort is from age-1 observations in the commercial fishery
in 2024. Given the unique seasonal
fishing conditions during the year and that this fishery-dependent data point
can be overly influential on the
estimated 2023 recruitment, estimated recruitment in 2023 was
based solely on the stock--recruitment relationship, with no estimated
recruitment deviations (i.e., deviations fixed at zero, giving average recruitment).
By necessity, this was also done for 2024 and the
projection years. This differs to previous assessment models, for which
recruitments at the end of the time series included a random component (extra variability
around the stock-recruitment relationship).

This assessment continues to use (since 2014) time-varying
(rather than constant) selectivity to maintain flexibility within the
fishery dynamics given variability in `r sp` distribution patterns.
The Dirichlet-multinomial estimation approach to weighting composition data
was retained, and a sensitivity to an alternative data-weighting approach was
investigated. Time-varying fecundity, which was introduced in 2019, was
retained and improved upon with time-varying estimates of maturity in 2024.
Assumptions for the forecast period for weight at age, maturity at age, and
selectivity continue to be based on conditions during the last five years,
as done since the 2020 assessment.

## Stock biomass {-}

Results from the base model
indicate that since the 1960s, `r sp` female spawning biomass has ranged from
well below to above unfished equilibrium (Figures~\@ref(fig:es-biomass-fig)
and~\@ref(fig:es-relative-biomass-fig)). Model estimates suggest
that it was below the unfished equilibrium in the 1960s, at the start of the
assessment period, due to lower than average recruitment.

(ref:es-biomass-cap) Median (solid line) of the posterior distribution for
beginning of the year female spawning biomass ($B_t$ in year $t$; Mt) through
`r end_yr` with 95% posterior credibility intervals (shaded area). The
left-most circle with a 95% posterior credibility interval is the estimated
unfished equilibrium biomass, `r b_0`.

(ref:es-biomass-alt) This figure shows that the median spawning biomass has
been increasing in size since 2021.

```{r es-biomass-fig, fig.cap = "(ref:es-biomass-cap)"}

plot_biomass(list(base_model),
             list(base_model_name),
             ylim = c(0, 5),
             point_shape = 1,
             leg_pos = "none")
```

The stock is estimated to have increased rapidly and was above unfished
equilibrium in the mid-1970s and mid-1980s (after two large recruitment
events in the early 1980s). It then declined steadily to a low in 1999. This
was followed by a brief increase to a peak in 2002 as the very large 1999 year
class matured. The 1999 year class largely supported the fishery for several
years due to relatively small recruitment events between 2000 and 2007. With
the aging 1999 year class, median female spawning biomass declined throughout
the late 2000s, reaching a time-series low of `r median_bio_min`~Mt in
`r median_bio_min_yr`. Median female spawning biomass is estimated to have
peaked again in 2014 due to a very large 2010 year class and an
above-average 2008 year class. The subsequent decline from 2014 to 2016 is
primarily from the 2010 year class surpassing the age at which the gains in
weight from growth are greater than the losses in weight from mortality
(growth-mortality transition). The 2014 year class is estimated to be large,
though not as large as the 1999 and 2010 year classes, resulting in increasing
biomass through 2018.
The estimated biomass declined
from 2018 to 2022 due to the 2014 and 2016 year classes moving through the
growth-mortality transition during a period of high catches. The increase in
female spawning biomass from 2022--2025 is due to the above-average 2020 and
2021 cohorts entering maturity and the recent declining trend in catch.

The median estimate of the `r end_yr` relative spawning biomass (spawning
biomass at the start of `r end_yr` divided by that at unfished equilibrium,
`r b_0`) is `r curr_depl_median`%. However, the uncertainty is large, with a
95% posterior credibility interval from `r curr_depl_lower`% to
`r curr_depl_upper`% (Table~\@ref(tab:es-biomass-tab)), partly due to remaining
unknowns about the size of the
potentially large 2021 cohort because it has only been observed once by the acoustic survey.

The median estimate of the `r end_yr` female spawning biomass is
`r curr_bio_median` (with a 95% posterior credibility interval from
`r curr_bio_lower` to `r curr_bio_upper`)~Mt.
The current estimate of
the `r end_yr - 1` female spawning biomass is `r prev_bio_median`
(`r prev_bio_lower`--`r prev_bio_upper`)~Mt, giving a much narrower range of
uncertainty compared to the estimate from the `r end_yr - 1` assessment of `r prev_bio_median_last_assess`
(`r prev_bio_lower_last_assess`--`r prev_bio_upper_last_assess`)~Mt. The
median is reduced from last year's assessment due to the reduction in the estimate of
the 2022 year class with updated data, the aforementioned fixed zero
recruitment deviation for the 2023 recruitment, and removal of the age-1 index
from the model (which in particularly reduced estimates of several recent
year classes).

(ref:es-relative-biomass-cap) Median (solid line) of the posterior
distribution for relative spawning biomass ($B_t / B_0$) through `r end_yr`
with 95% posterior credibility intervals (shaded area). Dashed horizontal
lines show 10%, 40%, and 100% of the unfished equilibrium (`r b_0`).

(ref:es-relative-biomass-alt) This figure shows that the relative spawning
biomass has been increasing since 2021. The value for 2023 is just above B0.

```{r es-relative-biomass-fig, fig.cap = "(ref:es-relative-biomass-cap)"}

plot_rel_biomass(list(base_model),
                 list(base_model_name),
                 point_shape = 1,
                 ylim = c(0, 3),
                 alpha = 0.2,
                 leg_pos = "none")
```

```{r es-biomass-tab, results = "asis", echo = FALSE}

table_biomass(
  base_model,
  start_yr = end_yr - 9,
  end_yr = end_yr,
  caption = paste0(
    "Recent trends in estimated beginning of the year female spawning ",
    "biomass (SB; kt) and SB relative to estimated SB at unfished equilibrium ",
    "(Rel. SB; \\%)."),
  font_size = 10,
  header_font_size = 8)
```
\clearpage

## Recruitment {-}

`r sp` have low to moderate recruitment (relative to the long-term average)
with occasional large year classes
(Table~\@ref(tab:es-recruitment-tab) and Figure~\@ref(fig:es-recruitment-fig)).
Very large year classes in 1980, 1984,
and 1999 supported much of the commercial catch from the 1980s to the
mid-2000s. From 2000 to 2007, estimated recruitment was at some of the
lowest values in the time series but this was followed by an above average
2008 year class and a very strong 2010 year class. Above average year classes
have occurred since then in 2014, 2016, 2020 and 2021
(median recruitment above the mean of all median recruitments),
which have been sustaining the fishery over the
last decade, with below average year classes for all other years from 2011--2022.

<!-- yrs_since_2010_recruitment_med_below_mean -- check that for the last sentence -->

```{r es-recruitment-tab, results = "asis", echo = FALSE}

table_recruitment(
  base_model,
  start_yr = end_yr - 10,
  end_yr = end_yr - 1,
  caption = paste0(
    "Estimates of recent recruitment (millions of age-0 fish) and ",
    "recruitment deviations, where deviations below (above) zero indicate ",
    "recruitment below (above) that estimated from the stock--recruitment ",
    "relationship."),
  font_size = 10,
  header_font_size = 9)
```

(ref:es-recruitment-cap) Medians (solid circles) and means ($\mathrm{X}$) of the
posterior distribution for recruitment (billions of age-0 fish) with 95%
posterior credibility intervals (vertical lines). The median of the
posterior distribution for mean unfished equilibrium recruitment ($R_0$) is
shown as the horizontal dashed line with the 95% posterior credibility
interval shaded between the dotted lines.

(ref:es-recruitment-alt) This figure shows that recruitment for each cohort.
There are currently three above-average cohorts in the stock with 2020 being
the fourth. The 2020 cohort is highly uncertain which can be seen in the
size of the credible interval.

```{r es-recruitment-fig, fig.cap = "(ref:es-recruitment-cap)"}
plot_recruitment(list(base_model),
                 list(base_model_name),
                 inc_means = TRUE,
                 leg_pos = "none")
```

The addition of `r last_data_yr` data for this assessment do not significantly
change the general pattern of recruitment estimated in recent assessments.
However, estimates of absolute recent recruitments are all reduced from the
previous assessment due to new data, updated assumptions about recent
recruitments and, in particular, removal of the age-1 index.
The estimate of 2020 recruitment is above average, whereas in the previous
two assessments it was highly uncertain but thought to be possibly very large.
The 2021 recruitment is estimated to be potentially large with a median of
`r f(base_model$mcmccalcs$rmed["2021"], 1)`~billion fish based on
several years of fishery data and the 2023 survey. The 2022 cohort was observed
by the age-1 index in 2023 and fit to in the 2024 assessment, which suggested it is
average to below average in size; however, with the removal of the age-1 index
in this year's assessment the 2022 cohort is now estimated to be very small,
based on fishery age data.
There are also no survey data available to inform the estimates of
the `r end_yr - 2`--`r end_yr - 1` year class sizes, for which recruitment
deviations were set to zero.
The general notion remains that recent `r sp` recruitment is
highly uncertain, and estimates for recent years (based on limited data) can
change substantially as new data refines estimates. Retrospective analyses
of year class strength for young fish have shown the estimates of recent
recruitment to be unreliable prior to at least a modelled age of 3
(observed as age-2 fish the previous year) without a survey in the most recent
year and a modelled age of 2 with a survey, giving
further motivation for fixing recruitment deviations to 0 for `r end_yr - 2` this year.

## Default harvest policy {-}

The default `r f_40_40_10` harvest policy prescribes the maximum rate of fishing
mortality to equal `r fspr_40`. This rate gives a spawning potential ratio (SPR)
of 40%, meaning that the female spawning biomass per recruit with `r fspr_40` is
40% of that without fishing. If female spawning biomass is below `r b_40`
(40% of `r b_0`), the policy reduces the TAC linearly until it equals zero at
`r b_10` (10% of `r b_0`). Relative fishing intensity for fishing rate
$\mathrm{F}$ is `r fishing_rate`, where `r spr_40` is an SPR of 40%;
it is reported here interchangeably as a proportion or a percentage. A
relative fishing intensity above 1.0 means fishing at a rate above `r fspr_40`.

## Exploitation status {-}

```{r es-fishing-intensity-tab, results = "asis", echo = FALSE}

table_fishing_intensity(
  base_model,
  start_yr = end_yr - 10,
  end_yr = end_yr - 1,
  digits = 3,
  caption = paste0(
    "Recent estimates of relative fishing intensity, ",
    rel_fishing_intensity_for_latex_table, ", and exploitation ",
    "fraction (catch divided by age-2$+$ biomass)."),
  font_size = 10,
  header_font_size = 9)

```

The median estimated relative fishing intensity on the stock is below the
management level of 1.0 `r median_intensity_above_1_text` (see
Table~\@ref(tab:es-fishing-intensity-tab) for recent years and
Figure~\@ref(fig:es-fishing-intensity-fig)). Over the last five years, it was the
highest in 2019 at `r median_intensity_2019`%, dropped
in 2020 to `r median_intensity_2020`%, increased through 2021 and 2022
to `r median_intensity_2021`% and `r median_intensity_2022`% respectively,
then dropped in 2023 to
`r median_intensity_2023`% and in 2024 was
`r median_intensity_2024`%
(Table~\@ref(tab:es-fishing-intensity-tab) and
Figure~\@ref(fig:es-fishing-intensity-fig)).
Although there is a considerable amount of imprecision around these
estimates due to uncertainty in recruitment and spawning biomass,
the 95% posterior credibility interval of relative fishing intensity was
below 1.0 from 2013--2015 and again in 2020, 2021, and 2023
(Figure~\@ref(fig:es-fishing-intensity-fig)).

(ref:es-fishing-intensity-cap) Trend in median relative fishing intensity
(relative to the `r fspr_40` management level) through `r end_yr - 1` with
95% posterior credibility intervals. The `r fspr_40` management level defined
in the Joint U.S.-Canada Agreement for `r sp` is shown as a horizontal line
at 1.0.

(ref:es-fishing-intensity-alt) This figure shows that we have been below
the management value of 1 for FSPR 40 percent throughout the entire time
series.

```{r es-fishing-intensity-fig, fig.cap = "(ref:es-fishing-intensity-cap)"}

plot_fishing_intensity(base_model, show_arrows = TRUE, line_color="grey32")
```

The median exploitation fraction (catch divided by biomass of fish of age-2 and
above) peaked in 2006 and 2008 (Figure~\@ref(fig:es-exploitation-fraction-fig)).
The median exploitation fraction has decreased from a recent high in 2021 of
`r exploitation_med_2021` to `r exploitation_med_2024` in 2024, which is the
lowest over the past 10 years (Table~\@ref(tab:es-fishing-intensity-tab) and
Figure~\@ref(fig:es-exploitation-fraction-fig)).

## Management performance {-}

Over the last decade (`r end_yr - 10`--`r end_yr - 1`), the mean coast-wide
utilization rate (proportion of catch target removed) has been
`r tot_last_10_yrs_attainment`% and catches have been below coast-wide
targets (Table~\@ref(tab:es-landings-tac-tab)). From `r end_yr - 5` to
`r end_yr - 1`, the mean utilization rates differed between the U.S.
(`r us_last_5_yrs_attainment`%) and Canada (`r can_last_5_yrs_attainment`%).
While Canada's rate was higher than the U.S.'s in 2020, it has dropped considerably
over the past few years to historic lows. The utilization rate for the coast-wide
fishery this year was the lowest of the previous decade (`r tot_2024_attainment`%)
due, in part, to difficulties locating aggregations of fish during the spring and
throughout the year in northern areas.
The usual `r us_allotment_percent`% and `r can_allotment_percent`%
allocation of coast-wide TAC, as specified in the Joint U.S.-Canada
Agreement for `r sp`, was implemented for the `r last_assess_yr` fishery.
Total landings last exceeded the coast-wide quota in 2002 when utilization
was 112%.

(ref:es-exploitation-fraction-cap) Trend in median exploitation fraction
(catch divided by age-2$+$ biomass) through `r end_yr - 1` with 95% posterior
credibility intervals.

(ref:es-exploitation-fraction-alt) This figure shows that the current
exploitation fraction of the female spawning biomass is approximately 0.05.
This is a drop from the last five years which have been approximately 0.1.

```{r es-exploitation-fraction-fig, fig.cap = "(ref:es-exploitation-fraction-cap)"}

plot_exploitation_fraction(base_model, show_arrows = TRUE, line_color="grey32")
```

```{r es-landings-tac-tab, results = "asis", echo = FALSE}

table_landings_tac(
  ct,
  start_yr = end_yr - 10,
  end_yr = end_yr - 1,
  caption = paste0(
    "Recent trends in ", sp, " landings and management decisions. Catch ",
    "targets in 2020 and 2021 were specified unilaterally. All landings ",
    "and catch targets are given in tonnes."),
  font_size = 7,
  header_font_size = 7,
  longtable = TRUE)
```

(ref:es-phase-cap) Estimated historical path of median relative spawning
biomass in year $t$ and corresponding median relative fishing intensity in
year $t - 1$. Labels show the time series start and end years; labels
correspond to year $t$ (i.e., year of the relative spawning biomass).
Gray bars span the 95% credibility intervals for `r end_yr` relative
spawning biomass (horizontal) and `r end_yr - 1` relative fishing
intensity (vertical).

(ref:es-phase-alt) This figure shows that we are currently not overfishing
nor in an overfished state.

```{r es-phase-fig, fig.cap = "(ref:es-phase-cap)"}

plot_phase(base_model,
           start_yr,
           end_yr,
           cross_line_width = 0.5,
           cross_line_color = "black",
           init_lbl_x_off = -0.04,
           init_lbl_y_off = -0.04,
           final_lbl_x_off = 0.04,
           final_lbl_y_off = 0.04,
           title_y_font_size = axis_title_font_size * 0.92)
```

\clearpage

The median relative spawning biomass was above the `r b_40`
reference level in all years except 2007--2009 and 2011
(Figures~\@ref(fig:es-relative-biomass-fig)
and~\@ref(fig:es-phase-fig)), and the median relative fishing intensity has
always been below
1.0 (Figure~\@ref(fig:es-phase-fig)).
Relative spawning biomass increased from
the lows in 2007--2012 with above average recruitment in 2008, 2010, 2014,
2016, 2020, and 2021. Correspondingly, median relative fishing intensity has
remained below 1, and total catch has been declining since the
time series high in 2017. While there is large uncertainty in the `r end_yr-1`
estimates of relative fishing intensity and relative spawning biomass,
the model estimates a `r joint_percent_prob_above_below`% joint probability
of being both above the target relative fishing intensity (`r fspr_40`) in
`r end_yr - 1` and below the relative spawning biomass level of `r b_40`
at the start of `r end_yr`.

## Reference points {-}

The term 'reference points' is used throughout this document to describe common
conceptual summary metrics (Table~\@ref(tab:es-reference-points-tab)).
The Agreement specifically identifies `r fspr_40` as the default harvest rate
and `r b_40` as a point where the 40:10 TAC adjustment is triggered
(see the Glossary in Appendix~\@ref(sec:app-glossary)).
The medians of sustainable yields and biomass reference points are lower
that those reported in the `r last_assess_yr` assessment, due to the
absolute scale of the biomass being lower (due to updated data and changes in
model assumptions). The probability
that female spawning biomass at the beginning of `r assess_yr` is below
`r b_40` is P(*B*~`r assess_yr`~ < `r b_40`) = `r probs_curr_below_b40`%,
and of being below `r b_25` is
P(*B*~`r assess_yr`~ < `r b_25`) = `r probs_curr_below_b25`%.
The probability that the relative fishing intensity was above the `r fspr_40`
level of 1.0 at the end of `r end_yr - 1`
is~`r probs_curr_rel_fish_intens_above_1`%.

```{r es-reference-points-tab, results = "asis", echo = FALSE}

table_reference_points(
  base_model,
  category_bold = TRUE,
  category_italics = TRUE,
  category_underline = TRUE,
  category_line_above = FALSE,
  category_line_below = FALSE,
  caption = paste0(
    "Summary of median and 95\\% credibility intervals of equilibrium ",
    "conceptual reference points for the base assessment model. ",
    "Equilibrium reference points were computed using ", start_yr_age_comps,
    "--", end_yr - 1, " averages for mean weight-at-age and baseline ",
    "selectivity-at-age (1966--1990; prior to time-varying deviations). ",
    "Dashes (--) indicate values that are static at one value and do not ",
    "have a credible interval associated with them."),
  font_size = 10,
  header_font_size = 11,
  longtable = TRUE)
```

## Unresolved problems and major uncertainties {-}

Measures of uncertainty in the base model underestimate the total uncertainty
in the current stock status and projections because they do not account for
possible alternative structural models for `r simple_name` population
dynamics and fishery processes (e.g., selectivity) and the scientific basis
for prior probability distributions. To address such structural uncertainties,
sensitivity analyses were performed to investigate a range of alternative
assumptions and present the key ones in the main document.

The `r sp` stock displays high recruitment variability relative to other West
Coast groundfish stocks, resulting in large and rapid biomass changes. This
leads to a dynamic fishery that potentially targets strong cohorts and results
in time-varying fishery selectivity. This volatility results in a high level
of uncertainty in estimates of current stock status and stock projections
because, with limited data to estimate incoming recruitment, the cohorts are
fished before the assessment can accurately determine how big they are (i.e.,
cohort strength is typically not well known until it is observed by the
fishery and survey, typically at a minimum age of three). Further, the impact
of interactions among variance parameters that
govern variability in fishery selectivity and recruitment parameters through
time, as well as those used in relative data weighting, are not well understood. If
variance parameters were estimated as random effects, such interactions could
propagate uncertainty beyond what is presented in this assessment.

While the removal of both the age-1 index and recent recruitment deviations in
this assessment reduced uncertainty around recent spawning stock biomass estimates,
it also results in a significant underestimate of uncertainty during the forecast period.
The model estimates the 2020 and 2021 cohorts as
above average in size, and while their absolute size remains highly uncertain, the
uncertainty is less than in last year's assessment (which is only partly due to
2024 data). This reduced uncertainty propagates directly into current and forecasted
estimates of female spawning biomass. The 2023 acoustic survey provided additional
information on the size of the 2020 year-class (as well as informed the 2021 year
class). Collectively, these lessened uncertainty around estimates of female
spawning biomass, as did the changes in model assumptions. However, information on the size
of the 2023 year class from the 2024 fishery was considered suspect given the unique
fishing conditions during the year and so, as mentioned earlier, recruitment
deviations from 2023 onwards were set to zero.
This does not allow very large (or very small) random recruitments to
occur and propagate through the projections as these cohorts mature. Thus, while
this results in calculated uncertainty for projections being less than for
previous assessments, the true uncertainty is underestimated because median
recruitment is assumed rather than allowing a broad distribution. This assumption was deemed
preferable this year to allowing potentially large recruitments that can inflate the forecast
biomass yet are based on limited or no data and so may not materialise in
practice.

\clearpage

## Forecast decision tables {-}

The catch limit for `r min(forecast_yrs)` based on the default `r f_40_40_10`
harvest policy has a median of `r ct_limit_quantiles["median"]`~t with a
wide range of uncertainty, the 95% credibility interval being
`r ct_limit_quantiles["lower"]`--`r ct_limit_quantiles["upper"]`~t.

Decision tables give the projected population status (relative spawning
biomass) and fishing intensity relative to the target under different
catch alternatives for the base model (Tables~\@ref(tab:es-decisions-biomass-tab)
and~\@ref(tab:es-decisions-spr-tab)). The tables are organized to show the
projected outcome for each potential catch level and year (row) across the
quantiles (columns) of the posterior distribution. Tables show results for up
to three years (only two years in subsequent assessments following JMC advice)
of future catch levels based on subsequent estimates of stock
status and fishing intensity.
Figure~\@ref(fig:es-depletion-comparison-fig) shows the projected relative
spawning biomass for several of the catch alternatives. Population dynamics
and governing parameters assumed during the forecast period include selectivity,
weight-at-age and fecundity-at-age averaged over the five
most recent years (`r assess_yr - 5`--`r assess_yr - 1`), and constant
values for all other parameters.

A relative fishing intensity of 1 should indicate fishing at the `r fspr_40`
default harvest rate catch target. But, the projected median relative fishing
intensity can be slightly different than the target because the `r fspr_40`
default harvest-rate catch limit is calculated using baseline
selectivity-at-age (1966--1990; prior to time-varying deviations), whereas the
forecasted catches use selectivity averaged over the last five
years. Recent changes in selectivity will thus be reflected in the
determination of fishing relative to the default harvest policy. For example,
fishing at the `r fspr_40` default harvest-rate catch limit
(scenario `r letters[ct_levels_vals$ct_default_policy_ind]`: default HR)
in `r assess_yr - 1` results in a median relative fishing intensity of
`r fi_at_hcr` (Table~\@ref(tab:es-decisions-spr-tab)).

Management metrics that were identified as important to the Joint Management
Committee and the Advisory Panel in 2012 are presented for
`r forecast_yrs[2]` and `r forecast_yrs[3]` projections
(Tables~\@ref(tab:es-risk-year-1-tab) and~\@ref(tab:es-risk-year-2-tab);
Figures~\@ref(fig:es-risk-year-1-fig) and~\@ref(fig:es-risk-year-2-fig)).
These metrics summarize the probability of various outcomes from the base model
given each potential management action. Although not linear, probabilities can
be interpolated from these results with reasonable accuracy for intermediate catch values in
`r assess_yr` (Table~\@ref(tab:es-risk-year-1-tab) and
Figure~\@ref(fig:es-risk-year-1-fig)).
However, interpolation is not appropriate for the default harvest rule scenario
in `r assess_yr + 1` because it is conditional on the `r assess_yr` catch.

```{r es-decisions-biomass-tab, results = "asis", echo = FALSE}

let <- letters[seq_along(base_model$forecasts[[length(base_model$forecasts)]])]
last_let <- let[length(let)]

table_decision(
  base_model,
  type = "biomass",
  forecast_inds =
    seq_along(base_model$forecasts[[length(base_model$forecasts)]]),
  inc_fi_stable_catch = length(base_model$forecasts[[1]]) == 13,
  caption = paste0(
      "Forecast quantiles of Pacific Hake relative spawning biomass at the ",
      "beginning of the year. Catch alternatives are defined by letters a-",
      last_let, " and are a constant value across all forecasted years unless ",
      "otherwise defined in the first column. Acronyms are defined in the ",
      "glossary (Appendix~\\@ref(sec:app-glossary))."),
  bold_letters = TRUE,
  digits = 2,
  # Font values higher than 8 and 11 for table and header respectively
  # will cause the table to wrap to a second page
  font_size = 8,
  header_font_size = 11,
  # If the font is changed it is almost guaranteed that `left_col_cm` and
  # `right_cols_cm` will have to be changed, especially if the font is made
  # larger. You will have to check this with trial-and-error, building the
  # document, checking the table and adjusting, over and over until it looks
  # right
  left_col_cm = 3,
  right_cols_cm = 1.2,
  longtable = TRUE)
```

\clearpage

```{r es-decisions-spr-tab, results = "asis", echo = FALSE}

table_decision(
  base_model,
  type = "spr",
  forecast_inds =
    seq_along(base_model$forecasts[[length(base_model$forecasts)]]),
  inc_fi_stable_catch = length(base_model$forecasts[[1]]) == 13,
  caption = paste0(
      "Forecast quantiles of Pacific Hake relative fishing intensity ",
      rel_fishing_intensity_for_latex_table, ", expressed as a proportion. ",
      "Catch alternatives are defined by letters a-", last_let, " and are a constant ",
      "value across all forecasted years unless otherwise defined in the ",
      "first column. Acronyms are defined in the glossary ",
      "(Appendix~\\@ref(sec:app-glossary))."),
  bold_letters = TRUE,
  digits = 2,
  # Font values higher than 8 and 11 for table and header respectively
  # will cause the table to wrap to a second page
  font_size = 8,
  header_font_size = 11,
  # If the font is changed it is almost guaranteed that `left_col_cm` and
  # `right_cols_cm` will have to be changed, especially if the font is made
  # larger
  left_col_cm = 3,
  right_cols_cm = 1.2,
  longtable = TRUE)
```

<!-- Commenting out in 2025 as did not happen, as we only have the one
bouncing-around catch alternatve.
This explains why probabilities can sometimes decline (rather than rise) with
increased assess_yr + 1 and assess_yr + 2 catch levels
(Tables~\@ref(tab:es-risk-year-2-tab) and~\@ref(tab:es-risk-year-3-tab);
Figures~\@ref(fig:es-risk-year-2-fig) and~\@ref(fig:es-risk-year-3-fig)).
-->

(ref:es-depletion-comparison-cap) Median and 95% posterior
credibility intervals of estimated relative spawning biomass to the start
of `r end_yr` from the base model and projections to the start of
`r forecast_yrs[length(forecast_yrs)]` for several catch alternatives, which
are defined in Table~\@ref(tab:es-decisions-biomass-tab).

(ref:es-depletion-comparison-alt) This figure shows that the median
relative spawning biomass is projected to remain flat for the next 3 years
with zero catch and to decline for all non-zero catch levels evaluated.

```{r es-depletion-comparison-fig, fig.cap = "(ref:es-depletion-comparison-cap)"}

# See the file `forecast-catch-levels.R` at the list called `ct_levels`. The values in
# `fore_inds` below are the indices of those forecast values in that list.
plot_depl_fore_comparison(base_model,
                          fore_inds = c(1, 2, 6, 10, 11),
                          forecast_yrs = forecast_yrs)
```

With zero catch for the next two years and median recruitment from 2023 onward, the biomass has a
`r zero_catch_prob_bio_down_1`% probability of decreasing from
`r forecast_yrs[1]` to `r forecast_yrs[2]` (Table~\@ref(tab:es-risk-year-1-tab) and
Figure~\@ref(fig:es-risk-year-1-fig)) and a
`r zero_catch_prob_bio_down_2`% probability of decreasing from
`r forecast_yrs[2]` to `r forecast_yrs[3]` (Table~\@ref(tab:es-risk-year-2-tab)
and Figure~\@ref(fig:es-risk-year-2-fig)).
<!--and a `r zero_catch_prob_bio_down_3`% probability of decreasing from-->
<!--`r forecast_yrs[3]` to `r forecast_yrs[4]` (Table~\@ref(tab:es-risk-year-3-tab)-->
<!--and Figure~\@ref(fig:es-risk-year-1-fig)).-->

For all explored catches, the maximum probability of female spawning biomass at
the start of `r end_yr + 1` dropping below `r b_10` is
`r prob_max_below_10_yr1`% and of dropping below `r b_40` is
`r prob_max_below_40_yr1`% (Table~\@ref(tab:es-risk-year-1-tab) and
Figure~\@ref(fig:es-risk-year-1-fig)).
With realized catches of 400,000 t in 2025 and 2026, it is estimated that the
stock will reach approximately `r b_40` at the start of
2027, given the current assumption of average recruitment from 2023 onward.
As the above average 2014 and 2016
cohorts continue to age, total biomass of these cohorts even without fishing
mortality is expected to decrease as losses from mortality outweigh increases
from growth. The estimated above-average 2021 cohort will continue to play a
large role in determining female spawning biomass during the forecast years
presented here.

(ref:es-risk-year-1-cap) Graphical representation of
the probabilities related to spawning biomass, relative fishing intensity, and
the `r end_yr + 1` default harvest policy catch for alternative `r end_yr`
catch options (explained in Table~\@ref(tab:es-decisions-biomass-tab)) as listed in
Table~\@ref(tab:es-risk-year-1-tab). The symbols indicate points that were computed
directly from model output and lines interpolate between the points.

(ref:es-risk-year-1-alt) This figure shows that the probability that the
stock declines in 2024 is 50 percent or greater for all catch levels including
zero. The probability that the stock falls under B40 is almost zero for
catches up to approximately 350 thousand tonnes.

```{r es-risk-year-1-fig, fig.cap = "(ref:es-risk-year-1-cap)", fig.height = 4.5}

plot_fore_compare(base_model,
                  forecast_yrs = forecast_yrs,
                  fore_yr = forecast_yrs[1],
                  leg_pos = c(0.25, 0.75),
                  leg_font_size = 9,
                  remove_x_val = c(270)) +
  # Following make the legend smaller and legend items closer together
  theme(legend.key.size = unit(0.25, "cm"),
        legend.spacing.y = unit(0.01, "cm"),
        legend.box.background = element_rect(colour = "black")) +
  guides(color = guide_legend(byrow = TRUE))
```

```{r es-risk-year-1-tab, results = "asis", echo = FALSE}

# Index in models[[]]$risks to use, e.g. 1 means forecast year 2 compared
# to forecast year 1
table_risk(
  base_model,
  forecast_yrs,
  index = 1,
  type = "probability",
  digits = 2,
  caption = paste0(
    "Probabilities related to spawning biomass, relative fishing intensity, ",
    "and the ", end_yr + 1, " default harvest policy catch for alternative ",
    end_yr, " catch options (catch options are explained in ",
    "Table~\\@ref(tab:es-decisions-biomass-tab))."),
  font_size = 10,
  header_font_size = 10,
  longtable = TRUE)
```

\newpage

(ref:es-risk-year-2-cap) Graphical representation
of the probabilities related to spawning biomass, relative fishing intensity,
and the `r end_yr + 2` default harvest policy catch for alternative
`r end_yr + 1` catch options (including associated `r end_yr` catch; catch
options explained in Table~\@ref(tab:es-decisions-biomass-tab)) as listed in
Table~\@ref(tab:es-risk-year-2-tab). The symbols indicate points that were
computed directly from model output and lines interpolate between the points.

(ref:es-risk-year-2-alt) This figure shows that the probability that the
stock declines in 2025 is 74 percent or greater for all catch levels
including zero. The probability that the stock falls under B40 is below
0.1 for catches up to approximately 380 thousand tonnes.

```{r es-risk-year-2-fig, fig.cap = "(ref:es-risk-year-2-cap)", fig.height = 4.5}

plot_fore_compare(base_model,
                  forecast_yrs = forecast_yrs,
                  fore_yr = forecast_yrs[2],
                  leg_pos = c(0.25, 0.75),
                  leg_font_size = 9,
                  remove_x_val = c(264, 342, 651)) +
  # Following make the legend smaller and legend items closer together
  theme(legend.key.size = unit(0.25, "cm"),
        legend.spacing.y = unit(0.01, "cm"),
        legend.box.background = element_rect(colour = "black")) +
  guides(color = guide_legend(byrow = TRUE))
```

```{r es-risk-year-2-tab, results = "asis", echo = FALSE}

table_risk(
  base_model,
  forecast_yrs,
  index = 2,
  type = "probability",
  digits = 2,
  caption = paste0(
    "Probabilities related to spawning biomass, relative fishing intensity, ",
    "and the ", end_yr + 2, " default harvest policy catch for alternative ",
    end_yr + 1, " catch options, given the ", end_yr, " catch level shown ",
    "in Table~\\@ref(tab:es-risk-year-1-tab) (catch options are explained in ",
    "Table~\\@ref(tab:es-decisions-biomass-tab))."),
  font_size = 10,
  header_font_size = 10,
  longtable = TRUE)
```

<!--(ref:es-risk-year-3-cap) Graphical representation of-->
<!--the probabilities related to spawning biomass, relative fishing intensity, and-->
<!--the `r end_yr + 3` default harvest policy catch for alternative `r end_yr + 2`-->
<!--catch options (including associated `r end_yr` and `r end_yr + 1` catches;-->
<!--catch options explained in Table~\@ref(tab:es-decisions-biomass-tab)) as listed in-->
<!--Table~\@ref(tab:es-risk-year-3-tab). The symbols indicate points that were computed-->
<!--directly from model output and lines interpolate between the points.-->

<!--(ref:es-risk-year-3-alt) This figure shows that the probability that the-->
<!--stock declines in 2026 is approximately 65 percent or greater for all catch-->
<!--levels including zero. The probability that the stock falls under B40 is-->
<!--below 0.1 for catches up to approximately 350 thousand tonnes.-->

<!--```{r es-risk-year-3-fig, fig.cap = "(ref:es-risk-year-3-cap)", fig.height = 4.5}-->

<!--plot_fore_compare(base_model,-->
<!--                  forecast_yrs = forecast_yrs,-->
<!--                  fore_yr = forecast_yrs[3],-->
<!--                  leg_pos = c(0.25, 0.75),-->
<!--                  leg_font_size = 9,-->
<!--                  remove_x_val = c(264, 605)) +-->
<!--  # Following make the legend smaller and legend items closer together-->
<!--  theme(legend.key.size = unit(0.25, "cm"),-->
<!--        legend.spacing.y = unit(0.01, "cm"),-->
<!--        legend.box.background = element_rect(colour = "black")) +-->
<!--  guides(color = guide_legend(byrow = TRUE))-->
<!--```

<!--```{r es-risk-year-3-tab, results = "asis", echo = FALSE}-->

<!--table_risk(-->
<!--  base_model,-->
<!--  forecast_yrs,-->
<!--  index = 3,-->
<!--  type = "probability",-->
<!--  digits = 2,-->
<!--  caption = paste0(-->
<!--    "Probabilities related to spawning biomass, relative fishing intensity, ",-->
<!--    "and the ", end_yr + 3, " default harvest policy catch for alternative ",-->
<!--    end_yr + 2, " catch options, given the ", end_yr, " and ", end_yr + 1,-->
<!--    " catch levels shown in Tables~\\@ref(tab:es-risk-year-1-tab) and~",-->
<!--    "\\@ref(tab:es-risk-year-2-tab) (catch options are explained in Table~",-->
<!--    "\\@ref(tab:es-decisions-biomass-tab))."),-->
<!--  font_size = 10,-->
<!--  header_font_size = 10,-->
<!--  longtable = TRUE)-->
<!--```-->
\clearpage

## Research and data needs {-}
```{r child = "010-research-needs/research-needs.rmd"}
```

EXECUTIVE SUMMARY EOF - do not remove - required by the post-processor
\clearpage
