\newpage

\rfoot{Figures}

# Figures {#sec:figures}

(ref:main-overview-map-cap) Overview map of the area in the Northeast Pacific
Ocean occupied by `r sp`. Ports and areas of interest referred to in this
document or past assessment documents are shown.

(ref:main-overview-map-alt) This figure shows many ports and cities of
interest for the hake fishery.

```{r main-overview-map-fig, fig.cap = "(ref:main-overview-map-cap)", is.fig = TRUE, alt.text = "(ref:main-overview-map-alt)", fig.height = 8, fig.width = 6, out.height = "\\textheight",  out.width = "\\textwidth"}
plot_overview_map(ports_df, states_df)
```

(ref:main-acoustic-age2-bs-cap) Spatial distribution of acoustic backscatter
attributable to age-2 and older `r sp` from the `r survey_name`
(`r survey_start_yr`--`r survey_end_yr`). Area of the circle is roughly
proportional to observed backscatter. Bar plots show survey-estimated biomass
for ages 2 to 20, with major cohorts highlighted in color. Figure produced
by Julia Clemons (NOAA).

(ref:main-acoustic-age2-bs-alt) This figure shows that `r sp`  migrate further
north in some years

```{r main-acoustic-age2-bs-fig, fig.cap = "(ref:main-acoustic-age2-bs-cap)", fig.height = 4, fig.width = 8, is.fig = TRUE, alt.text = "(ref:main-acoustic-age2-bs-alt)"}
include_graphics(
  here::here("doc",
             "main-figures", "hake_survey_1995-21_NASCTimeSeries_BiomassAtAgeHistograms_grayblue.png"))
```

