\newpage

\rfoot{Base model MCMC diagnostics}

# Base model MCMC diagnostics {#sec:app-mcmc-diagnostics}

(ref:app-mcmc-diag-m-r0-cap) Summary of Markov chain Monte Carlo diagnostics
for natural mortality (upper 4 panels) and the natural log of mean unfished
equilibrium recruitment (ln($R_0$); lower 4 panels) in the base
model. Top sub-panels show the trace of the sampled values across iterations
(absolute values, top left; cumulative running median with 2.5^th^ and
97.5^th^ percentiles, top right). The lower left sub-panel indicate the
autocorrelation present in the chain at different lag times (i.e., distance
between samples in the chain), and the lower right sub-panel shows the
distribution of the values in the chain (i.e., the marginal density from a
smoothed histogram of values in the trace plot).

(ref:app-mcmc-diag-m-r0-alt) This figure shows good Markov chain Monte Carlo
diagnostics for the base model for natural mortality and log R 0 parameters.

```{r app-mcmc-diag-m-r0-fig, fig.cap = "(ref:app-mcmc-diag-m-r0-cap)", fig.height = 8}
plist <- NULL
plist[[1]] <-
  plot_mcmc_diagnostics(base_model,
                        key_posteriors[[1]],
                        key_posteriors_titles[[1]],
                        # Trace lines and autocorrelation bar color
                        color = "royalblue",
                        # Iteration and density fill color
                        fill = "royalblue",
                        # Iteration and density transparency
                        rib_alpha = 0.3,
                        #Trace lines and autocorrelation bar transparency
                        line_bar_alpha = 0.8)
plist[[2]] <-
  plot_mcmc_diagnostics(base_model,
                        key_posteriors[[2]],
                        key_posteriors_titles[[2]],
                        # Trace lines and autocorrelation bar color
                        color = "royalblue",
                        # Iteration and density fill color
                        fill = "royalblue",
                        # Iteration and density transparency
                        rib_alpha = 0.3,
                        #Trace lines and autocorrelation bar transparency
                        line_bar_alpha = 0.8)
plot_grid(plotlist = plist, nrow = 2)
```

(ref:app-mcmc-diag-h-cap) Summary of Markov chain Monte Carlo
diagnostics for steepness in the base model.
Sub-panel descriptions as in Figure~\@ref(fig:app-mcmc-diag-m-r0-fig).

(ref:app-mcmc-diag-h-alt) This figure shows good Markov chain Monte
Carlo diagnostics for steepness in the base model.

```{r app-mcmc-diag-h-fig, fig.cap = "(ref:app-mcmc-diag-h-cap)", fig.height = 8}

plist <- NULL
plist[[1]] <-
  plot_mcmc_diagnostics(base_model,
                        key_posteriors[[3]],
                        key_posteriors_titles[[3]],
                        # Trace lines and autocorrelation bar color
                        color = "royalblue",
                        # Iteration and density fill color
                        fill = "royalblue",
                        # Iteration and density transparency
                        rib_alpha = 0.3,
                        #Trace lines and autocorrelation bar transparency
                        line_bar_alpha = 0.8)
plist[[2]] <-
  NULL
plot_grid(plotlist = plist, nrow = 2)
```
(ref:app-mcmc-diag-extra-sd-cap) Summary of Markov chain Monte Carlo
diagnostics for the additional standard deviation (SD) in the biomass
index. Sub-panel descriptions as in Figure~\@ref(fig:app-mcmc-diag-m-r0-fig).

(ref:app-mcmc-diag-extra-sd-alt) This figure shows good Markov chain Monte
Carlo diagnostics for the base model for the survey additional
standard deviation parameters.

```{r app-mcmc-diag-extra-sd-fig, fig.cap = "(ref:app-mcmc-diag-extra-sd-cap)", fig.height = 8}

plist <- NULL
plist[[1]] <-
  plot_mcmc_diagnostics(base_model,
                        key_posteriors[[4]],
                        key_posteriors_titles[[4]],
                        # Trace lines and autocorrelation bar color
                        color = "royalblue",
                        # Iteration and density fill color
                        fill = "royalblue",
                        # Iteration and density transparency
                        rib_alpha = 0.3,
                        #Trace lines and autocorrelation bar transparency
                        line_bar_alpha = 0.8)
# plist[[2]] <-
#   plot_mcmc_diagnostics(base_model,
#                         key_posteriors[[5]],
#                         key_posteriors_titles[[5]],
#                         # Trace lines and autocorrelation bar color
#                         color = "royalblue",
#                         # Iteration and density fill color
#                         fill = "royalblue",
#                         # Iteration and density transparency
#                         rib_alpha = 0.3,
#                         #Trace lines and autocorrelation bar transparency
#                         line_bar_alpha = 0.8)
plot_grid(plotlist = plist, nrow = 1)
```

(ref:app-mcmc-diag-dm-cap) Summary of Markov chain Monte Carlo diagnostics
for the Dirichlet-multinomial age-composition parameters for the
fishery ($\theta_{\text{fish}}$, upper 4 panels) and the survey
($\theta_{\text{surv}}$, lower 4 panels) in the base model. Sub-panel
descriptions as in Figure~\@ref(fig:app-mcmc-diag-m-r0-fig).

(ref:app-mcmc-diag-dm-alt) This figure shows good Markov chain Monte Carlo
diagnostics for the base model for the Dirichlet-multinomial parameters
for the fishery and the survey.

```{r app-mcmc-diag-dm-fig, fig.cap = "(ref:app-mcmc-diag-dm-cap)", fig.height = 8}

plist <- NULL
plist[[1]] <-
  plot_mcmc_diagnostics(base_model,
                        key_posteriors[[6]],
                        key_posteriors_titles[[6]],
                        # Trace lines and autocorrelation bar color
                        color = "royalblue",
                        # Iteration and density fill color
                        fill = "royalblue",
                        # Iteration and density transparency
                        rib_alpha = 0.3,
                        #Trace lines and autocorrelation bar transparency
                        line_bar_alpha = 0.8)
plist[[2]] <-
  plot_mcmc_diagnostics(base_model,
                        key_posteriors[[7]],
                        key_posteriors_titles[[7]],
                        # Trace lines and autocorrelation bar color
                        color = "royalblue",
                        # Iteration and density fill color
                        fill = "royalblue",
                        # Iteration and density transparency
                        rib_alpha = 0.3,
                        #Trace lines and autocorrelation bar transparency
                        line_bar_alpha = 0.8)
plot_grid(plotlist = plist, nrow = 2)
```
(ref:app-mcmc-diag-hists-cap) Summary histograms of Markov chain Monte Carlo
diagnostics for all base model parameters. The level of autocorrelation in
the chain (distribution across lag times, i.e., distance between samples in
the chain, shown in the top left panel) influences the effective sample size
(top right panel) used to estimate posterior distributions. The Geweke
statistic (lower left panel) tests for equality between means located in the
first part of the chain against means in the last part of the chain. The
Heidelberger and Welch statistic (lower right panel) tests if the sampled
values come from a stationary distribution by comparing different sections
of the chain. Values for the unfished equilibrium recruitment ($R_0$) are
explicitly highlighted. Values inside the bars represent the number of
parameters counted in that bin.

(ref:app-mcmc-diag-hists-alt) This figure shows good summary Markov chain
Monte Carlo diagnostics for all base model parameters.

```{r app-mcmc-diag-hists-fig, fig.cap = "(ref:app-mcmc-diag-hists-cap)", fig.height = 6}

plot_mcmc_diagnostics_all_params(base_model,
                                 show_ro = TRUE,
                                 ro_arrow_lengths = c(20, 30, 5, 30),
                                 ro_text_nudges = c(0.3, 0, -0.55, 0),
                                 ro_text_size = 5,
                                 y_lim_geweke = c(0, 40))
```

(ref:app-mcmc-pairs-cap) Posterior correlations among the objective
function which is minimized during model fitting, key base-model parameters,
and derived quantities. Numbers refer to the absolute correlation
coefficients, with font size proportional to the square root of the
coefficient. Straight lines on the scatterplots are linear regressions.

(ref:app-mcmc-pairs-alt) This figure shows pairs plots for many parameters
and derived quantities. Natural mortality and log R 0 show positive
correlation.

```{r app-mcmc-pairs-fig, fig.cap = "(ref:app-mcmc-pairs-cap)", fig.height = 8}

plot_pairs(base_model,
           type = "key",
           key_posteriors = key_posteriors,
           key_posteriors_titles = key_posteriors_titles,
           recr = c(2014, 2016),
           bratio = end_yr,
           point_size = 0.05,
           forecatch = c(end_yr,
                         end_yr + 1,
                         end_yr + 2))
```

(ref:app-mcmc-pairs-recruit-devs-cap) Posterior correlations among
recruitment deviations from recent years and mean unfished equilibrium
recruitment. Numbers refer to the absolute correlation coefficients, with
font size proportional to the square root of the coefficient.
Straight lines on the scatterplots are linear regressions.

(ref:app-mcmc-pairs-recruit-devs-alt) This figure shows pairs plots for
many derived quantities. There is some positive correlation between 2014
and 2016 recruitment deviations.

```{r app-mcmc-pairs-recruit-devs-fig, fig.cap = "(ref:app-mcmc-pairs-recruit-devs-cap)", fig.height = 8}

plot_pairs(base_model,
           type = "devs",
           key_posteriors = key_posteriors,
           key_posteriors_titles = key_posteriors_titles,
           recr = (end_yr - 10):(end_yr - 1))
```

\clearpage
