\newpage

\rfoot{Base model MCMC diagnostics}

# Base model MCMC diagnostics {#sec:app-mcmc-diagnostics}

(ref:app-mcmc-diag-m-r0-cap) Summary of MCMC diagnostics
for natural mortality (upper panels) and the natural log of mean unfished
equilibrium recruitment (ln($R_0$); lower panels) in the base
model. Top sub-panels show the trace of the sampled values across iterations
(absolute values, top left; cumulative running median with 2.5^th^ and
97.5^th^ percentiles, top right). The lower left sub-panel indicate the
autocorrelation present in the chain at different lag times (i.e., distance
between samples in the chain), and the lower right sub-panel shows the
distribution of the values in the chain (i.e., the marginal density from a
smoothed histogram of values in the trace plot).

(ref:app-mcmc-diag-m-r0-alt) This figure shows good MCMC diagnostics for the
base model for natural mortality and log R0 parameters.

```{r app-mcmc-diag-m-r0-fig, fig.cap = "(ref:app-mcmc-diag-m-r0-cap)", fig.height = 8}
plist <- NULL
plist[[1]] <-
  plot_mcmc_diagnostics(base_model,
                        key_posteriors[[1]],
                        key_posteriors_titles[[1]],
                        # Trace lines and autocorrelation bar color
                        color = "royalblue",
                        # Iteration and density fill color
                        fill = "royalblue",
                        # Iteration and density transparency
                        rib_alpha = 0.3,
                        #Trace lines and autocorrelation bar transparency
                        line_bar_alpha = 0.8)
plist[[2]] <-
  plot_mcmc_diagnostics(base_model,
                        key_posteriors[[2]],
                        key_posteriors_titles[[2]],
                        # Trace lines and autocorrelation bar color
                        color = "royalblue",
                        # Iteration and density fill color
                        fill = "royalblue",
                        # Iteration and density transparency
                        rib_alpha = 0.3,
                        #Trace lines and autocorrelation bar transparency
                        line_bar_alpha = 0.8)
plot_grid(plotlist = plist, nrow = 2)
```

(ref:app-mcmc-diag-h-extra-sd-cap) Summary of Markov chain Monte Carlo
diagnostics for steepness (upper panels) and the additional standard
deviation (SD) in the biomass index (lower panels) in the base model.
Sub-panel descriptions as in Figure~\@ref{fig:app-mcmc-diag-m-r0-fig}.

(ref:app-mcmc-diag-h-extra-sd-alt) This figure shows good MCMC diagnostics
for the base model for steepness and the survey extra standard deviation
parameters.

```{r app-mcmc-diag-h-extra-sd-fig, fig.cap = "(ref:app-mcmc-diag-h-extra-sd-cap)", fig.height = 8}

plist <- NULL
plist[[1]] <-
  plot_mcmc_diagnostics(base_model,
                        key_posteriors[[3]],
                        key_posteriors_titles[[3]],
                        # Trace lines and autocorrelation bar color
                        color = "royalblue",
                        # Iteration and density fill color
                        fill = "royalblue",
                        # Iteration and density transparency
                        rib_alpha = 0.3,
                        #Trace lines and autocorrelation bar transparency
                        line_bar_alpha = 0.8)
plist[[2]] <-
  plot_mcmc_diagnostics(base_model,
                        key_posteriors[[4]],
                        key_posteriors_titles[[4]],
                        # Trace lines and autocorrelation bar color
                        color = "royalblue",
                        # Iteration and density fill color
                        fill = "royalblue",
                        # Iteration and density transparency
                        rib_alpha = 0.3,
                        #Trace lines and autocorrelation bar transparency
                        line_bar_alpha = 0.8)
plot_grid(plotlist = plist, nrow = 2)
```
(ref:app-mcmc-diag-dm-cap) Summary of Markov chain Monte Carlo diagnostics
for the Dirichlet-multinomial age-composition parameters for the fishery ($\theta_{\text{fish}}$, upper panels) and the survey ($\theta_{\text{surv}}$,
lower panels) in the base model. Sub-panel descriptions as in Figure~\@ref{fig:app-mcmc-diag-m-r0-fig}.

(ref:app-mcmc-diag-dm-alt) This figure shows good MCMC diagnostics for the
base model for the two Dirichlet-multinomial parameters for the fishery and
survey.

```{r app-mcmc-diag-dm-fig, fig.cap = "(ref:app-mcmc-diag-dm-cap)", fig.height = 8}

plist <- NULL
plist[[1]] <-
  plot_mcmc_diagnostics(base_model,
                        key_posteriors[[5]],
                        key_posteriors_titles[[5]],
                        # Trace lines and autocorrelation bar color
                        color = "royalblue",
                        # Iteration and density fill color
                        fill = "royalblue",
                        # Iteration and density transparency
                        rib_alpha = 0.3,
                        #Trace lines and autocorrelation bar transparency
                        line_bar_alpha = 0.8)
plist[[2]] <-
  plot_mcmc_diagnostics(base_model,
                        key_posteriors[[6]],
                        key_posteriors_titles[[6]],
                        # Trace lines and autocorrelation bar color
                        color = "royalblue",
                        # Iteration and density fill color
                        fill = "royalblue",
                        # Iteration and density transparency
                        rib_alpha = 0.3,
                        #Trace lines and autocorrelation bar transparency
                        line_bar_alpha = 0.8)
plot_grid(plotlist = plist, nrow = 2)
```
(ref:app-mcmc-diag-hists-cap) Summary histograms of MCMC diagnostics for all
base model parameters. The level of autocorrelation in the chain
(distribution across lag times, i.e., distance between samples in the chain,
shown in the top left panel) influences the effective sample size (top right
panel) used to estimate posterior distributions. The Geweke statistic (lower
left panel) tests for equality between means located in the first part of
the chain against means in the last part of the chain. The Heidelberger and
Welch statistic (lower right panel) tests if the sampled values come from
a stationary distribution by comparing different sections of the chain.

(ref:app-mcmc-diag-hists-alt) This figure shows good summary MCMC
diagnostics for all base model parameters.

```{r app-mcmc-diag-hists-fig, fig.cap = "(ref:app-mcmc-diag-hists-cap)", fig.height = 6}

plot_mcmc_diagnostics_all_params(base_model,
                                 show_ro = TRUE,
                                 ro_arrow_lengths = c(10, 20, 7, 20),
                                 ro_text_nudges = c(0.2, 0, -0.55, 0),
                                 ro_text_size = 5)
```

(ref:app-mcmc-pairs-cap) Posterior correlations among the objective
function which is minimized during model fitting, key base-model parameters,
and derived quantities. Numbers refer to the absolute correlation
coefficients, with font size proportional to the square root of the
coefficient.

(ref:app-mcmc-pairs-alt) "This figure shows pairs plots for many parameters
and derived quantities. Natural mortality and log R0 show positive
correlation as do 2014 and 2016 recruitment.

```{r app-mcmc-pairs-fig, fig.cap = "(ref:app-mcmc-pairs-cap)", fig.height = 8}

plot_pairs(base_model,
           type = "key",
           key_posteriors = key_posteriors,
           key_posteriors_titles = key_posteriors_titles,
           recr = c(2014, 2016),
           bratio = end_yr,
           point_size = 0.05,
           forecatch = c(end_yr,
                         end_yr + 1,
                         end_yr + 2))
```

(ref:app-mcmc-pairs-recruit-devs-cap) Posterior correlations among
recruitment deviations from recent years and mean unfished equilibrium
recruitment. Numbers refer to the absolute correlation coefficients, with
font size proportional to the square root of the coefficient.

(ref:app-mcmc-pairs-recruit-devs-alt) This figure shows pairs plots for
many derived quantities. There is some positive correlation between 2014
and 2016 recruitment deviations.

```{r app-mcmc-pairs-recruit-devs-fig, fig.cap = "(ref:app-mcmc-pairs-recruit-devs-cap)", fig.height = 8}

plot_pairs(base_model,
           type = "devs",
           key_posteriors = key_posteriors,
           key_posteriors_titles = key_posteriors_titles,
           recr = (end_yr - 10):(end_yr - 1))
```

\clearpage
