\newpage

\rfoot{Glossary}

# Glossary of terms used in this document {#sec:app-glossary}

\noindent
\leftskip 0.7in
\parindent -0.7in

40:10 adjustment: A reduction in the overall total allowable catch that is
triggered when the female spawning biomass falls below 40% of its unfished
equilibrium level. This adjustment reduces the total allowable catch on a
straight-line basis from the 40% level such that the total allowable catch
would equal zero when the biomass is at 10% of its unfished equilibrium level.
This is one component of the default harvest policy.

Acceptable biological catch (ABC): The acceptable biological catch is a
scientific calculation of the sustainable harvest level of a fishery used
historically to set the upper limit for fishery removals by the Pacific
Fishery Management Council. It is calculated by applying the estimated (or
proxy) harvest rate that produces the maximum sustainable yield from the
estimated vulnerable biomass. For `r sp`, the calculation of the acceptable
biological catch and application of the 40:10 adjustment is now replaced with
the default harvest rate and the total allowable catch.

Adjusted: A term used to describe the total allowable catch or allocations that
account for carryovers of uncaught catch from previous years.

Advisory Panel (AP): The Advisory Panel on `r sp` established by the Agreement.

Agreement ('Treaty'): The Agreement between the government of the United
States and the government of Canada on `r sp`, signed in Seattle, Washington,
on November 21, 2003 and entered into force June 25, 2008.

Alaska Fisheries Science Center (AFSC): One of six regional NOAA Fisheries
Science Centers, primarily in Seattle, Washington but also present
throughout Alaska.

`r b_0`: Unfished equilibrium female spawning biomass.

`r b_10`: The level of female spawning biomass corresponding to 10% of
unfished equilibrium female spawning biomass, i.e., `r b_10` = 0.1`r b_0`. This
is the level below which the calculated total allowable catch is set to 0, based on
the 40:10 adjustment.

`r b_40`: The level of female spawning biomass corresponding to 40% of
unfished equilibrium female spawning biomass, i.e., `r b_40` = 0.4`r b_0`. This
is the level below which the total allowable catch is decreased from the value
associated with `r fspr_40`, based on the 40:10 adjustment.

`r b_msy`: The estimated female spawning biomass which theoretically would
produce the maximum sustainable yield under equilibrium fishing
conditions (constant fishing and average recruitment in every year).

Backscatter: The scattering by a target back in the direction of an acoustic
source. Specifically, the Nautical Area Scattering Coefficient (a measure of
scattering per area) is frequently referred to as backscatter.

Benchmark spawning potential ratio (`r bspr_40`): The spawning potential ratio
of 40%, where 40% relates to the default harvest rate of `r fspr_40` specified in
the Agreement. Even under equilibrium conditions, `r fspr_40` would not
necessarily result in a female spawning biomass of `r b_40` because `r fspr_40` is
defined in terms of the spawning potential ratio that depends on the female
spawning biomass per recruit.

California Current Ecosystem: The waters of the continental shelf and slope
off the west coast of North America, commonly referring to the area from
Central California to Southern British Columbia.

Carryover: If at the end of the year, there are unharvested allocations, then
there are provisions for some of these unharvested allocations to be carried
over into the next year's allocation process. The Agreement states that "If, in
any year, a Party's catch is less than its individual total allowable catch, an
amount equal to the shortfall shall be added to its individual total allowable
catch in the following year, unless otherwise recommended by the Joint
Management Committee. Adjustments under this sub-paragraph shall in no case
exceed 15 percent of a Party's unadjusted individual total allowable catch for
the year in which the shortfall occurred."

Catchability (*q*): The parameter defining the proportionality between a
relative index of abundance (often a fishery-independent survey) and the
estimated abundance available to that survey (as modified by selectivity) in
the assessment model.

Catch-per-unit-effort (CPUE): A raw or, frequently, standardized and
model-based metric of fishing success based on the catch and relative effort
expended to generate that catch. Catch-per-unit-effort is often used as an
index of abundance in the absence of fishery-independent indices and/or where
the two types of indices are believed to be proportional.

Catch target: A general term used to describe the catch value used for
management. Depending on the context, this may be a limit rather than a
target and may be equal to a total allowable catch, an acceptable biological
catch, the median result of applying the default harvest policy, or some other
number. The Joint Technical Committee welcomes input from the Joint Management
Committee on the best terminology to use for these quantities.

Closed-loop simulation: A subset of a management strategy evaluation that
iteratively simulates a population using an operating model, generates data
from that population and passes it to an estimation method, uses the estimation
method and a management strategy to provide management advice, which then feeds
back into the operating model to simulate an additional fixed set of time
before repeating this process.

Coefficient of variation (CV): A measure of uncertainty defined as the
standard deviation divided by the mean.

Cohort: A group of fish born in the same year. Also see recruitment and
year-class.

Constant catch: A catch scenario used for forecasting in which the same
catch is used in successive years.

Default harvest policy (rate): The application of `r fspr_40` with the 40:10
adjustment. Having considered any advice provided by the Joint Technical
Committee, Scientific Review Group, or Advisory Panel, the Joint Management
Committee may recommend a different harvest rate if the scientific evidence
demonstrates that a different rate is necessary to sustain the resource.

Department of Fisheries and Oceans (DFO) Canada: See Fisheries and Oceans
Canada.

Depletion: Prior to the 2015 assessment, depletion was used instead of relative
spawning biomass. 'Relative depletion' was also used.

El Niño: Abnormally warm ocean climate conditions in the California Current
Ecosystem as a result of broad changes in the Eastern Pacific Ocean across the
eastern coast of Latin America (centered on Peru) often around the end of the
calendar year.

Exploitation fraction: A metric of fishing intensity that represents the total
annual catch divided by the estimated population biomass over a range of ages
assumed to be vulnerable to the fishery (set to ages 2$+$ in this assessment;
note that in some previous assessments it was 3$+$). This value is not
equivalent to the instantaneous rate of fishing mortality or the spawning
potential ratio.

`r fspr_40`: The rate of fishing mortality estimated to give a spawning
potential ratio of 40%. Therefore, by definition this satisfies
\begin{align} 
  0.4
    &= \frac{\mbox{spawning biomass per recruit with }`r f_40_for_latex_table`}{\mbox{spawning biomass per recruit with no fishing}},
\end{align}
and SPR (`r f_40`) = 40%. The 40% value is specified in the Agreement.

`r fspr_40_10` harvest policy: The default harvest policy.

Female spawning biomass: The biomass of mature female fish at the beginning of
the year. Sometimes abbreviated to spawning biomass.

Fisheries and Oceans Canada (DFO): Federal organization that delivers programs
and services to support sustainable use and development of Canada's waterways
and aquatic resources. Was previously called Department of Fisheries and
Oceans.

Fishing intensity: A measure of the magnitude of fishing, defined for a
fishing rate (*F*) as:
\begin{align}
  \mbox{fishing intensity for }F &= 1 - \mbox{SPR}(F),
\end{align}
where SPR(*F*) is the spawning potential ratio for the value of *F* accumulated
over the entire year. It is often given as a percentage. Relative fishing
intensity (Figures~\@ref(fig:glossary-fishing-intensity-illustration-fig) and
\@ref(fig:glossary-spr-illustration-fig)) is the fishing intensity relative to
that at the SPR fishing rate `r fspr_40`, where `r fspr_40` is the *F* that gives an
SPR of 40% such that, by definition, SPR(`r f_40`) = 40% (the benchmark
spawning ratio). Therefore
\begin{align}
  (\#eq:appendix-glossary-spr)
  \mbox{relative fishing intensity for }F
    &= \frac{1-\mbox{SPR}(F)}{1-\mbox{SPR}(`r f_40_for_latex_table`)} \\
    &= \frac{1-\mbox{SPR}(F)}{1-0.4} \\
    &= \frac{1-\mbox{SPR}(F)}{0.6}.
\end{align}
For brevity we use `r fspr_40` = SPR(`r f_40`) in the text.
Although this simply equals 40%, it can be helpful to explicitly write:
\begin{align}
  \mbox{relative fishing intensity for }F
    &= \frac{1-\mbox{SPR}(F)}{1-\mbox{SPR}_{40\%}}.
\end{align}

Fishing mortality rate or instantaneous rate of fishing mortality (*F*):
A metric of fishing intensity that is usually reported in relation to the
most highly selected ages(s) or length(s), or occasionally as an average
over an age range that is vulnerable to the fishery. Because it is an
instantaneous rate operating simultaneously with natural mortality, it is
not equivalent to exploitation fraction, percent annual removal, or the
spawning potential ratio.

`r f_msy`: The rate of fishing mortality estimated to produce the maximum
sustainable yield from the population.

Harvest strategy: A formal system for managing a fishery that includes
the elements shown in Figure A.1 of @JTC2015.

Harvest control rule: A process for determining an acceptable biological catch from a stock
assessment. Also see default harvest policy.

Joint Management Committee (JMC): The Joint Management Committee is established
by the Agreement.

Joint Technical Committee (JTC): The Joint Technical Committee is established
by the Agreement. The formal name is 'Joint Technical Committee of the
`r sp`/Whiting Agreement Between the Governments of the United States and
Canada'.

Kilotonne (kt). Metric abbreviation for 1,000 metric tonnes.

Logistic transformation: A mathematical transformation used to translate
between numbers bounded within some range to numbers on the real line
($-\infty$ to $+\infty$).

Magnuson--Stevens Fishery Conservation and Management Act (MSFCMA): The MSFCMA,
sometimes known as the 'Magnuson--Stevens Act', established the 200-mile
fishery conservation zone, the regional fishery management council system, and
other provisions of U.S. marine fishery law.

Management Strategy Evaluation (MSE): A formal process for evaluating
harvest strategies.

Markov chain Monte Carlo (MCMC): A numerical method used to sample from the
posterior distribution of parameters and derived quantities in a Bayesian
analysis. It is more computationally intensive than computing the maximum
likelihood estimate but provides a more accurate depiction of parameter
uncertainty. See @StewartHicksEtAl2013 for a discussion of issues related to
differences between Markov chain Monte Carlo and maximum likelihood estimation.

Maximum sustainable yield (MSY): An estimate of the largest sustainable
annual catch that can be continuously taken over a long period of time
from a population under equilibrium ecological and environmental conditions.

Megatonne (Mt): Metric abbreviation for 1,000,000 metric tonnes.

Metric tonne (t): A unit of mass equal to 1,000 kilograms or 2,204.62 pounds.
Some previous stock assessments used the abbreviation 'mt'.

National Marine Fisheries Service (NMFS): See NOAA Fisheries.

No-U-Turn Sampler (NUTS): An advanced Hamiltonian Bayesian Markov chain Monte Carlo
sampling algorithm used to efficiently create posterior distributions and used
in `r sp` Bayesian assessments beginning in 2021.

NOAA Fisheries: The division of the United States National Oceanic and
Atmospheric Administration (NOAA) responsible for conservation and
management of offshore fisheries (and inland salmon). This is also known
as the National Marine Fisheries Service (NMFS), and both names are commonly
used at this time.

North Pacific Groundfish and Halibut Observer Program Database (NORPAC): A
database that stores data collected at sea by U.S. fishery observers.

Northwest Fisheries Science Center (NWFSC): One of six regional NOAA Fisheries
Science Centers, primarily in Seattle, Washington but also in
various locations in Oregon and Washington.

Not available (NA): Something that is not available, e.g., an entry in a table.

Operating model (OM): A model used to simulate data for use in the management
strategy evaluation. The operating model includes components for the population
and fishery dynamics, as well as the simulation of the data sampling process,
potentially including observation error. Cases in the management strategy
evaluation represent alternative configurations of the operating model.

Pacific Biological Station (PBS): The Pacific Biological Station of Fisheries
and Oceans Canada located in Nanaimo, British Columbia.

Pacific Fisheries Information Network (PacFIN): A database that provides
a central repository for commercial fishery information from Washington,
Oregon, and California.

Pacific Fishery Management Council (PFMC): The U.S. organization under
which historical stock assessments for `r sp` were conducted.

`r sp`: Common name for *`r science_name`*, the species whose offshore
population in the waters of the United States and Canada is subject of this
assessment.

`r common_name`: An alternative name for `r sp` commonly used in the
United States.

Posterior distribution: The probability distribution for parameters or derived
quantities from a Bayesian model representing the result of the prior
probability distributions being updated by the observed data via the likelihood
equation. For stock assessments, posterior distributions are approximated via
numerical methods; one frequently employed method is Markov chain Monte Carlo
sampling.

Prior distribution: A probability distribution for a parameter in a Bayesian
analysis that represents the information available before evaluating the
observed data via the likelihood equation. For some parameters, uninformative
priors can be constructed that allow the data to dominate the posterior
distribution. For other parameters, informative priors can be constructed
based on auxiliary information and/or expert knowledge or opinions.

`r r_0`: Estimated annual recruitment at unfished equilibrium.

Random walk Metropolis Hastings (rwMH): Bayesian Markov chain Monte Carlo
sampling algorithm used to create posterior distributions used in `r sp`
Bayesian stock assessment models prior to 2021.

Recruits/recruitment: the estimated number of new members in a fish
population born in the same age. In this assessment, recruitment is
reported at age~0. See cohort and year-class.

Recruitment deviation: The offset of the recruitment in a given year
relative to the stock--recruitment relationship; values occur on a logarithmic
scale and are relative to the expected recruitment at a given female spawning
biomass.

Relative fishing intensity: See fishing intensity.

Relative spawning biomass: The ratio of the beginning-of-the-year female
spawning biomass to the unfished equilibrium female spawning biomass (`r b_0`).
Thus, lower values are associated with fewer mature female fish. This term was
introduced in the 2015 stock assessment as a replacement for 'depletion'.

Scientific Review Group (SRG): The Scientific Review Group established by
the Agreement.

Scientific and Statistical Committee (SSC): The scientific advisory
committee to the Pacific Fishery Management Council. The Magnuson--Stevens
Fishery Conservation and Management Act requires that each council maintain
a Scientific and Statistical Committee to assist in gathering and analyzing
statistical, biological, ecological, economic, social, and other scientific
information that is relevant to the management of the Council.

Simulation: A model evaluation under a particular state of nature, including
combinations of parameters controlling stock productivity, stock status, and
the time series of recruitment deviations. In this assessment, there are
`r f(num_mcmc_samples)` simulations used to characterize alternative states of
nature, each of which are based on a sample from the posterior distribution of
the parameters, as calculated using Markov chain Monte Carlo, for a particular
model (e.g., the base model).

Spawning biomass: Abbreviated term for female spawning biomass.

Spawning biomass per recruit: The expected lifetime contribution of an
age-0 recruit, calculated as the sum across all ages of the product of
spawning biomass at each age and the probability of surviving to that age.
See Figure~\@ref(fig:glossary-spr-illustration-fig) for a graphical
demonstration of the calculation of this value, which is found in both
numerator and denominator of the spawning potential ratio.

Spawning potential ratio (SPR): The ratio of the spawning biomass per recruit
under a given level of fishing to the estimated spawning biomass per recruit
in the absence of fishing.
<!-- \begin{equation}  -->
<!-- \mbox{SPR}(F) = \frac{\mbox{spawning biomass per recruit with }F}{\mbox{spawning biomass per recruit with no fishing}}. -->
<!-- \end{equation} -->
Often expressed as a percentage, it achieves a value of 100% in the absence
of fishing and declines toward zero as fishing intensity increases
(Figure~\@ref(fig:glossary-spr-illustration-fig)).

Standard deviation (sd): A measure of variability about the mean within a
sample.

Steepness (*h*): A parameter of the stock--recruitment relationship
representing the proportion of `r r_0` expected (on average) when the female
spawning biomass is reduced to 20% of `r b_0` (i.e.,~when relative spawning
biomass is equal to 20%).

Stock Synthesis (SS3): The age-structured stock assessment model applied in
this stock assessment.

Target strength (TS): The amount of backscatter from an individual acoustic
target.

Total allowable catch (TAC): The maximum fishery removal under the terms of
the Agreement.

U.S./Canadian allocation: The division of the total allowable catch as
`r us_allotment_percent`% for the U.S. share and
`r can_allotment_percent`% for the Canadian share.

Vulnerable biomass: The demographic portion of the population available for
harvest by the fishery.

Year-class: A group of fish born in the same year. See 'cohort' and
'recruitment'.

\leftskip 0in
\parindent 0in

(ref:glossary-fishing-intensity-illustration-cap) Fishing intensity as a
function of the spawning potential ratio (SPR; top axis) and 1-SPR (bottom
axis); given the benchmark SPR of 40%, the solid blue line is simply $1/0.6$,
as shown in equation \@ref(eq:appendix-glossary-spr).

(ref:glossary-fishing-intensity-illustration-alt) Fishing intensity linearly
increases with SPR from the origin and passes through 1-SPR of 0.6 and fishing
intensity of 1.0.

```{r glossary-fishing-intensity-illustration-fig, fig.cap = "(ref:glossary-fishing-intensity-illustration-cap)", fig.width = 5}
plot_intensity_illustration(0.4)
```
(ref:glossary-spr-illustration-cap) Illustration of the spawning potential
ratio (SPR) calculation based on the combination of maturity and fecundity used
in the model, using the Markov chain Monte Carlo (MCMC) estimates of natural
mortality, selectivity, and fishing mortality in the final year of the base
model used in this year's assessment. The light blue bars represent unfished
values, the dark blue bars represent fished values.

(ref:glossary-spr-illustration-alt) Numbers per recruit decrease exponentially from
zero. Biomass per recruit peaks at age-3 fish which is the age at which fishing
significantly decreases the value from an unfished state. Overlaying the spawning
biomass per recruit from a fished state over an unfished state to visualize how
SPR is calculated illustrates why it is less than one.

```{r glossary-spr-illustration-fig, fig.cap = "(ref:glossary-spr-illustration-cap)", fig.height = 7, fig.width = 6}
plot_spr_illustration(base_model,
  color = "royalblue",
  yrs = start_yr_age_comps:last_data_yr
)
```

\clearpage
