\newpage

\rfoot{Glossary}

# Glossary of terms and acronyms used in this document {#sec:app-glossary}

\noindent
\leftskip 0.7in
\parindent -0.7in

40:10 adjustment: a reduction in the overall total allowable catch that is
triggered when the female spawning biomass falls below 40% of its unfished
equilibrium level. This adjustment reduces the total allowable catch on a
straight-line basis from the 40% level such that the total allowable catch
would equal zero when the biomass is at 10% of its unfished equilibrium
level. This is one component of the default harvest policy (see below).

ABC: Acceptable biological catch. See below.

Acceptable biological catch (ABC): The acceptable biological catch is a
scientific calculation of the sustainable harvest level of a fishery used
historically to set the upper limit for fishery removals by the Pacific
Fishery Management Council. It is calculated by applying the estimated
(or proxy) harvest rate that produces maximum sustainable yield (MSY,
see below) to the estimated exploitable biomass (the portion of the fish
population that can be harvested). For `r sp`, the calculation of the
acceptable biological catch and application of the 40:10 adjustment is now
replaced with the default harvest rate and the Total Allowable Catch.

Adjusted: A term used to describe Total Allowable Catch or allocations that
account for carryovers of uncaught catch from previous years (see Carryover
below).

Advisory Panel (AP): The advisory panel on `r sp` established by th
e Agreement.

Agreement ('Treaty'): The Agreement between the government of the United
States and the government of Canada on `r sp`, signed at Seattle, Washington,
on November 21, 2003, and entered into force June 25, 2008.

AFSC: Alaska Fisheries Science Center (National Marine Fisheries Service).

`r b_0`: The unfished equilibrium female spawning biomass.

`r b_10`: The level of female spawning biomass corresponding to 10% of
unfished equilibrium female spawning biomass, i.e., `r b_10` = 0.1`r b_0`. This
is the level below which the calculated TAC is set to 0, based on the 40:10
adjustment (see above).

`r b_40`: The level of female spawning biomass corresponding to 40% of
unfished equilibrium female spawning biomass, i.e., ~$`r b_40` = 0.4B_0$.
This is the level below which the calculated TAC is decreased from the value
associated with `r f_40`, based on the 40:10 adjustment (see above).

`r b_msy`: The estimated female spawning biomass which theoretically would
produce the maximum sustainable yield (MSY) under equilibrium fishing
conditions (constant fishing and average recruitment in every year). Also
see `r b_40` (above).

Backscatter: The scattering by a target back in the direction of an acoustic
source. Specifically, the Nautical Area Scattering Coefficient (a measure of
scattering per area) is frequently referred to as backscatter.

Benchmark spawning potential ratio (`r bspr_40`): The spawning
potential ratio of 40%, where the 40% relates to the default harvest rate of
`r f_40` specified in the Agreement. Even under equilibrium conditions,
`r f_40` would not necessarily result in a female spawning biomass of
`r b_40` because `r f_40` is defined in terms of the spawning potential
ratio which depends on the female spawning biomass *per recruit*.

California Current Ecosystem: The waters of the continental shelf and slope
off the west coast of North America, commonly referring to the area from
central California to southern British Columbia.

Carryover: If at the end of the year, there are unharvested allocations, then
there are provisions for an amount of these fish to be carried over into the
next year's allocation process. The Agreement states that "If, in any year,
a Party's catch is less than its individual TAC, an amount equal to the
shortfall shall be added to its individual TAC in the following year, unless
otherwise recommended by the JMC. Adjustments under this sub-paragraph shall
in no case exceed 15 percent of a Party's unadjusted individual TAC for the
year in which the shortfall occurred."

Catchability (*q*): The parameter defining the proportionality between a
relative index of stock abundance (often a fishery-independent survey) and
the estimated stock abundance available to that survey (as modified by
selectivity) in the assessment model.

Catch-per-unit-effort (CPUE): A raw or (frequently) standardized and
model-based metric of fishing success based on the catch and relative effort
expended to generate that catch. Catch-per-unit-effort is often used as an
index of stock abundance in the absence of fishery-independent indices and/or
where the two are believed to be proportional.

Catch target: A general term used to describe the catch value used for
management. Depending on the context, this may be a limit rather than a
target and may be equal to a TAC, an ABC, the median result of applying the
default harvest policy, or some other number. The JTC welcomes input from
the JMC on the best terminology to use for these quantities.

Closed-loop simulation: A subset of an MSE that iteratively simulates a
population using an operating model, generates data from that population and
passes it to an estimation model, uses the estimation model and a management
strategy to provide management advice, which then feeds back into the
operating model to simulate an additional fixed set of time before repeating
this process.

Cohort: A group of fish born in the same year. Also see recruitment and
year-class.

Constant catch: A catch scenario used for forecasting in which the same
catch is used in successive years.

CPUE: Catch-per-unit-effort (see above).

CV: Coefficient of variation. A measure of uncertainty defined as the
standard deviation (SD, see below) divided by the mean.

Default harvest policy (rate): The application of `r f_40` (see below)
with the 40:10 adjustment (see above). Having considered any advice provided
by the JTC, SRG or AP, the JMC may recommend a different harvest rate if
the scientific evidence demonstrates that a different rate is necessary
to sustain the offshore `r sp` resource.

Depletion: Term used for relative spawning biomass (see below) prior to
the 2015 stock assessment. 'Relative depletion' was also used.

DFO: Department of Fisheries and Oceans (Canada). See Fisheries and
Oceans Canada.

El Niño: Abnormally warm ocean climate conditions in the California
Current Ecosystem (see above) as a result of broad changes in the Eastern
Pacific Ocean across the eastern coast of Latin America (centered on Peru)
often around the end of the calendar year.

Exploitation fraction: A metric of fishing intensity that represents the
total annual catch divided by the estimated population biomass over a range
of ages assumed to be vulnerable to the fishery (set to ages $2+$ in this
assessments; note that in previous assessments is was $3+$). This value
is not equivalent to the instantaneous rate of fishing mortality (see
below) or the spawning potential ratio (SPR, see below).

*F*: Instantaneous rate of fishing mortality (or fishing mortality rate);
see below.

`r fspr_40`: The rate of fishing mortality estimated to give a spawning
potential ratio (SPR, see below) of 40%. Therefore, by definition this
satisfies
\begin{align} 
  0.4
    &= \frac{\mbox{spawning biomass per recruit with }`r f_40_for_latex_table`}{\mbox{spawning biomass per recruit with no fishing}},
\end{align}
and SPR(`r f_40`) = 40%. The 40% value is specified in the Agreement.

`r fspr_40_10` harvest policy: The default harvest policy (see above).

Female spawning biomass: The biomass of mature female fish at the beginning
of the year. Sometimes abbreviated to spawning biomass.

Fisheries and Oceans Canada: Federal organization which delivers programs
and services that support sustainable use and development of Canada's
waterways and aquatic resources.

Fishing intensity: A measure of the magnitude of fishing, defined for a
fishing rate *F* as:
\begin{align}
  \mbox{fishing intensity for }F &= 1 - \mbox{SPR}(F),
\end{align}
where SPR(*F*) is the spawning potential ratio for the value of *F*
accumulated over the entire year. It is often given as a percentage.
Relative fishing intensity is the fishing intensity relative to that at
the SPR fishing rate `r f_40`, where `r f_40` is the *F* that gives an
SPR of 40% such that, by definition, SPR(`r f_40`) = 40% (the benchmark
spawning ratio). Therefore
\begin{align}
  (\#eq:appendix-glossary-spr)
  \mbox{relative fishing intensity for }F
    &= \frac{1-\mbox{SPR}(F)}{1-\mbox{SPR}(`r f_40_for_latex_table`)} \\
    &= \frac{1-\mbox{SPR}(F)}{1-0.4} \\
    &= \frac{1-\mbox{SPR}(F)}{0.6},
\end{align}
as shown in Figure~\@ref(fig:glossary-fishing-intensity-illustration-fig).
For brevity we use `r spr_40` = SPR(`r f_40`) in the text.
Although this simply equals 40%, it can be helpful to explicitly write:
\begin{align}
  \mbox{relative fishing intensity for }F
    &= \frac{1-\mbox{SPR}(F)}{1-\mbox{SPR}_{40\%}}.
\end{align}
The calculation of relative fishing intensity is shown graphically in
Figure~\@ref(fig:glossary-spr-illustration-fig).

Fishing mortality rate, or instantaneous rate of fishing mortality (*F*):
A metric of fishing intensity that is usually reported in relation to the
most highly selected ages(s) or length(s), or occasionally as an average
over an age range that is vulnerable to the fishery. Because it is an
instantaneous rate operating simultaneously with natural mortality, it is
not equivalent to exploitation fraction (or percent annual removal; see
above) or the spawning potential ratio (SPR, see below).

`r f_msy`: The rate of fishing mortality estimated to produce the maximum
sustainable yield (MSY) from the stock.

Harvest strategy: A formal system for managing a fishery that includes
the elements shown in Figure A.1 of @JTC2015.

Harvest control rule: A process for determining an ABC from a stock
assessment. Also see default harvest policy (above).

Joint Management Committee (JMC): The joint management committee
established by the Agreement.

Joint Technical Committee (JTC): The joint technical committee established
by the Agreement. The full formal name is 'Joint Technical Committee of
the `r sp`/Whiting Agreement Between the Governments of the United States
and Canada'.

kt: Kilotonne(s). Metric abbreviation for 1,000 metric tonnes

Logistic transformation: A mathematical transformation used to translate
between numbers bounded within some range to numbers on the real line
($-\infty$ to $+\infty$).

Magnuson--Stevens Fishery Conservation and Management Act: The MSFCMA,
sometimes known as the 'Magnuson--Stevens Act', established the 200-mile
fishery conservation zone, the regional fishery management council system,
and other provisions of U.S. marine fishery law.

Management Strategy Evaluation (MSE): A formal process for evaluating
Harvest Strategies (see above).

Markov chain Monte Carlo (MCMC): A numerical method used to sample from the
posterior distribution (see below) of parameters and derived quantities in
a Bayesian analysis. It is more computationally intensive than the maximum
likelihood estimate (see below), but provides a more accurate depiction of
parameter uncertainty. See @StewartHicksEtAl2013 for a discussion of issues
related to differences between MCMC and MLE.

Maximum sustainable yield (MSY): An estimate of the largest sustainable
annual catch that can be continuously taken over a long period of time
from a stock under equilibrium ecological and environmental conditions.

MCMC: Markov chain Monte Carlo (see above).

MSE: Management Strategy Evaluation (see above).

MSY: Maximum sustainable yield (see above).

Mt: megatonne(s). Metric abbreviation for 1,000,000 metric tonnes.

NA: Not available.

National Marine Fisheries Service: See NOAA Fisheries below.

NMFS: National Marine Fisheries Service. See NOAA Fisheries below.

NOAA Fisheries: The division of the United States National Oceanic and
Atmospheric Administration (NOAA) responsible for conservation and
management of offshore fisheries (and inland salmon). This is also known
as the National Marine Fisheries Service (NMFS), and both names are commonly
used at this time.

NORPAC: North Pacific Database Program. A database storing U.S. fishery
observer data collected at sea.

NUTS: No-U-Turn Sampler is an advanced Hamiltonian Bayesian MCMC sampling
algorithm used to efficiently create posterior distributions and used in
`r sp` Bayesian stock assessments beginning in 2021.

NWFSC : Northwest Fisheries Science Center. A NOAA Fisheries Science Center
located primarily in Seattle, Washington, but also in Newport, Oregon and
other locations.

Operating Model (OM): A model used to simulate data for use in the MSE
(see above). The operating model includes components for the stock and
fishery dynamics, as well as the simulation of the data sampling process,
potentially including observation error. Cases in the MSE represent
alternative configurations of the operating model.

OM: Operating Model (see above).

PacFIN: Pacific Coast Fisheries Information Network. A database that
provides a central repository for commercial fishery information from
Washington, Oregon, and California.

PBS: Pacific Biological Station of Fisheries and Oceans Canada (DFO, see
above), located in Nanaimo, British Columbia.

Pacific Fishery Management Council (PFMC): The U.S. organization under
which historical stock assessments for `r sp` were conducted.

`r sp`: Common name for `r science_name`, the species whose offshore
stock in the waters of the United States and Canada is subject of this
assessment.

`r common_name`: an alternative name for `r sp` commonly used in the
United States.

Posterior distribution: The probability distribution for parameters or
derived quantities from a Bayesian model representing the result of the
prior probability distributions (see below) being updated by the observed
data via the likelihood equation. For stock assessments, posterior
distributions are approximated via numerical methods; one frequently
employed method is MCMC (see above).

Prior distribution: Probability distribution for a parameter in a Bayesian
analysis that represents the information available before evaluating the
observed data via the likelihood equation. For some parameters,
uninformative priors can be constructed which allow the data to dominate
the posterior distribution (see above). For other parameters, informative
priors can be constructed based on auxiliary information and/or expert
knowledge or opinions.

*q*: Catchability (see above).

`r r_0`: Estimated annual recruitment at unfished equilibrium.

Recruits/recruitment: the estimated number of new members in a fish
population born in the same age. In this assessment, recruitment is
reported at age~0. See also cohort and year-class.

Recruitment deviation: The offset of the recruitment in a given year
relative to the stock-recruit function; values occur on a logarithmic scale
and are relative to the expected recruitment at a given spawning biomass
(see below).

Relative fishing intensity: See definition of fishing intensity.

Relative spawning biomass: The ratio of the beginning-of-the-year female
spawning biomass to the unfished equilibrium female spawning biomass (`r b_0`,
see above). Thus, lower values are associated with fewer mature female fish.
This term was introduced in the 2015 stock assessment as a replacement
for 'depletion' (see above) which was a source of some confusion.

rwMH: Random walk Metropolis Hastings Bayesian MCMC sampling algorithm
used to create posterior distributions used in `r sp` Bayesian stock
assessment models prior to 2021.

Scientific Review Group (SRG): The scientific review group established by
the Agreement.

Scientific and Statistical Committee (SSC): The scientific advisory
committee to the PFMC. The Magnuson--Stevens Act requires that each council
maintain an SSC to assist in gathering and analyzing statistical,
biological, ecological, economic, social, and other scientific information
that is relevant to the management of council fisheries.

SD: Standard deviation. A measure of variability within a sample.

Simulation: A model evaluation under a particular state of nature, including
combinations of parameters controlling stock productivity, stock status,
and the time series of recruitment deviations. In this assessment,
there are `r f(num_mcmc_samples)` simulations used to characterize
alternative states of nature, each of which are based on a sample from the
posterior distribution of the parameters, as calculated using MCMC, for a
particular model (e.g., the base model).

Spawning biomass: Abbreviated term for female spawning biomass (see above).

Spawning biomass per recruit: The expected lifetime contribution of an
age-0 recruit, calculated as the sum across all ages of the product of
spawning biomass at each age and the probability of surviving to that age.
See Figure~\@ref(fig:glossary-spr-illustration-fig) for a graphical
demonstration of the calculation of this value, which is found in both
numerator and denominator of the Spawning potential ratio (SPR, see below).

Spawning potential ratio (SPR): The ratio of the spawning biomass per recruit
under a given level of fishing to the estimated spawning biomass per recruit
in the absence of fishing; i.e.~for fishing mortality rate *F*
<!-- \begin{equation}  -->
<!-- \mbox{SPR}(F) = \frac{\mbox{spawning biomass per recruit with }F}{\mbox{spawning biomass per recruit with no fishing}}. -->
<!-- \end{equation} -->
Often expressed as a percentage, it achieves a value of 100% in the absence
of fishing and declines toward zero as fishing intensity increases. See
Figure~\@ref(fig:glossary-spr-illustration-fig) for a graphical demonstration
of the calculation of SPR.

SPR: Spawning potential ratio (see above).

`r spr_40`: See benchmark spawning potential ratio.

SS: Stock Synthesis (see below).

Steepness (*h*): A stock-recruit relationship parameter representing the
proportion of `r r_0` expected (on average) when the female spawning biomass
is reduced to 20% of `r b_0` (i.e.,~when relative spawning biomass is equal
to 20%).

Stock Synthesis (SS): The age-structured stock assessment model applied in
this stock assessment.

t: Metric tonne(s). A unit of mass (often referred to as weight) equal to
1,000 kilograms or 2,204.62 pounds. Some previous stock assessments used
the abbreviation 'mt' (metric tonnes).

Target strength (TS): The amount of backscatter from an individual acoustic
target.

TAC: Total allowable catch (see below).

Total allowable catch (TAC): The maximum fishery removal under the terms of
the Agreement.

U.S./Canadian allocation: The division of the total allowable catch of
`r us_allotment_percent`% as for the U.S. share and
`r can_allotment_percent`% for the Canadian share.

Vulnerable biomass: The demographic portion of the stock available for
harvest by the fishery.

Year-class: A group of fish born in the same year. See also 'cohort' and
'recruitment'.

\leftskip 0in
\parindent 0in

(ref:glossary-fishing-intensity-illustration-cap) Fishing intensity as a function
of SPR (top axis) and 1-SPR (bottom axis); given the benchmark SPR of 40%,
the solid blue line is simply $1/0.6$, as shown in equation
\@ref(eq:appendix-glossary-spr).

(ref:glossary-fishing-intensity-illustration-alt) This figure shows how fishing
intensity linearly increases with SPR.

```{r glossary-fishing-intensity-illustration-fig, fig.cap = "(ref:glossary-fishing-intensity-illustration-cap)", fig.width = 5}

plot_intensity_illustration(0.4)
```
(ref:glossary-spr-illustration-cap) Illustration of the spawning potential ratio
(SPR) calculation based on the combination of maturity and fecundity used
in the model, using the MCMC estimates of natural mortality, selectivity,
and fishing mortality in the final year of the base model used in this
year's assessment.

(ref:glossary-spr-illustration-alt) This figure shows how SPR is calculated.

```{r glossary-spr-illustration-fig, fig.cap = "(ref:glossary-spr-illustration-cap)", fig.height = 7, fig.width = 6}

plot_spr_illustration(base_model,
                      color = "royalblue",
                      yrs = start_yr_age_comps:last_data_yr)
```

\clearpage
