\newpage

\rfoot{U.S. fishery report}

<!-- \titleformat{\section}[display] -->
<!--   {\normalfont\Large\bfseries}{\appendixname\enspace\thesection}{.5em}{} -->

# Report of the `r assess_yr - 1` `r sp` fishery in the United States {#sec:app-us-fishery-report}

**Prepared by the United States Advisory Panel on 17 January 2024 for inclusion in this assessment document.**

Based on data from the Pacific Fisheries Information Network (PacFIN), total
U.S. harvest in the 2023 whiting fishery was 240,189~t, which is 52% of the
U.S. allocation of 461,750~t. Total U.S. harvest from these same sectors in
the 2022 whiting fishery was 289,726~t. Compared to 2022, total U.S. catch
was down 17% in 2023 (see Tables below).

**Shoreside (SS) Fishery:**
Spring fishing in the SS sector started strong shortly after May 1 but
slowed considerably by the end of May, and didn't pick back up until later
in the year. Spring fishing was described as very spotty for both the fleet
fishing around the Columbia River and north, as well as the fleet fishing out
of Newport, Oregon. By June, almost all of the fish were observed to be off
Newport and well to the south. The most consistent volumes in the SS fishery
were observed from late June to early September, and the majority of the SS
late summer and fall fishery occurred off the central OR coast and closer to
the California border. Fishing in the SS sector slowed by October, which is normal.

Larger fish were reported further north during the times when fish were up north.
The fleet fishing north of the Columbia River and in WA landed fish as large as 900
grams. Fish caught off the south coast of OR and CA were reported to be sub-450 gram
at best and got smaller later in the season.

Bycatch encounters in the SS sector consisted primarily of Chinook salmon, sablefish,
darkblotched rockfish, yellowtail rockfish, and some mackerel off Newport late in the
season. The SS whiting cooperative implemented several hot spot closures/advisory areas
during the season to avoid/minimize bycatch.

Overall, the total 2023 SS whiting catch (100,392~t) represented 56% of the 2023 SS
allocation and was slightly lower than total 2022 SS catch (104,323~t).

**At-Sea Fishery:**
The U.S. at-sea fishery is comprised of the Mothership (MS) and Catcher
Processor (CP) sectors.

_Mothership (MS) Sector_ -- In the spring fishery, one MS fleet was on the
grounds on May 2, and another joined on May 10. Two other platforms joined
on May 15. Spring fishing was strong until late May, and all four MS fleets
concluded operations by May 30.

The size of whiting in the MS spring fishery generally ranged from 400-600
grams. However, location of fish further south and in shallower waters during
the spring increased bycatch. By the end of May, slower fishing rates combined
with high bycatch encounters and restrictive bycatch movement rules led to an
early end to the spring fishery for the MS sector.

In the “fall” fishery (which began mid-summer this year), one MS fleet was on
the grounds on August 11, with another joining on September 27. Fall catch
occurred primarily off of Oregon, with clean fishing and low bycatch encounters,
but smaller fish size, averaging around 300 grams. The 2023 MS fishery concluded
on November 1.

Overall, the total 2023 MS sector catch (32,744~t) represented 32% of the 2023
MS allocation and was significantly lower than the total 2022 MS catch
(59,157~t). Four out of six MS platforms participated in the 2023 fishery,
with one MS platform changing ownership mid-year.

_Catcher Processor (CP) Sector_ -- In the spring fishery, the first CPs were
on the grounds on May 5. The CP sector ended their spring fishery the first
week of June, as vessels transition to the Alaska pollock fishery which begins
June 10. Overall, spring whiting harvest rates for the CPs were lower as fish
were mostly absent from the WA and northern OR coastlines. Whiting were mainly
schooled in southern OR and shallower than previous years. The shoreward and more
shallow distribution of whiting contributed to much higher levels of incidental catch.
The CPs observed higher encounters with Chinook salmon compared to previous years
and record high encounters with some rockfish species during the spring fishery.
The average whiting size in the spring CP fishery was approximately 450 grams.

The fall fishery began with the first CPs arriving in OR late August and continued
through the beginning of November. Unlike spring fishing efforts, the fall was a
turnaround for whiting harvest levels. A greater abundance of whiting were seen
further north into OR and more normal depths. Southern OR exhibited steady fishing
with good catch per unit effort (CPUE), and far lower bycatch than the spring fishery.
Overall, there was very little CP catch and effort off Washington. The observed fish
size in the fall fishery was smaller compared to the spring fishery, averaging
approximately 350 grams.

Overall, the total 2023 CP sector catch (107,053~t) represented 74% of the 2023 CP
allocation and was lower than total 2022 CP catch (126,247~t), due to two vessels
not participating during the 2023 whiting fishery. One CP vessel underwent repairs
during the fall. Another vessel experienced a fire and was not operational in the
whiting fishery this year.

```{r us-ap-catch-tab, results = "asis", echo = FALSE}
d <- tibble(` ` = c("Allocation (t)",
                    "Catch (t)",
                    "Utilization (%)"),
            `U.S. TAC` = c(461000,
                           240190,
                           52.1),
            `Shoreside` = c(178581,
                            100392,
                            56.2),
            `Catcher Processor` = c(144566,
                                    107053,
                                    74.1),
            `Mothership` = c(102047,
                             32744,
                             32.1),
            `Tribal` = c(35806,
                         0,
                         0.0)) |> 
  mutate(across(-` `, ~{.x <- ifelse(row_number() == n(),
                                     paste0(f(.x, 1), "%"),
                                     f(.x))}))

kbl(d,
    align = "lrrrrr",
    format = "latex",
    booktabs = TRUE,
    caption = paste0("Final 2023 allocations (after reallocation of tribal ",
                     "quota) and catch totals (tonnes, t). Note that ",
                     "461,750 t U.S. TAC is reduced by 750 t for research ",
                     "and incidental catch set. Minor differences in catch ",
                     "in this table compared to that used in the stock ",
                     "assessment can occur due to the timing of data ",
                     "extractions. Source: PacFIN Whiting Report.")) |> 
  row_spec(0, bold = TRUE) |> 
  column_spec(1, bold = TRUE)
  
```

```{r us-ap-catch-prev-tab, results = "asis", echo = FALSE}
d <- tibble(` ` = c("Allocation (t)",
                    "Catch (t)",
                    "Utilization (%)"),
            `U.S. TAC` = c(401896,
                           289726,
                           72.1),
            `Shoreside` = c(156002,
                            104323,
                            66.9),
            `Catcher Processor` = c(126287,
                                    126247,
                                    100),
            `Mothership` = c(89144,
                             59157,
                             66.4),
            `Tribal` = c(30463,
                         1174,
                         3.9)) |> 
  mutate(across(-` `, ~{.x <- ifelse(row_number() == n(),
                                     paste0(f(.x, 1), "%"),
                                     f(.x))}))

kbl(d,
    align = "lrrrrr",
    format = "latex",
    booktabs = TRUE,
    caption = paste0("Final 2022 allocations (after reallocation of tribal ",
                     "quota) and catch totals (tonnes, t). Note that ",
                     "402,646 t U.S. TAC is reduced by 750 t for research ",
                     "and incidental catch set. Minor differences in catch ",
                     "in this table compared to that used in the stock ",
                     "assessment can occur due to the timing of data ",
                     "extractions. Source: 2023 Whiting Stock Assessment Report ",
                     "and PacFIN Whiting Report.")) |> 
  row_spec(0, bold = TRUE) |> 
  column_spec(1, bold = TRUE)
  
```

\clearpage