\newpage

\rfoot{Maturity analysis}

# Modeling temporal and spatial trends in hake maturity-at-age data {#sec:app-maturity-analysis}

Contributed by Melissa A. Head, Kelli F. Johnson, Kristin N. Marshall, and Eric
J. Ward.

## Methods

### Data filtering

We assembled a dataset representing hake functional maturity collected from
three sources, the West Coast Groundfish Bottom Trawl Survey (WCGBTS; Keller et
al. 2017), the Northwest Fisheries Science Center Integrated Pacific Hake
Ecosystem and Acoustic-Trawl  Survey, and gonad tissue samples from the At-Sea
Hake Observer program (ASHOP). The first two sources represent
fishery-independent samples, while ASHOP samples are fishery dependent. After
filtering, this dataset consisted of 2836 samples, from years 2009 to 2021
(Table \@ref(tab:app-maturity-analysis-sampling-platform-tab);
Figure \@ref(fig:app-maturity-analysis-sampling-platform-age-years-fig)
). An additional 180 samples exist with unknown ages and 394 samples exist with
uncertain functional maturity; but, these were omitted from our analysis.
Similarly, there are 73 samples that were collected in British Columbia (72 of
73 mature; 70 of 73 age 5 or older) but they have limited temporal coverage
(primarily 2013, 2015) and were omitted from our analysis.
Note that these samples from British Columbia were included in the 2018
analysis of maturity-at-age that was previously included in the fecundity
relationship.

### Statistical modeling

As each sample in our dataset is geo-referenced with a unique latitude and
longitude, we constructed a series of spatiotemporal models to model variation
in `r sp` maturity. Our statistical modeling framework can be seen as a
version of generalized linear mixed model (GLMM), with a series of fixed
and random components. We constructed three models to test hypotheses and
help improve understanding of spatiotemporal variability in `r sp` maturity;
these models can generally be described as

1. a null model representing the status quo, similar to models used in previous
  `r sp` assessments but with additional data and an effect for calendar day;

1. a spatiotemporal model incorporating temporal and spatial trends but no
   covariates;

1. a spatiotemporal model incorporating temperature as an environmental
   predictor.

To maintain consistency with the status quo, our null model contained no spatial
or temporal variation. We included quadratic effects of age (to account for
potential skip spawning of older individuals), a smooth effect of calendar day
(modeled with a penalized regression or P-spline; Eilers and Marx 1996), and a
linear offset corresponding to the ASHOP samples (allowing for differences
between fishery independent and dependent samples). Previous `r sp` assessments
have not allowed maturity to vary over time or space and have not estimated
coefficients corresponding to ASHOP samples. Earlier versions of our first model
also included offsets allowing for differences between the WCGBTS and
Acoustic-Trawl samples, however these estimates were small in magnitude and had
large standard errors, which suggests there were not meaningful differences
between these sampling platforms. The null model can be written as
\begin{align}
E[\bm{y}] = g^{-1} \left( \bm{X} \bm{\beta} + \bm{Z} \bm{b}  \right)
\end{align}
where $g^{-1}()$ represents the inverse logit function, $\bm{X}$ represents the
design matrix of fixed effects with estimated parameters $\bm{\beta}$, and the
P-spline is represented with random effect design matrix $\bm{Z}$ and
corresponding coefficients $\bm{b}$.

As a second model, we extended our null model to include spatial and temporal
variation. We modeled year effects (intercepts) with a time-varying AR(1) random
walk. Spatial effects were modeled using the stochastic partial differential
equation (SPDE) approximation to Gaussian Random Fields [@LindgrenEtAl2011].
This approach can be seen as a predictive process method, where a
spatial surface is approximated by a series of estimated random effects
(locations referred to knots or vertices) which are then projected to locations
of sample collections. Our mesh representing the spatial field used a cutoff
distance of 50 km, resulting in 97 mesh vertices. Due to the sparsity of data in
some years, we only considered models with spatial, and not spatiotemporal,
fields. However, to account for interactions between space and age, we also
included spatially varying coefficients in age effects, as a quadratic
relationship (spatial fields for the intercept, age, age$^2$). This model can
be written as
\begin{align}
E[\bm{y}] = g^{-1} \left( \bm{X} \bm{\beta} + \bm{Z} \bm{b} + \bm{\omega}_{s} +
	\bm{x}_{age} * \bm{\zeta}_{s,age} + \bm{x}_{age^{2}} * \bm{\zeta}_{s,age^{2}} +
	\bm{X}^{tvc}_{t} \bm{\gamma_t} \right)
\end{align}
where new components $\bm{\omega}_{s}$ represent a constant spatial field shared
across years (analogous to a spatial intercept), $\bm{\zeta}_{s,age}$ and
$\bm{\zeta}_{s,age^{2}}$ represent spatially varying coefficient effects of age,
and $\bm{X}^{tvc}_{t}$ represents the design matrix of year effects with
estimated coefficients $\bm{\gamma_t}$. The $\bm{\gamma_t}$
terms were modeled as AR(1) terms such as in the example $\gamma_{2010} \sim
N\left(\rho\gamma_{2009}, \sqrt{1-\rho^{2}}\sigma \right)$, where $\rho$
represents the AR(1) parameter.

Our third model also extended the null model to include an estimated spatial
field and spatially varying coefficients for the quadratic function of age; but,
instead of modeling year effects as a random walk, year effects were modeled as a
function of subsurface (at 130.67 m; see below for details) temperature indices
in the domain of the WCGBTS survey. Replacing random year effects with a
temperature covariate has the potential to add mechanistic relationships to the
modeling and also reduce uncertainty in years where no or few samples are
collected. We explored several forms of the temperature relationship, including
linear, quadratic, or P-splines and chose to use quadratic relationships
because these introduced fewer parameters than P-splines, while also allowing
for parabolic relationships. This model can be written in the same form as
Model 2, without the time varying intercept,
\begin{align}
E[\bm{y}] = g^{-1} \left( \bm{X} \bm{\beta} + \bm{Z} \bm{b} + \bm{\omega}_{s} +
\bm{x}_{age} * \bm{\zeta}_{s,age} + \bm{x}_{age^{2}} * \bm{\zeta}_{s,age^{2}} \right)
\end{align}
where the added quadratic effects of temperature are in the fixed effects
components $\bm{X}$ and $\bm{\beta}$.

Parameter estimation was done using the \texttt{sdmTMB} package (Anderson et
al. 2022) in R (R Core Development Team 2024). \texttt{sdmTMB} provides a
convenient interface between R and Template Model Builder (TMB; Kristensen
et al. 2016), which allows for fast marginal maximum likelihood estimation.
Model convergence was assessed by examining the Hessian and standard errors
of parameter estimates and the maximum gradient at convergence. Area under
the curve (AUC) estimates were also calculated using the \texttt{pROC}
package (Robin et al. 2011) in R.

### Deriving temperature indices

Subsurface ocean temperature has previously been linked to `r sp` distribution
(Malick et al. 2020) and co-occurrence of `r sp` with prey (Phillips et al. 2003);
and, more recently, marine heat waves have been found to delay maturity in other
groundfish species (Rosemond 2023). Given that temperature sampling is not done
from all sampling platforms, we relied on modeled temperature
products. Specifically, we used sea water potential temperature (referred to as
'temperature' throughout) from the \texttt{GLORYS12v1} product (1/12°
resolution, 50 vertical levels, Global Ocean Physics Reanalysis for
1993--September 2023 and Global Ocean Physics Analysis and Forecast for October
2023--January 2024; Global Ocean Physics Reanalysis 2024, Global Ocean
Physics Analysis and Forecast 2024; Lellouche et al. 2021). We processed
monthly averages of temperature and used data from a subset of depths
corresponding to the vertical distribution of `r sp` (25.21 m, 40.34 m,
55.76 m, 77.85 m, 92.33 m, 109.73 m, 130.67 m). These data show that, as
expected, temperature generally decreases with depth
(Figure \@ref(fig:app-maturity-analysis-temp-depth-fig)) and unlike
surface temperature, which is warmest in summer months, the warmest temperatures
at depth often occur in winter 
(Figure \@ref(fig:app-maturity-analysis-raw-feb-temp-fig)).
Data from each month--depth combination was alternately used to generate annual
indices of temperature to relate to maturity. As a final stratification, we
also considered indices generated using
(1) coastwide GLORYS12v1 temperatures,
(2) temperature north of Point Conception,
and (3) temperature south of Point Conception.

Rather than take a spatial average of temperature by year for each month--depth
combination, we generated biomass weighted averages of temperature (weighting
temperature by the spatial distribution of `r sp` biomass, rather than weighting
each spatial location equally). To generate biomass weights, we constructed a
spatial model of `r sp` catch per unit effort (CPUE, kg / km$^2$), using 2003--2023
data from the WCGBTS. We adopted the same SPDE approach used in modeling
maturity. Our biomass model included a smooth effect of calendar day (as a
P-spline, dates range from May--October), a time varying intercept modeled with
a random walk, a spatial field (representing spatial variation shared across
years), and spatiotemporal variation (representing year to year variation in
spatial patterning) modeled as an AR(1) process. Given the skewed distribution
of catches, we modeled CPUE with a Tweedie distribution (Shono 2008). We
identified spatial cells from the GLORYS12v1 re-analysis that were in the
spatial domain of the WCGBTS (Keller et al. 2017) and made predictions of
biomass to those cells on July 1 of each year (July 1 was arbitrarily chosen as
a date in the middle of the WCGBTS survey).  Because of the random walk model
for year effects, our predictions of `r sp` biomass in future years 2024--2025
are identical to 2023. Temperature indices were then generated by taking a
weighted average of temperature across space, with estimated `r sp` biomass used
as weights. As the WCGBTS survey only provides an annual snapshot of biomass,
the same biomass weights were used for all depths and months with temperature
data. In general, weighted indices remained highly correlated with unweighted
temperature indices ($\rho$ = 0.98 across all depths and months;
Figure \@ref(fig:app-maturity-analysis-temp-weight-effect-fig)).

## Model selection and sensitivity analysis

We performed two main sensitivity analyses across the three models used.
First, we evaluated the sensitivity of our model selection results to include
(or not) the fishery dependent ASHOP samples. Second, we evaluated a
sensitivity to including samples south of Point Conception (previous maturity
modeling has imposed a cutoff and did not include samples south of Point
Conception). After ensuring that models converged (using the `sanity()`
function in \texttt{sdmTMB}), we evaluated the relative support of models using
Akaike information criterion (AIC; Akaike 1973). Similarly, alternative
temperature indices were also compared using AIC, and the model(s) with the
lowest AIC values were deemed to have the most support.

### Generation of annual maturity at age

To create a single index of maturity for each age--year combination and
generate maturity ogives, we used results from the best model selected with
temperature as a driver alongside model results for Models 1--2. For each of
these three models, we generated model predictions onto the WCGBTS design grid
for non-ASHOP samples (with a larger intercept, ASHOP samples have earlier
maturity at age) on the 278th day of the year or October 5th
(Table \@ref(tab:app-maturity-analysis-estimates-tab)).
Rather than take a simple average of these estimates (which weights each
spatial cell equally), we calculated a weighted average, using biomass
weights. Biomass was predicted using the same spatiotemporal model fit to
the WCGBTS CPUE data, used in generating weighted indices of temperature.
Weights were applied to estimated probabilities of maturity in logit space,
and the total weighted average for each age--year combination was converted
to normal space with an inverse logit transformation.

## Results

Comparing the spatiotemporal model of `r sp` maturity to the baseline model
representing the status quo provides an evaluation of support for maturation
varying over time and space. In our comparison, most models showed greater
support for models that included spatiotemporal processes than the null model
(Table \@ref(tab:app-maturity-analysis-aic-tab)). Similarly, we found that
the model with the temperature index to predict year effects received the
most support when ASHOP samples were included and data south of Pt.
Conception were excluded
(Table \@ref(tab:app-maturity-analysis-aic-tab); AIC > 10).
For other analysis with different subsets of data, the time varying random
walk model without temperature as a driver received more support. For
consistency with previous `r sp` stock assessment models, we focus the
remainder of our results on models that were only fit to data north of Point
Conception and included the ASHOP samples.

All three models estimated a similar quadratic effect of age and higher
maturity at age in ASHOP samples
(Table \@ref(tab:app-maturity-analysis-estimates-tab)). All three models had
similar high AUC values (Model 1 = 0.951, Model 2 = 0.963, Model 3 = 0.962)
indicating high abilities to discriminate between whether or not `r sp` are
mature. Similarly, all three models estimated similar effects of calendar day, 
with a rapid increase in maturity estimated in summer months
(Figure \@ref(fig:app-maturity-analysis-day-of-year-fig)).

For models that include spatiotemporal variation, we found similar patterns of
year effects and spatial variation. Year effects from the time varying model
without temperature indicated lower than average maturity in a number of years,
including 2012, 2016, and 2019
(Figure \@ref(fig:app-maturity-analysis-year-effects-nocovar-fig)). Including
spatially varying coefficients of age allowed each age to differ slightly;
but, in general, spatial patterning was similar across ages
(Figure \@ref(fig:app-maturity-analysis-predicted-maps-byage-fig)). Biomass
weighted predictions of maturity also appeared similar between the
spatiotemporal models with and without temperature effects
(Figure \@ref(fig:app-maturity-analysis-temp-model-sensitivities-fig)). The
largest differences between these models appeared to be in years like 2016,
when the temperature driven model predicts maturation rates lower than the
random walk model (the classification ability of these models in 2016 was
nearly identical, AUC = 0.957 for both;
Figure \@ref(fig:app-maturity-analysis-model-comparison-fig)).

The estimated marginal effect of temperature in our best model (Tables
\@ref(tab:app-maturity-analysis-aic-tab) and
\@ref(tab:app-maturity-analysis-estimates-tab))
indicated a concave relationship between temperature and functional maturity
(Figure \@ref(fig:app-maturity-analysis-temp-marginal-fig)). Temperatures in
2018 and 2020 were near the peak of this relationship, while most years
were cooler (maturity increasing with temperature over this region).
Temperatures in 2016 and 2019 were high
(Figures \@ref(fig:app-maturity-analysis-temp-depth-fig)--\@ref(fig:app-maturity-analysis-temp-weight-effect-fig)),
above the threshold corresponding to the peak of the temperature--maturity
relationship, and maturity at age was estimated to decline in these years.
Contrasts between years can also be seen in the estimated ogives
(Figure \@ref(fig:app-maturity-analysis-age-marginal-fig)) with a delay in
maturity occurring in years that are both cooler and warmer than 2020 (age
at 50% maturity = 2.81 in 2020, versus 3.58 in 2012 or 3.82 in 2016).

The estimate of the spatial variance for the model used to weight spatial 
estimates based on estimated biomass of `r sp` was higher than the estimate
of the spatiotemporal variance suggesting that differences in locations are
more prominent than differences in locations between years
(Table \@ref(tab:app-maturity-analysis-biomass-tab)).
That is, `r sp` have a patchy distribution but those patches appear in largely
the same locations year after year. The center of gravity of the distribution
was furthest to the north in years that correspond to high temperatures and
subsequent decreases in maturity
(Figure \@ref(fig:app-maturity-analysis-cog-latitude-fig)).

## Citations

Akaike, H. 1973. Information theory and an extension of the maximum likelihood principle. In B.N. Petrov and F. Csaki (Eds.), Second International Symposium on Information Theory (pp. 267--281). Budapest: Akademiai Kiado.

Anderson, S.C., Ward, E.J., English, P.A., and Barnett, L.A.K. 2022. sdmTMB: an R package for fast, flexible, and user-friendly generalized linear mixed effects models with spatial and spatiotemporal random fields. bioRxiv 2022.03.24.485545. https://doi.org/10.1101/2022.03.24.485545

Eilers, P.H.C., and Marx, B.D. 1996. Flexible smoothing with B-splines and penalties. Statistical Science, 11(2): 89--121. https://doi.org/10.1214/ss/1038425655

Global Ocean Physics Reanalysis. 2024. E.U. Copernicus Marine Service Information (CMEMS). Marine Data Store (MDS). Retrieved January 10, 2024, from https://doi.org/10.48670/moi-00021

Global Ocean Physics Analysis and Forecast. 2024. E.U. Copernicus Marine Service Information (CMEMS). Marine Data Store (MDS). Retrieved January 10, 2024, from https://doi.org/10.48670/moi-00016

Keller, A.A., Wallace, J., and Methot, R. 2017. NWFSC's West Coast groundfish bottom trawl survey: History, design, description. U.S. Dept. Comm., NOAA Tech. Memo. NMFS-NWFSC-136.

Kristensen, K., Nielsen, A., Berg, C.W., Skaug, H., and Bell, B.M. 2016. TMB: Automatic Differentiation and Laplace Approximation. Journal of Statistical Software, 70(5): 1--21. https://doi.org/10.18637/jss.v070.i05

Lellouche, J.-M., Greiner, E., Bourdallé-Badie, R., Garric, G., Melet, A., Drévillon, M., Bricaud, C., Hamon, M., Le Galloudec, O., Regnier, C., Candela, T., Testut, C.-E., Gasparin, F., Ruggiero, G., Benkiran, M., Drillet, Y., and Le Traon, P.-Y. 2021. The Copernicus Global 1/12° Oceanic and Sea Ice GLORYS12 Reanalysis. Frontiers in Earth Science, 9. https://doi.org/10.3389/feart.2021.698876

Lindgren, F., Rue, H., and Lindström, J. 2011. An explicit link between Gaussian fields and Gaussian Markov random fields: The stochastic partial differential equation approach. Journal of the Royal Statistical Society Series B: Statistical Methodology 73: 423--498. https://doi.org/10.1111/j.1467-9868.2011.00777.x

Malick, M. J., Hunsicker, M. E., Haltuch, M. A., Parker-Stetter, S. L., Berger, A. M., and Marshall, K. N. 2020. Relationships between temperature and Pacific hake distribution vary across latitude and life-history stage. Marine Ecology Progress Series 639: 185--197. https://doi.org/10.3354/meps13286

Phillips, E. M., Malick, M. J., Gauthier, S., Haltuch, M. A., Hunsicker, M. E., Parker-Stetter, S. L., and Thomas, R. E. 2023. The influence of temperature on Pacific hake co-occurrence with euphausiids in the California Current Ecosystem. Fisheries Oceanography 32(3): 267--279. https://doi.org/10.1111/fog.12628

R Core Team. 2024. R: A Language and Environment for Statistical Computing. R Foundation for Statistical Computing, Vienna, Austria. https://www.R-project.org/

Robin, N., Turck, N., Hainard, A., Tiberti, N., Lisacek, F., Sanchez, J.C., and Müller, M. 2011.
pROC: an open-source package for R and S+ to analyze and compare ROC curves. BMC Bioinformatics 12: 77. https://doi.org/10.1186/1471-2105-12-77

Rosemond, R.C. 2023. Influence of novel ocean conditions on life history characteristics of a nearshore rockfish with implications for population assessment and management. Oregon State University. URL: https://ir.library.oregonstate.edu/concern/graduate_thesis_or_dissertations/8p58pp02d

Shono, H. 2008. Application of the Tweedie distribution to zero-catch data in CPUE analysis. Fisheries Research 93(1--2): 154--162. https://doi.org/10.1016/j.fishres.2008.03.006

\clearpage

## Tables

```{r app-maturity-analysis-sampling-platform-tab, results = "asis", echo = FALSE}

# Adapting from table_assessment_changes(); don't need function as these tables
# are one-offs.
d <- tribble(~Platform , ~"2009", ~"2012", ~"2013", ~"2014",
             ~"2015", ~"2016", ~"2017", ~"2018", ~"2019", ~"2021",
"ASHOP", 0, 0, 135, 196, 131, 194, 177, 0, 0, 0,
"Acoustic", 0, 181, 186, 0, 160, 131, 57, 54, 59, 68,
"WCGBT", 244, 64, 63, 197, 216, 66, 102, 109, 46, 0)

# Keep this in case need extra formatting.
#  col_names <- c("Year",
#                  "Framework",
#                  "Survey",
#                  "Comp\nMethod",
#                  "Num.\nMCMC\nsamples",
#                  "Change")

# Insert custom header fontsize before linebreaker
#   if(is.null(header_font_size)){
#     header_font_size <- font_size
#   }
#   hdr_font_str <- create_fontsize_str(header_font_size,
#                                       header_vert_spacing,
#                                       header_vert_scale)
#   col_names <- gsub("\\n", paste0("\n", hdr_font_str$quad), col_names)
#   col_names <- paste0(hdr_font_str$dbl, col_names)
# Add \\makecell{} latex command to headers with newlines
#   col_names <- linebreaker(col_names, align = "c")

  kbl(d,
      format = "latex",
      position = "h",
      booktabs = TRUE,
      align = c("l", "r", "r", "r", "r", "r", "r", "r", "r", "r", "r"),
      linesep = "",
      # col.names = col_names,
      escape = FALSE,
      caption = paste0("Samples included in our analysis (after ",
                       "filtering), by sampling platform and year.")) |>
    row_spec(0, bold = TRUE) |>
#    column_spec(ncol(d), width = "5cm") |>
    kable_styling(font_size = 12,
                  latex_options = c("repeat_header"))
```

```{r app-maturity-analysis-aic-tab, results = "asis", echo = FALSE}
d2 <- tribble(
  ~"ASHOP", ~"Include South", ~"Model 1", ~"Model 2", ~"Model 3",
  "Y", "Y", 1440.12, latex_bold("1334.68"), "1366.41",
  "Y", "N", 1277.58, "1209.28", latex_bold("1195.94"),
  "N", "N", 1688.75, latex_bold("893.45"), "902.61",
  "N", "Y", 1912.61, latex_bold("1014.13"), "1025.47")

  kbl(d2,
      format = "latex",
      booktabs = TRUE,
      align = c("c", "c", "r", "r", "r"),
      linesep = "",
      # col.names = col_names,
      escape = FALSE,
      caption = paste0(
        "Comparison of Akaike information criterion (AIC) values from the ",
        "three models in our analysis. ",
        "Model~1 represents the baseline model, Model~2 represents the model ",
        "with spatiotemporal variation but no covariates, and Model~3 ",
        "represents the model with spatial variation and a temperature ",
        "effect. For the temperature effect, this table represents estimates ",
        "from models using temperature in February, at a depth of 130.67~m, ",
        "and only north of Point Conception. The best models (lowest AIC) ",
        "for each combination are in bold.")) |>
    row_spec(0, bold = TRUE) |>
#    column_spec(ncol(d), width = "5cm") |>
    kable_styling(font_size = 12,
                  latex_options = c("repeat_header"))
```

\clearpage

```{r app-maturity-analysis-estimates-tab, results = "asis", echo = FALSE}
d3 <- tribble(
  ~"Model", ~"Term", ~"Estimate", ~"Std Error",
  1, "age", 4.46, 0.201,
  1, "age$^2$", -1.06, 0.0557,
  1, "ashopFALSE", 3.51, 0.19,
  1, "ashopTRUE", 4.29, 0.22,
  2, "age", 4.52, 0.284,
  2, "age$^2$", -1.35, 0.105,
  2, "ashopFALSE", 3.74, 0.37,
  2, "ashopTRUE", 5.2, 0.691,
  2, "range", 191, 85.4,
  2, "$\\sigma_O$", 0.653, 0.366,
  3, "age", 4.51, 0.288,
  3, "age$^2$", -1.35, 0.102,
  3, "temp", 0.421, 0.0994,
  3, "temp$^2$", -0.535, 0.0754,
  3, "ashopFALSE", 4.36, 0.305,
  3, "ashopTRUE", 6.05, 0.677,
  3, "range", 202, 95.2,
  3, "$\\sigma_O$", 0.544, 0.448)

  kbl(d3,
      format = "latex",
      booktabs = TRUE,
      align = c("c", "c", "r", "r"),
      linesep = "",
      # col.names = col_names,
      escape = FALSE,
      caption = paste0(
        "Parameter estimates and standard errors estimated for the three ",
        "models of maturity in our analyses (including samples from the ",
        "At-Sea Hake Observer Program (ASHOP) and only samples north of ",
        "Pt.~Conception). Estimates of fixed effects are in logit space. ",
        "The spatial range and spatial variance ($\\sigma_O$) are also ",
        "included for models with those terms.")) |>
    row_spec(0, bold = TRUE) |>
#    column_spec(ncol(d), width = "5cm") |>
    kable_styling(font_size = 12,
                  latex_options = c("repeat_header"))
```

```{r app-maturity-analysis-biomass-tab, results = "asis", echo = FALSE}
d4 <- tribble(
  ~"Term", ~"Estimate", ~"Std.~Error",
  "range", 33.5, 2.20,
  "$\\phi$", 21.8, 0.367,
  "$\\sigma_O$", 3.78, 0.197,
  "$\\sigma_E$", 1.68, 0.0541,
  "$p$", 1.64, 0.00368)

  kbl(d4,
      format = "latex",
      booktabs = TRUE,
      align = c("c", "r", "r"),
      linesep = "",
      # col.names = col_names,
      escape = FALSE,
      caption = paste0(
        "Parameter estimates and standard errors estimated for the model of ",
        "hake biomass from the West Coast Groundfish Bottom Trawl Survey ",
        "(WCGBTS). The spatial range is included, with ",
        "spatial variance ($\\sigma_O$), spatiotemporal variance ",
        "($\\sigma_E$), and Tweedie parameters ($\\phi, p$).")) |>
    row_spec(0, bold = TRUE) |>
#    column_spec(ncol(d), width = "5cm") |>
    kable_styling(font_size = 12,
                  latex_options = c("repeat_header"))
```

\clearpage

## Figures

(ref:app-maturity-analysis-sampling-platform-age-years-cap) Breakdown of the
number of observations by age, year, and sampling platform (i.e., West Coast
Groundfish Bottom Trawl Survey (WCGBTS), At-Sea Hake Observer Program (ASHOP),
and the Northwest Fisheries Science Center Integrated Pacific Hake Ecosystem
and Acoustic-Trawl Survey).

(ref:app-maturity-analysis-sampling-platform-age-years-alt) There is good coverage of
age samples from all platforms, particularly from 2012--2019.

```{r app-maturity-analysis-sampling-platform-age-years-fig, fig.cap = "(ref:app-maturity-analysis-sampling-platform-age-years-cap)", results = "asis"}

include_graphics(file.path(figures_dir,
                          "Fig_S3_samplingplatform_age_years.png"),
                 error = FALSE)
```

(ref:app-maturity-analysis-temp-depth-cap) Average GLORYS12v1 potential
temperature (degrees Celsius) within the domain of the West Coast Groundfish
Bottom Trawl Survey (WCGBTS) north of Point Conception, in February by depth
(m; colors).

(ref:app-maturity-analysis-temp-depth-alt) Temperatures in all months between
2015--2022 were higher than historical temperatures for a given month.

```{r app-maturity-analysis-temp-depth-fig, fig.cap = "(ref:app-maturity-analysis-temp-depth-cap)", results = "asis"}

include_graphics(file.path(figures_dir,
                           "Fig_S4_temp_by_depth.png.png"),
                 error = FALSE)
```

(ref:app-maturity-analysis-raw-feb-temp-cap) Average GLORYS12v1 potential
temperature (degrees Celsius) within the domain of the West Coast Groundfish
Bottom Trawl Survey (WCGBTS) north of Point Conception, at a depth of 130.67 m
by month (colors).

(ref:app-maturity-analysis-raw-feb-temp-alt) Temperatures for all months measured
at a depth of 130.67 meters increased between 2010 and 2020.

```{r app-maturity-analysis-raw-feb-temp-fig, fig.cap = "(ref:app-maturity-analysis-raw-feb-temp-cap)", results = "asis"}

include_graphics(file.path(figures_dir,
                           "Fig_S5_raw_feb_temp.png"),
                 error = FALSE)
```

(ref:app-maturity-analysis-temp-weight-effect-cap) Comparison of temperature
indices (Celsius) using raw averages of temperature (red) and biomass weighted
averages of temperature (blue). Shown is temperature at a depth of 130.67 m in
January but only for north of Point Conception.

(ref:app-maturity-analysis-temp-weight-effect-alt) Weighted by biomass versus
unweighted average temperatures were similar across the time series.  

```{r app-maturity-analysis-temp-weight-effect-fig, fig.cap = "(ref:app-maturity-analysis-temp-weight-effect-cap)", results = "asis"}

include_graphics(file.path(figures_dir,
                           "Fig_S6_temp_weight_effect.png"),
                 error = FALSE)
```

(ref:app-maturity-analysis-day-of-year-cap) The estimated effect of day of the year
on maturation from Model 3 (see Table \@ref(tab:app-maturity-analysis-aic-tab))
using a penalized spline.

(ref:app-maturity-analysis-day-of-year-alt) Maturation increases steeply during
the middle of the year and slightly declines towards the end of the year.  

```{r app-maturity-analysis-day-of-year-fig, fig.cap = "(ref:app-maturity-analysis-day-of-year-cap)", results = "asis"}

include_graphics(file.path(figures_dir,
                           "maturity_spline_doy.png"),
                 error = FALSE)
```

(ref:app-maturity-analysis-year-effects-nocovar-cap) Estimated and predicted
year effects from the spatiotemporal hake maturity model without covariates
(Model 2 in Tables \@ref(tab:app-maturity-analysis-aic-tab) and
\@ref(tab:app-maturity-analysis-estimates-tab)). Year effects are included as
an autocorrelated random walk (variance is larger in years without data, such
as 2010--2011 or 2022--2025), and spatiotemporal effects are modeled with an
AR(1) process.

(ref:app-maturity-analysis-year-effects-nocovar-alt) The year effects from the
spatiotemporal hake maturity model without covariates shows annual differences
in maturity from year to year.

```{r app-maturity-analysis-year-effects-nocovar-fig, fig.cap = "(ref:app-maturity-analysis-year-effects-nocovar-cap)", results = "asis"}

include_graphics(file.path(figures_dir,
                           "Fig_S8_year_effects_nocovar.png"),
                 error = FALSE)
```

(ref:app-maturity-analysis-predicted-maps-byage-cap) Spatial anomalies in 
predictions of maturity for ages 1--5. Predictions are centered such that blue
represents lower than average maturation and red represents higher than
average. Predictions are from Model 3
(see Table \@ref(tab:app-maturity-analysis-aic-tab)) for year 2020. Slight
variations between ages are driven by the spatially varying coefficient effect
of age.

(ref:app-maturity-analysis-predicted-maps-byage-alt) This figure shows spatial
anomalies for ages 1 to 5 on seperate maps of the coastline, where lower than
average maturation was apparent in the south and clear higher and lower maturation
patches elsewhere. 

```{r app-maturity-analysis-predicted-maps-byage-fig, fig.cap = "(ref:app-maturity-analysis-predicted-maps-byage-cap)", results = "asis"}

include_graphics(file.path(figures_dir,
                           "Fig_S9_predicted_maps_byage.png"),
                 error = FALSE)
```

(ref:app-maturity-analysis-temp-model-sensitivities-cap) Sensitivity results
for the effect of temperature, with data coming from different months and
depths, summarized by different regions (`N` = north of Point Conception,
`S` = south of Point Conception) and modeled using different functional
relationships (linear, quadratic, and penalized spline, i.e., 'smooth').
In all cases, the raw Akaike information criterion (AIC) values are shown
where a lower AIC corresponds to support for the model from the data.

(ref:app-maturity-analysis-temp-model-sensitivities-alt) Sensitivity results of
the effect of temperature by month, region, depth, and functional form assumption
(linear, quadratic, or smoothed using a spline) on AIC.

```{r app-maturity-analysis-temp-model-sensitivities-fig, fig.cap = "(ref:app-maturity-analysis-temp-model-sensitivities-cap)", results = "asis"}

include_graphics(file.path(figures_dir,
                           "Fig_S10_temp_model_sensitivities.png"),
                 error = FALSE)
```

(ref:app-maturity-analysis-model-comparison-cap) Biomass weighted estimates of
maturity for each of the three models in our analysis (using samples from the
At-Sea Hake Observer Program (ASHOP) and data north of Point Conception).
Predictions of functional maturity are for non-ASHOP samples.

(ref:app-maturity-analysis-model-comparison-alt) This figure shows differences in
biomass weighted estimates of maturity across non-spatial, spatial, and the temperature effect models.

```{r app-maturity-analysis-model-comparison-fig, fig.cap = "(ref:app-maturity-analysis-model-comparison-cap)", results = "asis"}

include_graphics(file.path(figures_dir,
                         "Fig_S11_model_comparison.png"),
               error = FALSE)
```

(ref:app-maturity-analysis-temp-marginal-cap) Estimated marginal effect of
February temperature (Celsius) at a depth of 130.67 m when fit to data that
included samples from the At-Sea Hake Observer Program (ASHOP) and only data
north of Point Conception. Predictions are made for age-3 fish, using
coefficients corresponding to the non-ASHOP surveys, and for the 278th day of
the year.

(ref:app-maturity-analysis-temp-marginal-alt) This figure shows the marginal
quadratic effect of February temperature in Celsius at a depth of 130.67 m for
age-3 fish, with a peak in maturity around 9.0 Celsius.

```{r app-maturity-analysis-temp-marginal-fig, fig.cap = "(ref:app-maturity-analysis-temp-marginal-cap)", results = "asis"}

include_graphics(file.path(figures_dir,
                           "Fig_S12_temp_marginal.png"),
                 error = FALSE)
```

(ref:app-maturity-analysis-age-marginal-cap) Estimated ogives in three years
representing low temperatures (2012), average temperatures (2020), and high
temperatures (2016). The model of maturity used February temperature at a
depth of 130.67 m and was fit to data that included samples from the At-Sea
Hake Observer Program (ASHOP) and only data north of Point Conception. Ogives
represent Pacific Hake not sampled by ASHOP. The estimated age at 50%
maturity is 2.81 in 2020, versus 3.58 in 2012, and 3.82 in 2016.

(ref:app-maturity-analysis-age-marginal-alt) The ogive shifts to older ages
at 50% maturity at higher temperatures.

```{r app-maturity-analysis-age-marginal-fig, fig.cap = "(ref:app-maturity-analysis-age-marginal-cap)", results = "asis"}

include_graphics(file.path(figures_dir,
                           "Fig_S13_age_marginal.png"),
                 error = FALSE)
```

(ref:app-maturity-analysis-cog-latitude-cap) Estimated center of gravity of 
Pacific Hake biomass from the West Coast Groundfish Bottom Trawl Survey
(WCGBTS), using 2003--2023 data.

(ref:app-maturity-analysis-cog-latitude-alt) The center of gravity of Pacific
Hake biomass was considerably lower from 2011 to 2014 compared to other years.

```{r app-maturity-analysis-cog-latitude-fig, fig.cap = "(ref:app-maturity-analysis-cog-latitude-cap)", results = "asis"}

include_graphics(file.path(figures_dir,
                            "Fig_S7_cog_latitude.png"),
                  error = FALSE)
```

\clearpage
