\newpage

\rfoot{eDNA index}

# Developing an index of relative abundance using environmental DNA samples {#sec:app-eDNA-index}

Contributed by Andrew O. Shelton.

## Methods

### Data filtering

We assembled a dataset 

### Statistical modeling

As each sample 

### Deriving temperature indices

Subsurface ocean temperature 

## Model selection and sensitivity analysis

We performed two main 

### Generation of annual maturity at age

To create a single index o

## Results

Comparing the spatiotemporal 

## Citations

Akaike, H. 1973. Information theory and an extension of the maximum likelihood principle. In B.N. Petrov and F. Csaki (Eds.), Second International Symposium on Information Theory (pp. 267--281). Budapest: Akademiai Kiado.

Anderson, S.C., Ward, E.J., English, P.A., and Barnett, L.A.K. 2022. sdmTMB: an R package for fast, flexible, and user-friendly generalized linear mixed effects models with spatial and spatiotemporal random fields. bioRxiv 2022.03.24.485545. https://doi.org/10.1101/2022.03.24.485545

Eilers, P.H.C., and Marx, B.D. 1996. Flexible smoothing with B-splines and penalties. Statistical Science, 11(2): 89--121. https://doi.org/10.1214/ss/1038425655

Global Ocean Physics Reanalysis. 2024. E.U. Copernicus Marine Service Information (CMEMS). Marine Data Store (MDS). Retrieved January 10, 2024, from https://doi.org/10.48670/moi-00021

Global Ocean Physics Analysis and Forecast. 2024. E.U. Copernicus Marine Service Information (CMEMS). Marine Data Store (MDS). Retrieved January 10, 2024, from https://doi.org/10.48670/moi-00016

Keller, A.A., Wallace, J., and Methot, R. 2017. NWFSC's West Coast groundfish bottom trawl survey: History, design, description. U.S. Dept. Comm., NOAA Tech. Memo. NMFS-NWFSC-136.

Kristensen, K., Nielsen, A., Berg, C.W., Skaug, H., and Bell, B.M. 2016. TMB: Automatic Differentiation and Laplace Approximation. Journal of Statistical Software, 70(5): 1--21. https://doi.org/10.18637/jss.v070.i05

Lellouche, J.-M., Greiner, E., Bourdallé-Badie, R., Garric, G., Melet, A., Drévillon, M., Bricaud, C., Hamon, M., Le Galloudec, O., Regnier, C., Candela, T., Testut, C.-E., Gasparin, F., Ruggiero, G., Benkiran, M., Drillet, Y., and Le Traon, P.-Y. 2021. The Copernicus Global 1/12° Oceanic and Sea Ice GLORYS12 Reanalysis. Frontiers in Earth Science, 9. https://doi.org/10.3389/feart.2021.698876

Lindgren, F., Rue, H., and Lindström, J. 2011. An explicit link between Gaussian fields and Gaussian Markov random fields: The stochastic partial differential equation approach. Journal of the Royal Statistical Society Series B: Statistical Methodology 73: 423--498. https://doi.org/10.1111/j.1467-9868.2011.00777.x

Malick, M. J., Hunsicker, M. E., Haltuch, M. A., Parker-Stetter, S. L., Berger, A. M., and Marshall, K. N. 2020. Relationships between temperature and Pacific hake distribution vary across latitude and life-history stage. Marine Ecology Progress Series 639: 185--197. https://doi.org/10.3354/meps13286

Phillips, E. M., Malick, M. J., Gauthier, S., Haltuch, M. A., Hunsicker, M. E., Parker-Stetter, S. L., and Thomas, R. E. 2023. The influence of temperature on Pacific hake co-occurrence with euphausiids in the California Current Ecosystem. Fisheries Oceanography 32(3): 267--279. https://doi.org/10.1111/fog.12628

R Core Team. 2024. R: A Language and Environment for Statistical Computing. R Foundation for Statistical Computing, Vienna, Austria. https://www.R-project.org/

Robin, N., Turck, N., Hainard, A., Tiberti, N., Lisacek, F., Sanchez, J.C., and Müller, M. 2011.
pROC: an open-source package for R and S+ to analyze and compare ROC curves. BMC Bioinformatics 12: 77. https://doi.org/10.1186/1471-2105-12-77

Rosemond, R.C. 2023. Influence of novel ocean conditions on life history characteristics of a nearshore rockfish with implications for population assessment and management. Oregon State University. URL: https://ir.library.oregonstate.edu/concern/graduate_thesis_or_dissertations/8p58pp02d

Shono, H. 2008. Application of the Tweedie distribution to zero-catch data in CPUE analysis. Fisheries Research 93(1--2): 154--162. https://doi.org/10.1016/j.fishres.2008.03.006

\clearpage

## Tables

```{r app-maturity-analysis-sampling-platform-tab, results = "asis", echo = FALSE}

# Adapting from table_assessment_changes(); don't need function as these tables
# are one-offs.
d <- tribble(~Platform , ~"2009", ~"2012", ~"2013", ~"2014",
             ~"2015", ~"2016", ~"2017", ~"2018", ~"2019", ~"2021",
"ASHOP", 0, 0, 135, 196, 131, 194, 177, 0, 0, 0,
"Acoustic", 0, 181, 186, 0, 160, 131, 57, 54, 59, 68,
"WCGBT", 244, 64, 63, 197, 216, 66, 102, 109, 46, 0)

# Keep this in case need extra formatting.
#  col_names <- c("Year",
#                  "Framework",
#                  "Survey",
#                  "Comp\nMethod",
#                  "Num.\nMCMC\nsamples",
#                  "Change")

# Insert custom header fontsize before linebreaker
#   if(is.null(header_font_size)){
#     header_font_size <- font_size
#   }
#   hdr_font_str <- create_fontsize_str(header_font_size,
#                                       header_vert_spacing,
#                                       header_vert_scale)
#   col_names <- gsub("\\n", paste0("\n", hdr_font_str$quad), col_names)
#   col_names <- paste0(hdr_font_str$dbl, col_names)
# Add \\makecell{} latex command to headers with newlines
#   col_names <- linebreaker(col_names, align = "c")

  kbl(d,
      format = "latex",
      position = "h",
      booktabs = TRUE,
      align = c("l", "r", "r", "r", "r", "r", "r", "r", "r", "r", "r"),
      linesep = "",
      # col.names = col_names,
      escape = FALSE,
      caption = paste0("Samples included in our analysis (after ",
                       "filtering), by sampling platform and year.")) |>
    row_spec(0, bold = TRUE) |>
#    column_spec(ncol(d), width = "5cm") |>
    kable_styling(font_size = 12,
                  latex_options = c("repeat_header"))
```

```{r app-maturity-analysis-aic-tab, results = "asis", echo = FALSE}
d2 <- tribble(
  ~"ASHOP", ~"Include South", ~"Model 1", ~"Model 2", ~"Model 3",
  "Y", "Y", 1440.12, latex_bold("1334.68"), "1366.41",
  "Y", "N", 1277.58, "1209.28", latex_bold("1195.94"),
  "N", "N", 1688.75, latex_bold("893.45"), "902.61",
  "N", "Y", 1912.61, latex_bold("1014.13"), "1025.47")

  kbl(d2,
      format = "latex",
      booktabs = TRUE,
      align = c("c", "c", "r", "r", "r"),
      linesep = "",
      # col.names = col_names,
      escape = FALSE,
      caption = paste0(
        "Comparison of Akaike information criterion (AIC) values from the ",
        "three models in our analysis. ",
        "Model~1 represents the baseline model, Model~2 represents the model ",
        "with spatiotemporal variation but no covariates, and Model~3 ",
        "represents the model with spatial variation and a temperature ",
        "effect. For the temperature effect, this table represents estimates ",
        "from models using temperature in February, at a depth of 130.67~m, ",
        "and only north of Point Conception. The best models (lowest AIC) ",
        "for each combination are in bold.")) |>
    row_spec(0, bold = TRUE) |>
#    column_spec(ncol(d), width = "5cm") |>
    kable_styling(font_size = 12,
                  latex_options = c("repeat_header"))
```

\clearpage

```{r app-maturity-analysis-estimates-tab, results = "asis", echo = FALSE}
d3 <- tribble(
  ~"Model", ~"Term", ~"Estimate", ~"Std Error",
  1, "age", 4.46, 0.201,
  1, "age$^2$", -1.06, 0.0557,
  1, "ashopFALSE", 3.51, 0.19,
  1, "ashopTRUE", 4.29, 0.22,
  2, "age", 4.52, 0.284,
  2, "age$^2$", -1.35, 0.105,
  2, "ashopFALSE", 3.74, 0.37,
  2, "ashopTRUE", 5.2, 0.691,
  2, "range", 191, 85.4,
  2, "$\\sigma_O$", 0.653, 0.366,
  3, "age", 4.51, 0.288,
  3, "age$^2$", -1.35, 0.102,
  3, "temp", 0.421, 0.0994,
  3, "temp$^2$", -0.535, 0.0754,
  3, "ashopFALSE", 4.36, 0.305,
  3, "ashopTRUE", 6.05, 0.677,
  3, "range", 202, 95.2,
  3, "$\\sigma_O$", 0.544, 0.448)

  kbl(d3,
      format = "latex",
      booktabs = TRUE,
      align = c("c", "c", "r", "r"),
      linesep = "",
      # col.names = col_names,
      escape = FALSE,
      caption = paste0(
        "Parameter estimates and standard errors estimated for the three ",
        "models of maturity in our analyses (including samples from the ",
        "At-Sea Hake Observer Program (ASHOP) and only samples north of ",
        "Pt.~Conception). Estimates of fixed effects are in logit space. ",
        "The spatial range and spatial variance ($\\sigma_O$) are also ",
        "included for models with those terms.")) |>
    row_spec(0, bold = TRUE) |>
#    column_spec(ncol(d), width = "5cm") |>
    kable_styling(font_size = 12,
                  latex_options = c("repeat_header"))
```

```{r app-maturity-analysis-biomass-tab, results = "asis", echo = FALSE}
d4 <- tribble(
  ~"Term", ~"Estimate", ~"Std.~Error",
  "range", 33.5, 2.20,
  "$\\phi$", 21.8, 0.367,
  "$\\sigma_O$", 3.78, 0.197,
  "$\\sigma_E$", 1.68, 0.0541,
  "$p$", 1.64, 0.00368)

  kbl(d4,
      format = "latex",
      booktabs = TRUE,
      align = c("c", "r", "r"),
      linesep = "",
      # col.names = col_names,
      escape = FALSE,
      caption = paste0(
        "Parameter estimates and standard errors estimated for the model of ",
        "hake biomass from the West Coast Groundfish Bottom Trawl Survey ",
        "(WCGBTS). The spatial range is included, with ",
        "spatial variance ($\\sigma_O$), spatiotemporal variance ",
        "($\\sigma_E$), and Tweedie parameters ($\\phi, p$).")) |>
    row_spec(0, bold = TRUE) |>
#    column_spec(ncol(d), width = "5cm") |>
    kable_styling(font_size = 12,
                  latex_options = c("repeat_header"))
```

\clearpage

## Figures

(ref:app-maturity-analysis-sampling-platform-age-years-cap) Breakdown of the
number of observations by age, year, and sampling platform (i.e., West Coast
Groundfish Bottom Trawl Survey (WCGBTS), At-Sea Hake Observer Program (ASHOP),
and the Northwest Fisheries Science Center Integrated Pacific Hake Ecosystem
and Acoustic-Trawl Survey).

(ref:app-maturity-analysis-sampling-platform-age-years-alt) There is good
coverage of age samples from all platforms particularly from 2012 to 2019.

```{r app-maturity-analysis-sampling-platform-age-years-fig, fig.cap = "(ref:app-maturity-analysis-sampling-platform-age-years-cap)", results = "asis"}

include_graphics(file.path(figures_dir,
                          "Fig_S3_samplingplatform_age_years.png"),
                 error = FALSE)
```

(ref:app-maturity-analysis-temp-depth-cap) Average GLORYS12v1 potential
temperature (degrees Celsius) within the domain of the West Coast Groundfish
Bottom Trawl Survey (WCGBTS) north of Point Conception, in February by depth
(m; colors).

(ref:app-maturity-analysis-temp-depth-alt) Temperatures in all months between
2015 to 2022 were higher than historical temperatures for a given month.

```{r app-maturity-analysis-temp-depth-fig, fig.cap = "(ref:app-maturity-analysis-temp-depth-cap)", results = "asis"}

include_graphics(file.path(figures_dir,
                           "Fig_S4_temp_by_depth.png"),
                 error = FALSE)
```

(ref:app-maturity-analysis-raw-feb-temp-cap) Average GLORYS12v1 potential
temperature (degrees Celsius) within the domain of the West Coast Groundfish
Bottom Trawl Survey (WCGBTS) north of Point Conception, at a depth of 130.67 m
by month (colors).

(ref:app-maturity-analysis-raw-feb-temp-alt) Temperatures for all months
measured at a depth of 130 meters increased between 2010 and 2020.

```{r app-maturity-analysis-raw-feb-temp-fig, fig.cap = "(ref:app-maturity-analysis-raw-feb-temp-cap)", results = "asis"}

include_graphics(file.path(figures_dir,
                           "Fig_S5_raw_feb_temp.png"),
                 error = FALSE)
```

(ref:app-maturity-analysis-temp-weight-effect-cap) Comparison of temperature
indices (Celsius) using raw averages of temperature (red) and biomass weighted
averages of temperature (blue). Shown is temperature at a depth of 130.67 m in
January but only for north of Point Conception.

(ref:app-maturity-analysis-temp-weight-effect-alt) Weighted by biomass versus
unweighted average temperatures were similar across the time series.

```{r app-maturity-analysis-temp-weight-effect-fig, fig.cap = "(ref:app-maturity-analysis-temp-weight-effect-cap)", results = "asis"}

include_graphics(file.path(figures_dir,
                           "Fig_S6_temp_weight_effect.png"),
                 error = FALSE)
```

(ref:app-maturity-analysis-day-of-year-cap) The estimated effect of day of
the year on maturation from Model 3 (see Table
\@ref(tab:app-maturity-analysis-aic-tab)) using a penalized spline.

(ref:app-maturity-analysis-day-of-year-alt) Maturation increases steeply during
the middle of the year and slightly declines towards the end of the year.

```{r app-maturity-analysis-day-of-year-fig, fig.cap = "(ref:app-maturity-analysis-day-of-year-cap)", results = "asis"}

include_graphics(file.path(figures_dir,
                           "maturity_spline_doy.png"),
                 error = FALSE)
```

(ref:app-maturity-analysis-year-effects-nocovar-cap) Estimated and predicted
year effects from the spatiotemporal hake maturity model without covariates
(Model 2 in Tables \@ref(tab:app-maturity-analysis-aic-tab) and
\@ref(tab:app-maturity-analysis-estimates-tab)). Year effects are included as
an autocorrelated random walk (variance is larger in years without data, such
as 2010--2011 or 2022--2025), and spatiotemporal effects are modeled with an
AR(1) process.

(ref:app-maturity-analysis-year-effects-nocovar-alt) The year effects from the
spatiotemporal hake maturity model without covariates shows annual differences
in maturity from year to year.

```{r app-maturity-analysis-year-effects-nocovar-fig, fig.cap = "(ref:app-maturity-analysis-year-effects-nocovar-cap)", results = "asis"}

include_graphics(file.path(figures_dir,
                           "Fig_S8_year_effects_nocovar.png"),
                 error = FALSE)
```

(ref:app-maturity-analysis-predicted-maps-byage-cap) Spatial anomalies in 
predictions of maturity for ages 1--5. Predictions are centered such that blue
represents lower than average maturation and red represents higher than
average. Predictions are from Model 3
(see Table \@ref(tab:app-maturity-analysis-aic-tab)) for year 2020. Slight
variations between ages are driven by the spatially varying coefficient effect
of age.

(ref:app-maturity-analysis-predicted-maps-byage-alt) This figure shows spatial
anomalies for ages 1 to 5 on separate maps of the coastline where lower than
average maturation was apparent in the south and clear higher and lower
maturation patches elsewhere. 

```{r app-maturity-analysis-predicted-maps-byage-fig, fig.cap = "(ref:app-maturity-analysis-predicted-maps-byage-cap)", results = "asis"}

include_graphics(file.path(figures_dir,
                           "Fig_S9_predicted_maps_byage.png"),
                 error = FALSE)
```

(ref:app-maturity-analysis-temp-model-sensitivities-cap) Sensitivity results
for the effect of temperature, with data coming from different months and
depths, summarized by different regions (`N` = north of Point Conception,
`S` = south of Point Conception) and modeled using different functional
relationships (linear, quadratic, and penalized spline, i.e., 'smooth').
In all cases, the raw Akaike information criterion (AIC) values are shown
where a lower AIC corresponds to support for the model from the data.

(ref:app-maturity-analysis-temp-model-sensitivities-alt) Sensitivity results
of the effect of temperature by month region depth and functional form
assumption linear quadratic or smoothed using a spline on AIC.

```{r app-maturity-analysis-temp-model-sensitivities-fig, fig.cap = "(ref:app-maturity-analysis-temp-model-sensitivities-cap)", results = "asis"}

include_graphics(file.path(figures_dir,
                           "Fig_S10_temp_model_sensitivities.png"),
                 error = FALSE)
```

(ref:app-maturity-analysis-model-comparison-cap) Biomass weighted estimates of
maturity for each of the three models in our analysis (using samples from the
At-Sea Hake Observer Program (ASHOP) and data north of Point Conception).
Predictions of functional maturity are for non-ASHOP samples.

(ref:app-maturity-analysis-model-comparison-alt) This figure shows
differences in biomass weighted estimates of maturity across non spatial
spatial and the temperature effect models.

```{r app-maturity-analysis-model-comparison-fig, fig.cap = "(ref:app-maturity-analysis-model-comparison-cap)", results = "asis"}

include_graphics(file.path(figures_dir,
                         "Fig_S11_model_comparison.png"),
               error = FALSE)
```

(ref:app-maturity-analysis-temp-marginal-cap) Estimated marginal effect of
February temperature (Celsius) at a depth of 130.67 m when fit to data that
included samples from the At-Sea Hake Observer Program (ASHOP) and only data
north of Point Conception. Predictions are made for age-3 fish, using
coefficients corresponding to the non-ASHOP surveys, and for the 278th day of
the year.

(ref:app-maturity-analysis-temp-marginal-alt) This figure shows the marginal
quadratic effect of February temperature at a depth of 130 meters for
age 3 fish with a peak in maturity around 9 degrees Celsius.

```{r app-maturity-analysis-temp-marginal-fig, fig.cap = "(ref:app-maturity-analysis-temp-marginal-cap)", results = "asis"}

include_graphics(file.path(figures_dir,
                           "Fig_S12_temp_marginal.png"),
                 error = FALSE)
```

(ref:app-maturity-analysis-age-marginal-cap) Estimated ogives in three years
representing low temperatures (2012), average temperatures (2020), and high
temperatures (2016). The model of maturity used February temperature at a
depth of 130.67 m and was fit to data that included samples from the At-Sea
Hake Observer Program (ASHOP) and only data north of Point Conception. Ogives
represent Pacific Hake not sampled by ASHOP. The estimated age at 50%
maturity is 2.81 in 2020, versus 3.58 in 2012, and 3.82 in 2016.

(ref:app-maturity-analysis-age-marginal-alt) The ogive shifts to older ages
at 50 percent maturity at higher temperatures.

```{r app-maturity-analysis-age-marginal-fig, fig.cap = "(ref:app-maturity-analysis-age-marginal-cap)", results = "asis"}

include_graphics(file.path(figures_dir,
                           "Fig_S13_age_marginal.png"),
                 error = FALSE)
```

(ref:app-maturity-analysis-cog-latitude-cap) Estimated center of gravity of 
Pacific Hake biomass from the West Coast Groundfish Bottom Trawl Survey
(WCGBTS), using 2003--2023 data.

(ref:app-maturity-analysis-cog-latitude-alt) The center of gravity of Pacific
Hake biomass was considerably lower from 2011 to 2014 compared to other years.

```{r app-maturity-analysis-cog-latitude-fig, fig.cap = "(ref:app-maturity-analysis-cog-latitude-cap)", results = "asis"}

include_graphics(file.path(figures_dir,
                            "Fig_S7_cog_latitude.png"),
                  error = FALSE)
```

\clearpage
