\newpage

\rfoot{Ecosystem report}

# Hake-specific ecosystem summary {#sec:app-ecosystem-report}

Contributed by Kristin N. Marshall, Mary E. Hunsicker, and Andrew M. Edwards

The base model for this stock assessment includes
year-specific maturity-at-age that explicitly accounts for changes in temperature, and
empirical weight-at-age data that may be due to ecosystem effects. As such, the
assessment is consistent with an `Ecosystem Approach to Fisheries
Management'.

Section~\@ref(sec:recruitment-variables) discusses
relevant ecosystem information that has been previously
found to influence `r sp` recruitment [@VestfalsEtAl2023].
We focus on easily-available and updatable
information, and what is presented here is not exhaustive. As such it should be
considered a first step in providing an operational summary (updatable and
expanded upon every year) of relevant
ecosystem information for `r sp`. Section~\@ref(sec:ecosystem-conditions) then describes
broader ecosystem and environmental conditions relevant to `r sp`. A risk table
(Table~\@ref(tab:app-ecosystem-report-risk-tab)) summarizes conditions, uncertainty,
and concerns related to `r sp`.

## Ecosystem variables relevant for recruitment {#sec:recruitment-variables}

We present some of the indicators that @VestfalsEtAl2023
and subsequent analyses (Marshall et al., pers. comm.) found to correlate with
higher
`r sp` recruitment deviations (Table
\@ref(tab:app-ecosystem-report-indicators-tab)).
@VestfalsEtAl2023 used estimated hake recruitment deviations from 1980 to 2010, based on results in
the @JTC2020 hake assessment and ocean model variables from the University of
California, Santa Cruz Regional Ocean Modeling System (ROMS) hindcast. We also conducted a preliminary update using
a newer ocean modeling product (GLORYS, described below) that extends the analysis to a more
recent time period (1993 to 2023), and used extended statistical methods that focus
on within-sample and out-of-sample prediction for variable selection
(K.~Marshall, pers.~comm.).

\begin{table}[hbp]
\centering
\caption{\label{tab:app-ecosystem-report-indicators-tab}Descriptions of easily
available ecosystem variables that were found to influence `r sp`
recruitment either by Vestfals et al. (2023) or our updated analyses (unpublished).
Variables are in order of life-history stage, following Table~A1 of Vestfals et
al. (2023); see that reference for full details. Shelf break is considered
between 100 and 2,000~m isobaths, defining the longitudinal extent for several
variables. The first subscripts refer to life-history stage
(`pre` is preconditioning, while JA is Jan-Apr, in the egg to late larvae stage).}
\centering
\fontsize{10}{12}\selectfont
\begin{tabular}[t]{p{3cm}p{6cm}p{6cm}}
\toprule
Abbreviation~of variable & Definition & Effect on recruitment; expectation for an increase in
variable\\
\midrule

PREY$_{\mbox{pre,her}}$ & Pacific Herring spawning biomass off the west coast of
Vancouver Island & Increased competition with herring on summer feeding grounds
leads to poorer feeding conditions and reduced adult condition;
$\downarrow$ recruitment the following year\\

BI$_{\mbox{pre}}$ & North Pacific Current Bifurcation Index & Northward-shifted
bifurcation leads to increased advection of prey southwards, leading to poorer
feeding conditions off British Columbia, Washington, and Oregon, and reduced
adult condition;
$\downarrow$ recruitment the following year\\

PDO$_{\mbox{pre}}$ & Pacific Decadal Oscillation during preconditioning (Apr-Sep) & Indicator of basin-scale
processes, negative phase linked to higher productivity and improved adult condition (Apr-Sep);
$\downarrow$ recruitment the following year\\

NPGO$_{\mbox{pre}}$ & North Pacific Gyre Oscillation during preconditioning
(Apr-Sep) & Indicator of basin-scale
processes, positive phase linked to higher nutrient concentrations and
productivity, and improved adult condition;
$\uparrow$ recruitment the following year\\

TEMP$_{\mbox{spawn}}$ & Mean temperature during spawning (shelf break,
Jan-Mar, 130-500~m depth, 31-36°~N) &
At higher temperatures, fish are less likely to spawn but growth rate of larvae
increases;
$\cup$-shaped relationship with recruitment that year\\

AST$_{\mbox{eggs}}$ & Net along-shore transport (shelf break,
Jan-Mar, 40-60~m depth, 31-36°~N)
& Increased northward advection away from juvenile nursery areas decreases
recruitment; $\downarrow$ recruitment that year\\

MLD$_{\mbox{yolk}}$ & Mean mixed layer depth (shelf break
Jan-Apr, 31-36°~N)
& Larvae aggregate at base of mixed layer so mixed layer depth may limit how far
they rise in the water column affecting later transport; $\downarrow$ recruitment that year\\

SSH$_{\mbox{JA.c}}$ & Average sea-surface
height off California as an indicator of basin-scale processes (from coast to
30~km offshore, Jan-Apr, 34.5-42.5°~N) &
Higher sea surface is indicative of higher productivity and better conditions for copepods;
$\uparrow$ recruitment that year\\

MLD$_{\mbox{latelarv}}$ & Mean mixed layer depth (shelf break
Mar-Jun, 31-37°~N)
& Larvae aggregate at base of mixed layer so mixed layer depth may limit how far they rise in the
water column affecting later transport, and possibly less competition and
predation when mixed layer shallower; % Kristin's guess
$\uparrow$ recruitment that year\\

PU$_{\mbox{latelarv}}$ & Strength of poleward undercurrent (from coast to 275~m isobath,
Mar-Jun, 75-275~m depth, 33.5-34.5°~N)
& Increased northward
advection away from juvenile nursery areas decreases recruitment; $\downarrow$ recruitment that year \\

PRED$_{\mbox{age0.age1hake}}$ & Biomass of age-1 Pacific Hake (from this stock assessment)
& Age-1 hake predate on pelagic juveniles (roughly Apr-Sep); $\downarrow$ recruitment that year \\

\bottomrule
\end{tabular}
\end{table}

Overall, this resulted in 11 ecosystem indices described in Table~\@ref(tab:app-ecosystem-report-indicators-tab) that correlate with recruitment deviations of `r sp`. These include three of the five indices included in
the best-fitting model of @VestfalsEtAl2023 (see their Figure~7), and three of
the further nine indices found in their top 16 candidate models (their
Table~2).
Time series for five indices are based on values amalgamated in the pacea R
package [@EdwardsEtAl2024]. The other six indices
were calculated from outputs of the Global
Ocean Physics Reanalysis ([GLORYS12V1]((https://data.marine.copernicus.eu/product/GLOBAL_MULTIYEAR_PHY_001_030/description))) product, which is a global ocean
eddy-resolving oceanographic model covering 1993 onwards. Details of spatial,
depth, and temporal ranges are given in Table~\@ref(tab:app-ecosystem-report-indicators-tab).

The following variables are taken from pacea. Pacific Herring (\emph{Clupea pallasii}) spawning biomass index was
calculated from latest results [@DFO2024] of the stock assessment, which is conducted using
a statistical catch-at-age model [@ClearyEtAl2019]. The North Pacific Current
Bifurcation Index (BI) was developed by @MalickEtAl2017, who found that a northward-shifted bifurcation was
associated with increased salmon productivity in British Columbia and
Washington State waters. The index is
[updated annually](https://github.com/michaelmalick/bifurcation-index/) (Michael
Malick, pers.~comm.).
The Pacific Decadal Oscillation (PDO) is a monthly index which is a long-lived
El Niño-like pattern of Pacific climate variability [@MantuaEtAl1997].
The North Pacific Gyre Oscillation (NPGO) is a climate pattern
that is significantly correlated with fluctuations of salinity,
nutrients, and chlorophyll-a in long-term observations in the
California Current and Gulf of Alaska [@DiLorenzoEtAl2024].
The estimates of age-1 `r sp` are taken from this current assessment model (and will
be updated in pacea). The six further indices were calculated from
GLORYS outputs by K.~Marshall.

Estimates of `r sp` recruitment from this assessment are presented alongside the
five indices calculated using outputs from pacea
(Figure~\@ref(fig:app-ecosystem-summary-from-pacea-fig))
and the six indices calculated from GLORYS output
(Figure~\@ref(fig:app-ecosystem-summary-from-glorys-fig)).
All indices are standardised over the ranges of years shown (different for each
figure), such that each index has a mean of zero and standard deviation of
one. The x-axis corresponds to the year for which recruitment is expected to be
influenced by the ecosystem variable represented by the index. For example,
PREY$_{\mbox{pre,her}}$ is an index representing Pacific Herring spawning biomass off the west coast of
Vancouver Island (Table~\@ref(tab:app-ecosystem-report-indicators-tab)). @VestfalsEtAl2023 found that increased herring biomass led to
increased competition with hake on summer feeding grounds, leading to poorer
feeding conditions and reduced adult condition. `r sp` recruitment would then be
affected the following year. Thus, the PREY$_{\mbox{pre,her}}$ index for year 2020 in
Figure~\@ref(fig:app-ecosystem-summary-from-pacea-fig)
represents the herring spawning biomass in 2019, because that is the biomass
expected to influence hake recruitment in 2020. A similar shift is done for the
other three variables that influence the adult preconditioning stage of hake.

The notation PREY$_{\mbox{pre,her}}$ represents herring being a prey item for
adult hake in the preconditioning stage, although @VestfalsEtAl2023 found a
competition effect (not a predator-prey effect as originally hypothesised).

Some variables are plotted with a flipped y-axis, so that upwards in all plots
consistently corresponds to conditions supposedly good for hake recruitment.
For example, a lower herring biomass is expected to correspond to an increase in hake
recruitment, and so the y-axis for the herring index in
Figure~\@ref(fig:app-ecosystem-summary-from-pacea-fig)
is flipped, so that lower-than-average herring biomass is upwards on the
plot. It is coloured blue to represent a negative herring biomass
anomaly. Similarly, red represents a positive herring biomass anomaly but
values point downwards to indicate a negative potential effect on hake
recruitment. A similar flip is done for all variables for which a negative index
was found to
correspond to positive hake recruitment, to make it easier to
visualise potential effects. A similar approach is taken for
Figure~\@ref(fig:app-ecosystem-summary-from-glorys-fig).

We have not conducted further analyses on these time series, but present them as
a first attempt to compile varied ecosystem information into single figures that
can
stimulate thinking about ecosystem effects, and
that can be updated and expanded upon for future assessments. Note that the
strongest driver of hake recruitment found by
@VestfalsEtAl2023 was eddy kinetic energy between May and September (during the
female spawning preconditioning stage) from point Conception to Cape Blanco, but
an up-to-date index of this was not easily available.

<!-- Figures currently built in pacea/R-temp/ecosystem-summary-hake-make-figures.R on dev-andy branch -->

(ref:app-ecosystem-summary-from-pacea-cap) Estimated hake recruitment from this assessment (top), plus five ecosystem indices
based on the pacea R package. The x-axis corresponds to the
expected influenced year
of `r sp` recruitment (see
text). Red (blue) bars represent a positive (negative) index, with the y-axis flipped for four
indices so that
upwards represents a positive expected influence on recruitment.

(ref:app-ecosystem-summary-from-pacea-alt) This figure shows
time series of hake recruitment plus five ecosystem indices.

```{r app-ecosystem-summary-from-pacea-fig, fig.cap = "(ref:app-ecosystem-summary-from-pacea-cap)", results = "asis"}

include_graphics(file.path(figures_dir,
                          "ecosystem_summary_from_pacea.png"),
                 error = FALSE)
```

(ref:app-ecosystem-summary-from-glorys-cap) Estimated `r sp` recruitment from
the current assessment model (top), plus six ecosystem calculated from GLORYS
output. Axes are defined as in
Figure~\@ref(fig:app-ecosystem-summary-from-pacea-fig) and in the
text. *Recruitment has a $\cup$-shaped relationship
with mean temperature during spawning and for simplicity we do not flip the axis.

(ref:app-ecosystem-summary-from-glorys-alt) This figure shows
time series of hake recruitment plus six further ecosystem indices.

```{r app-ecosystem-summary-from-glorys-fig, fig.cap = "(ref:app-ecosystem-summary-from-glorys-cap)", results = "asis"}

include_graphics(file.path(figures_dir,
                          "ecosystem_summary_from_glorys.png"),
                 error = FALSE) #
```

\clearpage

\begin{table}[tbp]
\centering
\caption{\label{tab:app-ecosystem-report-risk-tab}
`Risk table' for Pacific Hake, to document ecosystem and climate factors
potentially affecting stock productivity and uncertainty or other concerns
arising from the stock assessment (see text). Level~1 is a favourable ranking,
Level~2 neutral, and Level~3 is unfavourable. CVA is the Climate Variability
Assessment approach (McClure et al., 2023).}
\centering
\fontsize{10}{12}\selectfont
\begin{tabular}[t]{p{5cm}p{5cm}p{5cm}}
\toprule
Ecosystem and environmental conditions & Assessment data inputs &
Assessment model fits and structural uncertainty\\
\midrule
\begin{itemize}
  \itemindent = -8pt
  \item Recruitment: 2021-2024 recruitment indicators neutral to favorable
  \item Prey: favorable (krill, juvenile hake)
  \item Predators: unfavorable (increasing)
  \item CVA rank: low
  \end{itemize}
  &
  \begin{itemize}
  \itemindent = -8pt
  \item Very reliable catch reporting
  \item Generally well-sampled fishery-dependent and \protect{-independent} age
  compositions
  \item Informative age-2+ fishery-independent survey biomass index every other
  year
  \item Informative age-1 recruitment index every other year
  \item Includes externally estimated time-varying weight-at-age (growth) and
  time-varying and temperature-dependent maturity (fecundity) as data inputs
  \end{itemize}
  &
  \begin{itemize}
  \itemindent = -8pt
  \item Fully Bayesian stock assessment, integrating over multiple sources of
  parametric uncertainty
  \item High recruitment variability and no information on recent recruitment in
  assessment model from 2023 onwards, given no survey in 2024
  \item Key demographics estimated using priors (natural mortality and
  steepness)
  \item Clear identity of large cohorts after at least age-3
  \item Model fits well to age compositions, though occasionally at the expense
  of the survey index of abundance
  \item Uncertain how changes in the distribution of fishing relate to migration
  patterns and stock abundance
  \end{itemize} \\
\hline
Level~2 (medium agreement, robust evidence) & Level~1 & Level 2\\
\bottomrule
\end{tabular}
\end{table}

## Ecosystem and environmental conditions {#sec:ecosystem-conditions}

To start the process of discussing the vulnerability of `r sp` to climate change,
we evaluated recent trends in environmental drivers of hake recruitment and
growth, predators, and prey, along with the climate vulnerability assessment
(CVA) rank assigned to hake by @McClureEtAl2023. We did not consider
competitors, habitat, or non-fisheries human activities (such as offshore wind
development) during this evaluation. Overall, we consider ecosystem and
environmental conditions to be neutral (Level 2) for hake, with medium to high
confidence, based on medium agreement among indicators and robust evidence.
We use this, plus information related to this stock assessment, to fill out
the `risk table'
in Table~\@ref(tab:app-ecosystem-report-risk-tab), based on the framework
outlined by the [California Current Integrated Ecosystem Assessment (CCIEA) team](https://www.pcouncil.org/documents/2024/07/review-material-cciea-team-report-on-fep-initiative-4.pdf/).


**Recruitment**

A strong El Niño in 2023-24 caused warmer than average ocean temperatures in
winter and spring. As expected during an El Niño, the biomass of lipid-rich
northern copepods was generally lower during this period and indicators of krill
abundance were below average. However, these conditions rapidly subsided in late
spring. A delayed but strong spring upwelling ushered in cool and productive
conditions, and the biomass of northern copepods and krill rebounded to near
average levels for the remainder of the year. Overall, environmental conditions
in winter and spring were likely less favorable for age-0 hake in 2024
[@VestfalsEtAl2023, Table A.1] but conditions transitioned to those more favorable for
hake productivity in summer and fall. Observations of larval hake off Southern
California were above average during 2022-2024 and juvenile hake from Central
California were at or above average 2021-2024.

In 2025, the ecosystem is transitioning back to La Niña conditions, however
large areas of warmer than average temperatures are still prevalent. In
addition, marine heatwaves are forecasted to occur in offshore waters with the
possibility of moving into coastal regions in summer and fall. It’s uncertain
whether these conditions will negatively impact hake recruitment.

**Hake distribution**

Seasonal forecasts of hake distribution in the northern region of the California
Current Ecosystem
[@MalickHunsickerEtAl2020] were not available at the time of writing this
summary, however these temperature-driven forecasts will be presented at the
2025 SRG meeting. Given what we know about the influence of temperature on hake
distribution and the role of temperature as a proxy for prey availability
[@MalickHunsickerEtAl2020, @Phillips2022], we suspect that the delayed
upwelling observed in 2024 may have delayed the extent of the northern migration
of hake in the spring. Return to average conditions later in summer may have
supported a later northern shift as feeding conditions for hake improved.

**Predators and prey**

`r sp` are common in many predator's diets (e.g., Bluefin Tuna, Swordfish,
sharks, marine mammals, Sablefish, Arrowtooth Flounder, and adult hake). Recent
trends (i.e. over the last five years) in many of these populations of hake
predators are stable or increasing, suggesting mild concern about increased
predation. For example, the consumption of hake by Bluefin Tuna and Swordfish
has been well above average in recent years and the spawning biomass of these
species has increased over this period as well (Leising et al., in prep).
<!-- We
assume that long term trends, in particular those related to recovery of marine
mammals over several decades, are implicitly represented in the stock assessment
and do not represent notable changes that warrant inclusion in the risk
table.-->
However, recent indices of prey abundance are favorable. Krill is a
dominant diet item for juvenile and adult hake
[@WippelEtAl2017, @Phillips2022, @BizzarroEtAl2023]. The CCIEA krill indicator shows an
increasing trend in the central CCE over the last five years.

**Climate vulnerability assessment results**

Hake are highly exposed with low sensitivity to climate change, with an overall
rank of low [@McClureEtAl2023]. However, we note that the CVA work pre-dates
recent studies on the relationships between hake distribution and recruitment
and ocean conditions [@MalickHunsickerEtAl2020, @VestfalsEtAl2023].

\clearpage
