\newpage

\rfoot{Ecosystem report}

# Hake-specific ecosystem summary {#sec:app-ecosystem-report}

Contributed by Kristin N. Marshall, Mary E. Hunsicker, and Andrew M. Edwards

The base model for this stock assessment includes
year-specific maturity-at-age that explicitly accounts for changes in temperature, and
empirical weight-at-age data that may be due to ecosystem effects. As such, the
assessment is consistent with an `Ecosystem Approach to Fisheries
Management'

<!-- TODO add ref related to Jenny's talk if Bridget has something. -->

Here we
present further relevant ecosystem information that has been previously
found to influence `r sp` recruitment [@VestfalsEtAl2023].
We focus on easily-available and updatable
information, and what is presented here is not exhaustive. As such it should be
considered a first step in providing an operational summary (updatable and
expanded upon every year) of relevant
ecosystem information for `r sp`. We then present a NOAA-style risk table (TODO
get ref, see document).

## Ecosystem variables relevant for recruitment

We present some of the indicators that @VestfalsEtAl2023 found to lead to higher
`r sp` recruitment (Table \@ref(tab:app-ecosystem-report-indicators-tab)). That
analysis used estimated hake recruitment up to 2010, based on results in
the @JTC2020 hake assessment. We conducted a preliminary update of
that study using more recent recruitment estimates from the 2024 assessment
[@JTC2024], finding .... (K.~Marshall, pers.~comm.). TODO: checkwith Kristin
how to say that. Table~\@ref(tab:app-ecosystem-report-indicators-tab) describes
11 variables of recruitment that we assimilated and their expected effected on
recruitment of `r sp`. Time series for five variables (and associated plotting
functions) are based on values amalgamated in the pacea R package TODO and six
were calculated from outputs of the Global
Ocean Physics Reanalysis (GLORYS12V1) product, which is a global ocean
eddy-resolving oceanographic model covering 1993 onwards
(https://data.marine.copernicus.eu/product/GLOBAL_MULTIYEAR_PHY_001_030/description).


\begin{table}[hbp]
\centering
\caption{\label{tab:app-ecosystem-report-indicators-tab}Descriptions of easily
available ecosystem variables that were found to influence `r sp`
recruitment either by Vestfals et al. (2023) or our updated analyses (unpublished).
Variables are in order of life-history stage, following Table~A1 of Vestfals et
al. (2023); see that reference for full details. Shelf break is considered
between 100 and 2,000~m isobaths, defining the longitudinal extent for several
variables. Subscripts refer to life-history stage: TODO}
\centering
\fontsize{10}{12}\selectfont
\begin{tabular}[t]{p{3cm}p{6cm}p{6cm}}
\toprule
Abbreviation~of variable & Definition & Effect on recruitment; expectation for an increase in
variable\\
\midrule

PREY$_{\mbox{pre,her}}$ & Pacific Herring spawning biomass off the west coast of
Vancouver Island & Increased competition with herring on summer feeding grounds
leads to poorer feeding conditions and reduced adult condition;
$\downarrow$ recruitment the following year\\

BI$_{\mbox{pre}}$ & North Pacific Current Bifurcation Index & Northward-shifted
bifurcation leads to increased advection of prey southwards, leading to poorer
feeding conditions off British Columbia, Washington, and Oregon, and reduced
adult condition;
$\downarrow$ recruitment the following year\\

PDO$_{\mbox{pre}}$ & Pacific Decadal Oscillation during preconditioning (Apr-Sep) & Indicator of basin-scale
processes, negative phase linked to higher productivity and improved adult condition (Apr-Sep);
$\downarrow$ recruitment the following year\\

NPGO$_{\mbox{pre}}$ & North Pacific Gyre Oscillation during preconditioning
(Apr-Sep) & Indicator of basin-scale
processes, positive phase linked to higher nutrient concentrations and
productivity, and improved adult condition;
$\uparrow$ recruitment the following year\\

TEMP$_{\mbox{spawn}}$ & Mean temperature during spawning (shelf break,
Jan-Mar, 130-500~m depth, 31-36~\textdegree~N) & Fish less likely to spawn at
higher temperatures; $\downarrow$ recruitment that year\\

AST$_{\mbox{eggs}}$ & Net along-shore transport (shelf break,
Jan-Mar, 40-60~m depth, 31-36~\textdegree~N)
& Increased northward advection away from juvenile nursery areas decreases
recruitment; $\downarrow$ recruitment that year\\

MLD$_{\mbox{yolk}}$ & Mean mixed layer depth (shelf break
Jan-Apr, 31-36~\textdegree~N)
& Larvae aggregate at base of mixed layer so mixed layer depth may limit how far
they rise in the water column affecting later transport; $\downarrow$ recruitment that year\\

SSH$_{\mbox{JA.c}}$ & Average sea-surface
height off California as an indicator of basin-scale processes (from coast to
30~km offshore, Jan-Apr, 34.5-42.5~\textdegree~N)
& Not clear which way it goes (not in Table A3 Vestfals). TODO ???\\

MLD$_{\mbox{latelarv}}$ & Mean mixed layer depth (shelf break
Mar-Jun, 31-37~\textdegree~N)
& Larvae aggregate at base of mixed layer so mixed layer depth may limit how far they rise in the
water column affecting later transport; $\downarrow$ recruitment that year\\

PU$_{\mbox{latelarv}}$ & Strength of poleward undercurrent (from coast to 275~m isobath,
Mar-Jun, 75-275~m depth, 33.5-34.5~\textdegree~N)
& Increased northward
advection away from juvenile nursery areas decreases recruitment; $\downarrow$ recruitment that year \\

PRED$_{\mbox{age0.age1hake}}$ & Biomass of age-1 Pacific Hake (from this stock assessment)
& Age-1 hake predate on pelagic juveniles (roughly Apr-Sep); $\downarrow$ recruitment that year \\

\bottomrule
\end{tabular}
\end{table}



TODO add refs for pacea outputs

Estimates of `r sp` recruitment from this assessment are presented alongside the
five indices calculated using outputs from pacea
(Figure~\@ref(fig:app-ecosystem-summary-from-pacea-fig))
and the six indices calculated from GLORYS output
(Figure~\@ref(fig:app-ecosystem-summary-from-glorys-fig)).
All indices are standardised over the ranges of years shown (different for each
figure), such that each index has a mean of zero and standard deviation of
one. The x-axis corresponds to the year for which recruitment is expected to be
influenced by the ecosystem variable represented by the index. For example,
PREY$_{\mbox{pre,her}}$ is an index representing Pacific Herring spawning biomass off the west coast of
Vancouver Island. @VestfalsEtAl2023 found that increased herring biomass led to
increased competition with hake on summer feeding grounds, leading to poorer
feeding conditions and reduced adult condition. `r sp` recruitment would then be
affected the following year. Thus, the PREY$_{\mbox{pre,her}}$ index year 2020 in
Figure~\@ref(fig:app-ecosystem-summary-from-pacea-fig)
represents the herring spawning biomass in 2019, because that is the biomass
expected to influence hake recruitment in 2020. A similar shift is done for the
other three variables that influence the adult preconditioning stage of hake.

The notation PREY$_{\mbox{pre,her}}$ represents herring being a prey item for
adult hake in the preconditioning stage, although @VestfalsEtAl2023 found a
competition effect (not a predator-prey effect as originally hypothesised).

Since a higher herring biomass is expected to correspond to a decrease in hake
recruitment, the y-axis for the herring index in
Figure~\@ref(fig:app-ecosystem-summary-from-pacea-fig)
is flipped, so that lower-than-average herring biomass is are high on the plot
(yet are coloured blue to represent a negative herring biomass
anomaly). Similarly, red represents a positive herring biomass anomaly but
values point downwards to indicate a negative potential effect on hake
recruitment. A similar flip is done for all variables for which a negative index
was found to
correspond to positive hake recruitment. Thus, `up` in the plots can be
interpeted as supposedly good for hake recruitment, to make it easier to
visualise potential effects. A similar approach is taken for
Figure~\@ref(fig:app-ecosystem-summary-from-glorys-fig).

We have not conducted further analyses on these time series, but present them as
a first attempt to compile varied ecosystem information into single figures that
can
stimulate thinking about ecosystem effects, and
that can be updated and expanded upon for future assessments.

<!-- Figures currently built in pacea/R-temp/ecosystem-summary-hake-make-figures.R on dev-andy branch -->

(ref:app-ecosystem-summary-from-pacea-cap) Estimated hake recruitment from this assessment (top), plus five ecosystem indices
using values from the pacea R package. The x-axis corresponds to the
expected influenced year
of `r sp` recruitment (see
text). Red bars represent a positive index, with the y-axis flipped for four
indices so that
upwards represents a positive expected influence on recruitment.

(ref:app-ecosystem-summary-from-pacea-alt) Alt text here. TODO

```{r app-ecosystem-summary-from-pacea-fig, fig.cap = "(ref:app-ecosystem-summary-from-pacea-cap)", results = "asis"}

include_graphics(file.path(figures_dir,
                          "ecosystem_summary_from_pacea.png"),
                 error = FALSE)
```

(ref:app-ecosystem-summary-from-glorys-cap) Estimated `r sp` recruitment from
the current assessment model (top), plus six ecosystem calculated from GLORYS
output. Axes are defined as in
Figure~\@ref(fig:app-ecosystem-summary-from-pacea-fig) and in the text.

(ref:app-ecosystem-summary-from-glorys-alt) Alt text here. TODO

```{r app-ecosystem-summary-from-glorys-fig, fig.cap = "(ref:app-ecosystem-summary-from-glorys-cap)", results = "asis"}

include_graphics(file.path(figures_dir,
                          "ecosystem_summary_from_glorys.png"),
                 error = FALSE) #
```

\clearpage

\begin{table}[hbp]
\centering
\caption{\label{tab:app-ecosystem-report-risk-tab}Risk table ....}
\centering
\fontsize{10}{12}\selectfont
\begin{tabular}[t]{p{5cm}p{5cm}p{5cm}}
\toprule
Ecosystem and environmental conditions & Assessment data inputs &
Assessment model fits and structural uncertainty\\
\midrule
Recruitment: 2020-2021 recruitment indicators were positive (environmental
conditions) & & \\
 & & \\
Prey: increasing (krill, juvenile hake) & & \\
 & & \\
Predators: no trend & & \\
 & & \\
CVA rank: low & & \\
\hline
Level 2 (medium agreement, robust evidence) & Level 3 (maturity-at-age linked
explicitly to temperature) & Level X\\
\bottomrule
\end{tabular}
\end{table}

TODO Kristin and Mary: please carefully check the first table; think I've got
the directions right (though one was not in Vestfals Table A3 so I presume
Kristin found it useful recently). I then need to update text in figure also.

## Ecosystem and Environmental Conditions (need to update, write last, this is sablefish, or just start from text in main section that is copied into the Google Doc)

We evaluated recent trends in environmental drivers of sablefish recruitment and growth, predators, and prey, along with the climate vulnerability assessment (CVA) rank assigned to hake by McClure et al. (2023). We did not consider competitors, habitat, or non-fisheries human activities (such as offshore wind development) during this evaluation. Overall, we consider ecosystem and environmental conditions to be neutral (Level 2) for hake, with medium to high confidence, based on medium agreement among indicators and robust evidence. Recent trends in prey abundance have been positive and the evidence for this trend is robust. However, other indices (potential negative impacts of El Niño and a moderate CVA rank) do not portend favorable conditions for hake productivity, though the evidence for these indicators is not as strong.
Environmental drivers
Recruitment
Over the past three years, environmental conditions in the California Current Ecosystem have been largely warmer than average even with the backdrop of a prolonged La Niña event, which provided favorable recruitment conditions.

[relates to 2023-2024] Overall, these data suggest a XX in stock productivity in
coming years, (in)consistent with the assessment model. However, forecasts
suggest an intensifying El Niño during fall 2023/winter 2024. During El Niño
events that impact the California Current Ecosystem, upwelling is generally
weaker (Jacox et al. 2015), and northern copepod populations are generally
lower. These changes have the potential to negatively impact hake recruitment
(Vestfals et al. 2023).

Hake distribution

Predators and prey
Hake is common in many predator’s diets (e.g., Albacore, arrowtooth flounder, sharks (common and bigeye thresher, blue), swordfish (broadbill), CA sea lion, harbor seal, humboldt squid, northern fur seal, dolphins, pacific hake, jack mackerel, spiny dogfish, sablefish, shortspine thornyhead).  Recent trends (i.e. over the last 5 years) in these populations of hake predators are stable or increasing, suggesting mild concern about increased predation. We assume that long term trends, in particular those related to recovery of marine mammals over several decades, are implicitly represented in the stock assessment and do not represent notable changes that warrant inclusion in the risk table. However, recent indices of prey abundance are favorable. Krill is a dominant diet item for juveniles and adult hake (Wippel et al. 2017, Phillips et al. 2022, Bizzarro et al. 2023). The CCIEA krill indicator shows an increasing trend over the last five years.
CVA results
Hake are highly exposed with low sensitivity to climate change, with an overall rank of low (McClure et al. 2023).  However, we note that the CVA work pre-dates recent studies on the relationships between hake distribution and recruitment and ocean conditions (Malick et al. 2020, Vestfals et al. 2023).

\clearpage
