# Projections

## Harvest-rule predicted catch for `r assess_yr`
:::::: {.columns}
::: {.column width="38%"}
* Using the defined *F~SPR=40%~* harvest rate with a 40:10 adjustment, the
  median projected `r end_yr` TAC is \textbf{`r ct_limit_quantiles["median"]` t}
* 2.5% and 97.5% quantiles: `r ct_limit_quantiles["lower"]` and
  `r ct_limit_quantiles["upper"]` t
:::

::: {.column width="62%"}
```{r main-projected-catch-density, out.height = "80%"}
plot_param_density(base_model,
                   param_nm = "ForeCatch_2024",
                   y_lim = c(0, 0.0013),
                   expand_vec = c(100, 100),
                   show_y_labels = FALSE,
                   x_lab = paste0("Projected ", assess_yr, " catch (kt) ",
                                  "based on the default harvesy policy"))
```
:::
::::::

## Projection methods

* Projections estimate the biomass at start of `r end_yr + 1`, `r end_yr + 2`,
  and `r end_yr + 3`
  -  Mean of fishery selectivity from `r end_yr - 5`--`r end_yr - 1` used
     in projections
  -  Mean of weight-at-age from `r end_yr - 5`--`r end_yr - 1` used in
     projections
  -  Recruitment from stock--recruitment relationship (with uncertain
     deviations)
  -  Used for default HR calculations
  -  Alternative future catch levels explored
* Equilibrium calculations (`r b_0`, `r f_spr`, MSY, etc.)
  - Base selectivity (used for years before 1991 as well)
  - Mean of weight-at-age across 1975-`r last_data_yr`
  - Recruitment at estimated `r r_0` or from stock--recruitment relationship
* Catch alternatives presented for some specific cases

## Three-year projections
:::::: {.columns}
::: {.column width="38%"}

* No fishing results in increase in *median* relative spawning biomass
  from `r assess_yr` to `r assess_yr + 2` then leveling off
* All others shown result in eventual declines in the median
* Uncertainty is large and increases from `r end_yr` to `r end_yr + 3`
:::

::: {.column width="62%"}
```{r jmc-main-forecast-depletion-comparison, fig.height = 4, out.height = "80%"}

plot_depl_fore_comparison(base_model,
                          fore_inds = c(1, 2, 6, 12, 14),
                          forecast_yrs = forecast_yrs,
                          leg_pos = c(0.18, 0.8))
```
:::
::::::
