# Decision tables

## Decision tables

* Decision table format (as improved last year)
  - Quantiles from the posterior distribution for relative spawning biomass
    and fishing intensity
* Catch alternatives
  - a: `r ct_levels[[1]][[2]]` (zero catch)
  - b, c, d, g, i, k: Constant catches of `r ct_levels[[2]][[2]]`, 
    `r ct_levels[[3]][[2]]`, `r ct_levels[[4]][[2]]`, `r ct_levels[[7]][[2]]`,
       `r ct_levels[[9]][[2]]`, and `r ct_levels[[11]][[2]]`.
  - f: Constant catch of `r ct_levels[[6]][[2]]`
  - l: Constant catch of `r ct_levels[[12]][[2]]`
  - e, h, j: Annual reductions of 10% from: `r f(ct_levels[[5]][[1]][1])` t,
    `r f(ct_levels[[8]][[1]][1])` t, and `r f(ct_levels[[10]][[1]][1])` t.
  - m: Fishing Intensity = 100% in each year conditioned on fixed catch in
    previous year
  - n: Median default Harvest Rule in each year conditioned on fixed catch
    in previous year
  - o: Fishing intensity giving 50% prob.~that the median `r assess_yr`
    catch equals median `r assess_yr + 1` catch
* Constant catch of 525,000 t added per request at SRG (see Appendix I)

## Relative spawning biomass, zero catch
```{r jmc-decisions-biomass-zero-table, results = "asis"}

table_decision(base_model,
               type = "biomass",
               rows_to_show = c("a"),
               font_size = 6,
               header_font_size = 7)
```

## Relative spawning biomass, constant catch
```{r jmc-decisions-biomass-constant-table, results = "asis"}

table_decision(base_model,
               type = "biomass",
               rows_to_show = c("b", "c", "d", "g", "i", "k"),
               font_size = 5,
               header_font_size = 6)
```

## Relative spawning biomass, `r last_assess_yr` catch and TAC

```{r jmc-decisions-biomass-last-year-catch-tac-table, results = "asis"}

table_decision(base_model,
               type = "biomass",
               rows_to_show = c("f", "l"),
               font_size = 6,
               header_font_size = 7,
               left_col_cm = 1.5) |> 
  # For a list of colors you can use here see:
  # https://ctan.math.utah.edu/ctan/tex-archive/macros/latex/contrib/latexcolors/latexcolors.pdf
  row_spec(2:4,
           bold = table_highlight_bold,
           background = table_highlight_color)
```

## Relative spawning biomass, annual 10% reduction

```{r jmc-decisions-biomass-10-percent-reduction-tac-table, results = "asis"}

table_decision(base_model,
               type = "biomass",
               rows_to_show = c("e", "h", "j"),
               font_size = 6,
               header_font_size = 7, left_col_cm = 1.5)
```

## Fishing intensity (selected streams)
```{r jmc-decisions-fishin-intensity-selected-table, results = "asis"}

table_decision(base_model,
               type = "spr",
               rows_to_show = c("a", "b", "f", "h", "l"),
               font_size = 5,
               header_font_size = 6) |> 
  # For a list of colors you can use here see:
  # https://ctan.math.utah.edu/ctan/tex-archive/macros/latex/contrib/latexcolors/latexcolors.pdf
  row_spec(7:9,
           bold = table_highlight_bold,
           background = table_highlight_color)
```
