## Request 2 -- alternative projections with late devs estimated

Request: The SRG requests that decision tables and probability tables be produced with 2023 and onward recruitment estimated and incorporating uncertainty. This would be done on the model without the age-1 index.

Response: Decision tables and probabilities have been provided along with tables of recent spawning biomass and recruitment estimates.

## Request 2 -- spawning biomass

```{r biomass-with-late-devs, fig.height = 4, out.height = "80%"}
#base_with_late_devs <- sens_models[[2]][[1]]

#table_biomass(
#  base_with_late_devs,
#  start_yr = end_yr - 9,
#  end_yr = end_yr,
#  caption = paste0(
#    "Recent trends in estimated beginning of the year female spawning ",
#    "biomass (SB; kt) and SB relative to estimated SB at unfished equilibrium ",
#    "(Rel. SB; \\%)."),
#  font_size = 10,
#  header_font_size = 8)
```

## Request 2 -- recruitment

```{r recruits-with-late-devs, fig.height = 4, out.height = "80%"}
#table_recruitment(
#  base_with_late_devs ,
#  start_yr = end_yr - 10,
#  end_yr = end_yr - 1,
#  caption = paste0(
#    "Estimates of recent recruitment (millions of age-0 fish) and ",
#    "recruitment deviations, where deviations below (above) zero indicate ",
#    "recruitment below (above) that estimated from the stock--recruitment ",
#    "relationship."),
#  font_size = 10,
#  header_font_size = 9)
```