\newpage

\rfoot{Executive summary}

# Executive summary {-}

## Stock {-}

This assessment reports the status of the coastal `r sp` (or `r common_name`,
*`r science_name`*) stock off the west coast of the United States and Canada
at the start of `r assess_yr`. This stock exhibits seasonal migratory
behavior, ranging from offshore and generally southern waters during the
winter spawning season to coastal areas between northern California and
northern British Columbia during the spring, summer, and fall when the
fishery is conducted. In years with warmer water the stock tends to move
farther to the north during the summer. Older `r simple_name` tend to migrate
farther north than younger fish in all years, with catches in the Canadian
zone typically consisting of fish greater than four years old. Separate, and
much smaller, populations of `r simple_name` occurring in the major inlets
of the Northeast Pacific Ocean, including the Strait of Georgia, Puget Sound,
and the Gulf of California, are not included in this analysis.

(ref:es-catches-cap) Total `r sp` catch used in the assessment by sector, `r start_yr`--`r last_data_yr`. U.S. tribal catches are included in the sectors where they are represented.

```{r es-catches, fig.cap = "(ref:es-catches-cap)", fig.height = 4, fig.width = 8, fig.width = 8, is.fig = TRUE, alt.text = "This figure shows that catches in four of the last six years have been the largest in the time series."}
plot_catches(ct, leg.y.loc = 650)
```

## Catches {-}

Coast-wide fishery landings of `r sp` averaged `r f(mean(ct$Total))`~t
from `r min(ct$Year)` to `r max(ct$Year)`, with a low of
`r f(min(ct$Total))`~t in
`r ct$Year[ct$Total == min(ct$Total)]` and a peak of
`r f(max(ct$Total))`~t in
`r ct$Year[ct$Total == max(ct$Total)]`
(Figure \@ref(fig:es-catches)).
Prior to `r min(ct$Year)`, total removals were negligible compared to the
modern fishery. Over the early period (`r min(ct$Year)`--1990) most removals
were from foreign or joint-venture fisheries. Across the time series, annual
catch in U.S. waters averaged `r f(mean(ct[["U.S. Total"]]))`~t
(`r f(sum(ct[["U.S. Total"]]) / sum(ct$Total) * 100, 1)`% of the total catch),
while catch from Canadian waters averaged `r f(mean(ct[["Canada Total"]]))`~t.
Over the last 10 years, `r max(ct$Year) - 9`--`r max(ct$Year)`
(Table \@ref(tab:es-catches)), the average coast-wide catch was
`r ct_mean_10yrs`~t with U.S. and Canadian catches averaging
`r ct_us_mean_10yrs`~t and `r ct_can_mean_10yrs`~t, respectively. Since 2017,
the coast-wide catch has been declining annually through `r end_yr - 1`,
when it was `r last_yr_landings`~t out of a total allowable catch (TAC,
adjusted for carryovers) of `r last_yr_tac`~t. Attainment in the U.S. was
`r last_yr_us_attained`% of its quota and in Canada it was
`r last_yr_can_attained`%.

```{r es-catch-table, results = "asis", echo = FALSE}
table_catch(ct,
            start_yr = assess_yr - 10,
            end_yr = assess_yr - 1,
            caption = paste0(
              "Recent commercial fishery catch (t). Tribal catches are",
              "included in the sector totals. Research catch includes landed",
              "catch associated with certain research-related activities.",
              "Catch associated with surveys and discarded bycatch in",
              "fisheries not targeting hake is relatively small and not included in",
              "the table or model."))
```

In this document, the terms catch and landings are used interchangeably.
Estimates of discard within the target fishery are included, but discarding
of `r sp` in non-target fisheries is not. Discard from all fisheries, 
including those that do not target hake, is estimated to be less than 1% of
landings in recent years. During the last five years, catches were
considerably above the long-term average catch (`r f(long_term_avge_ct)`~t),
but have been in decline over that period (especially in Canada). Landings
between 2001 and 2008 were predominantly comprised of fish from the very large
1999 year class, with the cumulative removal (through `r end_yr - 1`) from
that cohort estimated at approximately
`r f(cohort_catch_1999 / 1e6, 2)` million~t. Through `r last_data_yr`, the
cumulative catch of the 2010, 2014, and 2016 year classes is estimated to be
about `r f(cohort_catch_2010 / 1e6, 2)` million~t,
`r f(cohort_catch_2014 / 1e6, 2)` million~t, and
`r f(cohort_catch_2016 / 1e6, 2)` million~t, respectively. In the
`r end_yr - 1` catch, `r top_coh(base_model, last_data_yr, 3, cap = FALSE)`.

## Data and assessment {-}

(ref:es-survey-biomass-cap) Acoustic survey biomass index of age-2+ fish
(millions of tons). Approximate 95% confidence intervals are based on
sampling variability (intervals without squid/hake apportionment
uncertainty in 2009 are displayed in black).
  
```{r es-survey-biomass, fig.cap = "(ref:es-survey-biomass-cap)", fig.height=5, fig.width=8, is.fig = TRUE, alt.text = "This figure shows that the survey estimate has decreased from 2019 to 2021."}
plot_survey_biomass(base_model, index = "age2")
```

(ref:es-survey-age1-cap) Relative index of age-1 fish (numbers of fish) and
approximate 95% confidence intervals based on sampling variability. The index
is relative because the survey does not attempt to sample all available age-1
fish and the analysis does not include kriging as is done to estimate age-2+
biomass.

```{r es-survey-age1, fig.cap = "(ref:es-survey-age1-cap)", fig.height = 5, fig.width = 8, is.fig = TRUE, alt.text = "This figure shows that the age-1 survey estimate has increased from 2019 to 2021."}
plot_survey_biomass(base_model, index = "age1", y_lim = c(0, 16))
```

This Joint Technical Committee (JTC) assessment depends on the fishery
landings (`r start_yr`--`r last_data_yr`), an acoustic survey biomass index
of age-2+ fish (Figure~\@ref(fig:es-survey-biomass) and age compositions
(`r survey_start_yr`--`r survey_end_yr`), a relative index of age-1 fish (Figure~\@ref(fig:es-survey-age1); `r survey_start_yr`--`r survey_end_yr`),
fishery age compositions (`r start_yr_age_comps`--`r last_data_yr`), and
mean weight-at-age data (`r start_yr_age_comps`--`r last_data_yr`). In 2011
the survey biomass index was the lowest in the time series and was followed
by the index increasing in 2012, 2013, and again in 2015 before decreasing to
near the time series average in 2017. The 2019 estimate is the fourth highest
of the series, and the 2021 estimate is near the time series average.
Age-composition data from the aggregated fisheries and the acoustic survey,
along with the age-1 index, provide data that facilitates estimating relative
cohort strength, i.e., strong and weak cohorts. The age-1 index suggests
particularly large numbers of age-1 fish in 2009, 2011, 2015, and 2021 (2008,
2010, 2014, and 2020 year classes, respectively), and is not available for
most even years (odd year classes). There is not data to inform the size of
the `r last_data_yr` year class.

The assessment uses a Bayesian estimation approach, sensitivity analyses, and
retrospective investigations to evaluate the potential consequences of
parameter uncertainty, alternative structural models, and historical
performance of the assessment model, respectively. The Bayesian approach
combines prior knowledge about natural mortality, stock-recruitment steepness
(a parameter for stock productivity), and several other parameters, with
likelihoods for the acoustic survey biomass index, acoustic survey
age-composition data, the relative age-1 index, and fishery age-composition
data. Integrating the joint posterior distribution over model parameters
provides probabilistic inferences about uncertain model parameters and
forecasts derived from those parameters; this is done via Markov chain Monte
Carlo sampling using the efficient No-U-Turn Sampler (NUTS) that was
successfully tested in 2020 and used in subsequent assessments. Sensitivity
analyses are used to identify alternative model assumptions that may also
be consistent with the data. All models, including bridging, sensitivity,
and retrospective models, use a Bayesian framework for estimation.
Retrospective analyses identify possible poor performance of the assessment
model with respect to future predictions. Past assessments have conducted
closed-loop simulations that provide insights into how alternative
combinations of survey frequency, assessment model selectivity assumptions,
changes in hake distribution, and harvest control rules affect expected
management outcomes given repeated application of these procedures over
the long-term. The results of past (and ongoing) closed-loop simulations
help inform decisions made for this assessment.

This `r assess_yr` assessment retained the same general population dynamics
structure as the base assessment model from `r last_assess_yr` and again is
configured using Stock Synthesis. This includes the continued use (since 2014)
of time-varying (rather than fixed) selectivity to maintain flexibility with
fishing dynamics given variability in `r sp` distribution patterns.

The Dirichlet-multinomial estimation approach to weighting composition data
was retained, and sensitivity to an alternative data-weighting approach was
investigated. Time-varying fecundity, which was introduced in 2019, was
retained. Assumptions for the forecast period for weight at age and
selectivity continue to be based on conditions during the last five years,
as done since the 2020 assessment. The main change from the `r last_assess_yr`
assessment is the addition of `r last_data_yr` data.

