\newpage

\rfoot{Executive summary}

# Executive summary {-}

## Stock {-}

This assessment reports the status of the coastal `r sp` (or `r common_name`,
*`r science_name`*) stock off the west coast of the United States and Canada
at the start of `r assess_yr`. This stock exhibits seasonal migratory
behavior, ranging from offshore and generally southern waters during the
winter spawning season to coastal areas between northern California and
northern British Columbia during the spring, summer, and fall when the
fishery is conducted. In years with warmer water the stock tends to move
farther to the north during the summer. Older `r simple_name` tend to migrate
farther north than younger fish in all years, with catches in the Canadian
zone typically consisting of fish greater than four years old. Separate, and
much smaller, populations of `r simple_name` occurring in the major inlets
of the Northeast Pacific Ocean, including the Strait of Georgia, Puget Sound,
and the Gulf of California, are not included in this analysis.

(ref:es-catches-cap) Total `r sp` catch used in the assessment by sector, `r start_yr`--`r last_data_yr`. U.S. tribal catches are included in the sectors where they are represented.

```{r es-catches, fig.cap = "(ref:es-catches-cap)", fig.height = 4, fig.width = 8, fig.width = 8, is.fig = TRUE, alt.text = "This figure shows that catches in four of the last six years have been the largest in the time series."}
plot_catches(ct, leg.y.loc = 650)
```

## Catches {-}

Coast-wide fishery landings of `r sp` averaged `r f(mean(ct$Total))`~t
from `r min(ct$Year)` to `r max(ct$Year)`, with a low of
`r f(min(ct$Total))`~t in
`r ct$Year[ct$Total == min(ct$Total)]` and a peak of
`r f(max(ct$Total))`~t in
`r ct$Year[ct$Total == max(ct$Total)]`
(Figure \@ref(fig:es-catches)).
Prior to `r min(ct$Year)`, total removals were negligible compared to the
modern fishery. Over the early period (`r min(ct$Year)`--1990) most removals
were from foreign or joint-venture fisheries. Across the time series, annual
catch in U.S. waters averaged `r f(mean(ct[["U.S. Total"]]))`~t
(`r f(sum(ct[["U.S. Total"]]) / sum(ct$Total) * 100, 1)`% of the total catch),
while catch from Canadian waters averaged `r f(mean(ct[["Canada Total"]]))`~t.
Over the last 10 years, `r max(ct$Year) - 9`--`r max(ct$Year)`
(Table \@ref(tab:es-catches)), the average coast-wide catch was
`r ct_mean_10yrs`~t with U.S. and Canadian catches averaging
`r ct_us_mean_10yrs`~t and `r ct_can_mean_10yrs`~t, respectively. Since 2017,
the coast-wide catch has been declining annually through `r end_yr - 1`,
when it was `r last_yr_landings`~t out of a total allowable catch (TAC,
adjusted for carryovers) of `r last_yr_tac`~t. Attainment in the U.S. was
`r last_yr_us_attained`% of its quota and in Canada it was
`r last_yr_can_attained`%.

```{r es-catch-table, results = "asis", echo = FALSE}
table_catch(ct,
            start_yr = assess_yr - 10,
            end_yr = assess_yr - 1,
            caption = paste0(
              "Recent commercial fishery catch (t). Tribal catches are",
              "included in the sector totals. Research catch includes landed",
              "catch associated with certain research-related activities.",
              "Catch associated with surveys and discarded bycatch in",
              "fisheries not targeting hake is relatively small and not included in",
              "the table or model."))
```

In this document, the terms catch and landings are used interchangeably.
Estimates of discard within the target fishery are included, but discarding
of `r sp` in non-target fisheries is not. Discard from all fisheries, 
including those that do not target hake, is estimated to be less than 1% of
landings in recent years. During the last five years, catches were
considerably above the long-term average catch (`r f(long_term_avge_ct)`~t),
but have been in decline over that period (especially in Canada). Landings
between 2001 and 2008 were predominantly comprised of fish from the very large
1999 year class, with the cumulative removal (through `r end_yr - 1`) from
that cohort estimated at approximately
`r f(cohort_catch_1999 / 1e6, 2)` million~t. Through `r last_data_yr`, the
cumulative catch of the 2010, 2014, and 2016 year classes is estimated to be
about `r f(cohort_catch_2010 / 1e6, 2)` million~t,
`r f(cohort_catch_2014 / 1e6, 2)` million~t, and
`r f(cohort_catch_2016 / 1e6, 2)` million~t, respectively. In the
`r end_yr - 1` catch, `r top_coh(base_model, last_data_yr, 3, cap = FALSE)`.

## Data and assessment {-}

(ref:es-survey-biomass-cap) Acoustic survey biomass index of age-2+ fish
(millions of tons). Approximate 95% confidence intervals are based on
sampling variability (intervals without squid/hake apportionment
uncertainty in 2009 are displayed in black).
  
```{r es-survey-biomass, fig.cap = "(ref:es-survey-biomass-cap)", fig.height=5, fig.width=8, is.fig = TRUE, alt.text = "This figure shows that the survey estimate has decreased from 2019 to 2021."}
plot_survey_biomass(base_model, index = "age2")
```

(ref:es-survey-age1-cap) Relative index of age-1 fish (numbers of fish) and
approximate 95% confidence intervals based on sampling variability. The index
is relative because the survey does not attempt to sample all available age-1
fish and the analysis does not include kriging as is done to estimate age-2+
biomass.

```{r es-survey-age1, fig.cap = "(ref:es-survey-age1-cap)", fig.height = 5, fig.width = 8, is.fig = TRUE, alt.text = "This figure shows that the age-1 survey estimate has increased from 2019 to 2021."}
plot_survey_biomass(base_model, index = "age1", y_lim = c(0, 16))
```

This Joint Technical Committee (JTC) assessment depends on the fishery
landings (`r start_yr`--`r last_data_yr`), an acoustic survey biomass index
of age-2+ fish (Figure~\@ref(fig:es-survey-biomass) and age compositions
(`r survey_start_yr`--`r survey_end_yr`), a relative index of age-1 fish (Figure~\@ref(fig:es-survey-age1); `r survey_start_yr`--`r survey_end_yr`),
fishery age compositions (`r start_yr_age_comps`--`r last_data_yr`), and
mean weight-at-age data (`r start_yr_age_comps`--`r last_data_yr`). In 2011
the survey biomass index was the lowest in the time series and was followed
by the index increasing in 2012, 2013, and again in 2015 before decreasing to
near the time series average in 2017. The 2019 estimate is the fourth highest
of the series, and the 2021 estimate is near the time series average.
Age-composition data from the aggregated fisheries and the acoustic survey,
along with the age-1 index, provide data that facilitates estimating relative
cohort strength, i.e., strong and weak cohorts. The age-1 index suggests
particularly large numbers of age-1 fish in 2009, 2011, 2015, and 2021 (2008,
2010, 2014, and 2020 year classes, respectively), and is not available for
most even years (odd year classes). There is not data to inform the size of
the `r last_data_yr` year class.

The assessment uses a Bayesian estimation approach, sensitivity analyses, and
retrospective investigations to evaluate the potential consequences of
parameter uncertainty, alternative structural models, and historical
performance of the assessment model, respectively. The Bayesian approach
combines prior knowledge about natural mortality, stock-recruitment steepness
(a parameter for stock productivity), and several other parameters, with
likelihoods for the acoustic survey biomass index, acoustic survey
age-composition data, the relative age-1 index, and fishery age-composition
data. Integrating the joint posterior distribution over model parameters
provides probabilistic inferences about uncertain model parameters and
forecasts derived from those parameters; this is done via Markov chain Monte
Carlo sampling using the efficient No-U-Turn Sampler (NUTS) that was
successfully tested in 2020 and used in subsequent assessments. Sensitivity
analyses are used to identify alternative model assumptions that may also
be consistent with the data. All models, including bridging, sensitivity,
and retrospective models, use a Bayesian framework for estimation.
Retrospective analyses identify possible poor performance of the assessment
model with respect to future predictions. Past assessments have conducted
closed-loop simulations that provide insights into how alternative
combinations of survey frequency, assessment model selectivity assumptions,
changes in hake distribution, and harvest control rules affect expected
management outcomes given repeated application of these procedures over
the long-term. The results of past (and ongoing) closed-loop simulations
help inform decisions made for this assessment.

This `r assess_yr` assessment retained the same general population dynamics
structure as the base assessment model from `r last_assess_yr` and again is
configured using Stock Synthesis. This includes the continued use (since 2014)
of time-varying (rather than fixed) selectivity to maintain flexibility with
fishing dynamics given variability in `r sp` distribution patterns.

The Dirichlet-multinomial estimation approach to weighting composition data
was retained, and sensitivity to an alternative data-weighting approach was
investigated. Time-varying fecundity, which was introduced in 2019, was
retained. Assumptions for the forecast period for weight at age and
selectivity continue to be based on conditions during the last five years,
as done since the 2020 assessment. The main change from the `r last_assess_yr`
assessment is the addition of `r last_data_yr` data.

## Stock Biomass {-}

Results from the base model
indicate that since the 1960s, `r sp` female spawning biomass has ranged from
well below to above unfished equilibrium (Figures~\@ref(fig:es-spawning-biomass)
and~\@ref(fig:es-relative-spawning-biomass)). Model estimates suggest
that it was below the unfished equilibrium in the 1960s, at the start of the
assessment period, due to lower than average recruitment.

(ref:es-spawning-biomass-cap) Median (solid line) of the posterior
distribution for beginning of the year female spawning biomass
($B_t$ in year $t$; million t) through `r end_yr` (solid line) with 95%
posterior credibility intervals (shaded area). The left-most circle with a 95%
posterior credibility interval is the estimated unfished equilibrium biomass,
$B_0$.

```{r es-spawning-biomass, fig.cap = "(ref:es-spawning-biomass-cap)", fig.height = 5, fig.width = 8, is.fig = TRUE, alt.text = "This figure shows that the median spawning biomass has been increasing in size since 2021."}
plot_biomass(list(base_model),
             list(base_model_name),
             ylim = c(0, 5),
             point_shape = 1,
             leg_pos = "none")
```

(ref:es-relative-spawning-biomass-cap) Median (solid line) of the posterior
distribution for relative spawning biomass ($B_t / B_0$) through `r end_yr`
with 95% posterior credibility intervals (shaded area). Dashed horizontal
lines show 10%, 40%, and 100% of the unfished equilibrium ($B_0$).

```{r es-relative-spawning-biomass, fig.cap = "(ref:es-relative-spawning-biomass-cap)", fig.height = 5, fig.width = 8, is.fig = TRUE, alt.text = "This figure shows that the relative spawning biomass has been increasing since 2021. The value for 2023 is just above B0."}
plot_rel_biomass(list(base_model),
                 list(base_model_name),
                 point_shape = 1,
                 ylim = c(0, 3),
                 alpha = 0.2,
                 leg_pos = "none")
```

The stock is estimated to have increased rapidly and was above unfished
equilibrium in the mid-1970s and mid-1980s (after two large recruitment
events in the early 1980s). It then declined steadily to a low in 1999. This
was followed by a brief increase to a peak in 2002 as the very large 1999 year
class matured. The 1999 year class largely supported the fishery for several
years due to relatively small recruitment events between 2000 and 2007. With
the aging 1999 year class, median female spawning biomass declined throughout
the late 2000s, reaching a time-series low of `r median_bio_min` million~t in
`r median_bio_min_yr`. Median female spawning biomass is estimated to have
peaked again in 2013 and 2014 due to a very large 2010 year class and an
above-average 2008 year class. The subsequent decline from 2014 to 2016 is
primarily from the 2010 year class surpassing the age at which the gains in
weight from growth are greater than the losses in weight from mortality
(growth-mortality transition). The 2014 year class is estimated to be large,
though not as large as the 1999 and 2010 year classes, increasing the biomass
in 2017. The estimated biomass was relatively steady from 2017 to 2019 and then
declined in 2020 and 2021 due to the 2014 and 2016 year classes moving through
the growth-mortality transition during a period of high catches. The increase
in female spawning biomass since 2021 is due to the expected above average
2020 cohort entering maturity and the recent declining trend in catch.

The median estimate of the `r end_yr` relative spawning biomass (female
spawning biomass at the start of `r end_yr` divided by that at unfished
equilibrium, $B_0$) is `r curr_depl_median`%. However, the uncertainty
is particularly large this year, with a 95% posterior credibility interval
from `r curr_depl_lower`% to `r curr_depl_upper`% (Table~\@ref(tab:es-biomass),
due to high uncertainty about the size of the 2020 cohort, which has not yet
been sampled in the acoustic survey biomass index of age-2+ fish. The median
estimate of the `r end_yr` female spawning biomass is
`r curr_bio_median` million~t (with a 95% posterior credibility interval from
`r curr_bio_lower` to `r curr_bio_upper` million~t. The current estimate of the
`r end_yr - 1` female spawning biomass is `r prev_bio_median`
(`r prev_bio_lower`--`r prev_bio_upper`) million~t. This is higher than the
`r prev_bio_median_last_assess` (`r prev_bio_lower_last_assess`--
`r prev_bio_upper_last_assess`) million~t estimated in the `r end_yr - 1`
assessment. The increase appears to be due to the addition of 2022 fishery
age-composition data, which suggests the 2020 cohort may be larger than the
age-1 index alone was indicating in the last assessment.

The stock is estimated to have increased rapidly and was above unfished
equilibrium in the mid-1970s and mid-1980s (after two large recruitment events
in the early 1980s). It then declined steadily to a low in 1999. This was
followed by a brief increase to a peak in 2002 as the very large 1999 year
class matured. The 1999 year class largely supported the fishery for several
years due to relatively small recruitment events between 2000 and 2007. With
the aging 1999 year class, median female spawning biomass declined throughout
the late 2000s, reaching a time-series low of `r median_bio_min` million~t in
`r median_bio_min_yr`. Median female spawning biomass is estimated to have
peaked again in 2013 and 2014 due to a very large 2010 year class and an
above-average 2008 year class. The subsequent decline from 2014 to 2016 is
primarily from the 2010 year class surpassing the age at which the gains in
weight from growth are greater than the losses in weight from mortality
(growth-mortality transition). The 2014 year class is estimated to be large,
though not as large as the 1999 and 2010 year classes, increasing the biomass
in 2017. The estimated biomass was relatively steady from 2017 to 2019 and
then declined in 2020 and 2021 due to the 2014 and 2016 year classes moving
through the growth-mortality transition during a period of high catches. The
increase in female spawning biomass since 2021 is due to the expected above
average 2020 cohort entering maturity and the recent declining trend in catch.

The median estimate of the `r end_yr` relative spawning biomass (female
spawning biomass at the start of `r end_yr` divided by that at unfished
equilibrium, $B_0$) is `r curr_depl_median`%. However, the uncertainty is
particularly large this year, with a 95% posterior credibility interval from
`r curr_depl_lower`% to `r curr_depl_upper`%
(Table~\@ref(tab:es-biomass-table), due to high uncertainty about the size of
the 2020 cohort, which has not yet been sampled in the acoustic survey
biomass index of age-2+ fish. The median estimate of the `r end_yr` female
spawning biomass is `r curr_bio_median` million~t (with a 95% posterior
credibility interval from `r curr_bio_lower` to 
`r curr_bio_upper` million~t). The current estimate of the `r end_yr - 1`
female spawning biomass is `r prev_bio_median`
(`r prev_bio_lower`--`r prev_bio_upper`) million~t. This is higher than the
`r prev_bio_median_last_assess` (`r prev_bio_lower_last_assess`--
`r prev_bio_upper_last_assess`) million~t estimated in the `r end_yr - 1`
assessment. The increase appears to be due to the addition of 2022 fishery
age-composition data, which suggests the 2020 cohort may be larger than the
age-1 index alone was indicating in the last assessment.

```{r es-biomass-table, results = "asis", echo = FALSE}
table_biomass(base_model,
              start_yr = end_yr - 9,
              end_yr = end_yr,
              font_size = 12,
              caption = paste0(
                "Recent trends in estimated beginning of the year female ",
                "spawning biomass (SSB; thousand~t) and spawning biomass ",
                "relative to estimated unfished equilibrium (Rel. SSB; \\%)."))
```

## Recruitment {-}

```{r es-recruitment-table, results = "asis", echo = FALSE}
table_recruitment(base_model,
                  start_yr = end_yr - 10,
                  end_yr = end_yr - 1,
                  font_size = 12,
                  caption = paste0(
                    "Estimates of recent recruitment (millions of age-0 ",
                    "fish) and recruitment deviations, where deviations ",
                    "below (above) zero indicate recruitment below ",
                    "(above) that estimated from the stock-recruit ",
                    "relationship."))
```

The addition of `r last_data_yr` data does not substantially change estimates
of historical recruitment but recent recruitment estimates have changed
substantially. For example, this assessment's median estimate of the 2020
recruitment is
`r f(((recruitment_med_to_compare - prev_assess_recruitment_med)["2020"]), 1)`~billion
fish higher than in the last assessment (a 
`r f(((((recruitment_med_to_compare - prev_assess_recruitment_med)["2020"]) /
(prev_assess_recruitment_med)["2020"]) * 100), 0)`% increase). Similarly,
estimates for 2019 and 2021 recruitments have changed by
`r f(((((recruitment_med_to_compare - prev_assess_recruitment_med)["2019"]) /
(prev_assess_recruitment_med)["2019"]) * 100), 0)`%
(`r f((recruitment_med_to_compare - prev_assess_recruitment_med)["2019"], 1)`~billion
fish) and
`r f(((((recruitment_med_to_compare - prev_assess_recruitment_med)["2021"]) /
(prev_assess_recruitment_med)["2021"]) * 100), 0)`%
(`r f(((recruitment_med_to_compare - prev_assess_recruitment_med)["2021"]), 1)`~billion
fish), respectively, but the general notion remains that recent recruitment is
highly uncertain.

`r sp` have low to moderate recruitment with occasional large year classes
(Table~\@ref(tab:es-recruitment) and Figure~\@ref(fig:es-recruitment)).

(ref:es-recruitment) Medians (solid circles) and means ($\mathrm{X}$) of the
posterior distribution for recruitment (billions of age-0 fish) with 95%
posterior credibility intervals (blue, vertical lines). The median of the
posterior distribution for mean unfished equilibrium recruitment ($R_0$) is
shown as the horizontal dashed line with the 95% posterior credibility
interval shaded between the dotted lines.

```{r recruitment, fig.cap = "(ref:es-recruitment)", fig.height = 5, fig.width = 8, is.fig = TRUE, alt.text = "This figure shows that recruitment for each cohort. There are currently three above-average cohorts in the stock with 2020 being the fourth. The 2020 cohort is highly uncertain which can be seen in the size of the credible interval."}
plot_recruitment(list(base_model),
                 list(base_model_name),
                 single_line_color = "blue",
                 inc_means = TRUE,
                 leg_pos = "none")
```

Large year classes in 1980, 1984, and 1999 supported much of the commercial
catch from the 1980s to the mid-2000s. From 2000 to 2007, estimated
recruitment was at some of the lowest values in the time series but this
was followed by an above average 2008 year class. The strong 2010 year class
comprised `r top_coh(base_model, 2014, ret_cohort = 2010)`% of the
coast-wide commercial catch in 2014,
`r top_coh(base_model, 2016, ret_cohort = 2010)`% of the 2016 catch,
`r top_coh(base_model, 2018, ret_cohort = 2010)`% of the 2018 catch,
`r top_coh(base_model, 2020, ret_cohort = 2010)`% of the 2020 catch, and
`r top_coh(base_model, 2022, ret_cohort = 2010)`% of the 2022 catch.
The decline from 2014 to 2016 was partly due to the large influx of the 2014
year class (`r top_coh(base_model, 2016, ret_cohort = 2014)`% of the 2016
catch was age-2 fish from the 2014 year class; this was larger than the
proportion of age-2 fish, `r top_coh(base_model, 2012, ret_cohort = 2010)`%,
from the 2010 year class in 2012). Since 2010, the model currently
estimates small 2011, 2012, 2013, 2015, 2018, 2019 and 2021 year classes
(median recruitment well below the mean of all median recruitments).

The 2014 and 2016 year classes are both larger than average, with 2014
larger than 2016 but smaller than 2010. With the inclusion of the
relative age-1 index, there is information beyond just fishery encounters in
the data to estimate the size of the 2020 year class. Collectively, these
data indicate that the 2020 year class is likely well above average. The
much smaller 2019 year class is informed by the `r last_survey_yr`
biomass index and fishery data but is not informed by the relative age-1
index, and the 2021 year class is informed only by 2022 fishery data.
There is no information in the data to estimate the sizes of the
`r end_yr - 1` and `r end_yr` year classes. Retrospective analyses of
year-class strength for young fish have shown the estimates of recent
recruitment to be unreliable prior to at least a model age of three (i.e.,
fish observed at age two) without a survey in the most recent year and
two (i.e., fish observed at age one) with a survey. While the 2020 cohort
was observed by the relative age-1 index in 2021, it will not be observed
by the acoustic survey until 2023.

## Default harvest policy {-}

The default \Ffortyten harvest policy prescribes the maximum rate of fishing
mortality to equal $\Fforty$. This rate gives a spawning potential ratio (SPR)
of 40%, meaning that the female spawning biomass per recruit with $\Fforty$ is
40% of that without fishing. If female spawning biomass is below $\Bforty$
(40% of $B_0$), the policy reduces the TAC linearly until it equals zero at
$\Bten$ (10% of $B_0$). Relative fishing intensity for fishing rate
$\mathrm{F}$ is \FishingRate, where $\mathrm{SPR_{40\%}}$ is an SPR of 40%;
it is reported here interchangeably as a proportion or a percentage. A
relative fishing intensity above 1.0 means fishing at a rate above $\Fforty$.

## Exploitation status {-}

```{r es-fishing-intensity-table, results = "asis", echo = FALSE}
table_fishing_intensity(base_model,
                        start_yr = end_yr - 10,
                        end_yr = end_yr - 1,
                        digits = 3,
                        font_size = 12,
                        caption = paste0(
                          "Recent estimates of relative fishing intensity, ",
                          "\\FishingRate, and exploitation ",
                          "fraction (catch divided by age-2+ biomass)."))
```
