\newpage

\rfoot{Executive summary}

# Executive summary {-}

## Stock {-}

This assessment reports the status of the coastal `r sp` (or `r common_name`,
*`r science_name`*) stock off the west coast of the United States and Canada
at the start of `r assess_yr`. This stock exhibits seasonal migratory
behavior, ranging from offshore and generally southern waters during the
winter spawning season to coastal areas between northern California and
northern British Columbia during the spring, summer, and fall when the
fishery is conducted. In years with warmer water the stock tends to move
farther to the north during the summer. Older `r simple_name` tend to migrate
farther north than younger fish in all years, with catches in the Canadian
zone typically consisting of fish greater than four years old. Separate, and
much smaller, populations of `r simple_name` occurring in the major inlets
of the Northeast Pacific Ocean, including the Strait of Georgia, Puget Sound,
and the Gulf of California, are not included in this analysis.

(ref:es-catches-cap) Total `r sp` catch used in the assessment by sector, `r start_yr`--`r last_data_yr`. U.S. tribal catches are included in the sectors where they are represented.

```{r es-catches, fig.cap = "(ref:es-catches-cap)", fig.height = 4, fig.width = 8, fig.width = 8, is.fig = TRUE, alt.text = "This figure shows that catches in four of the last six years have been the largest in the time series."}
plot_catches(ct, leg.y.loc = 650)
```

## Catches {-}

Coast-wide fishery landings of `r sp` averaged `r f(mean(ct$Total))`~t
from `r min(ct$Year)` to `r max(ct$Year)`, with a low of
`r f(min(ct$Total))`~t in
`r ct$Year[ct$Total == min(ct$Total)]` and a peak of
`r f(max(ct$Total))`~t in
`r ct$Year[ct$Total == max(ct$Total)]`
(Figure \@ref(fig:es-catches)).
Prior to `r min(ct$Year)`, total removals were negligible compared to the
modern fishery. Over the early period (`r min(ct$Year)`--1990) most removals
were from foreign or joint-venture fisheries. Across the time series, annual
catch in U.S. waters averaged `r f(mean(ct[["U.S. Total"]]))`~t
(`r f(sum(ct[["U.S. Total"]]) / sum(ct$Total) * 100, 1)`% of the total catch),
while catch from Canadian waters averaged `r f(mean(ct[["Canada Total"]]))`~t.
Over the last 10 years, `r max(ct$Year) - 9`--`r max(ct$Year)`
(Table \@ref(tab:es-catches)), the average coast-wide catch was
`r ct_mean_10yrs`~t with U.S. and Canadian catches averaging
`r ct_us_mean_10yrs`~t and `r ct_can_mean_10yrs`~t, respectively. Since 2017,
the coast-wide catch has been declining annually through `r end_yr - 1`,
when it was `r last_yr_landings`~t out of a total allowable catch (TAC,
adjusted for carryovers) of `r last_yr_tac`~t. Attainment in the U.S. was
`r last_yr_us_attained`% of its quota and in Canada it was
`r last_yr_can_attained`%.

```{r es-catch-table, results = "asis", echo = FALSE}
table_catch(ct,
            start_yr = assess_yr - 10,
            end_yr = assess_yr - 1,
            caption = paste0(
              "Recent commercial fishery catch (t). Tribal catches are",
              "included in the sector totals. Research catch includes landed",
              "catch associated with certain research-related activities.",
              "Catch associated with surveys and discarded bycatch in",
              "fisheries not targeting hake is relatively small and not included in",
              "the table or model."))
```

In this document, the terms catch and landings are used interchangeably.
Estimates of discard within the target fishery are included, but discarding
of `r sp` in non-target fisheries is not. Discard from all fisheries, 
including those that do not target hake, is estimated to be less than 1% of
landings in recent years. During the last five years, catches were
considerably above the long-term average catch (`r f(long_term_avge_ct)`~t),
but have been in decline over that period (especially in Canada). Landings
between 2001 and 2008 were predominantly comprised of fish from the very large
1999 year class, with the cumulative removal (through `r end_yr - 1`) from
that cohort estimated at approximately
`r f(cohort_catch_1999 / 1e6, 2)` million~t. Through `r last_data_yr`, the
cumulative catch of the 2010, 2014, and 2016 year classes is estimated to be
about `r f(cohort_catch_2010 / 1e6, 2)` million~t,
`r f(cohort_catch_2014 / 1e6, 2)` million~t, and
`r f(cohort_catch_2016 / 1e6, 2)` million~t, respectively. In the
`r end_yr - 1` catch, `r top_coh(base_model, last_data_yr, 3, cap = FALSE)`.

## Data and assessment {-}

(ref:es-survey-biomass-cap) Acoustic survey biomass index of age-2+ fish
(millions of tons). Approximate 95% confidence intervals are based on
sampling variability (intervals without squid/hake apportionment
uncertainty in 2009 are displayed in black).
  
```{r es-survey-biomass, fig.cap = "(ref:es-survey-biomass-cap)", fig.height=5, fig.width=8, is.fig = TRUE, alt.text = "This figure shows that the survey estimate has decreased from 2019 to 2021."}
plot_survey_biomass(base_model, index = "age2")
```

(ref:es-survey-age1-cap) Relative index of age-1 fish (numbers of fish) and
approximate 95% confidence intervals based on sampling variability. The index
is relative because the survey does not attempt to sample all available age-1
fish and the analysis does not include kriging as is done to estimate age-2+
biomass.

```{r es-survey-age1, fig.cap = "(ref:es-survey-age1-cap)", fig.height = 5, fig.width = 8, is.fig = TRUE, alt.text = "This figure shows that the age-1 survey estimate has increased from 2019 to 2021."}
plot_survey_biomass(base_model, index = "age1", y_lim = c(0, 16))
```

