
\rfoot{Catches}

# Catches {#sec:catches}

(ref:es-catches-cap) Total `r sp` catch used in the assessment by sector,
`r start_yr`--`r last_data_yr`. U.S. tribal catches are included in the
sectors where they are represented.

(ref:es-catches-alt) This figure shows that coast wide catches have generally 
declined in recent years.

```{r es-catches-fig, fig.cap = "(ref:es-catches-cap)", fig.height = 4, out.height = "4in"}

plot_catches(ct, xlim = c(start_yr, last_data_yr))
```


Coast-wide fishery landings of `r sp` averaged `r f(mean(ct$Total))`~t
from `r min(ct$Year)` to `r max(ct$Year)`, with a low of
`r f(min(ct$Total))`~t in
`r ct$Year[ct$Total == min(ct$Total)]` and a peak of
`r f(max(ct$Total))`~t in
`r ct$Year[ct$Total == max(ct$Total)]`
(Figure \@ref(fig:es-catches-fig)).
Prior to `r min(ct$Year)`, total removals were negligible compared to the
modern fishery. Over the early period (`r min(ct$Year)`--1990) most removals
were from foreign or joint-venture fisheries. Across the time series, annual
catch in U.S. waters averaged `r f(mean(ct[["U.S. Total"]]))`~t
(`r f(sum(ct[["U.S. Total"]]) / sum(ct$Total) * 100, 1)`% of the total catch),
while catch from Canadian waters averaged `r f(mean(ct[["Canada Total"]]))`~t.
Over the last 10 years, `r max(ct$Year) - 9`--`r max(ct$Year)`
(Table \@ref(tab:es-catches-tab)), the average coast-wide catch was
`r ct_mean_10yrs`~t with U.S. and Canadian catches averaging
`r ct_us_mean_10yrs`~t and `r ct_can_mean_10yrs`~t, respectively. Since the peak
in 2017,
the coast-wide catch declined annually until 2024, with catches 
increasing in `r end_yr-1` to `r last_yr_landings`~t out of a total allowable catch (TAC, adjusted for
carryovers) of `r last_yr_tac`~t. Attainment in the U.S. was
`r last_yr_us_attained`% of its quota and in Canada it was
`r last_yr_can_attained`% in `r assess_yr - 1`.


```{r es-catches-tab, results = "asis", echo = FALSE}

table_catch(
  ct,
  inc_foreign_jv = FALSE,
  start_yr = end_yr - 10,
  end_yr = end_yr - 1,
  caption = paste0(
    "Total ", sp, " catch used in the assessment by sector for the most recent ",
    "ten years. U.S. tribal catches are included in the sectors where they are ",
    "represented."),
  font_size = 7,
  header_font_size = 7,
  longtable = TRUE)
```

In this document, the terms catch and landings are used interchangeably.
Estimates of discard within the target fishery are included but discarding
of `r sp` in non-target fisheries is not. Discard from all fisheries,
including those that do not target `r sp`, is estimated to be less than 1% of
landings in recent years. The coast-wide catches in `r  last_data_yr` are near the 
long-term average catch (`r f(long_term_avge_ct)`~t), but, particularly in Canada,
the catches have sharply declined over recent years. 

\rfoot{Stock biomass and recruitment}

# Stock biomass and recruitment {#sec:biomass-and-recruitment}

Results from the base model
indicate that since the 1960s, `r sp` female spawning biomass has ranged from
well below to above unfished equilibrium (Figure~\@ref(fig:es-biomass-fig)); see
@JTC2025 for historical details. 
The median of the `r end_yr` female spawning biomass is
`r curr_bio_median`~Mt (with a 95% posterior credibility interval from
`r curr_bio_lower` to `r curr_bio_upper`~Mt). All 95% credibility intervals are calculated as the 2.5% and 97.5%
quantiles of posterior distributions from Markov chain Monte Carlo samples, to give equal-tailed intervals.

The median of the `r end_yr` relative spawning biomass (spawning
biomass at the start of `r end_yr` divided by that at unfished equilibrium,
`r b_0`) is `r curr_depl_median`%. However, the uncertainty is large, with a
95% posterior credibility interval from `r curr_depl_lower`% to
`r curr_depl_upper`%, partly due to remaining
unknowns about the size of the
potentially large 2021 cohort because it has still only been observed once by the acoustic survey.

The probability that female spawning biomass at the start of
`r assess_yr` is below the `r b_40` (40% of `r b_0`) reference point is
`r probs_curr_below_b40`%, and the probability that relative fishing
intensity exceeded 1 in `r end_yr - 1` is
`r probs_curr_rel_fish_intens_above_1`%. The joint
probability of both these occurring is `r joint_percent_prob_above_below`%.

`r sp` have low to moderate recruitment (relative to the long-term average)
with occasional large year classes
(Figure~\@ref(fig:es-recruitment-fig)). Estimates of recruitment are
similar to those from @JTC2025. The size of the 2021 cohort remains highly uncertain due to limited
data (e.g., compare the uncertainty to that of of the 2016 cohort, a cohort that
that has a comparable median). 

(ref:es-biomass-cap) Median (solid line) of the posterior distribution for
beginning of the year female spawning biomass ($B_t$ in year $t$; Mt) through
`r end_yr` with 95% posterior credibility intervals (shaded area). The
left-most circle with a 95% posterior credibility interval is the estimated
unfished equilibrium biomass, `r b_0`.

(ref:es-biomass-alt) This figure shows that the median spawning biomass increased
from 2021 to 2025 and then declined in 2026.

```{r es-biomass-fig, fig.cap = "(ref:es-biomass-cap)", fig.height = 4.5, out.height = "4in"}

plot_biomass(list(base_model),
             list(base_model_name),
             ylim = c(0, 5),
             point_shape = 1,
             leg_pos = "none")
```

(ref:es-recruitment-cap) Medians (solid circles) and means ($\mathrm{X}$) of the
posterior distribution for recruitment (billions of age-0 fish) with 95%
posterior credibility intervals (vertical lines). The median of the
posterior distribution for mean unfished equilibrium recruitment ($R_0$) is
shown as the horizontal dashed line with the 95% posterior credibility
interval shaded between the dotted lines.

(ref:es-recruitment-alt) This figure shows that recruitment for each cohort.
There are currently three above-average cohorts in the stock with 2021 being
the fourth. The 2021 cohort is highly uncertain which can be seen in the
size of the credible interval.

```{r es-recruitment-fig, fig.cap = "(ref:es-recruitment-cap)", fig.height = 4.5, out.height = "4in"}

plot_recruitment(list(base_model),
                 list(base_model_name),
                 inc_means = TRUE,
                 leg_pos = "none")
```

\rfoot{Management performance}

# Management performance {#sec:management-performance}

Over the last decade (`r end_yr - 10`--`r end_yr - 1`), the mean coast-wide
utilization rate (proportion of catch target removed) has been
`r tot_last_10_yrs_attainment`% and catches have been below coast-wide
targets (Table~\@ref(tab:es-landings-tac-tab)). From `r end_yr - 5` to
`r end_yr - 1`, the mean utilization rates differed between the U.S.
(`r us_last_5_yrs_attainment`%) and Canada (`r can_last_5_yrs_attainment`%).
While Canada's rate was higher than the U.S.'s in 2020, it has dropped considerably
over the past several years to historic lows. The utilization rate for the coast-wide
fishery this year (`r tot_2025_attainment`%) increased relative to the last two years 
which had low attainment due to difficulties locating aggregations of fish during the spring and
throughout the year in northern areas.
The usual `r us_allotment_percent`% and `r can_allotment_percent`%
allocation of coast-wide TAC, as specified in the Joint U.S.-Canada
Agreement for `r sp`, was implemented for the `r last_assess_yr` fishery.
The U.S. proportion of the coast-wide catch has exceeded 90% in each of the last
four years. Total landings last exceeded the coast-wide quota in 2002
when utilization was 112%.

```{r es-landings-tac-tab, results = "asis", echo = FALSE}

table_landings_tac(
  ct,
  start_yr = end_yr - 10,
  end_yr = end_yr - 1,
  caption = paste0(
    "Recent trends in ", sp, " landings and management decisions. Catch ",
    "targets in 2020 and 2021 were specified unilaterally. All landings ",
    "and catch targets are given in tonnes."),
  font_size = 7,
  header_font_size = 7,
  longtable = TRUE)
```

\rfoot{Forecast decision tables}

# Forecast decision tables {#sec:forecast}

For the 2025 stock assessment [@JTC2025], the spawning biomass was estimated at the start
of 2025, and then projections were done assuming different catch scenarios that
specified catches in 2025 (now known) and 2026 (assumed alternatives). This
gave projected biomass quantities at the start of 2026. The
recruitment deviations were set to 0 for 2023 to 2026. This covers the two years
(2023 and 2024) for which no survey age data was used to fit the model, and the
two projection years (2025 and 2026). 
This was a change from previous stock assessments, in which deviations were
drawn from a distribution that could allow very large (or very small)
recruitments to occur and propagate through the projection years as the
cohorts matured. The change to no recruitment deviations was deemed
preferable for the 2025 assessment for several reasons, including that the
"information on the size 
of the 2023 year class from the 2024 fishery was considered suspect given the
unique fishing conditions during the year" [@JTC2025]. 
Allowing for recruitment deviations during forecast years could have allowed
 "potentially large recruitments that can inflate the forecast
biomass yet are based on limited or no data and so may not materialise in
practice" [@JTC2025]. 
We continue to apply no recruitment deviations for the 2026 base model for 2023 onwards
as we are using the same assumptions as for the 2025 base model, and we are not
fitting to new data. 

The assumption of not allowing for recruitment deviations in forecasts did cause the projected populations to decline for the 2025
assessment [@JTC2025] even with 0~t catch in the projection years. This is because the assumption removes the lognormal (skewed) distribution of recruitments,
with occasional large
recruitments that can pull the stock out of a decline, that has been seen
historically (Figure~\@ref(fig:es-recruitment-fig)). Instead, average recruitment (i.e., the
median resulting from the bias-corrected mean of the lognormal distribution)
leads to a constant recruitment level close to 0.38$R_0$ (Figure~\@ref(fig:es-recruitment-fig)), and does not allow for the occasional large recruitments 
seen when applying the lognormal distribution of recruitment deviations [e.g.,
see the broader distribution of potential 2023 and 2024 recruitments shown in Figure~f of the
2024 assessment, @JTC2024]. 

For this assessment, we present projections for just one year, rather than three
years as for previous assessments. Projections assume
various catch scenarios for 2026 and then forecast the biomass at the start of 2027.
This was done for two reasons:

1. As just outlined, the assumption of not using recruitment deviations during
   the forecast period is not a feasible
   long-term model assumption because the median recruitment is too low to sustain
   the population in perpetuity. Forecasting further years
   ahead will exacerbate this and lead to unrealistic results given past
   levels of `r sp` recruitment. 
1. The models in the 2024 and 2025 assessments both estimated a stock biomass
   somewhat larger than the biomass index from the 2023 survey; Figure~18 of
   @JTC2024 and Figure~17 of @JTC2025. Inclusion of the 2025 survey biomass
   index would have helped to determine the validity of this overfitting.
   Without the 2025 survey biomass index, it was deemed pragmatic to not overextend
   the forecasts too far ahead from 2023 survey.

In future assessments, the JTC will again consider reimplementing recruitment deviations and return to
providing multiple forecast years, as the model should be fit to more up-to-date data (including
the 2025 survey biomass and age data). 

The catch limit for `r min(forecast_yrs)` based on the default `r f_40_40_10`
harvest policy has a median of `r ct_limit_quantiles["median"]`~t with a
wide range of uncertainty, the 95% credibility interval being
`r ct_limit_quantiles["lower"]`--`r ct_limit_quantiles["upper"]`~t.

```{r es-decisions-biomass-tab, results = "asis", echo = FALSE}

let <- letters[seq_along(base_model$forecasts[[length(base_model$forecasts)]])]
last_let <- let[length(let)]

table_decision(
  base_model,
  is_catch_proj_model = TRUE,
  type = "biomass",
  forecast_inds =
    seq_along(base_model$forecasts[[length(base_model$forecasts)]]),
  num_yrs_to_show = 1,
  caption = paste0(
      "Forecast quantiles of Pacific Hake relative spawning biomass at the ",
      "beginning of the year. Catch alternatives are defined by letters a-",
      last_let, ". TAC: total allowable catch. HR: harvest rate."),
  bold_letters = TRUE,
  digits = 2,
  # Font values higher than 8 and 11 for table and header respectively
  # will cause the table to wrap to a second page
  font_size = 8,
  header_font_size = 11,
  # If the font is changed it is almost guaranteed that `left_col_cm` and
  # `right_cols_cm` will have to be changed, especially if the font is made
  # larger. You will have to check this with trial-and-error, building the
  # document, checking the table and adjusting, over and over until it looks
  # right
  left_col_cm = 3,
  right_cols_cm = 1.2,
  longtable = TRUE)
```

<!-- \clearpage -->

```{r es-decisions-spr-tab, results = "asis", echo = FALSE}

table_decision(
  base_model,
  type = "spr",
  is_catch_proj_model = TRUE,
  forecast_inds =
    seq_along(base_model$forecasts[[length(base_model$forecasts)]]),
  num_yrs_to_show = 1,
  inc_fi_stable_catch = length(base_model$forecasts[[1]]) == 13,
  caption = paste0(
      "Forecast quantiles of Pacific Hake relative fishing intensity ",
      rel_fishing_intensity_for_latex_table, ", expressed as a proportion. ",
      "Catch alternatives are defined by letters a-", last_let,
      ". TAC: total allowable catch. HR: harvest rate."),
  bold_letters = TRUE,
  digits = 2,
  # Font values higher than 8 and 11 for table and header respectively
  # will cause the table to wrap to a second page
  font_size = 8,
  header_font_size = 11,
  # If the font is changed it is almost guaranteed that `left_col_cm` and
  # `right_cols_cm` will have to be changed, especially if the font is made
  # larger
  left_col_cm = 3,
  right_cols_cm = 1.2,
  longtable = TRUE)
```

Decision tables give the projected population status (i.e., relative spawning
biomass) and fishing intensity relative to the target under different
catch alternatives for the base model (Tables~\@ref(tab:es-decisions-biomass-tab)
and~\@ref(tab:es-decisions-spr-tab)). The tables are organized to show the
projected outcome for each potential catch level and year (row) across the
quantiles (columns) of the posterior distribution. Tables show results for
one year of future catch levels based on subsequent projected stock
status and fishing intensity.
Figure~\@ref(fig:es-depletion-comparison-fig) shows the projected relative
spawning biomass for several of the catch alternatives. Population dynamics
and governing parameters assumed during the forecast period include selectivity,
weight-at-age and fecundity-at-age averaged over the five
most recent years of data (`r assess_yr - 6`--`r assess_yr - 2`), and constant
values for all other parameters; see @JTC2025.

(ref:es-depletion-comparison-cap) Median and 95% posterior
credibility intervals of relative spawning biomass to the start
of `r end_yr` from the base model and projections to the start of
`r forecast_yrs[2]` for several catch alternatives, which
are defined in Table~\@ref(tab:es-decisions-biomass-tab).

(ref:es-depletion-comparison-alt) This figure shows that the median
relative spawning biomass is projected to remain flat for the next year
with zero catch and to decline for all non-zero catch levels evaluated.

```{r es-depletion-comparison-fig, fig.cap = "(ref:es-depletion-comparison-cap)", fig.height = 4, out.height = "4in"}

# See the file `forecast-catch-levels.R` at the list called `ct_levels`. The values in
# `fore_inds` below are the indices of those forecast values in that list.
plot_depl_fore_comparison(base_model,
                          fore_inds = c(1, 2, 6, 7, 10),
                          forecast_yrs = forecast_yrs[1:2],
                          is_catch_proj = TRUE)
```

A relative fishing intensity of 1 should indicate fishing at the `r fspr_40`
default harvest rate catch target. But the projected median relative fishing
intensity can be slightly different than the target because the `r fspr_40`
default harvest-rate catch limit is calculated using baseline
selectivity-at-age (1966--1990; prior to time-varying deviations), whereas the
forecasted catches use selectivity averaged over the last five
years. Recent changes in selectivity will thus be reflected in the
determination of fishing relative to the default harvest policy. For example,
fishing at the `r fspr_40` default harvest-rate catch limit
(scenario `r letters[ct_levels_vals$ct_default_policy_ind]`: default HR)
in `r assess_yr` results in a median relative fishing intensity of
`r fi_at_hcr` (Table~\@ref(tab:es-decisions-spr-tab)).

With zero catch for 2026 and no recruitment deviations from 2023 onward, the biomass has an
`r zero_catch_prob_bio_down_1`% probability of decreasing from
`r forecast_yrs[1]` to `r forecast_yrs[2]` (Table~\@ref(tab:es-risk-year-1-tab) and
Figure~\@ref(fig:es-risk-year-1-fig)).
<!--and a `r zero_catch_prob_bio_down_3`% probability of decreasing from-->
<!--`r forecast_yrs[3]` to `r forecast_yrs[4]` (Table~\@ref(tab:es-risk-year-3-tab)-->
<!--and Figure~\@ref(fig:es-risk-year-1-fig)).-->

For all explored catches, the maximum probability of female spawning biomass at
the start of `r end_yr + 1` dropping below `r b_10` is
`r prob_max_below_10_yr1`% and of dropping below `r b_40` is
`r prob_max_below_40_yr1`% (Table~\@ref(tab:es-risk-year-1-tab) and
Figure~\@ref(fig:es-risk-year-1-fig)).
As the above average 2014 and 2016
cohorts continue to age, total biomass of these cohorts even without fishing
mortality is expected to decrease as losses from mortality outweigh increases
from growth. The estimated above-average 2021 cohort will continue to play a
large role in determining female spawning biomass during the forecast year
presented here.

\clearpage

(ref:es-risk-year-1-cap) Graphical representation of
the probabilities related to spawning biomass, relative fishing intensity, and
the `r end_yr + 1` default harvest policy catch for alternative `r end_yr`
catch options (explained in Table~\@ref(tab:es-decisions-biomass-tab)) as listed in
Table~\@ref(tab:es-risk-year-1-tab). The symbols indicate points that were computed
directly from model output and lines interpolate between the points.

(ref:es-risk-year-1-alt) This figure shows that the probability that the
stock declines in 2026 is 50 percent or greater for all catch levels including
zero. The probability that the stock falls under B40 is almost zero for
catches up to approximately 350 thousand tonnes.

```{r es-risk-year-1-fig, fig.cap = "(ref:es-risk-year-1-cap)", fig.height = 4.5, out.height = "4in"}

plot_fore_compare(base_model,
                  forecast_yrs = forecast_yrs,
                  fore_yr = forecast_yrs[1],
                  leg_pos = c(0.25, 0.65),
                  leg_font_size = 9,
                  remove_x_val = c(270)) +
  # Following make the legend smaller and legend items closer together
  theme(legend.key.size = unit(0.25, "cm"),
        legend.spacing.y = unit(0.01, "cm"),
        legend.box.background = element_rect(colour = "black")) +
  guides(color = guide_legend(byrow = TRUE))
```

```{r es-risk-year-1-tab, results = "asis", echo = FALSE}

# Index in models[[]]$risks to use, e.g. 1 means forecast year 2 compared
# to forecast year 1
table_risk(
  base_model,
  forecast_yrs,
  index = 1,
  type = "probability",
  is_catch_proj = TRUE,
  digits = 2,
  caption = paste0(
    "Probabilities related to spawning biomass, relative fishing intensity, ",
    "and the ", end_yr + 1, " default harvest policy catch for alternative ",
    end_yr, " catch options (catch options are explained in ",
    "Table~\\@ref(tab:es-decisions-biomass-tab))."),
  font_size = 10,
  header_font_size = 10,
  longtable = TRUE)
```

\clearpage

\rfoot{Response to `r end_yr - 1` SRG review}

# Response to `r end_yr - 1` Scientific Review Group (SRG) review {#sec:assessment-response-review}

The Scientific Review Group (SRG) meeting was held from February
10--14th, 2025, as a virtual meeting.

While this year is a projection based assessment, the JTC provides the following responses to the 2025 'SRG Recommendations and Conclusions for the Stock Assessment' to update the SRG about ongoing and future research plans:

1. **The SRG recommends a thorough analysis of catch and biomass distribution for Canada and US that examines latitudinal shifts over time, and seeks to explain poor fishery performance in recent years. The SRG recommends developing a limited set of standardized descriptive spatial distribution metrics (such as center of gravity) to support future year discussions.**

*Response -- The JTC continues to support an analysis across available data sources to better understand the current distribution of the stock along the U.S. West Coast. The planned work of building species distribution models incorporating environmental factors across the transboundary range of Pacific has been delayed due to staffing changes at the NWFSC.*

*The JTC is also continuing work evaluating patterns of Pacific Hake in the U.S. West Coast Bottom Trawl Survey in California waters where fishery data are limited. The JTC will also continue work investigating spatial fishing effort, catch, and revenue over time using data summary tools (e.g., [Pacific Fishing Effort Mapping Project](https://geo.psmfc.org/portal/apps/storymaps/stories/7bc1a025e2fd43e49efb011cd15e1d4e)).*

2. **The SRG recommends continuing sensitivities for steepness, natural mortality, σR, including the age-1 index, alternative standard deviations for time-varying selectivity, and down-weighting fishery age-composition data.**

*Response -- The recommended set of sensitivity model runs were not applicable
for the 2026 base model, which is based solely on a projection of the 2025 base
model where the realized total catch in 2025 is specifically used. The standard
set of sensitivity model runs was presented for the 2025 base model in the 2025
assessment [@JTC2025] and 
will be incorporated into next year's stock assessment.*

3. **The SRG recommends that the JTC continue exploring alternative ways of estimating natural mortality to update the current approach in the model, and particularly consider options which have age-based natural mortality, and may be external to SS3.**

*Response -- `r sp` have several natural predators, including themselves, particularly on younger ages. Recently, [Trzcinski et al. (2024)](https://www.int-res.com/articles/meps_oa/m743p113.pdf) identified `r sp` as the largest mean proportion of the diet of harbor seals. Additionally, the abundance of harbor seals is near carrying capacity in Canadian waters and has been since the late 1990s. Stock Synthesis allows for the inclusion of a predator index to estimate predation mortality in addition to baseline natural mortality. Data for predation mortality can be
absolute numbers of dead fish due to the predator, an index of predator effort, and predation composition (age or length) data. A predation index based on estimated abundance of harbor seals could be added to the assessment model, but this has not been explored.*

*A potential, better path forward is to use Dynamic Structural Equation Modeling (DSEM) to include indices for multiple predators and allow for two-way interactions between them and $M$. This capability is not, and will not be,
available within Stock Synthesis but is possible using models written in Template Model Builder. A proof of concept has been implemented at the Alaska Fisheries Science Center and work is ongoing to implement this in the Fisheries Integrated Modeling System (FIMS).*

*In 2025, the JTC presented sensitivities to using estimates of age-specific $M$ from the Climate- Enhanced, Age-based model with Temperature-specific Trophic Linkages and Energetics (CEATTLE) model as a way forward [@HolsmanEtAl2016]. Output from CEATTLE includes time series of estimates of baseline $M$ and estimates of $M$ at age for ages 0--1, 2, 3, 4, 5, and 6$^+$, where the $M$ at-age estimates are strictly natural mortality due to cannibalism.* 

*The JTC plans to continue to evaluate how to account for age-based and potentially time-varying mortality in future assessments.*

4. **The SRG recommends examining alternative structural assumptions for the stock assessment. More complex structural assumptions may utilize the data more thoroughly, explain different trends across areas and/or fleets, and estimate stock status more accurately, but simpler models may be more appropriate for determination of the TAC. The MSE can be used to determine best performing assessment models for management. Priority avenues of examinations include multiple fleets (e.g., fleets-as-areas) and alternative parametric and time-varying (or time-invariant) selectivity patterns.**

*Response -- The JTC plans to continue work to evaluate the multitude of changes in the assessment process itself (e.g., data availability, assumptions, etc.) that would be needed to develop alternative model structures. This includes the development of a research plan, including complimentary or standalone analyses, alternative model structures to explore, and simulation analyses to evaluate and compare alternative models (e.g., using one or more tools, such as MSE).*

*The JTC has begun the preliminary work of splitting catch and age data starting in 1991 for each country to evaluate an alternative model structure that splits data by country from 1991 onward with all historical data (1966-1990) in a combined U.S./Canada fleet. The JTC will brief the SRG about preliminary work at the 2026 meeting.*

*Other steps the JTC plans to take in the future include evaluating alternative data and model assumptions that arise for validity given proposed new model structures; evaluating variance and bias trade-offs associated with new parameterizations (e.g., doubling the number of time-varying selectivity parameters when doubling the number of fleets); comparing alternative spatially-implicit assessment approaches (e.g., time-varying selectivity versus area-varying selectivity, or both); and developing states of nature scenarios to test model structure robustness in an MSE framework.
Additionally, model complexity in the spatial domain needs to be addressed relative to other structural assumptions in the assessment model. Other assumptions may be more influential or have confounding or complimentary impacts on model sensitivity and robustness. These may include data weighting, improving estimates of natural mortality via predator time series, multiple fleets instead of a single aggregated fleet, and using fleet-specific weight-at-age data instead of aggregated weight-at-age (the JTC has looked at this before, but it hasn’t been revisited in over a decade).*

*Changes to the structure of the assessment model may not be the most immediate
need for understanding changes in hake distribution. Some of the other (higher
priority) SRG requests noted above will help with understanding fundamental
mechanisms, which can help to formulate hypotheses to inform relevant model
structures. These include spatial CPUE modeling, investigating hake distribution
changes in bottom trawl surveys, and correlating hake distribution changes with
the California Current Integrated Ecosystem Assessment.*

5. **The SRG recommends considering including the eDNA index of abundance for inclusion in the assessment as a second index of abundance for Pacific Hake, also estimating additional variance for the index given the small nominal CV values.**

*Response -- The JTC will continue to consider the eDNA index in future full assessments. Water samples were collected during the 2025 survey for enumeration of eDNA, providing a fourth year in the eDNA index time series once laboratory processing and subsequent statistical analyses have been completed (expected by Spring 2026).*

6. **The SRG recommends that the JTC continue investigating how to include the age-1 index in the stock assessment in this or future assessment frameworks, but notes that the selectivity/catchability of the gear is expected to change depending on the AWT or MFT gear used in the survey.**

*Response -- The JTC is following the progress of the net selectivity work being conducted by the IWCPS team, which will be a critical component to better understand changes in the sampling of age-1 hake and the potential options for including any age-1 index in future stock assessments.*

7. **The SRG encourages the JTC to consider alternative methods to determine the maximum input sample size for the age compositions (e.g. Stewart and Hamel 2014, Hulson et al. 2023).**

*Response -- The JTC agrees that determining input sample sizes is important for fishery and survey age compositions, which then provides the basis from which model-based re-weighting is done. The JTC has considered alternative methods and has determined additional research is needed to inform the calculation of input sample size for both fishery and survey ages. Fishery input sample sizes are calculated using a mixture of either the number of hauls or trips, when haul information is not available (e.g., shoreside), and further work is needed to determine the effective sample sizes at the haul and trip level and how to calculate a fleet-wide input sample size.  Additionally, there is intersection between this research and alternative model fleet structure and the impact of alternative ways to determine input sample size within each fleet which the JTC will consider in ongoing research.*

*Sensitivity analyses using alternative input sample sizes, following the Stewart and Hamel (2014) approach, will continue to be evaluated in subsequent assessments.*

\newpage
