
\rfoot{Catches}

# Catches {#sec:catches}

(ref:es-catches-cap) Total `r sp` catch used in the assessment by sector,
`r start_yr`--`r last_data_yr`. U.S. tribal catches are included in the
sectors where they are represented.

(ref:es-catches-alt) This figure shows that catches in four of the last six
years have been the largest in the time series.

```{r es-catches-fig, fig.cap = "(ref:es-catches-cap)", fig.height = 4, out.height = "4in"}

plot_catches(ct, xlim = c(start_yr, last_data_yr))
```


Coast-wide fishery landings of `r sp` averaged `r f(mean(ct$Total))`~t
from `r min(ct$Year)` to `r max(ct$Year)`, with a low of
`r f(min(ct$Total))`~t in
`r ct$Year[ct$Total == min(ct$Total)]` and a peak of
`r f(max(ct$Total))`~t in
`r ct$Year[ct$Total == max(ct$Total)]`
(Figure \@ref(fig:es-catches-fig)).
Prior to `r min(ct$Year)`, total removals were negligible compared to the
modern fishery. Over the early period (`r min(ct$Year)`--1990) most removals
were from foreign or joint-venture fisheries. Across the time series, annual
catch in U.S. waters averaged `r f(mean(ct[["U.S. Total"]]))`~t
(`r f(sum(ct[["U.S. Total"]]) / sum(ct$Total) * 100, 1)`% of the total catch),
while catch from Canadian waters averaged `r f(mean(ct[["Canada Total"]]))`~t.
Over the last 10 years, `r max(ct$Year) - 9`--`r max(ct$Year)`
(Table \@ref(tab:es-catches-tab)), the average coast-wide catch was
`r ct_mean_10yrs`~t with U.S. and Canadian catches averaging
`r ct_us_mean_10yrs`~t and `r ct_can_mean_10yrs`~t, respectively. Since 2017,
the coast-wide catch has been declining annually through `r end_yr - 1` to
`r last_yr_landings`~t out of a total allowable catch (TAC, adjusted for
carryovers) of `r last_yr_tac`~t. Attainment in the U.S. was
`r last_yr_us_attained`% of its quota and in Canada it was
`r last_yr_can_attained`% in `r assess_yr - 1`.


```{r es-catches-tab, results = "asis", echo = FALSE}

table_catch(
  ct,
  inc_foreign_jv = FALSE,
  start_yr = end_yr - 10,
  end_yr = end_yr - 1,
  caption = paste0(
    "Total ", sp, " catch used in the assessment by sector for the most recent ",
    "ten years. U.S. tribal catches are included in the sectors where they are ",
    "represented."),
  font_size = 7,
  header_font_size = 7,
  longtable = TRUE)
```

In this document, the terms catch and landings are used interchangeably.
Estimates of discard within the target fishery are included but discarding
of `r sp` in non-target fisheries is not. Discard from all fisheries,
including those that do not target `r sp`, is estimated to be less than 1% of
landings in recent years. The catches in `r  last_data_yr` declined below
the long-term average catch (`r f(long_term_avge_ct)`~t), continuing the
pattern of declining catches over recent years (especially in Canada). 

\rfoot{Management performance}

# Management performance {#sec:management-performance}

Over the last decade (`r end_yr - 10`--`r end_yr - 1`), the mean coast-wide
utilization rate (proportion of catch target removed) has been
`r tot_last_10_yrs_attainment`% and catches have been below coast-wide
targets (Table~\@ref(tab:es-landings-tac-tab)). From `r end_yr - 5` to
`r end_yr - 1`, the mean utilization rates differed between the U.S.
(`r us_last_5_yrs_attainment`%) and Canada (`r can_last_5_yrs_attainment`%).
While Canada's rate was higher than the U.S.'s in 2020, it has dropped considerably
over the past several years to historic lows. The utilization rate for the coast-wide
fishery this year (`r tot_2025_attainment`%) increased relative to the last two years 
which had low attainment due to difficulties locating aggregations of fish during the spring and
throughout the year in northern areas.
The usual `r us_allotment_percent`% and `r can_allotment_percent`%
allocation of coast-wide TAC, as specified in the Joint U.S.-Canada
Agreement for `r sp`, was implemented for the `r last_assess_yr` fishery.
The U.S. proportion of the coastwide catch has exceeded 90% in each of the last
four years. Total landings last exceeded the coast-wide quota in 2002
when utilization was 112%.

```{r es-landings-tac-tab, results = "asis", echo = FALSE}

table_landings_tac(
  ct,
  start_yr = end_yr - 10,
  end_yr = end_yr - 1,
  caption = paste0(
    "Recent trends in ", sp, " landings and management decisions. Catch ",
    "targets in 2020 and 2021 were specified unilaterally. All landings ",
    "and catch targets are given in tonnes."),
  font_size = 7,
  header_font_size = 7,
  longtable = TRUE)
```

\rfoot{Forecast decision tables}

# Forecast decision tables {#sec:forecast}

TODO: Text here is unedited from last year's Executive summary.

The catch limit for `r min(forecast_yrs)` based on the default `r f_40_40_10`
harvest policy has a median of `r ct_limit_quantiles["median"]`~t with a
wide range of uncertainty, the 95% credibility interval being
`r ct_limit_quantiles["lower"]`--`r ct_limit_quantiles["upper"]`~t.

Decision tables give the projected population status (relative spawning
biomass) and fishing intensity relative to the target under different
catch alternatives for the base model (Tables~\@ref(tab:es-decisions-biomass-tab)
and~\@ref(tab:es-decisions-spr-tab)). The tables are organized to show the
projected outcome for each potential catch level and year (row) across the
quantiles (columns) of the posterior distribution. Tables show results for up
to three years (only two years in subsequent assessments following JMC advice)
of future catch levels based on subsequent estimates of stock
status and fishing intensity.
Figure~\@ref(fig:es-depletion-comparison-fig) shows the projected relative
spawning biomass for several of the catch alternatives. Population dynamics
and governing parameters assumed during the forecast period include selectivity,
weight-at-age and fecundity-at-age averaged over the five
most recent years (`r assess_yr - 5`--`r assess_yr - 1`), and constant
values for all other parameters.

A relative fishing intensity of 1 should indicate fishing at the `r fspr_40`
default harvest rate catch target. But, the projected median relative fishing
intensity can be slightly different than the target because the `r fspr_40`
default harvest-rate catch limit is calculated using baseline
selectivity-at-age (1966--1990; prior to time-varying deviations), whereas the
forecasted catches use selectivity averaged over the last five
years. Recent changes in selectivity will thus be reflected in the
determination of fishing relative to the default harvest policy. For example,
fishing at the `r fspr_40` default harvest-rate catch limit
(scenario `r letters[ct_levels_vals$ct_default_policy_ind]`: default HR)
in `r assess_yr - 1` results in a median relative fishing intensity of
`r fi_at_hcr` (Table~\@ref(tab:es-decisions-spr-tab)).

Management metrics that were identified as important to the Joint Management
Committee and the Advisory Panel in 2012 are presented for
`r forecast_yrs[2]` and `r forecast_yrs[3]` projections
(Tables~\@ref(tab:es-risk-year-1-tab) and~\@ref(tab:es-risk-year-2-tab);
Figures~\@ref(fig:es-risk-year-1-fig) and~\@ref(fig:es-risk-year-2-fig)).
These metrics summarize the probability of various outcomes from the base model
given each potential management action. Although not linear, probabilities can
be interpolated from these results with reasonable accuracy for intermediate catch values in
`r assess_yr` (Table~\@ref(tab:es-risk-year-1-tab) and
Figure~\@ref(fig:es-risk-year-1-fig)).
However, interpolation is not appropriate for the default harvest rule scenario
in `r assess_yr + 1` because it is conditional on the `r assess_yr` catch.

```{r es-decisions-biomass-tab, results = "asis", echo = FALSE}

let <- letters[seq_along(base_model$forecasts[[length(base_model$forecasts)]])]
last_let <- let[length(let)]

table_decision(
  base_model,
  is_catch_proj_model = TRUE,
  type = "biomass",
  forecast_inds =
    seq_along(base_model$forecasts[[length(base_model$forecasts)]]),
  caption = paste0(
      "Forecast quantiles of Pacific Hake relative spawning biomass at the ",
      "beginning of the year. Catch alternatives are defined by letters a-",
      last_let, " and are a constant value across all forecasted years unless ",
      "otherwise defined in the first column. Acronyms are defined in the ",
      "glossary (Appendix~\\@ref(sec:app-glossary))."),
  bold_letters = TRUE,
  digits = 2,
  # Font values higher than 8 and 11 for table and header respectively
  # will cause the table to wrap to a second page
  font_size = 8,
  header_font_size = 11,
  # If the font is changed it is almost guaranteed that `left_col_cm` and
  # `right_cols_cm` will have to be changed, especially if the font is made
  # larger. You will have to check this with trial-and-error, building the
  # document, checking the table and adjusting, over and over until it looks
  # right
  left_col_cm = 3,
  right_cols_cm = 1.2,
  longtable = TRUE)
```

\clearpage

```{r es-decisions-spr-tab, results = "asis", echo = FALSE}

table_decision(
  base_model,
  type = "spr",
  is_catch_proj_model = TRUE,
  forecast_inds =
    seq_along(base_model$forecasts[[length(base_model$forecasts)]]),
  inc_fi_stable_catch = length(base_model$forecasts[[1]]) == 13,
  caption = paste0(
      "Forecast quantiles of Pacific Hake relative fishing intensity ",
      rel_fishing_intensity_for_latex_table, ", expressed as a proportion. ",
      "Catch alternatives are defined by letters a-", last_let, " and are a constant ",
      "value across all forecasted years unless otherwise defined in the ",
      "first column. Acronyms are defined in the glossary ",
      "(Appendix~\\@ref(sec:app-glossary))."),
  bold_letters = TRUE,
  digits = 2,
  # Font values higher than 8 and 11 for table and header respectively
  # will cause the table to wrap to a second page
  font_size = 8,
  header_font_size = 11,
  # If the font is changed it is almost guaranteed that `left_col_cm` and
  # `right_cols_cm` will have to be changed, especially if the font is made
  # larger
  left_col_cm = 3,
  right_cols_cm = 1.2,
  longtable = TRUE)
```


(ref:es-depletion-comparison-cap) Median and 95% posterior
credibility intervals of estimated relative spawning biomass to the start
of `r end_yr` from the base model and projections to the start of
`r forecast_yrs[length(forecast_yrs)]` for several catch alternatives, which
are defined in Table~\@ref(tab:es-decisions-biomass-tab).

(ref:es-depletion-comparison-alt) This figure shows that the median
relative spawning biomass is projected to remain flat for the next 3 years
with zero catch and to decline for all non-zero catch levels evaluated.

```{r es-depletion-comparison-fig, fig.cap = "(ref:es-depletion-comparison-cap)", fig.height = 4, out.height = "4in"}

# See the file `forecast-catch-levels.R` at the list called `ct_levels`. The values in
# `fore_inds` below are the indices of those forecast values in that list.
plot_depl_fore_comparison(base_model,
                          fore_inds = c(1, 2, 6, 7, 10),
                          forecast_yrs = forecast_yrs,
                          is_catch_proj = TRUE)
```

\clearpage

\rfoot{Response to `r end_yr - 1` Scientific Review Group (SRG) review}

# Response to `r end_yr - 1` Scientific Review Group (SRG) review {#sec:assessment-response-review}

The Scientific Review Group (SRG) meeting was held from February
10--14th, 2025, as a virtual meeting.

While this year is a projection based assessment, the JTC provides the following responses to the 2025 'SRG Recommendations and Conclusions for the Stock Assessment' to update the SRG about ongoing and future research plans:

1. **The SRG recommends a thorough analysis of catch and biomass distribution for Canada and US that examines latitudinal shifts over time, and seeks to explain poor fishery performance in recent years. The SRG recommends developing a limited set of standardized descriptive spatial distribution metrics (such as center of gravity) to support future year discussions.**

*Response -- The JTC continues to support an analysis across available data sources to better understand the current distribution of the stock along the U.S. West Coast. The planned work of building species distribution models incorporating environmental factors across the transboundary range of Pacific has been delayed due to staffing changes at the NWFSC.*

*The JTC is also continuing work evaluating patterns of Pacific Hake in the U.S. West Coast Bottom Trawl Survey in California waters where fishery data are limited. The JTC will also continue work investigating spatial fishing effort, catch, and revenue over time using data summary tools (e.g., [Pacific Fishing Effort Mapping Project](https://geo.psmfc.org/portal/apps/storymaps/stories/7bc1a025e2fd43e49efb011cd15e1d4e)).*

2. **The SRG recommends continuing sensitivities for steepness, natural mortality, σR, including the age-1 index, alternative standard deviations for time-varying selectivity, and down-weighting fishery age-composition data.**

*Response -- The recommended set of sensitivity model runs were not applicable for the 2026 base model, which is based solely on a projection of the 2025 base model where the realized total catch in 2025 is specifically used. The standard set of sensitivity model runs will be incorporated into next year's stock assessment.*

3. **The SRG recommends that the JTC continue exploring alternative ways of estimating natural mortality to update the current approach in the model, and particularly consider options which have age-based natural mortality, and may be external to SS3.**

*Response -- `r sp` have several natural predators, including themselves, particularly on younger ages. Recently, [Trzcinski et al. (2024)](https://www.int-res.com/articles/meps_oa/m743p113.pdf) identified `r sp` as the largest mean proportion of the diet of harbor seals. Additionally, the abundance of harbor seals is near carrying capacity in Canadian waters and has been since the late 1990s. Stock Synthesis allows for the inclusion of a predator index to estimate predation mortality in addition to baseline natural mortality. Data for predation mortality can be
absolute numbers of dead fish due to the predator, an index of predator effort, and predation composition (age or length) data. A predation index based on estimated abundance of harbor seals could be added to the assessment model, but this has not been explored.*

*A potential, better path forward is to use Dynamic Structural Equation Modeling (DSEM) to include indices for multiple predators and allow for two-way interactions between them and $M$. This capability is not, and will not be,
available within Stock Synthesis but is possible using models written in Template Model Builder. A proof of concept has been implemented at the Alaska Fisheries Science Center and work is ongoing to implement this in the Fisheries Integrated Modeling System (FIMS).*

*In 2025, the JTC presented sensitivities to using estimates of age-specific $M$ from the Climate- Enhanced, Age-based model with Temperature-specific Trophic Linkages and Energetics (CEATTLE) model as a way forward [@HolsmanEtAl2016]. Output from CEATTLE includes time series of estimates of baseline $M$ and estimates of $M$ at age for ages 0--1, 2, 3, 4, 5, and 6$^+$, where the $M$ at-age estimates are strictly natural mortality due to cannibalism.* 

*The JTC plans to continue to evaluate how to account for age-based and potentially time-varying mortality in future assessments.*

4. **The SRG recommends examining alternative structural assumptions for the stock assessment. More complex structural assumptions may utilize the data more thoroughly, explain different trends across areas and/or fleets, and estimate stock status more accurately, but simpler models may be more appropriate for determination of the TAC. The MSE can be used to determine best performing assessment models for management. Priority avenues of examinations include multiple fleets (e.g., fleets-as-areas) and alternative parametric and time-varying (or time-invariant) selectivity patterns.**

*Response -- The JTC plans to continue work to evaluate the multitude of changes in the assessment process itself (e.g., data availability, assumptions, etc.) that would be needed to develop alternative model structures. This includes the development of a research plan, including complimentary or standalone analyses, alternative model structures to explore, and simulation analyses to evaluate and compare alternative models (e.g., using one or more tools, such as MSE).*

*The JTC has begun the preliminary work of splitting catch and age data starting in 1992 for each country to evaluate an alternative model structure that splits data by country from 1992 onward with all historical data (1996-1991) in a combined U.S./Canada fleet. The JTC will brief the SRG about preliminary work at the 2026 meeting.*

*Other steps the JTC plans to take in the future include evaluating alternative data and model assumptions that arise for validity given proposed new model structures; evaluating variance and bias trade-offs associated with new parameterizations (e.g., doubling the number of time-varying selectivity parameters when doubling the number of fleets); comparing alternative spatially-implicit assessment approaches (e.g., time-varying selectivity versus area-varying selectivity, or both); and developing states of nature scenarios to test model structure robustness in an MSE framework.
Additionally, model complexity in the spatial domain needs to be addressed relative to other structural assumptions in the assessment model. Other assumptions may have a higher propensity to be influential and be more sensitive to model results. These may include data weighting, improving estimates of natural mortality via predator time series, multiple fleets instead of a single aggregated fleet, and using fleet-specific weight-at-age data instead of aggregated weight-at-age (the JTC has looked at this before, but it hasn’t been revisited in over a decade).*

*Changes to the structure of the assessment model may not be the most immediate need for understanding changes in hake distribution. Some of the other (higher priority) SRG requests noted above will help with understanding fundamental mechanisms, which can help to formulate hypotheses to inform relevant model structures. These include spatial CPUE modeling, investigating hake distribution changes in bottom trawl surveys, correlating hake distribution changes with California Current Integrated Ecosystem Assessment.*

5. **The SRG recommends considering including the eDNA index of abundance for inclusion in the assessment as a second index of abundance for Pacific hake, also estimating additional variance for the index given the small nominal CV values.**

*Response -- The JTC will continue to consider the eDNA index in future full assessments. Water samples were collected during the 2025 survey for enumeration of eDNA, providing a fourth year in the eDNA index time series once laboratory processing and subsequent statistical analyses have been completed (expected by Spring 2026).*

6. **The SRG recommends that the JTC continue investigating how to include the age-1 index in the stock assessment in this or future assessment frameworks, but notes that the selectivity/catchability of the gear is expected to change depending on the AWT or MFT gear used in the survey.**

*Response -- The JTC is following the progress of the net selectivity work being conducted by the IWCPS team, which will be a critical component to better understand changes in the sampling of age-1 hake and the potential options for including any age-1 index in future stock assessments.*

7. **The SRG encourages the JTC to consider alternative methods to determine the maximum input sample size for the age compositions (e.g. Stewart and Hamel 2014, Hulson et al. 2023).**

*Response -- The JTC agrees that determining input sample sizes is important for fishery and survey age compositions, which then provides the basis from which model-based re-weighting is done. The JTC has considered alternative methods and has determined additional research is needed to inform the calculation of input sample size for both fishery and survey ages. Fishery input sample sizes are calculated using a mixture of either the number of hauls or trips, when haul information is not available (e.g., shoreside), and further work is needed to determine the effective sample sizes at the haul and trip level and how to calculate a fleet-wide input sample size.  Additionally, there is intersection between this research and alternative model fleet structure and the impact of alternative ways to determine input sample size within each fleet which the JTC will consider in ongoing research.*

*Sensitivity analyses using alternative input sample sizes, following the Stewart and Hamel (2014) approach, will continue to be evaluated in subsequent assessments.*

\newpage