
\rfoot{Assessment}

# Assessment {#sec:assessment}

## Modeling results {#sec:assessment-modeling-results}

### Changes from `r last_assess_yr` {#sec:assessment-changes}

A `bridging' model was constructed to evaluate the component-specific
effects of the steps to change from the `r last_assess_yr` base model to
the `r assess_yr` base model. The steps are as follows:

- Update to the latest version of Stock Synthesis, version `r ss_version`, to
follow current best practices;

Stock Synthesis version `r ss_version` includes a number of changes since the
version used by @JTC2024. However, none of the changes were specifically relevant
to this assessment, and thus, the software update had no effect on assessment
results (Figure~\@ref(fig:main-bridge-summary-1-fig)).

## Stock {-}

TODO: Text here is unedited from last year's Executive summary.

This assessment reports the status of the coastal `r sp` (or `r common_name`,
*`r science_name`*) stock off the west coast of the United States (U.S.) and Canada
at the start of `r assess_yr`. This stock exhibits seasonal migratory
behavior, ranging from offshore and generally southern waters during the
winter spawning season to coastal areas between northern California and
northern British Columbia during the spring, summer, and fall when the
fishery is conducted. The stock tends to move farther to the north during the
summer in years with warmer water compared to years with colder waters. Older
`r sp` tend to migrate farther north than younger `r sp` in all years, with
catches in Canadian waters typically consisting of fish greater than four years
old. Separate, and much smaller, populations of `r sp` occurring in the major
inlets of the Northeast Pacific Ocean, including the Strait of Georgia, Puget
Sound, and the Gulf of California, are not included in this analysis.

## Catches {-}

(ref:es-catches-cap) Total `r sp` catch used in the assessment by sector,
`r start_yr`--`r last_data_yr`. U.S. tribal catches are included in the
sectors where they are represented.

(ref:es-catches-alt) This figure shows that catches in four of the last six
years have been the largest in the time series.

```{r es-catches-fig, fig.cap = "(ref:es-catches-cap)", fig.height = 4}

plot_catches(ct, xlim = c(start_yr, last_data_yr))
```

TODO: Text here is unedited from last year's Executive summary.

Coast-wide fishery landings of `r sp` averaged `r f(mean(ct$Total))`~t
from `r min(ct$Year)` to `r max(ct$Year)`, with a low of
`r f(min(ct$Total))`~t in
`r ct$Year[ct$Total == min(ct$Total)]` and a peak of
`r f(max(ct$Total))`~t in
`r ct$Year[ct$Total == max(ct$Total)]`
(Figure \@ref(fig:es-catches-fig)).
Prior to `r min(ct$Year)`, total removals were negligible compared to the
modern fishery. Over the early period (`r min(ct$Year)`--1990) most removals
were from foreign or joint-venture fisheries. Across the time series, annual
catch in U.S. waters averaged `r f(mean(ct[["U.S. Total"]]))`~t
(`r f(sum(ct[["U.S. Total"]]) / sum(ct$Total) * 100, 1)`% of the total catch),
while catch from Canadian waters averaged `r f(mean(ct[["Canada Total"]]))`~t.
Over the last 10 years, `r max(ct$Year) - 9`--`r max(ct$Year)`
(Table \@ref(tab:es-catches-tab)), the average coast-wide catch was
`r ct_mean_10yrs`~t with U.S. and Canadian catches averaging
`r ct_us_mean_10yrs`~t and `r ct_can_mean_10yrs`~t, respectively. Since 2017,
the coast-wide catch has been declining annually through `r end_yr - 1` to
`r last_yr_landings`~t out of a total allowable catch (TAC, adjusted for
carryovers) of `r last_yr_tac`~t. Attainment in the U.S. was
`r last_yr_us_attained`% of its quota and in Canada it was
`r last_yr_can_attained`% in `r assess_yr - 1`.


```{r es-catches-tab, results = "asis", echo = FALSE}

table_catch(
  ct,
  inc_foreign_jv = FALSE,
  start_yr = end_yr - 10,
  end_yr = end_yr - 1,
  caption = paste0(
    "Total ", sp, " catch used in the assessment by sector for the most recent ",
    "ten years. U.S. tribal catches are included in the sectors where they are ",
    "represented."),
  font_size = 7,
  header_font_size = 7,
  longtable = TRUE)
```

In this document, the terms catch and landings are used interchangeably.
Estimates of discard within the target fishery are included but discarding
of `r sp` in non-target fisheries is not. Discard from all fisheries,
including those that do not target `r sp`, is estimated to be less than 1% of
landings in recent years. The catches in `r  last_data_yr` declined below
the long-term average catch (`r f(long_term_avge_ct)`~t), continuing the
pattern of declining catches over recent years (especially in Canada). Landings
between 2001 and 2008 were predominantly comprised of fish from the very large
1999 year class, with a cumulative removal (through `r end_yr - 1`) from
that cohort of
`r f(cohort_catch_1999 / 1e6, 2)` Mt [1~Mt = 1~million metric tonnes].
Through `r last_data_yr`, the cumulative catches of the 2010, 2014, and 2016
year classes were estimated at
`r f(cohort_catch_2010 / 1e6, 2)`~Mt,
`r f(cohort_catch_2014 / 1e6, 2)`~Mt, and
`r f(cohort_catch_2016 / 1e6, 2)`~Mt, respectively. In the
`r end_yr - 1` catch, `r top_coh(base_model, last_data_yr, 3, cap = FALSE)`.

## Data and assessment {-}

TODO: Text here is unedited from last year's Executive summary.

This Joint Technical Committee (JTC) assessment depends on fishery
landings (`r start_yr`--`r last_data_yr`), an acoustic survey biomass index
of age-2$+$ fish (Figure~\@ref(fig:es-survey-biomass-fig)) and age compositions
(`r survey_start_yr`--`r survey_end_yr`),
fishery age compositions (`r start_yr_age_comps`--`r last_data_yr`),
maturity-at-age data, and
weight-at-age data (`r start_yr_age_comps`--`r last_data_yr`). In 2011,
the survey biomass index of age-2$+$ fish was the lowest in the time series and was followed
by the index increasing in 2012, 2013, and again in 2015 before decreasing to
near the time series average in 2017. The survey
(Figure~\@ref(fig:es-survey-biomass-fig)) shows a decline from 2019 (the fourth
highest of the series) to 2023 (the third lowest of the series).
Age-composition data from the aggregated fisheries and the acoustic survey
provide data that facilitates estimating relative
cohort strength, i.e., strong and weak cohorts.
No survey data are used to inform the size of the
`r last_data_yr-2`--`r last_data_yr` year classes.

(ref:es-survey-biomass-cap) Acoustic survey biomass index of age-2$+$ fish
(Mt). Approximate 95% confidence intervals are based on
sampling variability (intervals without the additional squid/`r sp`
apportionment uncertainty included in 2009, black line).

(ref:es-survey-biomass-alt) This figure shows that the survey estimate has
decreased from 2019 to 2021.

```{r es-survey-biomass-fig, fig.cap = "(ref:es-survey-biomass-cap)"}

plot_survey_biomass(base_model, index = "age2")
```

The assessment uses a Bayesian estimation approach, sensitivity analyses, and
retrospective investigations to evaluate the potential consequences of
parameter uncertainty, alternative structural models, and historical
performance of the assessment model, respectively. The Bayesian approach
combines prior knowledge about natural mortality, stock--recruitment steepness
(e.g., a parameter for stock productivity), and several other parameters, with
likelihoods for the acoustic survey biomass index, acoustic survey
age-composition data, and fishery age-composition
data. Integrating the joint posterior distribution over model parameters
provides probabilistic inferences about uncertain model parameters and
forecasts derived from those parameters; this is done via Markov chain Monte
Carlo sampling using the efficient No-U-Turn Sampler (NUTS). Sensitivity
analyses are used to identify alternative model assumptions that may also
be consistent with the data. All models, including bridging, sensitivity,
and retrospective models, use a Bayesian framework for estimation.
Retrospective analyses identify possible poor performance of the assessment
model with respect to future predictions. Past assessments have conducted
closed-loop simulations that provide insights into how alternative
combinations of survey frequency, assessment model selectivity assumptions,
changes in the distribution or `r sp`, and harvest control rules affect expected
management outcomes given repeated application of these procedures over
the long term. The results of past (and ongoing) closed-loop simulations
help inform decisions made for this assessment.

This `r assess_yr` assessment is again configured using Stock Synthesis. The
same general population dynamics structure as the base assessment model from
`r last_assess_yr` was used except for terminal recruitment and forecast
recruitment deviations (so from 2023 onwards), which were fixed at zero in this assessment.
Updates to data in this assessment include incorporating
<!-- the new biomass estimate and age-composition data from the acoustic survey conducted in `r survey_end_yr`, -->
fishery catch and age-composition data from `r end_yr-1`, weight-at-age data for
`r end_yr-1`,
maturity-at-age data for `r end_yr-2`,
<!-- the `r survey_end_yr` age-1 index estimate, -->
and minor changes to pre-`r end_yr-1` data. The model-based
approaches used to develop the input weight-at-age matrix and time-varying
temperature-dependent maturity were retained from last year's assessment
to inform fecundity.

The relative index of age-1 fish from the survey was not used to fit this
assessment model because it was found to have a strong influence on estimates
of recruitment even for cohorts that had several years of data, and because it lacks
time-specific measurements of uncertainty.
Thus, the only data point that can directly inform the size of
the 2023 cohort is from age-1 observations in the commercial fishery
in 2024. Given the unique seasonal
fishing conditions during the year and that this fishery-dependent data point
can be overly influential on the
estimated 2023 recruitment, estimated recruitment in 2023 was
based solely on the stock--recruitment relationship, with no estimated
recruitment deviations (i.e., deviations fixed at zero, giving average recruitment).
By necessity, this was also done for 2024 and the
projection years. This differs to previous assessment models, for which
recruitments at the end of the time series included a random component (extra variability
around the stock-recruitment relationship).

This assessment continues to use (since 2014) time-varying
(rather than constant) selectivity to maintain flexibility within the
fishery dynamics given variability in `r sp` distribution patterns.
The Dirichlet-multinomial estimation approach to weighting composition data
was retained, and a sensitivity to an alternative data-weighting approach was
investigated. Time-varying fecundity, which was introduced in 2019, was
retained and improved upon with time-varying estimates of maturity in 2024.
Assumptions for the forecast period for weight at age, maturity at age, and
selectivity continue to be based on conditions during the last five years,
as done since the 2020 assessment.

## Management performance {-}

TODO: Text here is unedited from last year's Executive summary.

Over the last decade (`r end_yr - 10`--`r end_yr - 1`), the mean coast-wide
utilization rate (proportion of catch target removed) has been
`r tot_last_10_yrs_attainment`% and catches have been below coast-wide
targets (Table~\@ref(tab:es-landings-tac-tab)). From `r end_yr - 5` to
`r end_yr - 1`, the mean utilization rates differed between the U.S.
(`r us_last_5_yrs_attainment`%) and Canada (`r can_last_5_yrs_attainment`%).
While Canada's rate was higher than the U.S.'s in 2020, it has dropped considerably
over the past few years to historic lows. The utilization rate for the coast-wide
fishery this year was the lowest of the previous decade (`r tot_2024_attainment`%)
due, in part, to difficulties locating aggregations of fish during the spring and
throughout the year in northern areas.
The usual `r us_allotment_percent`% and `r can_allotment_percent`%
allocation of coast-wide TAC, as specified in the Joint U.S.-Canada
Agreement for `r sp`, was implemented for the `r last_assess_yr` fishery.
Total landings last exceeded the coast-wide quota in 2002 when utilization
was 112%.

```{r es-landings-tac-tab, results = "asis", echo = FALSE}

table_landings_tac(
  ct,
  start_yr = end_yr - 10,
  end_yr = end_yr - 1,
  caption = paste0(
    "Recent trends in ", sp, " landings and management decisions. Catch ",
    "targets in 2020 and 2021 were specified unilaterally. All landings ",
    "and catch targets are given in tonnes."),
  font_size = 7,
  header_font_size = 7,
  longtable = TRUE)
```


## Forecast decision tables {-}

TODO: Text here is unedited from last year's Executive summary.

The catch limit for `r min(forecast_yrs)` based on the default `r f_40_40_10`
harvest policy has a median of `r ct_limit_quantiles["median"]`~t with a
wide range of uncertainty, the 95% credibility interval being
`r ct_limit_quantiles["lower"]`--`r ct_limit_quantiles["upper"]`~t.

Decision tables give the projected population status (relative spawning
biomass) and fishing intensity relative to the target under different
catch alternatives for the base model (Tables~\@ref(tab:es-decisions-biomass-tab)
and~\@ref(tab:es-decisions-spr-tab)). The tables are organized to show the
projected outcome for each potential catch level and year (row) across the
quantiles (columns) of the posterior distribution. Tables show results for up
to three years (only two years in subsequent assessments following JMC advice)
of future catch levels based on subsequent estimates of stock
status and fishing intensity.
Figure~\@ref(fig:es-depletion-comparison-fig) shows the projected relative
spawning biomass for several of the catch alternatives. Population dynamics
and governing parameters assumed during the forecast period include selectivity,
weight-at-age and fecundity-at-age averaged over the five
most recent years (`r assess_yr - 5`--`r assess_yr - 1`), and constant
values for all other parameters.

A relative fishing intensity of 1 should indicate fishing at the `r fspr_40`
default harvest rate catch target. But, the projected median relative fishing
intensity can be slightly different than the target because the `r fspr_40`
default harvest-rate catch limit is calculated using baseline
selectivity-at-age (1966--1990; prior to time-varying deviations), whereas the
forecasted catches use selectivity averaged over the last five
years. Recent changes in selectivity will thus be reflected in the
determination of fishing relative to the default harvest policy. For example,
fishing at the `r fspr_40` default harvest-rate catch limit
(scenario `r letters[ct_levels_vals$ct_default_policy_ind]`: default HR)
in `r assess_yr - 1` results in a median relative fishing intensity of
`r fi_at_hcr` (Table~\@ref(tab:es-decisions-spr-tab)).

Management metrics that were identified as important to the Joint Management
Committee and the Advisory Panel in 2012 are presented for
`r forecast_yrs[2]` and `r forecast_yrs[3]` projections
(Tables~\@ref(tab:es-risk-year-1-tab) and~\@ref(tab:es-risk-year-2-tab);
Figures~\@ref(fig:es-risk-year-1-fig) and~\@ref(fig:es-risk-year-2-fig)).
These metrics summarize the probability of various outcomes from the base model
given each potential management action. Although not linear, probabilities can
be interpolated from these results with reasonable accuracy for intermediate catch values in
`r assess_yr` (Table~\@ref(tab:es-risk-year-1-tab) and
Figure~\@ref(fig:es-risk-year-1-fig)).
However, interpolation is not appropriate for the default harvest rule scenario
in `r assess_yr + 1` because it is conditional on the `r assess_yr` catch.

```{r es-decisions-biomass-tab, results = "asis", echo = FALSE}

let <- letters[seq_along(base_model$forecasts[[length(base_model$forecasts)]])]
last_let <- let[length(let)]

table_decision(
  base_model,
  type = "biomass",
  forecast_inds =
    seq_along(base_model$forecasts[[length(base_model$forecasts)]]),
  inc_fi_stable_catch = length(base_model$forecasts[[1]]) == 13,
  caption = paste0(
      "Forecast quantiles of Pacific Hake relative spawning biomass at the ",
      "beginning of the year. Catch alternatives are defined by letters a-",
      last_let, " and are a constant value across all forecasted years unless ",
      "otherwise defined in the first column. Acronyms are defined in the ",
      "glossary (Appendix~\\@ref(sec:app-glossary))."),
  bold_letters = TRUE,
  digits = 2,
  # Font values higher than 8 and 11 for table and header respectively
  # will cause the table to wrap to a second page
  font_size = 8,
  header_font_size = 11,
  # If the font is changed it is almost guaranteed that `left_col_cm` and
  # `right_cols_cm` will have to be changed, especially if the font is made
  # larger. You will have to check this with trial-and-error, building the
  # document, checking the table and adjusting, over and over until it looks
  # right
  left_col_cm = 3,
  right_cols_cm = 1.2,
  longtable = TRUE)
```

\clearpage

```{r es-decisions-spr-tab, results = "asis", echo = FALSE}

table_decision(
  base_model,
  type = "spr",
  forecast_inds =
    seq_along(base_model$forecasts[[length(base_model$forecasts)]]),
  inc_fi_stable_catch = length(base_model$forecasts[[1]]) == 13,
  caption = paste0(
      "Forecast quantiles of Pacific Hake relative fishing intensity ",
      rel_fishing_intensity_for_latex_table, ", expressed as a proportion. ",
      "Catch alternatives are defined by letters a-", last_let, " and are a constant ",
      "value across all forecasted years unless otherwise defined in the ",
      "first column. Acronyms are defined in the glossary ",
      "(Appendix~\\@ref(sec:app-glossary))."),
  bold_letters = TRUE,
  digits = 2,
  # Font values higher than 8 and 11 for table and header respectively
  # will cause the table to wrap to a second page
  font_size = 8,
  header_font_size = 11,
  # If the font is changed it is almost guaranteed that `left_col_cm` and
  # `right_cols_cm` will have to be changed, especially if the font is made
  # larger
  left_col_cm = 3,
  right_cols_cm = 1.2,
  longtable = TRUE)
```

<!-- Commenting out in 2025 as did not happen, as we only have the one
bouncing-around catch alternatve.
This explains why probabilities can sometimes decline (rather than rise) with
increased assess_yr + 1 and assess_yr + 2 catch levels
(Tables~\@ref(tab:es-risk-year-2-tab) and~\@ref(tab:es-risk-year-3-tab);
Figures~\@ref(fig:es-risk-year-2-fig) and~\@ref(fig:es-risk-year-3-fig)).
-->

(ref:es-depletion-comparison-cap) Median and 95% posterior
credibility intervals of estimated relative spawning biomass to the start
of `r end_yr` from the base model and projections to the start of
`r forecast_yrs[length(forecast_yrs)]` for several catch alternatives, which
are defined in Table~\@ref(tab:es-decisions-biomass-tab).

(ref:es-depletion-comparison-alt) This figure shows that the median
relative spawning biomass is projected to remain flat for the next 3 years
with zero catch and to decline for all non-zero catch levels evaluated.

```{r es-depletion-comparison-fig, fig.cap = "(ref:es-depletion-comparison-cap)"}

# See the file `forecast-catch-levels.R` at the list called `ct_levels`. The values in
# `fore_inds` below are the indices of those forecast values in that list.
plot_depl_fore_comparison(base_model,
                          fore_inds = c(1, 2, 6, 10, 11),
                          forecast_yrs = forecast_yrs)
```

\newpage
