
\rfoot{Assessment}

# Assessment {#sec:assessment}

## Data and assessment {-}

Add text here for the describing the catch-only projection.

## Catches {-}

(ref:es-catches-cap) Total `r sp` catch used in the assessment by sector,
`r start_yr`--`r last_data_yr`. U.S. tribal catches are included in the
sectors where they are represented.

(ref:es-catches-alt) This figure shows that catches in four of the last six
years have been the largest in the time series.

```{r es-catches-fig, fig.cap = "(ref:es-catches-cap)", fig.height = 4}

plot_catches(ct, xlim = c(start_yr, last_data_yr))
```

TODO: Text here is unedited from last year's Executive summary.

Coast-wide fishery landings of `r sp` averaged `r f(mean(ct$Total))`~t
from `r min(ct$Year)` to `r max(ct$Year)`, with a low of
`r f(min(ct$Total))`~t in
`r ct$Year[ct$Total == min(ct$Total)]` and a peak of
`r f(max(ct$Total))`~t in
`r ct$Year[ct$Total == max(ct$Total)]`
(Figure \@ref(fig:es-catches-fig)).
Prior to `r min(ct$Year)`, total removals were negligible compared to the
modern fishery. Over the early period (`r min(ct$Year)`--1990) most removals
were from foreign or joint-venture fisheries. Across the time series, annual
catch in U.S. waters averaged `r f(mean(ct[["U.S. Total"]]))`~t
(`r f(sum(ct[["U.S. Total"]]) / sum(ct$Total) * 100, 1)`% of the total catch),
while catch from Canadian waters averaged `r f(mean(ct[["Canada Total"]]))`~t.
Over the last 10 years, `r max(ct$Year) - 9`--`r max(ct$Year)`
(Table \@ref(tab:es-catches-tab)), the average coast-wide catch was
`r ct_mean_10yrs`~t with U.S. and Canadian catches averaging
`r ct_us_mean_10yrs`~t and `r ct_can_mean_10yrs`~t, respectively. Since 2017,
the coast-wide catch has been declining annually through `r end_yr - 1` to
`r last_yr_landings`~t out of a total allowable catch (TAC, adjusted for
carryovers) of `r last_yr_tac`~t. Attainment in the U.S. was
`r last_yr_us_attained`% of its quota and in Canada it was
`r last_yr_can_attained`% in `r assess_yr - 1`.


```{r es-catches-tab, results = "asis", echo = FALSE}

table_catch(
  ct,
  inc_foreign_jv = FALSE,
  start_yr = end_yr - 10,
  end_yr = end_yr - 1,
  caption = paste0(
    "Total ", sp, " catch used in the assessment by sector for the most recent ",
    "ten years. U.S. tribal catches are included in the sectors where they are ",
    "represented."),
  font_size = 7,
  header_font_size = 7,
  longtable = TRUE)
```

In this document, the terms catch and landings are used interchangeably.
Estimates of discard within the target fishery are included but discarding
of `r sp` in non-target fisheries is not. Discard from all fisheries,
including those that do not target `r sp`, is estimated to be less than 1% of
landings in recent years. The catches in `r  last_data_yr` declined below
the long-term average catch (`r f(long_term_avge_ct)`~t), continuing the
pattern of declining catches over recent years (especially in Canada). Landings
between 2001 and 2008 were predominantly comprised of fish from the very large
1999 year class, with a cumulative removal (through `r end_yr - 1`) from
that cohort of
`r f(cohort_catch_1999 / 1e6, 2)` Mt [1~Mt = 1~million metric tonnes].
Through `r last_data_yr`, the cumulative catches of the 2010, 2014, and 2016
year classes were estimated at
`r f(cohort_catch_2010 / 1e6, 2)`~Mt,
`r f(cohort_catch_2014 / 1e6, 2)`~Mt, and
`r f(cohort_catch_2016 / 1e6, 2)`~Mt, respectively. In the
`r end_yr - 1` catch, `r top_coh(base_model, last_data_yr, 3, cap = FALSE)`.

## Management performance {-}

TODO: Text here is unedited from last year's Executive summary.

Over the last decade (`r end_yr - 10`--`r end_yr - 1`), the mean coast-wide
utilization rate (proportion of catch target removed) has been
`r tot_last_10_yrs_attainment`% and catches have been below coast-wide
targets (Table~\@ref(tab:es-landings-tac-tab)). From `r end_yr - 5` to
`r end_yr - 1`, the mean utilization rates differed between the U.S.
(`r us_last_5_yrs_attainment`%) and Canada (`r can_last_5_yrs_attainment`%).
While Canada's rate was higher than the U.S.'s in 2020, it has dropped considerably
over the past few years to historic lows. The utilization rate for the coast-wide
fishery this year was the lowest of the previous decade (`r tot_2024_attainment`%)
due, in part, to difficulties locating aggregations of fish during the spring and
throughout the year in northern areas.
The usual `r us_allotment_percent`% and `r can_allotment_percent`%
allocation of coast-wide TAC, as specified in the Joint U.S.-Canada
Agreement for `r sp`, was implemented for the `r last_assess_yr` fishery.
Total landings last exceeded the coast-wide quota in 2002 when utilization
was 112%.

```{r es-landings-tac-tab, results = "asis", echo = FALSE}

table_landings_tac(
  ct,
  start_yr = end_yr - 10,
  end_yr = end_yr - 1,
  caption = paste0(
    "Recent trends in ", sp, " landings and management decisions. Catch ",
    "targets in 2020 and 2021 were specified unilaterally. All landings ",
    "and catch targets are given in tonnes."),
  font_size = 7,
  header_font_size = 7,
  longtable = TRUE)
```


## Forecast decision tables {-}

TODO: Text here is unedited from last year's Executive summary.

The catch limit for `r min(forecast_yrs)` based on the default `r f_40_40_10`
harvest policy has a median of `r ct_limit_quantiles["median"]`~t with a
wide range of uncertainty, the 95% credibility interval being
`r ct_limit_quantiles["lower"]`--`r ct_limit_quantiles["upper"]`~t.

Decision tables give the projected population status (relative spawning
biomass) and fishing intensity relative to the target under different
catch alternatives for the base model (Tables~\@ref(tab:es-decisions-biomass-tab)
and~\@ref(tab:es-decisions-spr-tab)). The tables are organized to show the
projected outcome for each potential catch level and year (row) across the
quantiles (columns) of the posterior distribution. Tables show results for up
to three years (only two years in subsequent assessments following JMC advice)
of future catch levels based on subsequent estimates of stock
status and fishing intensity.
Figure~\@ref(fig:es-depletion-comparison-fig) shows the projected relative
spawning biomass for several of the catch alternatives. Population dynamics
and governing parameters assumed during the forecast period include selectivity,
weight-at-age and fecundity-at-age averaged over the five
most recent years (`r assess_yr - 5`--`r assess_yr - 1`), and constant
values for all other parameters.

A relative fishing intensity of 1 should indicate fishing at the `r fspr_40`
default harvest rate catch target. But, the projected median relative fishing
intensity can be slightly different than the target because the `r fspr_40`
default harvest-rate catch limit is calculated using baseline
selectivity-at-age (1966--1990; prior to time-varying deviations), whereas the
forecasted catches use selectivity averaged over the last five
years. Recent changes in selectivity will thus be reflected in the
determination of fishing relative to the default harvest policy. For example,
fishing at the `r fspr_40` default harvest-rate catch limit
(scenario `r letters[ct_levels_vals$ct_default_policy_ind]`: default HR)
in `r assess_yr - 1` results in a median relative fishing intensity of
`r fi_at_hcr` (Table~\@ref(tab:es-decisions-spr-tab)).

Management metrics that were identified as important to the Joint Management
Committee and the Advisory Panel in 2012 are presented for
`r forecast_yrs[2]` and `r forecast_yrs[3]` projections
(Tables~\@ref(tab:es-risk-year-1-tab) and~\@ref(tab:es-risk-year-2-tab);
Figures~\@ref(fig:es-risk-year-1-fig) and~\@ref(fig:es-risk-year-2-fig)).
These metrics summarize the probability of various outcomes from the base model
given each potential management action. Although not linear, probabilities can
be interpolated from these results with reasonable accuracy for intermediate catch values in
`r assess_yr` (Table~\@ref(tab:es-risk-year-1-tab) and
Figure~\@ref(fig:es-risk-year-1-fig)).
However, interpolation is not appropriate for the default harvest rule scenario
in `r assess_yr + 1` because it is conditional on the `r assess_yr` catch.

```{r es-decisions-biomass-tab, results = "asis", echo = FALSE}

let <- letters[seq_along(base_model$forecasts[[length(base_model$forecasts)]])]
last_let <- let[length(let)]

table_decision(
  base_model,
  type = "biomass",
  forecast_inds =
    seq_along(base_model$forecasts[[length(base_model$forecasts)]]),
  inc_fi_stable_catch = length(base_model$forecasts[[1]]) == 13,
  caption = paste0(
      "Forecast quantiles of Pacific Hake relative spawning biomass at the ",
      "beginning of the year. Catch alternatives are defined by letters a-",
      last_let, " and are a constant value across all forecasted years unless ",
      "otherwise defined in the first column. Acronyms are defined in the ",
      "glossary (Appendix~\\@ref(sec:app-glossary))."),
  bold_letters = TRUE,
  digits = 2,
  # Font values higher than 8 and 11 for table and header respectively
  # will cause the table to wrap to a second page
  font_size = 8,
  header_font_size = 11,
  # If the font is changed it is almost guaranteed that `left_col_cm` and
  # `right_cols_cm` will have to be changed, especially if the font is made
  # larger. You will have to check this with trial-and-error, building the
  # document, checking the table and adjusting, over and over until it looks
  # right
  left_col_cm = 3,
  right_cols_cm = 1.2,
  longtable = TRUE)
```

\clearpage

```{r es-decisions-spr-tab, results = "asis", echo = FALSE}

table_decision(
  base_model,
  type = "spr",
  forecast_inds =
    seq_along(base_model$forecasts[[length(base_model$forecasts)]]),
  inc_fi_stable_catch = length(base_model$forecasts[[1]]) == 13,
  caption = paste0(
      "Forecast quantiles of Pacific Hake relative fishing intensity ",
      rel_fishing_intensity_for_latex_table, ", expressed as a proportion. ",
      "Catch alternatives are defined by letters a-", last_let, " and are a constant ",
      "value across all forecasted years unless otherwise defined in the ",
      "first column. Acronyms are defined in the glossary ",
      "(Appendix~\\@ref(sec:app-glossary))."),
  bold_letters = TRUE,
  digits = 2,
  # Font values higher than 8 and 11 for table and header respectively
  # will cause the table to wrap to a second page
  font_size = 8,
  header_font_size = 11,
  # If the font is changed it is almost guaranteed that `left_col_cm` and
  # `right_cols_cm` will have to be changed, especially if the font is made
  # larger
  left_col_cm = 3,
  right_cols_cm = 1.2,
  longtable = TRUE)
```


(ref:es-depletion-comparison-cap) Median and 95% posterior
credibility intervals of estimated relative spawning biomass to the start
of `r end_yr` from the base model and projections to the start of
`r forecast_yrs[length(forecast_yrs)]` for several catch alternatives, which
are defined in Table~\@ref(tab:es-decisions-biomass-tab).

(ref:es-depletion-comparison-alt) This figure shows that the median
relative spawning biomass is projected to remain flat for the next 3 years
with zero catch and to decline for all non-zero catch levels evaluated.

```{r es-depletion-comparison-fig, fig.cap = "(ref:es-depletion-comparison-cap)"}

# See the file `forecast-catch-levels.R` at the list called `ct_levels`. The values in
# `fore_inds` below are the indices of those forecast values in that list.
plot_depl_fore_comparison(base_model,
                          fore_inds = c(1, 2, 6, 10, 11),
                          forecast_yrs = forecast_yrs)
```

\newpage
