\newpage

\rfoot{Tables}

# Data Tables {#sec:tables}

This appendix contains empirical data tables only, there are no model output tables included. The `r last_data_yr` assessment is a simple projection model which includes only the total `r last_data_yr` catch. The tables presented here contain historical data as well as the data for `r last_data_yr`, even though they were not used in modelling for this year. The `r last_data_yr` data presented here will be used in future assessment years' model runs.

```{r main-catches-us-tab, results = "asis", echo = FALSE}
table_catch(
  ct,
  inc_foreign_jv = TRUE,
  start_yr = start_yr,
  end_yr = end_yr - 1,
  country = "us",
  caption = paste0(
    "Annual catches of ", sp, " (t) in U.S. waters by fleet, ", start_yr,
    "--", last_data_yr, ". Tribal catches are included in the fleet totals. ",
    "Research catch includes landed catch associated with research-related ",
    "activities. Catch associated with surveys and discarded bycatch in ",
    "fisheries not targeting hake is not currently included in the table or ",
    "model."),
  font_size = 8,
  header_font_size = 11,
  longtable = TRUE)
```

```{r main-catches-can-tab, results = "asis", echo = FALSE}
table_catch(
  ct,
  inc_foreign_jv = TRUE,
  start_yr = start_yr,
  end_yr = end_yr - 1,
  country = "can",
  caption = paste0(
    "Annual catches of ", sp, " (t) in Canadian waters by fleet, ",
    start_yr, "--", last_data_yr, "."),
  font_size = 10,
  header_font_size = 11,
  longtable = TRUE)
```

```{r main-landings-tac-tab, results = "asis", echo = FALSE}
table_landings_tac(
  ct,
  start_yr = start_yr,
  end_yr = last_data_yr,
  caption = paste0(
    sp,
    " landings and management decisions, ", start_yr, "--", last_data_yr, ". ",
    "A dash (--)  indicates the management decision was either not ",
    "specified or was unknown to the authors at the time of this ",
    "assessment."),
  font_size = 10,
  header_font_size = 11,
  longtable = TRUE) |>
  landscape()
```

```{r main-sampling-history-tab, results = "asis", echo = FALSE}
table_sampling_history(
  start_yr = start_yr_age_comps,
  end_yr = last_data_yr,
  replace_start_yr = 2010,
  caption = paste0(
    "Annual summary of U.S. and Canadian fishery sampling included in this ",
    "stock assessment by fleet, ", start_yr_age_comps, "--", last_data_yr,
    ". The majority of values are reported as number of hauls but U.S. ",
    "shoreside and Canadian Shoreside fleets are reported as the number ",
    "of trips. A dash (--) indicates there was no sampled catch. The ",
    "number of fish with otoliths sampled per haul has varied over time but ",
    "is typically small."),
  font_size = 10,
  header_font_size = 11,
  longtable = TRUE) |>
  landscape()
```

```{r main-us-cp-age-data-tab, results = "asis", echo = FALSE}
table_age_data(
  fleet = "us_cp",
  start_yr = end_yr - num_recent_yrs,
  end_yr = last_data_yr,
  caption = paste0(
    "Recent age-proportion data used in the assessment for the U.S. ",
    "Catcher-Processor fleet. Proportions are calculated from numbers of ",
    "individuals in each age group. Age 15$+$ is an accumulator group."),
  font_size = 10,
  header_font_size = 11,
  digits = 2,
  longtable = TRUE) |>
  landscape()
```

\newpage

```{r main-us-ms-age-data-tab, results = "asis", echo = FALSE}
table_age_data(
  fleet = "us_ms",
  start_yr = end_yr - num_recent_yrs,
  end_yr = last_data_yr,
  caption = paste0(
    "Recent age-proportion data used in the assessment for the U.S. ",
    "Mothership fleet. Proportions are calculated from numbers of ",
    "individuals in each age group. Age 15$+$ is an accumulator group."),
  font_size = 10,
  header_font_size = 11,
  digits = 2,
  longtable = TRUE) |>
  landscape()
```

```{r main-us-sb-age-data-tab, results = "asis", echo = FALSE}
table_age_data(
  fleet = "us_sb",
  start_yr = end_yr - num_recent_yrs,
  end_yr = last_data_yr,
  caption = paste0(
    "Recent age-proportion data used in the assessment for the U.S. ",
    "shoreside fleet. Proportions are calculated from numbers of ",
    "individuals in each age group. Age 15$+$ is an accumulator group."),
  font_size = 10,
  header_font_size = 11,
  digits = 2,
  longtable = TRUE) |>
  landscape()
```

```{r main-can-ss-age-data-tab, results = "asis", echo = FALSE}
table_age_data(
  fleet = "can_ss",
  start_yr = end_yr - num_recent_yrs,
  end_yr = last_data_yr,
  caption = paste0(
    "Recent age-proportion data used in the assessment for the Canadian ",
    "Shoreside fleet. Proportions are calculated from numbers of individuals ",
    "in each age group. Age 15$+$ is an accumulator group."),
  font_size = 10,
  header_font_size = 11,
  digits = 2,
  longtable = TRUE) |>
  landscape()
```

```{r main-can-ft-age-data-tab, results = "asis", echo = FALSE}
table_age_data(
  fleet = "can_ft",
  start_yr = end_yr - num_recent_yrs,
  end_yr = last_data_yr,
  caption = paste0(
    "Recent age-proportion data used in the assessment for the Canadian ",
    "Freezer trawler fleet. Proportions are calculated from numbers of ",
    "individuals in each age group. Age 15$+$ is an accumulator group."),
  font_size = 10,
  header_font_size = 11,
  digits = 2,
  longtable = TRUE) |>
  landscape()
```

<!--

```{r main-input-age-data-fishery-tab, results = "asis", echo = FALSE}
table_input_age_data(
  base_model,
  fleet = "fishery",
  start_yr = start_yr_age_comps,
  end_yr = last_data_yr,
  caption = paste0(
    "Aggregated fishery age-proportion data used in the base model. ",
    "Proportions are calculated from numbers of individuals in each age ",
    "group where the contributions from each fleet are weighted by the ",
    "catch in that fleet. Sample sizes are sum of hauls and trips from ",
    "individual fleets (shown in preceding tables) as described in ",
    "Section~\\@ref(sec:data-fishery-biological-data). Age 15$+$ is an ",
    "accumulator group."),
  font_size = 10,
  header_font_size = 11,
  digits = 2,
  longtable = TRUE) |>
  landscape()
```

-->

<!-- This is needed to cite within a table caption, see how it is included
the caption below. Note it is OUTSIDE of a knitr chunk. -->
(ref:cite-jtc2018) @JTC2018

