\newpage

\rfoot{Tables}

# Data Tables {#sec:app-tables}

This appendix contains empirical data tables only (though also see Appendix~\@ref(sec:app-srg-requests)). There are no model output tables included. The `r end_yr` assessment is a simple projection model which includes only the total `r last_data_yr` catch as new data. The tables presented here contain historical data as well as the data for `r last_data_yr`, even though only catch was updated in the modelling for this year. All the `r last_data_yr` data presented here will be used in future assessment years' model runs.

```{r main-catches-us-tab, results = "asis", echo = FALSE}
table_catch(
  ct,
  inc_foreign_jv = TRUE,
  start_yr = start_yr,
  end_yr = end_yr - 1,
  country = "us",
  caption = paste0(
    "Annual catches of ", sp, " (t) in U.S. waters by fleet, ", start_yr,
    "--", last_data_yr, ". Tribal catches are included in the fleet totals. ",
    "Research catch includes landed catch associated with research-related ",
    "activities. Catch associated with surveys and discarded bycatch in ",
    "fisheries not targeting hake is not currently included in the table or ",
    "model."),
  font_size = 8,
  header_font_size = 11,
  longtable = TRUE)
```

```{r main-catches-can-tab, results = "asis", echo = FALSE}
table_catch(
  ct,
  inc_foreign_jv = TRUE,
  start_yr = start_yr,
  end_yr = end_yr - 1,
  country = "can",
  caption = paste0(
    "Annual catches of ", sp, " (t) in Canadian waters by fleet, ",
    start_yr, "--", last_data_yr, "."),
  font_size = 10,
  header_font_size = 11,
  longtable = TRUE)
```

```{r main-landings-tac-tab, results = "asis", echo = FALSE}
table_landings_tac(
  ct,
  start_yr = start_yr,
  end_yr = last_data_yr,
  caption = paste0(
    sp,
    " landings and management decisions, ", start_yr, "--", last_data_yr, ". ",
    "A dash (--)  indicates the management decision was either not ",
    "specified or was unknown to the authors at the time of this ",
    "assessment."),
  font_size = 10,
  header_font_size = 11,
  longtable = TRUE) |>
  landscape()
```

```{r main-sampling-history-tab, results = "asis", echo = FALSE}
table_sampling_history(
  start_yr = start_yr_age_comps,
  end_yr = last_data_yr,
  replace_start_yr = 2010,
  caption = paste0(
    "Annual summary of U.S. and Canadian fishery sampling included in this ",
    "stock assessment by fleet, ", start_yr_age_comps, "--", last_data_yr,
    ", though data for ", assess_yr - 1,
    " are not yet included in the assessment model. ",
    "The majority of values are reported as number of hauls but U.S. ",
    "shoreside and Canadian Shoreside fleets are reported as the number ",
    "of trips. A dash (--) indicates there was no sampled catch. The ",
    "number of fish with otoliths sampled per haul has varied over time but ",
    "is typically small."),
  font_size = 10,
  header_font_size = 11,
  longtable = TRUE) |>
  landscape()
```

```{r main-us-cp-age-data-tab, results = "asis", echo = FALSE}
table_age_data(
  fleet = "us_cp",
  start_yr = end_yr - num_recent_yrs,
  end_yr = last_data_yr,
  caption = paste0(
    "Recent age-proportion data used in the assessment for the U.S. ",
    "Catcher-Processor fleet",
    ", though data for ", assess_yr - 1,
    " are not yet included in the assessment model. ",
    "Proportions are calculated from numbers of ",
    "individuals in each age group. Age 15$+$ is an accumulator group."),
  font_size = 10,
  header_font_size = 11,
  digits = 2,
  longtable = TRUE) |>
  landscape()
```

\newpage

```{r main-us-ms-age-data-tab, results = "asis", echo = FALSE}
table_age_data(
  fleet = "us_ms",
  start_yr = end_yr - num_recent_yrs,
  end_yr = last_data_yr,
  caption = paste0(
    "Recent age-proportion data used in the assessment for the U.S. ",
    "Mothership fleet,",
    " though data for ", assess_yr - 1,
    " are not yet included in the assessment model. ",
    "Proportions are calculated from numbers of ",
    "individuals in each age group. Age 15$+$ is an accumulator group."),
  font_size = 10,
  header_font_size = 11,
  digits = 2,
  longtable = TRUE) |>
  landscape()
```

```{r main-us-sb-age-data-tab, results = "asis", echo = FALSE}
table_age_data(
  fleet = "us_sb",
  start_yr = end_yr - num_recent_yrs,
  end_yr = last_data_yr,
  caption = paste0(
    "Recent age-proportion data used in the assessment for the U.S. ",
    "shoreside fleet,",
    " though data for ", assess_yr - 1,
    " are not yet included in the assessment model. ",
    "Proportions are calculated from numbers of ",
    "individuals in each age group. Age 15$+$ is an accumulator group."),
  font_size = 10,
  header_font_size = 11,
  digits = 2,
  longtable = TRUE) |>
  landscape()
```

```{r main-can-ss-age-data-tab, results = "asis", echo = FALSE}
table_age_data(
  fleet = "can_ss",
  start_yr = end_yr - num_recent_yrs,
  end_yr = last_data_yr,
  caption = paste0(
    "Recent age-proportion data used in the assessment for the Canadian ",
    "Shoreside fleet,",
    " though data for ", assess_yr - 1,
    " are not yet included in the assessment model. ",
    "Proportions are calculated from numbers of individuals ",
    "in each age group. Age 15$+$ is an accumulator group."),
  font_size = 10,
  header_font_size = 11,
  digits = 2,
  longtable = TRUE) |>
  landscape()
```

```{r main-can-ft-age-data-tab, results = "asis", echo = FALSE}
table_age_data(
  fleet = "can_ft",
  start_yr = end_yr - num_recent_yrs,
  end_yr = last_data_yr,
  caption = paste0(
    "Recent age-proportion data used in the assessment for the Canadian ",
    "Freezer trawler fleet, ",
    " though data for ", assess_yr - 1,
    " are not yet included in the assessment model. ",
    "Proportions are calculated from numbers of ",
    "individuals in each age group. Age 15$+$ is an accumulator group."),
  font_size = 10,
  header_font_size = 11,
  digits = 2,
  longtable = TRUE) |>
  landscape()
```

<!--

```{r main-input-age-data-fishery-tab, results = "asis", echo = FALSE}
table_input_age_data(
  base_model,
  fleet = "fishery",
  start_yr = start_yr_age_comps,
  end_yr = last_data_yr,
  caption = paste0(
    "Aggregated fishery age-proportion data used in the base model. ",
    "Proportions are calculated from numbers of individuals in each age ",
    "group where the contributions from each fleet are weighted by the ",
    "catch in that fleet. Sample sizes are sum of hauls and trips from ",
    "individual fleets (shown in preceding tables) as described in ",
    "Section~\\@ref(sec:data-fishery-biological-data). Age 15$+$ is an ",
    "accumulator group."),
  font_size = 10,
  header_font_size = 11,
  digits = 2,
  longtable = TRUE) |>
  landscape()
```

-->

<!--
```{r main-median-posterior-tab, results = "asis", echo = FALSE}
table_median_posteriors(
  base_model,
  start_yr = start_yr,
  end_yr = end_yr,
  digits = 1,
  caption = paste0(
    "Time series of median posterior population estimates from the base ",
    "model. Relative spawning biomass is spawning biomass relative to the ",
    "unfished equilibrium (", b_0_for_latex_table, "). Total biomass includes
    females and males of ages 0 and above. Age-2$+$ biomass includes females ",
    "and males ages 2 and above. Exploitation fraction is total catch ",
    "divided by total age-2$+$ biomass. Relative fishing intensity is ",
    rel_fishing_intensity_for_latex_table, " such that values below 100\\% ",
    "represent fishing below ", f_40_for_latex_table, ". In the last row, ",
    "dashes (--) indicate quantities requiring ", end_yr, " catch which has ",
    "not taken place yet."),
  font_size = 8,
  header_font_size = 9,
  longtable = TRUE)
```

```{r main-parameter-estimates-tab, results = "asis", echo = FALSE}

table_param_est(
  models = list(base_model, last_yr_base_model),
  model_nms = c(base_model_name, last_yr_base_model_name),
  section_bold = TRUE,
  section_italics = TRUE,
  section_underline = TRUE,
  section_line_above = FALSE,
  section_line_below = FALSE,
  digits = 3,
  caption = paste0(
    "Select parameters, derived quantities, and reference point posterior ",
    "median estimates for the (", end_yr, ") base model compared to the ",
    "previous assessment's (", end_yr - 1, ") base model. Dashes (--) in ",
    "column for the previous assessment indicate quantities that were ",
    " not available in that assessment"),
  font_size = 9,
  header_font_size = 9,
  longtable = TRUE)
```

```{r main-reference-points-tab, results = "asis", echo = FALSE}
table_reference_points(
  base_model,
  category_bold = TRUE,
  category_italics = TRUE,
  category_underline = TRUE,
  category_line_above = FALSE,
  category_line_below = FALSE,
  caption = paste0(
    "Summary of median and 95\\% credibility intervals of equilibrium ",
    "conceptual reference points for the base assessment model. ",
    "Equilibrium reference points were computed using ", start_yr_age_comps,
    "--", end_yr - 1, " averages for mean weight-at-age and baseline ",
    "selectivity-at-age (1966--1990; prior to time-varying deviations). ",
    "Dashes (--) indicate values that are static at one value and do not ",
    "have a credible interval associated with them."),
  font_size = 10,
  header_font_size = 11,
  longtable = TRUE)
```

-->

<!-- This is needed to cite within a table caption, see how it is included
the caption below. Note it is OUTSIDE of a knitr chunk. -->
(ref:cite-jtc2018) @JTC2018

