\newpage

\rfoot{Figures}

# Data Figures {#sec:figures}

This appendix contains empirical data figures only, there are no model output figures included. The `r last_data_yr` assessment is a simple projection model which includes only the total `r last_data_yr` catch. The figures presented here contain historical data as well as the data for `r last_data_yr`, even though they were not used in modelling for this year. The `r last_data_yr` data presented here will be used in future assessment years' model runs.


(ref:main-catches-cap) Total `r sp` catch used in the assessment by sector,
`r start_yr`--`r last_data_yr`. U.S. tribal catches are included in the
sectors where they are represented.

(ref:main-catches-alt) This figure shows that catches have declined each year
from the historical peak in 2017.

```{r main-catches-fig, fig.cap = "(ref:main-catches-cap)", fig.height = 4, out.height = "4in"}

plot_catches(ct, xlim = c(start_yr, last_data_yr))
```

(ref:main-us-depths-cap) Distribution of fishing depths (left) and bottom
depths (right), in meters, of hauls targeting `r sp` in the U.S.
Catcher-Processor and Mothership sectors from
`r last_data_yr - 4`--`r last_data_yr`. Horizontal lines in each box
represent the median depth and boxes encompass the middle 50% of the
data. Whiskers encompass the 95% quantiles.

(ref:main-us-depths-alt) This figure shows that bottom depths have been
approximately 500 meters and fishing depths approximately 300 meters on
average in the last 5 years for United States fleets.

```{r main-us-depths-fig, fig.cap = "(ref:main-us-depths-cap)", fig.height = 4, out.height = "4in"}

yrs <- (last_data_yr - 4):last_data_yr
depth_lims <- c(0, 700)
depth_breaks <- seq(depth_lims[1], depth_lims[2], 100)

plot_depth_2_panel(us_atsea_fishing_depth_df,
                   us_atsea_bottom_depth_df,
                   yrs = yrs,
                   y_lim = depth_lims,
                   y_breaks = depth_breaks)
```

(ref:main-can-depths-cap) Distribution of fishing depths (left) and bottom
depths (right), in meters, of hauls targeting `r sp` in the Canadian
fleets from `r last_data_yr - 4`--`r last_data_yr`. Horizontal lines in each
box represent the median depth and boxes encompass the middle 50% of the
data. Whiskers encompass the 95% quantiles.

(ref:main-can-depths-alt) This figure shows that for the last five years in
Canada freezer trawlers fished from 250 to 400 meters
and shoreside vessels more consistently fished at an approximate bottom depth of 200 meters.
Freezer trawlers fished at a gear depth of approximately 100 to 300 meters and
shoreside vessels at a depth of approximately 150 to 250 meters. Bottom depths
for both fleets have become shallower with fishing being closer to the bottom.

```{r main-can-depths-fig, fig.cap = "(ref:main-can-depths-cap)", fig.height = 8, out.height = "8in"}

plot_depth_4_panel(can_ft_gear_depth_df,
                   can_ft_bottom_depth_df,
                   can_ss_gear_depth_df,
                   can_ss_bottom_depth_df,
                   fleet_1_name = "Freezer trawlers",
                   fleet_2_name = "Shoreside",
                   yrs = yrs,
                   y_lim = depth_lims,
                   y_breaks = depth_breaks)
```

(ref:main-age-proportions-fig-cap) Add caption.

(ref:main-age-proportions-alt) Add alt caption.

```{r main-age-proportions-fig, fig.cap = "(ref:main-age-proportions-cap)", fig.height = 8, out.height = "8in"}

ages <- can_ss_age_df |>
  names() %>%
  grep("^[0-9]+$", ., value = TRUE) |>
  as.numeric() |> 
  sort()
plot_age_comp_bubbles_data(list(can_ss_age_df,
                                can_ft_age_df,
                                us_sb_age_df,
                                us_cp_age_df,
                                us_ms_age_df),
                           c("Canadian Shoreside",
                             "Canadian Freezer-Trawlers",
                             "U.S. Shoreside",
                             "U.S. Catcher-Processor",
                             "U.S. Mothership"),
                           years = c(last_data_yr - 6, last_data_yr)) +
  theme(#axis.title.x = element_text(size = 8),
        #axis.title.y = element_text(size = 8),
        axis.text.x = element_text(size = 8),
        axis.text.y = element_text(size = 8),
        strip.text = element_text(size = 8)) +
  scale_y_continuous(breaks = ages)
```


\clearpage