# Changes from `r last_assess_yr`
## Changes from the `r last_assess_yr` assessment

* Update Stock Synthesis to version `r ss_version`
* Years up to `r last_data_yr - 1`: incrementally update catch, maturity-at-age,
weight-at-age, fecundity-at-age, and fishery age-composition
data
* Data for `r last_data_yr`: incrementally add catch, maturity-at-age,
weight-at-age, fecundity-at-age,
<!-- biomass survey, survey age-composition, age-1 index, -->
and fishery age-composition data
  \pause
* Turn off estimation of recruitment deviations from `r last_data_yr - 1` onwards -- these
  recruitments were estimated solely from the
  stock-recruitment relationship.
* In previous assessment models we would have allowed a random lognormal
  component about the stock-recruitment relationships for recruitments from `r last_data_yr - 1`
  onwards.
  \pause
* All model runs in the assessment use MCMC

## Bridging: update SS3 and older data (biomass)

```{r bridge-biomass-1, fig.height = 4, out.height = "80%"}
p <- list()
p[[1]] <-
  plot_biomass(d_obj = d_obj_bridge_biomass[[1]],
               point_size = 1.5,
               xlim = c(1964, last_assess_yr),
               show_arrows = TRUE,
               dodge_bo = 0.75,
               leg_ncol = 2,
               leg_font_size = 5,
               x_labs_mod = 10,
               wrap_y_label = TRUE,
               tick_prop = 2,
               ylim = c(0, 5.5),
               leg_pos = c(0.5, 0.87))
p[[2]] <-
  plot_rel_biomass(d_obj = d_obj_bridge_rel_biomass[[1]],
                   xlim = c(1964, last_assess_yr),,
                   ylim = c(0, 2.5),
                   x_labs_mod = 10,
                   wrap_y_label = TRUE,
                   leg_pos = "none")

plot_grid(plotlist = p,
          nrow = 1,
          ncol = 2)
```

## Bridging: update SS3 and older data (biomass) (recruitment)

```{r bridge-recruit-1, fig.height = 4, out.height = "80%"}
  plot_recdevs(d_obj = d_obj_bridge_recdev[[1]],
               x_labs_mod = 10,
               leg_ncol = 2,
               leg_font_size = 6,
               line_width = 0.1,
               rev_colors = TRUE,
               leg_pos = c(0.22, 0.9))

```
<!--
## Bridging: update SS3 and older data (biomass) (survey)
Not showing in 2025 since no real difference
-->
```{r bridge-survey-1, fig.height = 4, out.height = "80%", eval = FALSE}
p <- list()
p[[1]] <-
  plot_survey_index_fits(base_model,
                         d_obj = d_obj_bridge_age2_index[[1]],
                         survey_type = "age2",
                         rev_colors = TRUE,
                         leg_pos = "none",
                         xlim = c(1995, end_yr))

p[[2]] <-
  plot_survey_index_fits(base_model,
                         d_obj = d_obj_bridge_age1_index[[1]],
                         survey_type = "age1",
                         xlim = c(1995, end_yr),
                         ylim = c(0, 11),
                         leg_ncol = 2,
                         leg_font_size = 5,
                         leg_pos = c(0.45, 0.9),
                         y_breaks = seq(0, 11, by = 2),
                         rev_colors = TRUE)

plot_grid(plotlist = p,
          nrow = 1,
          ncol = 2)
```
## Bridging: add 2024 data and change rec devs (biomass)

```{r bridge-biomass-2, fig.height = 4, out.height = "80%"}
p <- list()
p[[1]] <-
  plot_biomass(d_obj = d_obj_bridge_biomass[[2]],
               point_size = 1.5,
               show_arrows = TRUE,
               dodge_bo = 0.75,
               leg_ncol = 2,
               leg_font_size = 4.5,
               x_labs_mod = 10,
               wrap_y_label = TRUE,
               tick_prop = 2,
               ylim = c(0, 5.5),
               leg_pos = c(0.52, 0.87))
p[[2]] <-
  plot_rel_biomass(d_obj = d_obj_bridge_rel_biomass[[2]],
                   ylim = c(0, 2.5),
                   x_labs_mod = 10,
                   wrap_y_label = TRUE,
                   leg_pos = "none")

plot_grid(plotlist = p,
          nrow = 1,
          ncol = 2)
```
## Bridging: add 2024 data and change rec devs (biomass)

```{r bridge-rel-biomass-2, fig.height = 4, out.height = "80%"}
plot_rel_biomass(d_obj = d_obj_bridge_rel_biomass[[2]],
                 ylim = c(0, 2.5),
                 xlim = c(2015, assess_yr),
                 leg_ncol = 2,
                 leg_font_size = 4.5,
                 x_labs_mod = 1,
                 wrap_y_label = TRUE,
                 tick_prop = 1,
                 x_expansion = 0.5,
                 leg_pos = c(0.3, 0.85))
```

## Bridging: Add 2024 data and change rec devs (recruitment)

```{r bridge-recdevs-2, fig.height = 4, out.height = "80%"}
rec_dev_to_plot <- d_obj_bridge_recdev[[2]][[1]]
rec_dev_to_plot[is.na(rec_dev_to_plot)] <- 0
rec_dev_to_plot <- list(rec_dev_to_plot)
plot_recdevs(d_obj = rec_dev_to_plot,
             x_labs_mod = 1,
             xlim = c(2011, assess_yr),
             x_expansion = 0.5,
             leg_ncol = 2,
             leg_font_size = 5,
             leg_pos = c(0.2, 0.9),
             rev_colors = TRUE,
             line_width = 0.1,
             dodge_val = 0.5)
```

## Retrospectives of 2024 base model only for cohorts without age-1 index
```{r retro-last-yr-no-age1, fig.height = 3, out.height = "85%"}
plot_squid(last_yr_base_model,
           show_ci = TRUE,
           ci_yrs = c(2017, 2021),
           y_lim = y_lim_squid,
           cohorts = survey_age1_yrs) +
  theme(axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12), )
```


## Retrospectives of 2024 base model only for cohorts with age-1 index
```{r retro-last-yr-with-age1, fig.height = 3, out.height = "85%"}
plot_squid(last_yr_base_model,
           show_ci = TRUE,
           ci_yrs = c(2020, 2022),
           y_lim = y_lim_squid,
           cohorts = survey_age1_yrs - 1) +
  theme(axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12), )
```


=======

## Bridging: Add 2024 data and change rec devs (survey fits)

```{r bridge-survey-2, fig.height = 4, out.height = "80%"}
p <- list()
p[[1]] <-
  plot_survey_index_fits(base_model,
                         d_obj = d_obj_bridge_age2_index[[2]],
                         survey_type = "age2",
                         rev_colors = FALSE,
                         leg_pos = "none",
                         xlim = c(1995, end_yr))

p[[2]] <-
  plot_survey_index_fits(base_model,
                         d_obj = d_obj_bridge_age1_index[[2]],
                         survey_type = "age1",
                         xlim = c(1995, end_yr),
                         ylim = c(0, 11),
                         leg_ncol = 1,
                         leg_font_size = 5,
                         leg_pos = c(0.25, 0.82),
                         y_breaks = seq(0, 11, by = 2),
                         rev_colors = TRUE)

plot_grid(plotlist = p,
          nrow = 1,
          ncol = 2)
```

## Bridging: Summary

\bsmall

* Updating data for years up to `r last_data_yr-1` had very little effect on the
  stock trajectory
<!-- * Adding the `r last_data_yr` survey biomass estimate led to a downward shift in stock
  trajectory (and fit to biomass survey) going back to 2017
* Adding the `r last_data_yr` survey age compositions increased stock biomass from 2023 to
  2024 with increases in 2020 and 2021 recruitment
 * Adding the age-1 index resulted in a slight increase in 2022 recruitment -->
* Adding `r last_assess_yr` data:
  * changed the stock trajectory for recent years
  * decreased 2022 recruitment
  * suggested high 2023 recruitment.
  \pause
<!-- * Model-based weight-at-age altered stock size and status in the 1970s and 1980s (and
  equilibrium B~0~), but had little net effect since that time -->
* The only model change this year was setting the recruitment deviations for 2023
  and 2024 to zero, because:
  * estimated high 2023 recruitment was only based on age-1 fishery
  data
  * fishing showed unusual seasonal patterns in 2024
  * such recruitment estimates often become lower with subsequent years of data
  (e.g. as just shown for 2022 recruitment, and TODO see next plot).
* This lowered the estimated 2025 spawning biomass and reduced the associated uncertainty.

\esmall
