# Fits to data

## Fit to the acoustic survey index of abundance
```{r mcmc-survey-fit, fig.height = 4, out.height = "80%"}

plot_survey_fit_mcmc(base_model,
                     type = "acoustic",
                     n_posts = 1000,
                     y_lim = c(0, 6),
                     glow = TRUE,
                     glow_color = "black",
                     glow_offset = 0.5,
                     leg_ymax = 4.7,
                     leg_sep = 0.7,
                     leg_font_size = 10 / .pt)
```

## Fit to the age-1 relative index
```{r mcmc-age1-fit, fig.height = 4, out.height = "80%"}

plot_survey_fit_mcmc(base_model,
                     type = "age1",
                     n_posts = 1000,
                     y_lim = c(0, 10),
                     glow = TRUE,
                     y_labs_by = 1,
                     leg_ymax = 4.7,
                     leg_sep = 0.7,
                     leg_font_size = 10 / .pt) +
  theme(plot.margin = margin(2, 0, 12, 12))
```

## Fit to acoustic survey age comps
:::::: {.columns}
::: {.column width="40%"}
* Predicted higher: \textcolor{pink}{1999} cohort and \textcolor{yellow}{2010} cohort
  in 2017 survey
* Predicted lower: some young cohorts in 2003--2011, \textcolor{orange}{2014} cohort in
  2017 survey, **2021** cohort in 2023 survey
* Predictions for the \textcolor{brown}{2016} cohort have been lower than observed
  in the 2021 and 2023 surveys
:::

::: {.column width="60%"}
```{r survey-age-comp-fits, fig.height = 4, out.height = "80%"}
plot_age_comp_fit(base_model,
                  n_col = 4,
                  type = "survey",
                  x_breaks = seq(2, 15, 2),
                  label_font_size = 4,
                  label_loc = c(12, 0.7))
```
:::
::::::

## Fit to fishery age comps
:::::: {.columns}
::: {.column width="40%"}
* Large \textcolor{orange}{1999}, \textcolor{red}{2010}, \textcolor{orange}{2014},
  and \textcolor{purple}{2016} cohorts fit particularly well
* Some over- and under-fitting in \textcolor{red}{1980} and \textcolor{orange}{1984} cohorts
* The **2020** cohort is slightly under-fit in recent years
* Overall, fishery data in 2023 is fit well and implies age 2 and 3 fish made up
  a large contributon of the catch
:::

::: {.column width="60%"}
```{r fishery-age-comp-fits, fig.height = 4, out.height = "75%"}
plot_age_comp_fit(base_model,
                  label_font_size = 3,
                  type = "fishery",
                  n_col = 4)
```
:::
::::::

## Pearson residual for fit to the age data
:::::: {.columns}
::: {.column width="50%"}
\center Fishery \center
```{r fishery-pearson, fig.height = 4, fig.width = 6, out.height = "65%"}
plot_pearson_bubbles(base_model,
                     type = "fishery",
                     leg_pos = "top")
```
:::

::: {.column width="50%"}
\center Survey \center
```{r survey-pearson, fig.height = 4, fig.width = 6, out.height = "65%"}
plot_pearson_bubbles(base_model,
                     type = "survey",
                     alpha = 0.7)
```
:::
::::::
Dark bubbles are positive residuals (observed > expected) and white bubbles
are negative residuals (observed < expected)

