# Fits to data

## Fit to the acoustic survey index of abundance
```{r mcmc-survey-fit, fig.height = 4, out.height = "80%"}

plot_survey_fit_mcmc(base_model,
                     type = "acoustic",
                     n_posts = 1000,
                     y_lim = c(0, 6),
                     glow = TRUE,
                     glow_color = "black",
                     glow_offset = 0.5,
                     leg_ymax = 4.7,
                     leg_sep = 0.7,
                     leg_font_size = 10 / .pt)
```

## Fit to the age-1 relative index
```{r mcmc-age1-fit, fig.height = 4, out.height = "80%"}

plot_survey_fit_mcmc(base_model,
                     type = "age1",
                     n_posts = 1000,
                     y_lim = c(0, 10),
                     glow = TRUE,
                     y_labs_by = 1,
                     leg_ymax = 4.7,
                     leg_sep = 0.7,
                     leg_font_size = 10 / .pt) +
  theme(plot.margin = margin(2, 0, 12, 12))
```

## Fit to acoustic survey age comps
:::::: {.columns}
::: {.column width="40%"}
* Essentially the same as last year's assessment
* Overestimated:
  * \textcolor{blue}{1999} cohort in most surveys
  * \textcolor{yellow}{2010} cohort in 2017 survey
* Underestimated:
  * some young cohorts in 2003--2011
  * \textcolor{black}{2014} cohort in 2017 survey
  * \textcolor{yellow}{2021} cohort in 2023 survey
:::

::: {.column width="60%"}
```{r survey-age-comp-fits, fig.height = 4, out.height = "80%"}
plot_age_comp_fit(base_model,
                  n_col = 4,
                  type = "survey",
                  x_breaks = seq(2, 15, 2),
                  label_font_size = 4,
                  label_loc = c(12, 0.7))
```
:::
::::::

## Fit to fishery age comps
:::::: {.columns}
::: {.column width="40%"}
* Essentially the same as last year's assessment
* Large \textcolor{Purple}{1999}, \textcolor{Pink}{2010}, \textcolor{Purple}{2014},
  and \textcolor{Orange}{2016} cohorts fit particularly well
* Some over- and under-fitting in \textcolor{Pink}{1980} and \textcolor{Purple}{1984} cohorts
* The \textcolor{Green}{2020} cohort is fit better than last year
* Overall, fishery data in `r assess_yr` is fit well and implies age-3 and -4 fish made up
  a large contributon of the catch
:::

::: {.column width="60%"}
```{r fishery-age-comp-fits, fig.height = 4, out.height = "75%"}
plot_age_comp_fit(base_model,
                  label_font_size = 3,
                  type = "fishery",
                  n_col = 4)
```
:::
::::::

## Pearson residual for fit to the age data
:::::: {.columns}
::: {.column width="50%"}
\center Fishery \center
```{r fishery-pearson, fig.height = 4, fig.width = 6, out.height = "65%"}
plot_pearson_bubbles(base_model,
                     type = "fishery",
                     leg_pos = "top")
```
:::

::: {.column width="50%"}
\center Survey \center
```{r survey-pearson, fig.height = 4, fig.width = 6, out.height = "65%"}
plot_pearson_bubbles(base_model,
                     type = "survey",
                     alpha = 0.7)
```
:::
::::::
Dark bubbles are positive residuals (observed > expected) and white bubbles
are negative residuals (observed < expected)
