# Estimated Quantities
## Key parameters
:::::: {.columns}
::: {.column width="40%"}
* Prior for natural mortality looks to be influencing posterior
* Posterior for steepness does not shift much from prior
* DM for fishery has a relatively narrow posterior distribution
* Prior for survey DM parameter looks to be influencing posterior (discussed
  further in sensitivity section)
:::

::: {.column width="60%"}
```{r priors-posts, fig.height=4, out.height = "2.7in", out.width = "1\\columnwidth"}
plot_priors_vs_posts(base_model,
                     x_range = "prior",
                     ncol = 2,
                     nrow = 3)
```
:::
::::::

## Acoustic survey catchability (\emph{$q_b$}) posterior for this assessment
```{r catchability-density, fig.height=4, out.height = "2in", out.width = "0.8\\columnwidth"}
plot_catchability_density(base_model,
                          last_yr_base_model,
                          type = "age2",
                          line_widths = c(1, 1),
                          line_types = c("solid", "solid"))
```

```{r table-catchability-medians, results = "asis"}
k <- function(){

  d <- tibble(a = c(paste0("Median (", assess_yr, ")"),
                    f(median(last_yr_base_model$extra_mcmc$q_vector), 2)),
              b = c(paste0("Median (", last_assess_yr, ")"),
                    f(median(base_model$extra_mcmc$q_vector), 2)))

  kbl(d,
      format = "latex",
      booktabs = TRUE,
      col.names = NULL,
      align = c("c", "c"),
      linesep = "",
      escape = FALSE) |>
    row_spec(0, bold = TRUE) |> 
    column_spec(1, color = "blue") |> 
    column_spec(2, color = "red") |> 
    kable_styling(position = "center")
}

k()
```

## Time-varying selectivity
:::::: {.columns}
::: {.column width="50%"}
```{r selectivity-mountains, fig.height=4, out.height = "2.8in", out.width = "1\\columnwidth"}

tv_selex_start_yr <- 1990

plot_selex_mountains(base_model,
                     yrs = tv_selex_start_yr:last_data_yr,
                     ages = 1:8,
                     fill_num_colors = 50,
                     scale = 20)
```
:::

::: {.column width="50%"}
```{r selectivity-uncertainty, fig.height=4, out.height = "2.8in", out.width = "1\\columnwidth"}
plot_selex_uncertainty(base_model,
                       n_col = 2,
                       label_loc = c(1, 0.65),
                       label_font_size = 3)
```
:::
::::::

## Posterior distributions for survey (left) and fishery (right) selectivity
:::::: {.columns}
::: {.column width="50%"}
```{r selectivity-posterior-survey, fig.height=4, out.height = "2.8in", out.width = "1\\columnwidth"}
plot_selex_posteriors(base_model,
                      type = "survey",
                      age_range = c(1, 8),
                      post_med_line_color = "red3",
                      unc_line_color = "red3",
                      glow = TRUE)
```
:::

::: {.column width="50%"}
```{r selectivity-posterior-fishery, fig.height=4, out.height = "2.8in", out.width = "1\\columnwidth"}
plot_selex_posteriors(base_model,
                      type = "fishery",
                      age_range = c(1, 8),
                      glow = TRUE)
```
:::
::::::

## Key quantities
```{r table-parameter-ests, results = "asis"}
table_param_est(
  models = list(base_model, last_yr_base_model),
  model_nms = c(base_model_name, last_yr_base_model_name),
  end_yr = end_yr,
  section_bold = TRUE,
  section_italics = TRUE,
  section_underline = TRUE,
  section_line_above = FALSE,
  section_line_below = FALSE,
  digits = 3,
  font_size = 5.5,
  header_font_size = 7)
```
