# Estimated Quantities
## Key parameters
:::::: {.columns}
::: {.column width="40%"}
* **Prior** for natural mortality looks to be
  influencing \textcolor{Maroon}{median} of \textcolor{blue}{posterior}
* Posterior for steepness does not shift much from prior
* DM for fishery has a relatively narrow posterior distribution
* Prior for DM parameters essentially defines parameter bounds (discussed
  further in sensitivity section)
:::

::: {.column width="60%"}
```{r priors-posts, fig.height = 4, out.height = "80%"}
plot_priors_vs_posts(base_model,
                     x_range = "prior",
                     ncol = 3,
                     nrow = 3)
```
:::
::::::

## Acoustic survey catchability (\emph{$q_b$}) posterior for this assessment
```{r catchability-density-q, fig.height = 4, out.height = "60%"}
plot_catchability_density(base_model,
                          last_yr_base_model,
                          type = "age2",
                          line_widths = c(1, 1),
                          line_types = c("solid", "solid"))
```

```{r table-catchability-medians-q, results = "asis"}
k <- function(){

  d <- tibble(a = c(paste0("Median (", assess_yr, ")"),
                    f(median(base_model$extra_mcmc$q_vector), 2)),
              b = c(paste0("Median (", last_assess_yr, ")"),
                    f(median(last_yr_base_model$extra_mcmc$q_vector), 2)))

  kbl(d,
      format = "latex",
      booktabs = TRUE,
      col.names = NULL,
      align = c("c", "c"),
      linesep = "",
      escape = FALSE) |>
    row_spec(0, bold = TRUE) |>
    column_spec(1, color = "green") |>
    column_spec(2, color = "red") |>
    kable_styling(position = "center")
}

k()
```

## Age-1 index catchability (\emph{$q_1$}) posterior for this assessment
```{r catchability-density-1, fig.height = 4, out.height = "60%"}
plot_catchability_density(base_model,
                          last_yr_base_model,
                          type = "age1",
                          line_widths = c(1, 1),
                          line_types = c("solid", "solid"))
```

```{r table-catchability-medians-1, results = "asis"}
k <- function(){

  d <- tibble(a = c(paste0("Median (", assess_yr, ")"),
                    f(median(base_model$extra_mcmc$q_vector_age1), 2)),
              b = c(paste0("Median (", last_assess_yr, ")"),
                    f(median(last_yr_base_model$extra_mcmc$q_vector_age1), 2)))

  kbl(d,
      format = "latex",
      booktabs = TRUE,
      col.names = NULL,
      align = c("c", "c"),
      linesep = "",
      escape = FALSE) |>
    row_spec(0, bold = TRUE) |>
    column_spec(1, color = "green") |>
    column_spec(2, color = "red") |>
    kable_styling(position = "center")
}

k()
```

## Time-varying selectivity
:::::: {.columns}
::: {.column width="50%"}
```{r selectivity-mountains, fig.height = 4, out.height = "80%"}

tv_selex_start_yr <- 1990

plot_selex_mountains(base_model,
                     yrs = tv_selex_start_yr:last_data_yr,
                     ages = 1:8,
                     fill_num_colors = 50,
                     scale = 20)
```
:::

::: {.column width="50%"}
```{r selectivity-uncertainty, fig.height = 4, out.height = "80%"}

plot_selex_uncertainty(base_model,
                       n_col = 2,
                       pad_top = TRUE,
                       pad_bottom = TRUE,
                       label_loc = c(1, 0.65),
                       label_font_size = 3)
```
:::
::::::

## Posterior distributions for survey (left) and fishery (right) selectivity
:::::: {.columns}
::: {.column width="50%"}
```{r selectivity-posterior-survey, fig.height = 4, out.height = "80%"}
plot_selex_posteriors(base_model,
                      type = "survey",
                      age_range = c(1, 8),
                      n_posts = 1000,
                      post_med_line_color = "red3",
                      unc_line_color = "red3",
                      glow = TRUE)
```
:::

::: {.column width="50%"}
```{r selectivity-posterior-fishery, fig.height = 4, out.height = "80%"}
plot_selex_posteriors(base_model,
                      type = "fishery",
                      n_posts = 1000,
                      age_range = c(1, 8),
                      glow = TRUE)
```
:::
::::::

## Key quantities
```{r table-parameter-ests, results = "asis"}
table_param_est(
  models = list(base_model, last_yr_base_model),
  model_nms = c(base_model_name, last_yr_base_model_name),
  section_bold = TRUE,
  section_italics = TRUE,
  section_underline = TRUE,
  section_line_above = FALSE,
  section_line_below = FALSE,
  digits = 3,
  font_size = 4,
  header_font_size = 9,
  show_loglike = FALSE)
```

## Recruitment Deviations
```{r rec-dev, fig.height = 4, out.height = "80%"}

plot_recdevs(list(base_model),
             list(base_model_name),
             line_color = ts_single_line_color,
             leg_pos = "none")
```

## Absolute Recruitment
```{r rec-abs, fig.height = 4, out.height = "80%"}

plot_recruitment(list(base_model),
                 list(base_model_name),
                 inc_means = TRUE,
                 leg_pos = "none") |>
  suppressWarnings()
```

## Absolute Recruitment (`r assess_yr - 1` assessment)
```{r rec-abs-last-year, fig.height = 4, out.height = "80%"}

plot_recruitment(list(last_yr_base_model),
                 list(last_yr_base_model_name),
                 inc_means = FALSE,
                 leg_pos = "none") |>
  suppressWarnings()
```

## Estimates of above-average cohorts
```{r above-average-cohorts-table, results = "asis"}

cohorts <- sort(c(2016, 2017, 2020, 2021, 2022)) # large_cohorts includes
                                        # 2010, 2014
last_few_yrs <- c(last_assess_yr, assess_yr)
table_above_avg_cohorts_yrs(cohorts, last_few_yrs)
```

## Numbers-at-age (billions)
:::::: {.columns}
::: {.column width="30%"}
* Median posterior distribution estimates
* Red line is mean age for the year
* Increasing trend in mean age since 2021
* Mean age drops significantly in years with large age-0 cohorts,
  including in 2020 and 2021
:::

::: {.column width="70%"}
```{r main-numbers-at-age, fig.height = 4, out.height = "80%"}
plot_age_comp_bubbles(base_model, type = "fishery",
                      proportions = FALSE,
                      leg_pos = "top",
                      tick_prop = 0.3,
                      vjust_x_labels = -1.2,
                      remove_yr_labels = NULL)
```
:::
::::::

## Spawning Biomass
```{r main-biomass, fig.height = 4, out.height = "80%"}

plot_biomass(list(base_model),
             list(base_model_name),
             ylim = c(0, 5),
             point_shape = ts_single_model_pointshape,
             leg_pos = "none")
```

## Spawning Biomass (million t)

```{r spawn-bio-last-yr-vs-curr-yr, results = "asis"}
table_yearly_model_compare(last_yr_base_model,
                           base_model,
                           last_yr = last_assess_yr,
                           curr_yr = assess_yr,
                           digits = 3,
                           font_size = 10)
```
* The median estimate of *B*~`r assess_yr-1` has decreased slightly from last
  year's assessment.

## Uncertainty in Spawning Biomass
```{r main-historical-dispersion-fig, , fig.height = 4, out.height = "80%"}
p <- list()
p[[1]] <-
  plot_assessment_history_disp(base_model)
p[[2]] <-
  plot_assessment_history_disp(base_model,
                               type = "coeff",
                               y_lim = c(0, 0.6))
plot_grid(plotlist = p, nrow = 1)
```

## Relative Spawning Biomass
```{r main-rel-biomass, fig.height = 4, out.height = "70%"}

plot_rel_biomass(model_lst = list(base_model),
                 model_names = list(base_model_name),
                 ylim = c(0, 2.5),
                 alpha = 0.2,
                 leg_pos = "none") |>
  suppressWarnings()
```

## Fishing Intensity
```{r main-fish-inten, fig.height = 4, out.height = "70%"}

plot_fishing_intensity(base_model)
```

## Exploitation Fraction (ages 2+)
```{r main-expl-frac, fig.height = 4, out.height = "80%"}

plot_exploitation_fraction(base_model)
```
