# Response SRG
## `r end_yr-1` SRG Assessment Recommendations

We respond here to three requests that the JTC would like to get
feedback on at the meeting.

Responses to all other requests can be found in the assessment document, which include:

* Reference points in the MSE
* Conduct key sensitivities
* CPUE distribution
* Time-varying maturity
* Age-1 index distribution
* Age-1 index CVs
* Freezer trawler sampling
* Ageing error study
* 2D AR selectivity  

## Dynamic unfished spawning biomass

**The SRG recommends that the JTC include dynamic unfished spawning biomass
in the 2024 assessment as a comparator with the equilibrium unfished spawning
biomass used to provide management advice. The SRG also encourages the
continued outreach regarding the use of dynamic reference points to stakeholders
and managers, including identifying pros and cons of using dynamic unfished
spawning biomass.**

## **Response**: Dynamic unfished spawning biomass
:::::: {.columns}
::: {.column width="40%"}
* **Fished time series is the current estimates of spawning biomass**
* \textcolor{red}{Unfished time series removes fishing mortality from modeled
  population dynamics, thereby directly showing the influence due to fishing}
* Assume environment (not fishing) affects recruitment deviations
* Maintain assumptions of no density dependence in life history parameters
:::

::: {.column width="60%"}
```{r biomass-unfished, fig.height = 4, out.height = "80%"}
plot_biomass_fished_unfished(base_model,
                             model_nms = c("Base model - Fished",
                                           "Base model - Unfished"),
                             leg_pos = c(0.6, 0.9),
                             xlim = c(1963,
                                      year(Sys.time())),
                             rel = FALSE)
```
:::
::::::

## **Response**: Dynamic $B_0$
```{r biomass-dynamic-B0, fig.height = 4, out.height = "80%"}
plot_biomass_fished_unfished(base_model,
                             model_nms = c("Base model - Static B0",
                                           "Base model - Dynamic B0"),
                             leg_pos = c(0.6, 0.9),
                             ylim = c(0, 2.75),
                             rel = TRUE)
```

## Natural mortality

**The SRG recommends that the JTC explore alternative ways of estimating natural
mortality to update the current approach in the model, which is based on methods
from more than a decade ago, since newer methods are available. Information
presented during the SRG meeting implies that natural mortality on age-2 Pacific
Hake is higher than currently assumed in the assessment model and should be
explored more fully.**

## **Response**: Natural mortality

Investigate estimating a vector of natural mortality (*M*) parameters:

* Breakpoints at different ages -- no combination led to *M* decreasing with age as hypothesized given the diet data of predators of Pacific Hake (prior highly influential; no prior led to lower *M* for young fish)
* Tagging studies could be used to help inform age-specific *M*
* Diet data could be used to externally estimate *M* at age (CEATTLE model work)
* Other modeling frameworks, such as the Woods Hole Assessment Method have more
  flexibility in modeling natural mortality and might also be an option
  for future explorations

## Input sample size

**The SRG encourages the JTC to consider methods to determine the maximum
input sample size for the age compositions.**

## **Response**: Input sample size

Determining input sample sizes is important for how annual fishery and
survey age compositions are initially weighted, which then provides the basis from
which wholesale re-weighting of data sources (fishery or survey) is done with the
Dirichlet-multinomial data weighting model parameters.
 
* Considered alternative methods, including that of Stewart and Hamel (2014), and
  determined that the first step is to explore the handling of survey
  age-composition data
* Initial effective sample sizes and data source weighting is relative to other
  data sources in the model
* Survey age compositions represent age structure associated with the acoustic survey
  as viewed through an estimated selectivity curve for the acoustic-trawl sampling net
* Selectivity for ages two and older with acoustics is theoretically at or near one
* JTC plans to investigate whether there is a more informative way to utilize survey
  age-composition information in the stock assessment model in the coming year
