---
title: "`r assess_yr` Pacific Hake Stock Assessment Methods and Results"
params:
  sp: "Pacific Hake"
  common_name: "Pacific whiting"
  science_name: "Merluccius productus"
  simple_name: "hake"
  survey_name: "Joint U.S. and Canadian Integrated Acoustic and Trawl Survey"
  assess_yr: 2023
  last_assess_yr: 2022
  last_data_yr: 2022
  model_version: "01"
  last_yr_model_version: "01"
author: Pacific Hake Joint Technical Committee
date: "SRG meeting -- `r assess_yr`"
subtitle: "Disclaimer: These materials do not constitute a formal publication and are for information only. They are in a pre-review, pre-decisional state and should not be formally cited or reproduced. They are to be considered provisional and do not represent any determination or policy of NOAA or the Department of Commerce."
output:
  beamer_presentation:
    theme: Singapore
    slide_level: 2
    keep_tex: true
classoption: "aspectratio=169"
fontsize: 11pt
urlcolor: blue
header-includes:
  - \usepackage{makecell, booktabs, array}
  - \usepackage[outdir=./knitr-figs-pdf/]{epstopdf}
  - \AtBeginSubsection{}
  - \AtBeginSection{}
---

```{r setup, echo = FALSE, cache = FALSE, message = FALSE, results = "hide", warning = FALSE}
library(knitr)

if(is_latex_output()){
  knitr_figs_dir <<- "knitr-figs-pdf/"
  knitr_cache_dir <<- "knitr-cache-pdf/"
  fig_out_type <<- "png"
}else{
  knitr_figs_dir <<- "knitr-figs-docx/"
  knitr_cache_dir <<- "knitr-cache-docx/"
  fig_out_type <<- "png"
}
fig_width <<- 7.5
fig_dpi <<- 200
fig_align <<- "center"
fig_pos <<- "htb"
opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  results = "hide",
  comment = "#>",
  fig.path = knitr_figs_dir,
  cache.path = knitr_cache_dir,
  fig.width = fig_width,
  echo = FALSE,
  autodep = FALSE,
  cache = TRUE,
  cache.lazy = FALSE,
  cache.comments = FALSE,
  dev = fig_out_type,
  dpi = fig_dpi,
  fig.align = fig_align,
  fig.pos = fig_pos)

devtools::load_all(here::here())
fig_dir <- here::here("beamer", "srg", "assessment", "knitr-figs-pdf")
if(!dir.exists(fig_dir)){
  dir.create(fig_dir)
}
```

```{r loading, include = FALSE, results = "asis"}
res <- knitr::knit_child("../../../doc/001-load-packages.rmd")
cat(res, sep = '\n')
res <- knitr::knit_child("../../../doc/002-load-globals.rmd")
cat(res, sep = '\n')
res <- knitr::knit_child("../../../doc/003-load-models.rmd")
cat(res, sep = '\n')
res <- knitr::knit_child("../../../doc/004-load-project-variables.rmd")
cat(res, sep = '\n')
```

# Outline
* Model changes from `r last_assess_yr`
* Show some MCMC diagnostics
* Fits to data
* Estimates of key quantities
* Brief response to `r last_assess_yr` SRG assessment recommendations
* Summary

# Changes from `r last_assess_yr`
## Changes from the `r last_assess_yr` assessment
* Update Stock Synthesis to version `r ss_version`
* Add new catch data for `r last_assess_yr` and update historical catches 
* Add new weight-at-age data for `r last_assess_yr`and update
  weight-at-age data
* Add the `r last_assess_yr` acoustic survey biomass estimate and age data
* Add the `r last_assess_yr` age-1 index estimate
* Add new fishery age composition data for `r last_assess_yr` and historical
  fishery age composition data
* No changes to acoustic survey biomass estimates or age-1 index
  estimates this year
* All model runs in the assessment use MCMC

## Bridging: Model Updates and Additions
```{r bridge-biomass, fig.height=4, out.height = "2.7in", out.width = "1\\columnwidth"}
plist <- list()
plist[[1]] <-
  plot_rel_biomass(d_obj = d_obj_bridge_rel_biomass[[1]],
                   ylim = c(0, 2.5),
                   x_labs_mod = 10,
                   wrap_y_label = TRUE,
                   leg_pos = "none")
plist[[2]] <-
  plot_recdevs(d_obj = d_obj_bridge_recdev[[1]],
               leg_pos = "none",
               x_labs_mod = 10,
               line_width = 0.1)

plot_grid(plotlist = plist,
          nrow = 1,
          ncol = 2)
```

## Bridging: Model Updates and Additions (survey)
```{r bridge-survey, fig.height=4, out.height = "2.7in", out.width = "1\\columnwidth"}
plist <- list()
plist[[1]] <-
  plot_survey_index_fits(d_obj = d_obj_bridge_age2_index[[1]],
                         survey_type = "age2",
                         rev_colors = FALSE,
                         leg_pos = "none")

plist[[2]] <-
  plot_survey_index_fits(d_obj = d_obj_bridge_age1_index[[1]],
                         survey_type = "age1",
                         xlim = c(1995, 2022),
                         ylim = c(0, 11),
                         y_breaks = seq(0, 11, by = 2),
                         rev_colors = FALSE,
                         leg_pos = "none")

plot_grid(plotlist = plist,
          nrow = 1,
          ncol = 2)
```