## Request 3 -- "Selectivity for age-1 index"

Provide plots of selectivity in 2024 as well as mountain plots for sensitivities to removing age-1 index, to the alternative values of phi (deviations for selectivity), and for adding in the eDNA index

* Two time-varying selectivity figures and posterior selectivity for the survey
  and the fishery, each showing just 1000 draws, for the requested
  sensitivities are shown in the subsequent slides.

<!-- sensitivity 1 -->
## Remove age-1 index: time-varying selectivity
<!-- slide 1 -->
:::::: {.columns}
::: {.column width="50%"}
```{r selectivity-mountains-1, fig.height = 4, out.height = "80%"}

tv_selex_start_yr <- 1990

# Left
plot_selex_mountains(sens_models[[2]][[2]],
                     yrs = tv_selex_start_yr:last_data_yr,
                     ages = 1:8,
                     fill_num_colors = 50,
                     scale = 20)
```
:::

::: {.column width="50%"}
```{r selectivity-uncertainty-1, fig.height = 4, out.height = "80%"}

# Right
plot_selex_uncertainty(sens_models[[2]][[2]],
                       n_col = 2,
                       pad_top = TRUE,
                       pad_bottom = TRUE,
                       label_loc = c(1, 0.65),
                       label_font_size = 3)
```
:::
::::::

## Remove age-1 index: survey (left) and fishery (right)
<!-- slide 2 -->
:::::: {.columns}
::: {.column width="50%"}
```{r selectivity-posterior-survey-1, fig.height = 4, out.height = "80%"}
# Left
plot_selex_posteriors(sens_models[[2]][[2]],
                      type = "survey",
                      age_range = c(1, 8),
                      n_posts = 1000,
                      post_med_line_color = "red3",
                      unc_line_color = "red3",
                      glow = TRUE)
```
:::

::: {.column width="50%"}
```{r selectivity-posterior-fishery-1, fig.height = 4, out.height = "80%"}
# Right
plot_selex_posteriors(sens_models[[2]][[2]],
                      type = "fishery",
                      n_posts = 1000,
                      age_range = c(1, 8),
                      glow = TRUE)
```
:::
::::::

<!-- sensitivity 2 -->
## Phi 0.21: time-varying selectivity
<!-- slide 1 -->
:::::: {.columns}
::: {.column width="50%"}
```{r selectivity-mountains-2, fig.height = 4, out.height = "80%"}

tv_selex_start_yr <- 1990

# Left
plot_selex_mountains(sens_models[[3]][[2]],
                     yrs = tv_selex_start_yr:last_data_yr,
                     ages = 1:8,
                     fill_num_colors = 50,
                     scale = 20)
```
:::

::: {.column width="50%"}
```{r selectivity-uncertainty-2, fig.height = 4, out.height = "80%"}

# Right
plot_selex_uncertainty(sens_models[[3]][[2]],
                       n_col = 2,
                       pad_top = TRUE,
                       pad_bottom = TRUE,
                       label_loc = c(1, 0.65),
                       label_font_size = 3)
```
:::
::::::

## Phi 0.21: survey (left) and fishery (right)
<!-- slide 2 -->
:::::: {.columns}
::: {.column width="50%"}
```{r selectivity-posterior-survey-2, fig.height = 4, out.height = "80%"}
# Left
plot_selex_posteriors(sens_models[[3]][[2]],
                      type = "survey",
                      age_range = c(1, 8),
                      n_posts = 1000,
                      post_med_line_color = "red3",
                      unc_line_color = "red3",
                      glow = TRUE)
```
:::

::: {.column width="50%"}
```{r selectivity-posterior-fishery-2, fig.height = 4, out.height = "80%"}
# Right
plot_selex_posteriors(sens_models[[3]][[2]],
                      type = "fishery",
                      n_posts = 1000,
                      age_range = c(1, 8),
                      glow = TRUE)
```
:::
::::::

<!-- sensitivity 3 -->
## Phi 0.70: time-varying selectivity
<!-- slide 1 -->
:::::: {.columns}
::: {.column width="50%"}
```{r selectivity-mountains-3, fig.height = 4, out.height = "80%"}

tv_selex_start_yr <- 1990

# Left
plot_selex_mountains(sens_models[[3]][[3]],
                     yrs = tv_selex_start_yr:last_data_yr,
                     ages = 1:8,
                     fill_num_colors = 50,
                     scale = 20)
```
:::

::: {.column width="50%"}
```{r selectivity-uncertainty-3, fig.height = 4, out.height = "80%"}

# Right
plot_selex_uncertainty(sens_models[[3]][[3]],
                       n_col = 2,
                       pad_top = TRUE,
                       pad_bottom = TRUE,
                       label_loc = c(1, 0.65),
                       label_font_size = 3)
```
:::
::::::

## Phi 0.70: survey (left) and fishery (right)
<!-- slide 2 -->
:::::: {.columns}
::: {.column width="50%"}
```{r selectivity-posterior-survey-3, fig.height = 4, out.height = "80%"}
# Left
plot_selex_posteriors(sens_models[[3]][[3]],
                      type = "survey",
                      age_range = c(1, 8),
                      n_posts = 1000,
                      post_med_line_color = "red3",
                      unc_line_color = "red3",
                      glow = TRUE)
```
:::

::: {.column width="50%"}
```{r selectivity-posterior-fishery-3, fig.height = 4, out.height = "80%"}
# Right
plot_selex_posteriors(sens_models[[3]][[3]],
                      type = "fishery",
                      n_posts = 1000,
                      age_range = c(1, 8),
                      glow = TRUE)
```
:::
::::::

<!-- sensitivity 4 -->
## Phi 2.10: time-varying selectivity
<!-- slide 1 -->
:::::: {.columns}
::: {.column width="50%"}
```{r selectivity-mountains-4, fig.height = 4, out.height = "80%"}

tv_selex_start_yr <- 1990

# Left
plot_selex_mountains(sens_models[[3]][[4]],
                     yrs = tv_selex_start_yr:last_data_yr,
                     ages = 1:8,
                     fill_num_colors = 50,
                     scale = 20)
```
:::

::: {.column width="50%"}
```{r selectivity-uncertainty-4, fig.height = 4, out.height = "80%"}

# Right
plot_selex_uncertainty(sens_models[[3]][[4]],
                       n_col = 2,
                       pad_top = TRUE,
                       pad_bottom = TRUE,
                       label_loc = c(1, 0.65),
                       label_font_size = 3)
```
:::
::::::

## Phi 2.10: survey (left) and fishery (right)
<!-- slide 2 -->
:::::: {.columns}
::: {.column width="50%"}
```{r selectivity-posterior-survey-4, fig.height = 4, out.height = "80%"}
# Left
plot_selex_posteriors(sens_models[[3]][[4]],
                      type = "survey",
                      age_range = c(1, 8),
                      n_posts = 1000,
                      post_med_line_color = "red3",
                      unc_line_color = "red3",
                      glow = TRUE)
```
:::

::: {.column width="50%"}
```{r selectivity-posterior-fishery-4, fig.height = 4, out.height = "80%"}
# Right
plot_selex_posteriors(sens_models[[3]][[4]],
                      type = "fishery",
                      n_posts = 1000,
                      age_range = c(1, 8),
                      glow = TRUE)
```
:::
::::::

<!-- sensitivity 5 -->
## eDNA: time-varying selectivity
<!-- slide 1 -->
:::::: {.columns}
::: {.column width="50%"}
```{r selectivity-mountains-5, fig.height = 4, out.height = "80%"}

tv_selex_start_yr <- 1990

# Left
plot_selex_mountains(sens_models[[2]][[4]],
                     yrs = tv_selex_start_yr:last_data_yr,
                     ages = 1:8,
                     fill_num_colors = 50,
                     scale = 20)
```
:::

::: {.column width="50%"}
```{r selectivity-uncertainty-5, fig.height = 4, out.height = "80%"}

# Right
plot_selex_uncertainty(sens_models[[2]][[4]],
                       n_col = 2,
                       pad_top = TRUE,
                       pad_bottom = TRUE,
                       label_loc = c(1, 0.65),
                       label_font_size = 3)
```
:::
::::::

## eDNA: survey (left) and fishery (right)
<!-- slide 2 -->
:::::: {.columns}
::: {.column width="50%"}
```{r selectivity-posterior-survey-5, fig.height = 4, out.height = "80%"}
# Left
plot_selex_posteriors(sens_models[[2]][[4]],
                      type = "survey",
                      age_range = c(1, 8),
                      n_posts = 1000,
                      post_med_line_color = "red3",
                      unc_line_color = "red3",
                      glow = TRUE)
```
:::

::: {.column width="50%"}
```{r selectivity-posterior-fishery-5, fig.height = 4, out.height = "80%"}
# Right
plot_selex_posteriors(sens_models[[2]][[4]],
                      type = "fishery",
                      n_posts = 1000,
                      age_range = c(1, 8),
                      glow = TRUE)
```
:::
::::::
