# *h*, *M*, $\sigma_r$

## Sensitivity to steepness, *h*
```{r h-biomass-fig, fig.height = 3, out.height = "85%"}
plot_biomass(model_lst = list(sens_models[[1]][[1]],
                              sens_models[[1]][[2]],  # [[1]] is base model
                              sens_models[[1]][[3]]),
             model_names = c(base_model_name,
                             sens_models_desc[[1]][1],
                             sens_models_desc[[1]][2]),
             x_expansion = 4,
             ylim = c(0, 5),
             y_breaks = seq(0, 20, 2),
             leg_font_size = 5,
             leg_pos = c(0.7, 0.85),
             rev_colors = TRUE,
             ribbon_line_type = 0) +
  theme(axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12),
        legend.key.size = unit(0.5, units = "cm"),
        legend.text = element_text(size = 10))
```

## Sensitivity to steepness, *h*
```{r h-biomass-rel-fig, fig.height = 3, out.height = "85%"}
plot_rel_biomass(model_lst = list(sens_models[[1]][[1]],
                              sens_models[[1]][[2]],  # [[1]] is base model
                              sens_models[[1]][[3]]),
             model_names = c(base_model_name,
                             sens_models_desc[[1]][1],
                             sens_models_desc[[1]][2]),
             x_expansion = 4,
             ylim = c(0, 2.5),
             leg_font_size = 5,
             leg_pos = c(0.7, 0.85),
             rev_colors = TRUE,
             ribbon_line_type = 0) +
  theme(axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12),
        legend.key.size = unit(0.5, units = "cm"),
        legend.text = element_text(size = 10))
```

## Sensitivity to natural mortality, *M* (base has prior median 0.2, sd 0.1)
```{r m-biomass-fig, fig.height = 3, out.height = "85%"}
plot_biomass(model_lst = list(base_model,
                              sens_models[[1]][[6]],
                              sens_models[[1]][[7]],
                              sens_models[[1]][[8]]),
             model_names = c(base_model_name,
                             sens_models_desc[[1]][5],
                             sens_models_desc[[1]][6],
                             sens_models_desc[[1]][7]),
             x_expansion = 4,
             ylim = c(0, 20),
             y_breaks = seq(0, 20, 2),
             leg_font_size = 5,
             leg_pos = c(0.7, 0.80),
             rev_colors = TRUE,
             ribbon_line_type = 0) +
  theme(axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12),
        legend.key.size = unit(0.5, units = "cm"),
        legend.text = element_text(size = 10))
```

## Sensitivity to natural mortality, *M* (base has prior median 0.2, sd 0.1)
```{r m-biomass-fig-rel, fig.height 3, out.height = "85%"}
plot_rel_biomass(model_lst = list(base_model,
                                  sens_models[[1]][[6]],
                                  sens_models[[1]][[7]],
                                  sens_models[[1]][[8]]),
                 model_names = c(base_model_name,
                                 sens_models_desc[[1]][5],
                                 sens_models_desc[[1]][6],
                                 sens_models_desc[[1]][7]),
             x_expansion = 4,
             ylim = c(0, 4),
             leg_font_size = 5,
             leg_pos = c(0.7, 0.85),
             rev_colors = TRUE,
             ribbon_line_type = 0) +
  theme(axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12),
        legend.key.size = unit(0.5, units = "cm"),
        legend.text = element_text(size = 10))
```

## Sensitivity to natural mortality, *M* (base has prior median 0.2, sd 0.1)
```{r m-par-table, results = "asis"}
table_param_est(models = list(base_model,
                              sens_models[[1]][[6]],  # [[1]] is base model
                              sens_models[[1]][[7]],
                              sens_models[[1]][[8]]),
                model_nms = c(base_model_name,
                              sens_models_names[[1]][5],
                              sens_models_names[[1]][6],
                              sens_models_names[[1]][7]),
                end_yr = end_yr,
                digits = 3,
                font_size = 5,
                right_cols_cm = 0.75,
                header_font_size = 6,
                section_line_above = FALSE,
                section_line_below = FALSE)
```

## Sensitivity to s.d. of recruitment variability, $\sigma_r$; base `r sigma_r`
```{r sigmar-biomass-fig, fig.height = 3, out.height  = "85%"}
plot_biomass(model_lst = list(base_model,
                              sens_models[[1]][[4]],
                              sens_models[[1]][[5]]),
             model_names = c(base_model_name,
                             sens_models_desc[[1]][3],
                             sens_models_desc[[1]][4]),
             x_expansion = 4,
             ylim = c(0, 5),
             y_breaks = seq(0, 20, 2),
             leg_font_size = 5,
             leg_pos = c(0.7, 0.85),
             rev_colors = TRUE,
             ribbon_line_type = 0) +
  theme(axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12),
        legend.key.size = unit(0.5, units = "cm"),
        legend.text = element_text(size = 10))
```

## Sensitivity to s.d. of recruitment variability, $\sigma_r$; base `r sigma_r`
```{r sigmar-biomass-fig-rel, fig.height = 3, out.height = "85%"}
plot_rel_biomass(model_lst = list(base_model,
                                  sens_models[[1]][[4]],
                                  sens_models[[1]][[5]]),
                 model_names = c(base_model_name,
                                 sens_models_desc[[1]][3],
                                 sens_models_desc[[1]][4]),
             x_expansion = 4,
             ylim = c(0, 4),
             leg_font_size = 5,
             leg_pos = c(0.7, 0.85),
             rev_colors = TRUE,
             ribbon_line_type = 0) +
  theme(axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12),
        legend.key.size = unit(0.5, units = "cm"),
        legend.text = element_text(size = 10))
```

