# Historical


## Historical assessments
```{r historical-assessments, fig.height = 3, out.height = "85%"}

plot_assessment_history_biomass(base_model,
                                assess_history_df,
                                tick_prop = 1.5,
                                vjust_x_labels = -1,
                                leg_pos = c(0.75, 0.7)) +
  theme(axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12),
        legend.key.size = unit(0.1, units = "cm"),
        legend.text = element_text(size = 6))
```


## Historical performance of the Pacific Hake assessment

* General question -- how 'good' are projection probabilities? And why do
  they seem to change over time?
* For example, 2019 assessment Table i we had:

```{r historical-mini-tab, results = "asis"}
hdr <- c("Catch\nin 2019",
         "Probability\n\\emph{B}\\textsubscript{2020}<\\emph{B}\\textsubscript{2019}",
         "Probability\n \\emph{B}\\textsubscript{2020}<\\emph{B}\\textsubscript{40\\%}")
hdr <- linebreaker(hdr, align = "c")

d <- tibble(col1 = c("a: 0", "b: 180,000", "c: 350,000", "\\textcolor{red}{d: 410,000}"),
            col2 = c("17\\%", "40\\%", "57\\%", "\\textcolor{red}{57\\%}"),
            col3 = c("8\\%", "13\\%", "17\\%", "\\textcolor{red}{17\\%}"))
kbl(d,
    format = "latex",
    booktabs = TRUE,
    escape = FALSE,
    col.names = hdr) |>
  row_spec(0, bold = TRUE) |>
  kable_styling(position = "center")
```

\pause
* Now (since it's `r assess_yr`) we '*know*' the 2019 catch was
  `r f(filter(ct_last_10yrs, Year == 2019)$Total)` t, so row d was close
  enough.
\pause
* How do the probabilities in row~d compare to estimates of them from the
  current base model?

## Probabilities of decline in subsequent year
```{r historical-performance-1, fig.height = 3.5, out.height = "85%"}

plot_historical_probs(base_model,
                      type="decline_one_year")
```

## Probabilities of decline in subsequent year
```{r historical-performance-2, fig.height = 3.5, out.height = "85%"}

plot_historical_probs(base_model,
                      legend.inset = c(0.15, 0),
                      legend.cex = 0.8)
```

## Probabilities of decline in subsequent year
```{r historical-performance-3, fig.height = 3.5, out.height = "85%"}

plot_historical_probs(base_model,
                      add.projs = TRUE,
                      legend.inset = c(0.15, 0),
                      legend.cex = 0.8)
```


## Probabilities of decline in subsequent year

* Previous assessments have mostly 'correctly' projected an increase or decrease
  in subsequent year (exceptions: 2017, 2019, 2022, and 2023)
* An assessment's projection is almost always less definitive than from
  the current base model, since current model has more information
* Analysis gives confidence in the current expectation of the stock
  not declining next year
