# Past management

## Past management: Total Allowable Catch
```{r tac-vs-realized-catch-ts, fig.height = 3.5, fig.width = 7.5, out.height = "80%"}

plot_management_catch_vs_tac(catch_targets_df,
                             curr_assess_biomass = base_model$catch_default_policy[1],
                             leg_pos = c(0.12, 0.87),
                             leg_font_size = 8)

def_med_hr_tac <- catch_targets_df |> 
  filter(Year == last_assess_yr) |> 
  select(`Default HCR TAC`) |> 
  unlist()
```

## Past management: Total Allowable Catch
:::::: {.columns}
::: {.column width="40%"}
* March `r last_assess_yr`
  - Default median HR TAC is `r f(def_med_hr_tac)` t
  - Sum of unilateral TACs is `r last_yr_tac` t
* When default HR suggests a large catch, TAC is often set less
* Catches are often less than the TAC
* Box colors correspond to year in the time series
:::

::: {.column width="60%"}
```{r tac-vs-realized-catch, fig.height = 4, fig.width = 6.5, out.height = "75%"}

plot_management_catch_vs_tac_1_to_1(catch_targets_df,
                                    yrs_nudge_right = c(2006, 2010, 2011,
                                                        2012, 2014, 2019,
                                                        2020))
```
:::
::::::

## Past management: Performance
:::::: {.columns}
::: {.column width="30%"}
* P(B~`r assess_yr`~/B~0~ < 0.4) = `r probs_curr_below_b40`%
* P(relative fishing intensity at end of `r assess_yr - 1` > 1.0)
  = `r probs_curr_rel_fish_intens_above_1`%
* Joint probability of both is `r joint_percent_prob_above_below`%
* Fishing intensity has remained below target
* Biomass has mostly remained above target
:::

::: {.column width="70%"}
```{r main-phase, fig.height = 5, fig.width = 8, out.height = "80%"}

plot_phase(base_model,
           start_yr,
           end_yr,
           init_lbl_x_off = -0.04,
           init_lbl_y_off = -0.04,
           final_lbl_x_off = 0.04,
           final_lbl_y_off = 0.04,
           title_y_font_size = 13,
           cross_line_width = 0.5,
           cross_line_color = "black")
```
:::
::::::

