# Projections

## Projection methods

* Projections for 4 years; `r end_yr`--`r end_yr + 3`

* Projections estimate the biomass at start of those years
  - Mean of fishery selectivity from `r end_yr - 5`--`r end_yr - 1` used in
    projections
  - Mean of weight-at-age from `r end_yr - 5`--`r end_yr - 1` used in
    projections
  - Mean of maturity-at-age from `r end_yr - 5`--`r end_yr - 1` used in
    projections
  - Mean of fecundity from `r end_yr - 5`--`r end_yr - 1` used in
    projections
  - Recruitment from stock--recruitment relationship (with uncertain deviations)

* Alternative future catch levels explored

## Default harvest policy for `r assess_yr`
:::::: {.columns}
::: {.column width="38%"}
* Using the defined *F~SPR=40%~* harvest rate with a 40:10 adjustment, the
  median projected `r end_yr` TAC is \textbf{`r ct_limit_quantiles["median"]` t}
* 2.5% and 97.5% quantiles: `r ct_limit_quantiles["lower"]` and
  `r ct_limit_quantiles["upper"]` t
:::

::: {.column width="62%"}
```{r main-projected-catch-density, out.height = "80%"}

plot_param_density(base_model,
                   param_nm = "ForeCatch_2024",
                   y_lim = c(0, 0.0013),
                   expand_vec = c(100, 100),
                   show_y_labels = FALSE,
                   x_lab = paste0("Projected ", assess_yr, " catch (kt) ",
                                  "based on the default harvesy policy"))
```
:::
::::::

## Three-year projections
:::::: {.columns}
::: {.column width="38%"}
- No fishing results in a 1-yea increase in biomass followed by a flat
  relative spawning biomass from `r end_yr` to `r end_yr + 2`, then a
  very slight decline

- All positive catch options result in a 1-year increase in biomass followed
  by continuous decline through to start of 2027
  
- Uncertainty is large and increases from `r end_yr` to `r end_yr + 3`
:::

::: {.column width="62%"}
```{r main-forecast-depletion-comparison-plot, out.height = "80%"}

# See the file `forecast-catch-levels.R` at the list called `ct_levels`. The values in
# `fore_inds` below are the indices of those forecast values in that list.
plot_depl_fore_comparison(base_model,
                          fore_inds = c(1, 2, 6, 12, 14),
                          forecast_yrs = forecast_yrs)
```
:::
::::::

## Projected age proportions for `r end_yr` fishery catch
:::::: {.columns}
::: {.column width="45%"}
**Median proportions:**
```{r fore-age-props, results = "asis"}

table_fore_age_props(fore_catch_prop,
                     fore_catch_prop_wt,
                     ages_filt = 1:15,
                     font_size = 8) |> 
    # Highlight two largest cohorts
    row_spec(12:13,
           bold = table_highlight_bold,
           background = table_highlight_color)
```
:::

::: {.column width="55%"}
```{r main-age-comp-forecast, fig.height = 3.5, fig.width = 5.5, out.height = "80%"}
plot_fore_age_comps(base_model)
```
:::
::::::
