# Projections

## Projection methods

* Projections estimate the biomass at start of `r end_yr + 1`,
  `r end_yr + 2`, and `r end_yr + 3`
  - Mean of fishery selectivity from `r end_yr - 5`--`r end_yr - 1` used in
    projections
  - Mean of weight-at-age from `r end_yr - 5`--`r end_yr - 1` used in
    projections
  - Recruitment from stock--recruitment relationship (with uncertain deviations)
  - Used for default HR calculations
  - Alternative future catch levels explored
  - Equilibrium calculations (*B~0~*, *F~SPR~*, MSY, etc.)
* Base selectivity (used for years before 1991 as well)
  - Mean of weight-at-age across 1975-`r last_data_yr`
  - Recruitment at estimated *R~0~* or from stock--recruitment relationship
* Catch alternatives presented for some specific cases

## Harvest-rule predicted catch for `r assess_yr`
:::::: {.columns}
::: {.column width="38%"}
* Using the defined *F~SPR=40%~* harvest rate with a 40:10 adjustment, the
  median projected `r end_yr` TAC is \textbf{`r ct_limit_quantiles["median"]` t}
* 2.5% and 97.5% quantiles: `r ct_limit_quantiles["lower"]` and
  `r ct_limit_quantiles["upper"]` t
:::

::: {.column width="62%"}
```{r main-projected-catch-density, out.height = "80%"}

plot_catch_forecast_density(base_model,
                            yr = end_yr)
```
:::
::::::

## Three-year projections
:::::: {.columns}
::: {.column width="38%"}
* No fishing results in flat *median* relative spawning biomass from
  `r assess_yr` to `r assess_yr + 3` then leveling off
* 180,000 t catch shows similar biomass in `r end_yr + 1` followed by decline
* All others shown result in immediate declines in the median
* Uncertainty is large and increases from `r end_yr` to `r end_yr + 3`
:::

::: {.column width="62%"}
```{r main-forecast-depletion-comparison-plot, out.height = "80%"}

# See the file `forecast-catch-levels.R` at the list called `ct_levels`. The values in
# `fore_inds` below are the indices of those forecast values in that list.
plot_depl_fore_comparison(base_model,
                          fore_inds = c(1, 2, 6, 12, 14),
                          forecast_yrs = forecast_yrs)
```
:::
::::::

## Projected age proportions for `r end_yr` fishery catch
:::::: {.columns}
::: {.column width="45%"}
**Median proportions:**
```{r fore-age-props, results = "asis"}

table_fore_age_props(fore_catch_prop,
                     fore_catch_prop_wt,
                     ages_filt = 1:15,
                     font_size = 8) |> 
    # Highlight two largest cohorts
    row_spec(12:13,
           bold = table_highlight_bold,
           background = table_highlight_color)
```
:::

::: {.column width="55%"}
```{r main-age-comp-forecast, fig.height = 3.5, fig.width = 5.5, out.height = "80%"}
plot_fore_age_comps(base_model, )
```
:::
::::::
