# Decision Tables

## Decision Tables

* Decision table format
  - Quantiles from the posterior distribution for *Relative spawning biomass*
    (Table **g**) and *Fishing intensity* (Table **h**)
  - Look of the tables has changed but the information is the same as last year
  
* Catch alternatives
  - **a**: `r ct_levels[[1]][[2]]` (zero catch)
  - **b**, **c**, **d**, **g**, **i**, **k**: Constant catches of
    `r ct_levels[[2]][[2]]`, `r ct_levels[[3]][[2]]`,
    `r ct_levels[[4]][[2]]`, `r ct_levels[[7]][[2]]`,
    `r ct_levels[[9]][[2]]`, and `r ct_levels[[11]][[2]]`.
  - **f**: Constant catch equal to the `r ct_levels[[6]][[2]]`
  - **l**: Constant catch equal to the `r ct_levels[[12]][[2]]`,
  - **e**, **h**, **j**: Annual reductions of 10% from:
        `r f(ct_levels[[5]][[1]][1])` t,
        `r f(ct_levels[[8]][[1]][1])` t, and
        `r f(ct_levels[[10]][[1]][1])` t
  - **m**: Fishing Intensity = 100% in each year conditioned on fixed catch
       in previous year
  - **n**: Median Default Harvest Rule in each year conditioned on fixed catch
         in previous year
  - **o**: Fishing intensity giving 50% probability that the median
         `r assess_yr` catch equals median `r assess_yr + 1` catch

## Relative Spawning Biomass (select rows only)
```{r decisions-biomass-table, results = "asis"}

table_decision(base_model,
               type = "biomass",
               rows_to_show = c("a", "b", "f", "j", "l"),
               font_size = 6,
               header_font_size = 7)
```

## Probability table definitions

Probabilities associated with biomass and fishing-based metrics for different
fixed catch levels (see Executive Summary: Tables **i**, **j**, and **k**;
Figures **k**, **l**, and **m**)

* Fix the catch in `r assess_yr` to estimate *B*\textsubscript{`r assess_yr + 1`}
* Fix the catches in `r assess_yr` and `r assess_yr + 1` to estimate
  *B*\textsubscript{`r assess_yr + 2`}
* Fix the catches in `r assess_yr`, `r assess_yr + 1`, and `r assess_yr + 2`
  to estimate *B*\textsubscript{`r assess_yr + 3`}
* P(*B*\textsubscript{`r assess_yr + 1`} < *B*~y~): Probability that biomass in
  `r assess_yr + 1` is less a specified biomass such as
  *B*\textsubscript{`r assess_yr`} or `r b_40`
* P(relative FI > 100% target): Probability that relative fishing intensity
  in fixed catch year is greater than the target fishing intensity
* Probabilities are calculated as proportions of the MCMC samples meeting
  the criteria, e.g. 50% probability of being under `r b_40` means that
  4,000 of the 8,000 MCMC samples were under `r b_40`

## Probabilities based on `r end_yr` catch

```{r main-risk-forecast-year-1-table, results = "asis"}

table_risk(
  base_model,
  forecast_yrs,
  index = 1,
  type = "probability",
  font_size = 8,
  header_font_size = 9)
```

## Probabilities based on `r end_yr` catch
```{r forecast-risk-comparison-plot-year-1, fig.height = 3.5, out.height = "80%"}

plot_fore_compare(base_model,
                  forecast_yrs = forecast_yrs,
                  fore_yr = forecast_yrs[1],
                  leg_pos = c(0.25, 0.75),
                  leg_font_size = 9,
                  remove_x_val = c(270)) +
  # Following make the legend smaller and legend items closer together
  theme(legend.key.size = unit(0.25, "cm"),
        legend.spacing.y = unit(0.01, "cm"),
        legend.box.background = element_rect(colour = "black")) +
  guides(color = guide_legend(byrow = TRUE))
```

## Probabilities based on `r end_yr` and `r end_yr + 1` catches
```{r main-risk-forecast-year-2-table, results = "asis"}

table_risk(base_model,
           forecast_yrs,
           index = 2,
           type = "probability",
           font_size = 8,
           header_font_size = 9)
```

## Probabilities based on `r end_yr` and `r end_yr + 1` catches
```{r forecast-risk-comparison-plot-year-2, fig.height = 3.5, out.height = "80%"}

plot_fore_compare(base_model,
                  forecast_yrs = forecast_yrs,
                  fore_yr = forecast_yrs[2],
                  leg_pos = c(0.25, 0.3),
                  leg_font_size = 9,
                  remove_x_val = c(264, 342, 651)) +
  # Following make the legend smaller and legend items closer together
  theme(legend.key.size = unit(0.25, "cm"),
        legend.spacing.y = unit(0.01, "cm"),
        legend.box.background = element_rect(colour = "black")) +
  guides(color = guide_legend(byrow = TRUE))
```

## Probabilities based on `r end_yr`, `r end_yr + 1`, and `r end_yr + 2` catches
```{r main-risk-forecast-year-3-table, results = "asis"}

table_risk(base_model,
           forecast_yrs,
           index = 3,
           type = "probability",
           font_size = 8,
           header_font_size = 9)
```
## Probabilities based on `r end_yr`, `r end_yr + 1`, and `r end_yr + 2` catches
```{r forecast-risk-comparison-plot-year-3, fig.height = 3.5, out.height = "80%"}

plot_fore_compare(base_model,
                  forecast_yrs = forecast_yrs,
                  fore_yr = forecast_yrs[3],
                  leg_pos = c(0.25, 0.4),
                  leg_font_size = 9,
                  remove_x_val = c(264, 605)) +
  # Following make the legend smaller and legend items closer together
  theme(legend.key.size = unit(0.25, "cm"),
        legend.spacing.y = unit(0.01, "cm"),
        legend.box.background = element_rect(colour = "black")) +
  guides(color = guide_legend(byrow = TRUE))
```

