# Decision Tables

## Decision Tables

* Decision table format (as improved last year)
  - Quantiles from the posterior distribution for relative spawning biomass
    and fishing intensity
* Catch alternatives
  - a: `r ct_levels[[1]][[2]]` (zero catch)
  - b, c, d, g, i, k: Constant catches of `r ct_levels[[2]][[2]]`, 
    `r ct_levels[[3]][[2]]`, `r ct_levels[[4]][[2]]`, `r ct_levels[[7]][[2]]`,
    `r ct_levels[[9]][[2]]`, and `r ct_levels[[11]][[2]]`.
  - f: Constant catch equal to the `r ct_levels[[6]][[2]]`
  - l: Constant catch equal to the `r ct_levels[[12]][[2]]`,
  - e, h, j: Annual reductions of 10% from:
        `r f(ct_levels[[5]][[1]][1])` t,
        `r f(ct_levels[[8]][[1]][1])` t, and
        `r f(ct_levels[[10]][[1]][1])` t.
  - m: Fishing Intensity = 100% in each year conditioned on fixed catch
       in previous year
  - n: Median default Harvest Rule in each year conditioned on fixed catch
       in previous year
  - o: Fishing intensity giving 50% prob. that the median `r assess_yr`
       catch equals median `r assess_yr + 1` catch

## Relative Spawning Biomass
```{r decisions-biomass-table, results = "asis"}

table_decision(base_model,
               type = "biomass",
               rows_to_show = c("a", "b", "f", "j", "k"),
               font_size = 6,
               header_font_size = 7)
```

## Probability table definitions

Probabilities associated with biomass and fishing-based metrics for different
fixed catch levels (see Executive Summary: Tables i, j, and k; Figures k, l,
and m)

* Fix the catch in `r assess_yr` to estimate *B*\textsubscript{`r assess_yr + 1`}
* Fix the catches in `r assess_yr` and `r assess_yr + 1` to estimate
  *B*\textsubscript{`r assess_yr + 2`}
* Fix the catches in `r assess_yr`, `r assess_yr + 1`, and `r assess_yr + 2`
  to estimate *B*\textsubscript{`r assess_yr + 3`}
* P(*B*\textsubscript{`r assess_yr + 1`} < *B*~y~): Probability that biomass in
  `r assess_yr + 1` is less a specified biomass such as
  *B*\textsubscript{`r assess_yr`} or `r b_40`
* P(relative FI > 100% target): Probability that relative fishing intensity
  in fixed catch year is greater than the target fishing intensity
* Probabilities are calculated as proportions of the MCMC samples meeting
  the criteria, e.g. 50% probability of being under `r b_40` means that
  4,000 of the 8,000 MCMC samples were under `r b_40`

## Probabilities based on `r end_yr` catch

```{r main-risk-forecast-year-1-table, results = "asis"}

table_risk(
  base_model,
  forecast_yrs,
  index = 1,
  type = "probability",
  font_size = 8,
  header_font_size = 9)
```

## Probabilities based on `r end_yr` catch
```{r forecast-risk-comparison-plot-year-1, fig.height = 3.5, out.height = "75%"}

plot_fore_compare(base_model,
                  forecast_yrs = forecast_yrs,
                  fore_yr = forecast_yrs[1],
                  leg_pos = c(0.15, 0.28),
                  leg_font_size = 5,
                  remove_x_val = 325) +
  # Following make the legend smaller and legend items closer together
  theme(legend.key.size = unit(0.25, "cm"),
        legend.spacing.y = unit(0.01, "cm"),
        legend.box.background = element_rect(colour = "black")) +
  guides(color = guide_legend(byrow = TRUE))

```

## Probabilities based on `r end_yr` and `r end_yr + 1` catches
```{r main-risk-forecast-year-2-table, results = "asis"}

table_risk(base_model,
           forecast_yrs,
           index = 2,
           type = "probability",
           font_size = 8,
           header_font_size = 9)
```

## Probabilities based on `r end_yr` and `r end_yr + 1` catches
```{r forecast-risk-comparison-plot-year-2, fig.height = 3.5, out.height = "75%"}

plot_fore_compare(base_model,
                  forecast_yrs = forecast_yrs,
                  fore_yr = forecast_yrs[2],
                  leg_pos = c(0.15, 0.43),
                  leg_font_size = 5,
                  remove_x_val = c(315, 342, 740)) +
  # Following make the legend smaller and legend items closer together
  theme(legend.key.size = unit(0.25, "cm"),
        legend.spacing.y = unit(0.01, "cm"),
        legend.box.background = element_rect(colour = "black")) +
  guides(color = guide_legend(byrow = TRUE))
```

## Probabilities based on `r end_yr`, `r end_yr + 1`, and `r end_yr + 2` catches
```{r main-risk-forecast-year-3-table, results = "asis"}

table_risk(base_model,
           forecast_yrs,
           index = 3,
           type = "probability",
           font_size = 8,
           header_font_size = 9)
```
## Probabilities based on `r end_yr`, `r end_yr + 1`, and `r end_yr + 2` catches
```{r forecast-risk-comparison-plot-year-3, fig.height = 3.5, out.height = "75%"}

plot_fore_compare(base_model,
                  forecast_yrs = forecast_yrs,
                  fore_yr = forecast_yrs[3],
                  leg_pos = c(0.15, 0.4),
                  leg_font_size = 5,
                  remove_x_val = 621) +
  # Following make the legend smaller and legend items closer together
  theme(legend.key.size = unit(0.25, "cm"),
        legend.spacing.y = unit(0.01, "cm"),
        legend.box.background = element_rect(colour = "black")) +
  guides(color = guide_legend(byrow = TRUE))
```

