# Sampling summaries

## Monthly sampling summary for Canada in `r last_data_yr`

```{r age-comp-comparison, results = "asis"}

sample_df <- canada_load_sample_data() |> 
  filter(sex %in% c(1, 2))

samples_fleet_lst <- canada_get_fleet_samples(sample_df)
# Remove JV for this table
samples_fleet_lst <- samples_fleet_lst[names(samples_fleet_lst) != "jv"]

samples_summary_tbls_lst <- canada_extract_sampling_by_month(
  samples_fleet_lst,
  yr = last_data_yr)

```

:::::: {.columns}
::: {.column width="45%"}
\begin{center}\textbf{Freezer trawlers}\end{center}
```{r canada-sample-summary-ft, results = "asis"}
table_sampling_by_month(
  samples_summary_tbls_lst$ft,
  font_size = 8,
  header_font_size = 9)
```
:::

::: {.column width="45%"}
\begin{center}\textbf{Shoreside}\end{center}
```{r canada-sample-summary-ss, results = "asis"}
table_sampling_by_month(
  samples_summary_tbls_lst$ss,
  font_size = 8,
  header_font_size = 9)
```
:::
::::::

## Monthly sampling summary for U.S. in `r last_data_yr`

```{r calc-numread, echo = FALSE, eval = FALSE}
load("page.Rdat")
load("atsea.ages.Rdat")
```

```{r us-sample-summary-atsea, results = "asis", eval = FALSE}
# TODO: use this code rather than the pre-made tables below
table_sampling_by_month(
  us_extract_sampling_by_month(c("AGE", "LENGTH", "WEIGHT"), atsea.ages),
  font_size = 8,
  header_font_size = 9)
```


```{r us-sample-summary-sb, results = "asis", eval = FALSE}
# TODO: use this code rather than the pre-made tables below
table_sampling_by_month(
  us_extract_sampling_by_month(c("AGE", "FISH_LENGTH", "FISH_WEIGHT"), page),
  font_size = 8,
  header_font_size = 9)
```

:::::: {.columns}
::: {.column width="45%"}
\begin{center}\textbf{At-Sea}\end{center}
\begin{table}
\centering\begingroup\fontsize{8}{10}\selectfont

\begin{tabular}[t]{lR{1.5cm}R{1.5cm}R{1.5cm}}
\toprule
\textbf{\makecell[c]{ \fontsize{9}{12}\selectfont Month}} & \textbf{\makecell[c]{ \fontsize{9}{12}\selectfont Number\\ \fontsize{9}{12}\selectfont of ages}} & \textbf{\makecell[c]{ \fontsize{9}{12}\selectfont Number\\ \fontsize{9}{12}\selectfont of lengths}} & \textbf{\makecell[c]{ \fontsize{9}{12}\selectfont Number\\ \fontsize{9}{12}\selectfont of weights}}\\
\midrule
May & 1,015 & 1,023 & 1,023\\
Jun & 69 & 69 & 69\\
Aug & 0 & 153 & 153\\
Sep & 265 & 644 & 644\\
Oct & 376 & 848 & 848\\
Nov & 0 & 22 & 22\\
\midrule
\textbf{Total} & \textbf{1,725} & \textbf{2,759} & \textbf{2,759}\\
\bottomrule
\end{tabular}
\endgroup{}
\end{table}
:::

::: {.column width="45%"}
\begin{center}\textbf{Shore-Based}\end{center}
\begin{table}
\centering\begingroup\fontsize{8}{10}\selectfont
\begin{tabular}[t]{lR{1.5cm}R{1.5cm}R{1.5cm}}
\toprule
\textbf{\makecell[c]{ \fontsize{9}{12}\selectfont Month}} & \textbf{\makecell[c]{ \fontsize{9}{12}\selectfont Number\\ \fontsize{9}{12}\selectfont of ages}} & \textbf{\makecell[c]{ \fontsize{9}{12}\selectfont Number\\ \fontsize{9}{12}\selectfont of lengths}} & \textbf{\makecell[c]{ \fontsize{9}{12}\selectfont Number\\ \fontsize{9}{12}\selectfont of weights}}\\
\midrule
Mar & 0 & 20 & 20\\
May & 340 & 720 & 340\\
Jun & 448 & 540 & 448\\
Jul & 240 & 500 & 440\\
Aug & 60 & 500 & 400\\
Sep & 60 & 370 & 310\\
Oct & 180 & 560 & 479\\
Nov & 0 & 20 & 20\\
\midrule
\textbf{Total} & \textbf{1,328} & \textbf{3,230} & \textbf{2,457}\\
\bottomrule
\end{tabular}
\endgroup{}
\end{table}
:::
::::::
