## Request 4 -- "Peel age-1 index data"

The SRG requests running the base model with the age-1 index, keeping 2023 and beyond recruitment deterministic, and sequentially (backwards in time) removing the age-1 index from the data. Run the base model: 

* without the 2023 age-1 index, 

* then without the 2023 and 2021 age-1 indices, 

* then without the 2023, 2021, and 2019 age-1 indices, and 

* then without the 2023, 2021, 2019, 2017, and 2015 age-1 indices.

Present spawning biomass trajectories (with unfished equilibrium spawning biomass), recruitment deviation estimates, and fits to the acoustic survey index.

## Spawning biomass: full age 1 index (base model)
:::::: {.columns}
::: {.column width="50%"}
```{r main-biomass-base, fig.height = 4, out.height = "80%"}

model_age1_minus_1 <- request_models[[2]][[1]]
model_age1_minus_2 <- request_models[[2]][[2]]
model_age1_minus_3 <- request_models[[2]][[3]]
model_age1_minus_5 <- request_models[[2]][[4]]

# Left
plot_biomass(list(base_model),
             ylim = c(0, 5),
             point_shape = ts_single_model_pointshape,
             leg_pos = "none")
```
:::

::: {.column width="50%"}
```{r main-relative-biomass-base, fig.height = 4, out.height = "80%"}
# Right
plot_rel_biomass(model_lst = list(base_model),
                 ylim = c(0, 2.5),
                 alpha = 0.2,
                 leg_pos = "none") |>
  suppressWarnings()
```
:::
::::::

## Spawning biomass: remove back to 2023

:::::: {.columns}
::: {.column width="50%"}
```{r main-biomass-rm1, fig.height = 4, out.height = "80%"}
# Left
plot_biomass(list(model_age1_minus_1),
             ylim = c(0, 5),
             point_shape = ts_single_model_pointshape,
             leg_pos = "none")
```
:::

::: {.column width="50%"}
```{r main-relative-biomass-rm1, fig.height = 4, out.height = "80%"}
# Right
plot_rel_biomass(model_lst = list(model_age1_minus_1),
                 ylim = c(0, 2.5),
                 alpha = 0.2,
                 leg_pos = "none") |>
  suppressWarnings()
```
:::
::::::

## Spawning biomass: remove back to 2021

:::::: {.columns}
::: {.column width="50%"}
```{r main-biomass-rm2, fig.height = 4, out.height = "80%"}
# Left
plot_biomass(list(model_age1_minus_2),
             ylim = c(0, 5),
             point_shape = ts_single_model_pointshape,
             leg_pos = "none")
```
:::

::: {.column width="50%"}
```{r main-relative-biomass-rm2, fig.height = 4, out.height = "80%"}
# Right
plot_rel_biomass(model_lst = list(model_age1_minus_2),
                 ylim = c(0, 2.5),
                 alpha = 0.2,
                 leg_pos = "none") |>
  suppressWarnings()
```
:::
::::::

## Spawning biomass: remove back to 2019

:::::: {.columns}
::: {.column width="50%"}
```{r main-biomass-rm3, fig.height = 4, out.height = "80%"}
# Left
plot_biomass(list(model_age1_minus_3),
             ylim = c(0, 5),
             point_shape = ts_single_model_pointshape,
             leg_pos = "none")
```
:::

::: {.column width="50%"}
```{r main-relative-biomass-rm3, fig.height = 4, out.height = "80%"}
# Right
plot_rel_biomass(model_lst = list(model_age1_minus_3),
                 ylim = c(0, 2.5),
                 alpha = 0.2,
                 leg_pos = "none") |>
  suppressWarnings()
```
:::
::::::

## Spawning biomass: remove back to 2015

:::::: {.columns}
::: {.column width="50%"}
```{r main-biomass-rm5, fig.height = 4, out.height = "80%"}
# Left
plot_biomass(list(model_age1_minus_5),
             ylim = c(0, 5),
             point_shape = ts_single_model_pointshape,
             leg_pos = "none")
```
:::

::: {.column width="50%"}
```{r main-relative-biomass-rm5, fig.height = 4, out.height = "80%"}
# Right
plot_rel_biomass(model_lst = list(model_age1_minus_5),
                 ylim = c(0, 2.5),
                 alpha = 0.2,
                 leg_pos = "none") |>
  suppressWarnings()
```
:::
::::::

## Rec devs: full age 1 index (base model)

```{r main-recruitment-devs-base, fig.height = 4, out.height = "80%"}

plot_recdevs(list(base_model),
             line_color = ts_single_line_color,
             leg_pos = "none")
```

## Rec devs: remove back to 2023

```{r main-recruitment-devs-rm1, fig.height = 4, out.height = "80%"}

plot_recdevs(list(model_age1_minus_1),
             line_color = ts_single_line_color,
             leg_pos = "none")
```

## Rec devs: remove back to 2021

```{r main-recruitment-devs-rm2, fig.height = 4, out.height = "80%"}

plot_recdevs(list(model_age1_minus_2),
             line_color = ts_single_line_color,
             leg_pos = "none")
```

## Rec devs: remove back to 2019

```{r main-recruitment-devs-rm3, fig.height = 4, out.height = "80%"}

plot_recdevs(list(model_age1_minus_3),
             line_color = ts_single_line_color,
             leg_pos = "none")
```

## Rec devs: remove back to 2015

```{r main-recruitment-devs-rm5, fig.height = 4, out.height = "80%"}

plot_recdevs(list(model_age1_minus_5),
             line_color = ts_single_line_color,
             leg_pos = "none")
```

## Acoustic survey fit: full age 1 index (base model)

```{r main-survey-index-fit-mcmc-base, fig.height = 4, out.height = "80%"}

plot_survey_fit_mcmc(base_model,
                     type = "acoustic",
                     n_posts = 1000,
                     glow = TRUE,
                     glow_color = "black",
                     glow_offset = 0.5,
                     leg_ymax = 4.8,
                     leg_sep = 0.45,
                     x_lim = c(survey_start_yr, survey_end_yr),
                     y_lim = c(0, 6),
                     x_labs_mod = 5,
                     y_labs_by = 0.5,
                     tick_prop = 1,
                     vjust_x_labels = -2,
                     remove_yr_labels = NULL)
```

## Acoustic survey fit: remove back to 2023

```{r main-survey-index-fit-mcmc-rm1, fig.height = 4, out.height = "80%"}

plot_survey_fit_mcmc(model_age1_minus_1,
                     type = "acoustic",
                     n_posts = 1000,
                     glow = TRUE,
                     glow_color = "black",
                     glow_offset = 0.5,
                     leg_ymax = 4.8,
                     leg_sep = 0.45,
                     x_lim = c(survey_start_yr, survey_end_yr),
                     y_lim = c(0, 6),
                     x_labs_mod = 5,
                     y_labs_by = 0.5,
                     tick_prop = 1,
                     vjust_x_labels = -2,
                     remove_yr_labels = NULL)
```

## Acoustic survey fit: remove back to 2021

```{r main-survey-index-fit-mcmc-rm2, fig.height = 4, out.height = "80%"}

plot_survey_fit_mcmc(model_age1_minus_2,
                     type = "acoustic",
                     n_posts = 1000,
                     glow = TRUE,
                     glow_color = "black",
                     glow_offset = 0.5,
                     leg_ymax = 4.8,
                     leg_sep = 0.45,
                     x_lim = c(survey_start_yr, survey_end_yr),
                     y_lim = c(0, 6),
                     x_labs_mod = 5,
                     y_labs_by = 0.5,
                     tick_prop = 1,
                     vjust_x_labels = -2,
                     remove_yr_labels = NULL)
```

## Acoustic survey fit: remove back to 2019

```{r main-survey-index-fit-mcmc-rm3, fig.height = 4, out.height = "80%"}

plot_survey_fit_mcmc(model_age1_minus_3,
                     type = "acoustic",
                     n_posts = 1000,
                     glow = TRUE,
                     glow_color = "black",
                     glow_offset = 0.5,
                     leg_ymax = 4.8,
                     leg_sep = 0.45,
                     x_lim = c(survey_start_yr, survey_end_yr),
                     y_lim = c(0, 6),
                     x_labs_mod = 5,
                     y_labs_by = 0.5,
                     tick_prop = 1,
                     vjust_x_labels = -2,
                     remove_yr_labels = NULL)
```

## Acoustic survey fit: remove back to 2015

```{r main-survey-index-fit-mcmc-rm5, fig.height = 4, out.height = "80%"}

plot_survey_fit_mcmc(model_age1_minus_5,
                     type = "acoustic",
                     n_posts = 1000,
                     glow = TRUE,
                     glow_color = "black",
                     glow_offset = 0.5,
                     leg_ymax = 4.8,
                     leg_sep = 0.45,
                     x_lim = c(survey_start_yr, survey_end_yr),
                     y_lim = c(0, 6),
                     x_labs_mod = 5,
                     y_labs_by = 0.5,
                     tick_prop = 1,
                     vjust_x_labels = -2,
                     remove_yr_labels = NULL)
```
